### 2017-07-06 paper.tex
add structure

%
% File acl2012.tex
%
% Contact: Maggie Li (cswjli@comp.polyu.edu.hk), Michael White (mwhite@ling.osu.edu)
%%
%% Based on the style files for ACL2008 by Joakim Nivre and Noah Smith
%% and that of ACL2010 by Jing-Shin Chang and Philipp Koehn

\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper]{geometry}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{url}
\makeatletter
\newcommand{\@BIBLABEL}{\@emptybiblabel}
\newcommand{\@emptybiblabel}[1]{}
\makeatother
\usepackage[hidelinks]{hyperref}
\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{6.5cm}    % Expanding the titlebox

\title{Parsing Tweets into Universal Dependencies}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}

\end{abstract}

\section{Introduction}
Analyzing the syntax of tweets is challenging for traditional NLP tools because most of the tweet texts are informal and noisy.

In this paper, we propose to parse the tweets in the convention of universal dependencies and built up the whole pipeline to parse the tweets from the raw text form.

Contribution of this paper includes:
\begin{itemize}
\item We create a new version of tweet Treebank Tweebank 2.0
\item We propose a neural network method to parse tweets into universal dependencies
\item We study the adaptation of universal dependencies for analyzing tweets
\end{itemize}

\section{Related Work}
Eisenstein \shortcite{eisenstein:2013:NAACL-HLT} reviewed NLP approaches for analyzing text on social media, especially for tweets and showed that there are two major directions for NLP community to handle the tweets, including normalization and domain adaptation. He also pointed out that normalization can be problematic because precisely defining the normalization task is difficult.

Kong et al. \shortcite{kong-EtAl:2014:EMNLP2014} argues that the Penn Treebank approach to annotation is poorly suited to more informal genres of text, as some of the annotation challenges for tweets,
including token selection, multiword expressions, multiple roots, and structure within noun phrases diverge significantly from conventional approaches. 
They believe that rapid, small scale annotation efforts performed by imperfectly-trained annotators should provide enough evidence to train an effective parser, given the rapidly changing nature of tweets~\cite{eisenstein:2013:NAACL-HLT}, the attested difficulties of domain adaptation for parsing~\cite{dred07}, and the expense of creating Penn Treebank-style annotations~\cite{penn93}. 
Therefore, they build a new corpus of tweets (Tweebank), with conventions informed by the domain, using new syntactic annotations that can tackle all the forementioned problems annotated in a day by two dozen annotators, most of whom had only cursory training in the annotation scheme. Then, they modify the decoder of the TurboParser, a graph-based dependency parser, which is open-source and has been found to perform well on a range of parsing problems in different languages~\cite{turbo13} to adapt to the Tweebank dataset, and incorporate new features such as Brown Clusters and Penn Treebank features and changes to specification
in the output space into TurboParser.

\section{Data Annotation}
% Linguistic phenomena
	% word level
		% RT
		% Hashtag
		% Mention, urls
		% Emoticons
		% Partially Elided tokens
	% twitter level
		% RT, Answer
		% Parataxis	
% POS
	% Acronym priority	
% Depenency
	% Concentrate on NON-UD phenomena
% Statistics
	% Scale
	% Inter-annotator agreement
	% Proportion
		% how many hashtags, mentions, ....
		% how many acornyms
\subsection{}

\section{Pipeline}
\subsection{Tokenization}
We use the UDPipe\footnote{https://github.com/ufal/udpipe} to tokenize the tweets and then detokenize the wrongly tokenized usernames and hashtags.

\subsection{POS Tagging}
Different from standard sentences, special constructions in tweets exist in both the whole tweet-level and token-level.

\subsubsection{Token-level Unconventional Part-of-Speech}
In addition to standard language, tweets have the following specific constructions:
\begin{itemize}
\item Discourse marker, URL, hashtag, emoticon
	\begin{itemize}
		\item RT, http://bit.ly/xyz, \#acl, :-), @user
	\end{itemize}
\item Acronym
	\begin{itemize}
		\item wtf (what the fuck), smh (shake my hand), mfw (my face when), ima (i am going to), rn (right now), af (as fuck)
	\end{itemize}
\item Contraction
	\begin{itemize}
		\item Contraction with apostrophe: There’s, he’s, book’ll, buy’em
		\item Contraction without apostrophe: gonna, tryna, gimme, Iv, im, aint, whatis
	\end{itemize}
\item Partially Elided Tokens
\end{itemize}

Gimpel et al. \shortcite{Gimpel:2011:PTT:2002736.2002747} proposed a set of part-of-speech tags that handles most of these cases. 
We are inspired by their work but argue that, first different abbreviation can have different syntactic functions. 
Like “mfw” is usually followed by an adverbial clause and “ima” is usually followed by a clausal complement. 
It is not reasonable to treat them in the same part-of-speech. 
In this paper, when annotating the POS tagging for abbreviations, we first try to recover their original forms, then use the POS of the core-word as the POS for the abbreviation.
Second, four special POS tags (S, L, M, Y) were designed to handle contraction words in Gimpel et al. \shortcite{Gimpel:2011:PTT:2002736.2002747}. Major concern of designing such tags is to minimize the effort of tokenization. 
However, contractions of common nouns and pronouns are casted into the same category which increase the difficulty of distinguishing their syntactic function (say, there's and book'll are treated with the same syntactic function). What's more, only a small proportion of words can be categorized into these tags (2.7 \% in total), which cast a doubt of the usefulness of these certain tags. In this paper, we believe such contraction can be properly handled by tokenization module, so we suggest to tokenize the contraction word and annotate POS tag accordingly.
Besides the contraction that be conventionally tokenized, tweets also witness a set of unconventional contraction like iv (I've), whatis (what is). In this paper, we follow the same idea of annotation abbreviation to handle the unconventional contractions and use the POS of core word of the original form as their POS.
Third, special POS was designed to handle emoticon in Gimpel et al. \shortcite{Gimpel:2011:PTT:2002736.2002747}. However, in most cases, emoticon plays the same role as most of the symbolic tokens. In this paper, we follow the UD guideline to annotate the emoticon as symbol (SYM).
At last, it’s arguable that some of the hashtags, URLs can work as a nominal in tweets. Whether treating them as the same part-of-speech or different ones according to their context is an open question. A preliminary survey on the standard UD English data shows that URL, email address are all tagged as the foreign language (X), so we also tag them as X and leave the disambiguation of their syntactic function to the annotation of parse tree.

\subsubsection{Tweets-level Special Construction}
There are several tweet-level constructions which are unconventional to standard text, including:

\begin{itemize}
\item Retweet: RT @user : $\langle$ sentence $\rangle$
\item Leading or ending topic marked as hashtag: \#topic \#topic \#topic $\langle$ sentence $\rangle$ \#topic \#topic \#topic
\item Leading or ending complementary URL:  $\langle$ complementary URL $\rangle$ $\langle$ sentence $\rangle$ $\langle$ complementary URL $\rangle$
%\item Tokens like the RT mark, @user and URL that usually don’t carry any syntactic functions and can be eliminated from the sentence. Kong et al. \shortcite{kong-EtAl:2014:EMNLP2014} proposed an additional token selection process to eliminate these non-syntactic tokens
\end{itemize}

\subsection{Sentence Segmentation}

\section{Model}

\section{Experiments}

\section{Conclusion}

\bibliography{tacl}
\bibliographystyle{acl2012}
\end{document}

### 2017-07-06 tacl.tex
add structure

%
% File acl2012.tex
%
% Contact: Maggie Li (cswjli@comp.polyu.edu.hk), Michael White (mwhite@ling.osu.edu)
%%
%% Based on the style files for ACL2008 by Joakim Nivre and Noah Smith
%% and that of ACL2010 by Jing-Shin Chang and Philipp Koehn

\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper]{geometry}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{url}
\makeatletter
\newcommand{\@BIBLABEL}{\@emptybiblabel}
\newcommand{\@emptybiblabel}[1]{}
\makeatother
\usepackage[hidelinks]{hyperref}
\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{6.5cm}    % Expanding the titlebox

\title{Instructions for TACL Submissions}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  {\tt email@domain} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
  This document contains the instructions for preparing a manuscript for submission to TACL. The document itself conforms to its own specifications, and is therefore an example of what your manuscript should look like. These instructions should be used for both papers submitted for review and for final versions of accepted papers. Authors are asked to conform to all the directions reported in this document.
\end{abstract}

\section{Credits}

This document has been adapted from the instructions for ACL proceedings, including those for ACL-2008 by Johanna D. Moore, Simone Teufel, James Allan, and Sadaoki Furui, those for ACL-2005 by Hwee Tou Ng and Kemal Oflazer, those for ACL-2002 by Eugene Charniak and Dekang Lin, and earlier ACL and EACL formats. Those versions were written by several people, including John Chen, Henry S. Thompson and Donald Walker. Additional elements were taken from the formatting instructions of the {\em International Joint Conference on Artificial Intelligence}.

\section{Introduction}

The following instructions are directed to authors of papers submitted to TACL or accepted for publication. All authors are required to adhere to these specifications. Authors are required to provide a Portable Document Format (PDF)
% das: removed reference to PostScript
% and PostScript
version of their papers. \textbf{The proceedings will be printed on
  US-Letter paper}. Authors from countries in which access to
word-processing systems is limited should contact TACL editors at editors-in-chief@transacl.org as soon as possible.

\section{General Instructions}

Manuscripts must be in two-column format. Exceptions to the two-column format include the title,
authors' names and complete addresses, which must be centered at the top of the first page,
and any full-width figures or tables (see the guidelines in Subsection~\ref{ssec:first}). {\bf Type single-spaced}.
Start all pages directly under the top margin. See the guide-lines later regarding formatting the first page. Do not number the pages.

\subsection{Electronically-available resources}

TACL provides this description in \LaTeX2e (tacl.tex) and PDF format (tacl.pdf), along with the LATEX2e style file used to format it (acl2012.sty) and an ACL bibliography style (acl2012.bst).  A Microsoft Word template file (tacl.dot) is also available. We require the use of these style files, which have been appropriately tailored for TACL. If you have an option, we recommend that you use the \LaTeX2e version. \textbf{If you will be using the Microsoft Word template, we suggest that you anonymize your source file so that the pdf produced does not retain your identity.} This can be done by removing any personal information from your source
document properties.

\subsection{Format of Electronic Manuscript}
\label{sect:pdf}

For the production of the electronic manuscript you must use Adobe's
Portable Document Format (PDF). This format can be generated from
postscript files: on Linux/Unix systems, you can use {\tt ps2pdf} for this
purpose; under Microsoft Windows, you can use Adobe's Distiller, or
if you have {\tt cygwin} installed, you can use {\tt dvipdf} or
{\tt ps2pdf}.  Note
that some word processing programs generate PDF which may not include
all the necessary fonts (esp. tree diagrams, symbols). When you print
or create the PDF file, there is usually an option in your printer
setup to include none, all or just non-standard fonts.  Please make
sure that you select the option of including ALL the fonts.  {\em Before sending it, test your PDF by printing it from a computer different from the one where it was created}. Moreover,
some word processor may generate very large postscript/PDF files,
where each page is rendered as an image. Such images may reproduce
poorly.  In this case, try alternative ways to obtain the postscript
and/or PDF.  One way on some systems is to install a driver for a
postscript printer, send your document to the printer specifying
``Output to a file'', then convert the file to PDF.

Additionally, it is of utmost importance to specify the {\bf US-Letter format} (8.5in $\times$ 11in) when formatting the paper. When working with {\tt dvips}, for instance, one should specify {\tt -t letter}.

Print-outs of the PDF file on US-Letter paper should be identical to the
hardcopy version.  If you cannot meet the above requirements about the
production of your electronic submission, please contact the
publication chair above as soon as possible.

\subsection{Layout}
\label{ssec:layout}

Format manuscripts two columns to a page, in the manner these
instructions are formatted. The exact dimensions for a page on US-letter
paper are:

\begin{itemize}
\item Left and right margins: 1in
\item Top margin:1in
\item Bottom margin: 1in
\item Column width: 3.15in
\item Column height: 9in
\item Gap between columns: 0.2in
\end{itemize}

\noindent Papers should not be submitted on any other paper size. If you cannot meet the above requirements about the production of your electronic submission, please contact the publication chair above as soon as possible.

\subsection{Fonts}

For reasons of uniformity, Adobe's {\bf Times Roman} font should be
used. In \LaTeX2e{} this is accomplished by putting

\begin{quote}
\begin{verbatim}
\usepackage{times}
\usepackage{latexsym}
\end{verbatim}
\end{quote}
in the preamble. If Times Roman is unavailable, use {\bf Computer
  Modern Roman} (\LaTeX2e{}'s default).  Note that the latter is about
  10\% less dense than Adobe's Times Roman font.

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|rl|}
\hline \bf Type of Text & \bf Font Size & \bf Style \\ \hline
paper title & 15 pt & bold \\
author names & 12 pt & bold \\
author affiliation & 12 pt & \\
the word ``Abstract'' & 12 pt & bold \\
section titles & 12 pt & bold \\
document text & 11 pt  &\\
captions & 10 pt & \\
abstract text & 10 pt & \\
bibliography & 10 pt & \\
footnotes & 9 pt & \\
\hline
\end{tabular}
\end{center}
\caption{\label{font-table} Font guide. }
\end{table}

\subsection{The First Page}
\label{ssec:first}

Center the title, author's name(s) and affiliation(s) across both
columns. Do not use footnotes for affiliations.  Do not include the
paper ID number assigned during the submission process.
Use the two-column format only when you begin the abstract.

{\bf Title}: Place the title centered at the top of the first page, in
a 15 point bold font.  (For a complete guide to font sizes and styles, see Table~\ref{font-table}.)
Long title should be typed on two lines without
a blank line intervening. Approximately, put the title at 1in from the
top of the page, followed by a blank line, then the author's names(s),
and the affiliation on the following line.  Do not use only initials
for given names (middle initials are allowed). Do not format surnames
in all capitals (e.g., ``Zhou,'' not ``ZHOU'').  The affiliation should
contain the author's complete address, and if possible an electronic
mail address. Leave about 0.75in between the affiliation and the body
of the first page. The title, author names and addresses should be completely identical to those entered to the electronic paper submission website in order to maintain the consistency of author information among all publications of the conference.

{\bf Abstract}: Type the abstract at the beginning of the first
column.  The width of the abstract text should be smaller than the
width of the columns for the text in the body of the paper by about
0.25in on each side.  Center the word {\bf Abstract} in a 12 point
bold font above the body of the abstract. The abstract should be a
concise summary of the general thesis and conclusions of the paper.
It should be no longer than 200 words. The abstract text should be in 10 point font.

{\bf Text}: Begin typing the main body of the text immediately after
the abstract, observing the two-column format as shown in
the present document. Do not include page numbers.

{\bf Indent} when starting a new paragraph. For reasons of uniformity,
use Adobe's {\bf Times Roman} fonts, with 11 points for text and
subsection headings, 12 points for section headings and 15 points for
the title.  If Times Roman is unavailable, use {\bf Computer Modern
  Roman} (\LaTeX2e's default; see section \ref{sect:pdf} above).
Note that the latter is about 10\% less dense than Adobe's Times Roman
font.

\subsection{Sections}

{\bf Headings}: Type and label section and subsection headings in the
style shown on the present document.  Use numbered sections (Arabic
numerals) in order to facilitate cross references. Number subsections
with the section number and the subsection number separated by a dot,
in Arabic numerals. Do not number subsubsections.

{\bf Citations}: Citations within the text appear
in parentheses as~\cite{Gusfield:97} or, if the author's name appears in
the text itself, as Gusfield~\shortcite{Gusfield:97}. Append lowercase letters to the year in cases of ambiguities. Treat double authors as in~\cite{Aho:72}, but write as in~\cite{Chandra:81} when more than two authors are involved. Collapse multiple citations as in~\cite{Gusfield:97,Aho:72}. Also refrain from using full citations as sentence constituents. We suggest that instead of
\begin{quote}
  ``\cite{Gusfield:97} showed that ...''
\end{quote}
you use
\begin{quote}
``Gusfield \shortcite{Gusfield:97}   showed that ...''
\end{quote}

If you are using the provided \LaTeX{} and Bib\TeX{} style files, you
can use the command \verb|\newcite| to get ``author (year)'' citations.

As reviewing will be double-blind (except that action editors know author identity and authors know action-editor identity), the submitted version of the papers should not include the
authors' names and affiliations. Furthermore, self-references that
reveal the author's identity, e.g.,
\begin{quote}
``We previously showed \cite{Gusfield:97} ...''
\end{quote}
should be avoided. Instead, use citations such as
\begin{quote}
``Gusfield \shortcite{Gusfield:97}
previously showed ... ''
\end{quote}

To be clear: You should reference your prior work if it is relevant; but use the third person instead of the 1st person and in place of references like “(Anonymous) showed…”, since such anonymized references do not allow readers to examine relevant related work.

Authors’ names should also be removed from the ``Document Properties'' display that can be viewed using Adobe Acrobat’s ``File $\rightarrow$ Properties'' menu.

Please do not include acknowledgements when submitting your papers. Papers that do not conform
to these requirements may be rejected without review.

\textbf{References}: Gather the full set of references together under
the heading {\bf References}; place the section before any Appendices,
unless they contain references. Arrange the references alphabetically
by first author, rather than by order of occurrence in the text.
Provide as complete a citation as possible, using a consistent format,
such as the one for {\em Computational Linguistics\/} or the one in the
{\em Publication Manual of the American
Psychological Association\/}~\cite{APA:83}.  Use of full names for
authors rather than initials is preferred.  A list of abbreviations
for common computer science journals can be found in the ACM
{\em Computing Reviews\/}~\cite{ACM:83}.

The \LaTeX{} and Bib\TeX{} style files provided roughly fit the
American Psychological Association format, allowing regular citations,
short citations and multiple citations as described above.

{\bf Appendices}: Appendices, if any, directly follow the text and the
references (but see above).  Letter them in sequence and provide an
informative title: {\bf Appendix A. Title of Appendix}.

\textbf{Acknowledgment} sections should go as a last section immediately
before the references. Do not number the acknowledgement section.

\subsection{Footnotes}

{\bf Footnotes}: Put footnotes at the bottom of the page. They may
be numbered or referred to by asterisks or other
symbols.\footnote{This is how a footnote should appear.} Footnotes
should be separated from the text by a line.\footnote{Note the
line separating the footnotes from the text.}  Footnotes should be in 9 point font.

\subsection{Graphics}

{\bf Illustrations}: Place figures, tables, and photographs in the
paper near where they are first discussed, rather than at the end, if
possible.  Wide illustrations may run across both columns and should be placed at
the top of a page. Color illustrations are discouraged, unless you have verified that
they will be understandable when printed in black ink.

{\bf Captions}: Provide a caption for every illustration; number each one
sequentially in the form:  ``Figure 1. Caption of the Figure.'' ``Table 1.
Caption of the Table.''  Type the captions of the figures and
tables below the body, using 10 point text.

\section{Translation of non-English Terms}

It is also advised to supplement non-English characters and terms
with appropriate transliterations and/or translations
since not all readers understand all such characters and terms.

Inline transliteration or translation can be represented in
the order of: original-form transliteration ``translation''.

\section{Length of Submission}
\label{sec:length}

Submissions may consist of seven to ten (7-10) letter format (not A4) pages of content and unlimited additional pages (only) allowed for references. Papers that are revisions of submissions with prior (b) or (c) decisions may be allowed one to two additional pages of content to accommodate required revisions.

Appendices (if any) are counted as content pages. Papers that do not conform to the specified length and
formatting requirements are subject to re-submission.

\section*{Acknowledgments}

Do not number the acknowledgment section. Do not include this section when submitting your paper for review.
\bibliography{tacl}
\bibliographystyle{acl2012}

\end{document}

### 2017-07-11 paper.tex
linguistic phenomena 1

@@
 \setlength\titlebox{6.5cm}    % Expanding the titlebox
+
+%%%%%%%
+\usepackage{graphicx}
+\newcommand{\heart}{\ensuremath\heartsuit}
 
@@
 
-\section{Data Annotation}
+\section{Data}
 % Linguistic phenomena
@@
 		% Mention, urls
-		% Emoticons
-		% Partially Elided tokens
+		% Symbols and Emoticons
+		% Truncated tokens
 	% twitter level
@@
 		% how many acornyms
-\subsection{}
 
-\section{Pipeline}
-\subsection{Tokenization}
-We use the UDPipe\footnote{https://github.com/ufal/udpipe} to tokenize the tweets and then detokenize the wrongly tokenized usernames and hashtags.
+\subsection{Linguistic Phenomena of Twitter}
+As the representative of the web language, different from the standard languages such as newswire, twitter has its own linguistic phenomena, that could be categorized into word level and structure level phenomena, and we will discuss them separately.
+
+\subsubsection{Token Level}
+
+There are special tokens that will appear only or much more frequently in tweets, including
+
+\begin{itemize}
+\item Retweet discourse marker: RT
+\item URL: http://bit.ly/xyz
+\item Hashtag: \#ACL
+\item At-mentioned username: @user
+\item Emoticon, emoji and symbol: :), - - - - $\langle$$\langle$$\langle$, :-), …
+\item Acronym: wtf (what the fuck), smh (shake my hand), mfw (my face when), ima (i am going to), rn (right now), af (as fuck)
+\item Contraction: he's, buy'em, gonna, trma, gimme, im
+\item Truncated token: because each tweet can have only 140 characters, excessive characters will be cut off, and usually there could be token in the last of the tweet that is partially elided
+\end{itemize}
+
+Consider the following example
+
+\begin{center}
+RT @Yijia : \#ACL2017 im heading to Canada for ACL can u gimme some money :) http://url1 I would love to do it with th …
+\end{center}
+
+From the example, we argue that most of the the retweet discourse markers, URLs, hashtags, usernames and the emoticons/emojis/symbols usually do not have clear syntactic functions in the tweet, and therefore we should not include them in the analysis, and treat them all equally as non-syntactic tokens.
+Especially, for truncated tokens, although it might be possible to recover the original tokens from the context in some cases, and we can infer that the truncated token ``th" could be probably the token ``the" it is extremely hard to further predict the rest of the elided sentence.
+For the simplicity of the annotation, we will consider all the truncated tokens as non-syntactic tokens.
+
+For acronyms and contractions, it is obviously better if we could recover their original forms before analyzing the whole tweet, and we believe that all of these tokens will always be syntactically part of the tweet.
+
+However, consider another example
+
+\begin{center}
+@Yi u gonna $\heart$ it . \#NAACL will be \#Awesome . Check my new paper with @nlpnoah on http://url2 RT it !!
+\end{center}
+
+Similar in the analysis of Kong et al.
+\shortcite{kong-EtAl:2014:EMNLP2014}, in some cases, retweet marker (RT), URLS (http://url2), hashtags (\#NAACL, \#Awesome), usernames (@Yi, @nlpnoah) and emoticons ($\heart$) can also have syntactic functions, and we need to take them into the account in the syntactic analysis.
+
+We define acronyms and contractions as full syntactic tokens, truncated tokens as zero syntactic tokens, and all of the other tokens as partial syntactic tokens.
+
+\subsubsection{Structure Level}
+Besides the token level phenomena of twitter, there are also structural patterns appearing in the twitter.
+
+\begin{itemize}
+\item Retweet structure: RT @user :  $\langle$ tweet content $\rangle$ is a typical structural pattern when a user is retweeting from other users
+\item Parataxis: Very often, one tweet is comprised of many sentences or phrases without any delimiting punctuations, such as $\langle$ sentence1 $\rangle$ $\langle$ phrase1 $\rangle$ $\langle$ sentence2 $\rangle$ ...
+\end{itemize}
+
+We treat ``RT @user" as the structural patterns in tweet and keep their annotations consistent across tweets. For parataxis case
+
+%vocative X pos tags??
 
 \subsection{POS Tagging}
-Different from standard sentences, special constructions in tweets exist in both the whole tweet-level and token-level.
-
-\subsubsection{Token-level Unconventional Part-of-Speech}
-In addition to standard language, tweets have the following specific constructions:
-\begin{itemize}
-\item Discourse marker, URL, hashtag, emoticon
-	\begin{itemize}
-		\item RT, http://bit.ly/xyz, \#acl, :-), @user
-	\end{itemize}
-\item Acronym
-	\begin{itemize}
-		\item wtf (what the fuck), smh (shake my hand), mfw (my face when), ima (i am going to), rn (right now), af (as fuck)
-	\end{itemize}
-\item Contraction
-	\begin{itemize}
-		\item Contraction with apostrophe: There’s, he’s, book’ll, buy’em
-		\item Contraction without apostrophe: gonna, tryna, gimme, Iv, im, aint, whatis
-	\end{itemize}
-\item Partially Elided Tokens
-\end{itemize}
-
-Gimpel et al. \shortcite{Gimpel:2011:PTT:2002736.2002747} proposed a set of part-of-speech tags that handles most of these cases. 
+Gimpel et al. \shortcite{Gimpel:2011:PTT:2002736.2002747} proposed a set of part-of-speech tags that handle most of token level phenomena of tweet. 
 We are inspired by their work but argue that, first different abbreviation can have different syntactic functions. 
@@
 A preliminary survey on the standard UD English data shows that URL, email address are all tagged as the foreign language (X), so we also tag them as X and leave the disambiguation of their syntactic function to the annotation of parse tree.
+
+We use the Universal POS tags~\cite{PETROV12.274} to tag the tweet tokens.
+
+\subsection{Dependency Annotation}
+
+\section{Pipeline}
+\subsection{Tokenization}
+We use the UDPipe\footnote{https://github.com/ufal/udpipe} to tokenize the tweets and then detokenize the wrongly tokenized usernames and hashtags.
+
+\subsection{POS Tagging}
 

### 2017-07-21 paper.tex
Data convention finished

--- 2017-07-06 paper.tex
@@
 
+\section{Data}
+% Linguistic phenomena
+	% word level
+		% RT
+		% Hashtag
+		% Mention, urls
+		% Symbols and Emoticons
+		% Truncated tokens
+	% twitter level
+		% RT
+		% Parataxis	
+% POS
+	% Acronym priority
+	% URL tagged as X	
+% Depenency
+	% Concentrate on NON-UD phenomena
+% Statistics
+	% Scale
+	% Inter-annotator agreement
+	% Proportion
+		% how many hashtags, mentions, ....
+		% how many acornyms
+
+\subsection{Linguistic Phenomena of Twitter} \label{introduction}
+%Eisenstan
+As the representative of the web language, different from the standard languages such as newswire, twitter has its own linguistic phenomena, that could be categorized into word level and structure level phenomena, and we will discuss them separately.
+
+\subsubsection{Token Level}
+
+There are special tokens that will appear only or much more frequently in tweets.
+According to the syntactic functions these tokens have in the tweets, we classify them into three types: syntactic tokens, non-syntactic tokens and optionally syntactic tokens.
+Syntactic tokens are tokens that will always have syntactic functions in tweets, but they might not be in their normal orthographic form and we need to do some preprocessing to recover their standard form.
+Then we can treat them just as normal tokens in the standard text.
+Non-syntactic tokens are tokens that will not have syntactic function or semantic meaning in tweets, and they are not considered in the syntax analysis and need to be treated independently.
+Optionally syntactic tokens are tokens that can have either syntactic or non-syntactic functions based on the context.
+Usually they are tokens like URLs ad hashtags that do not participate in the syntax of the tweets, and we treat them as non-syntactic functions by default.
+However, similar in the analysis of Kong et al.
+\shortcite{kong-EtAl:2014:EMNLP2014}, in some cases they are perceived as the arguments or predicates of tweets and therefore have syntactic functions.
+In this case we treat them as syntactic tokens.
+
+Here is a complete list of the special tokens in tweets classified in three types.
+
+\begin{itemize}
+\item syntactic tokens
+	\begin{itemize}
+		\item phrasal abbreviations: {\tt wtf} (what the fuck), {\tt rn} (right now), etc.
+		\item orthographic variants: {\tt u} (you), {\tt sooooo}, {\tt dat} (that), etc.
+	\end{itemize}
+\item Non-syntactic tokens
+	\begin{itemize}
+		\item truncated tokens: last tokens that are truncated in tweets exceeding twitter character limits.
+It might be possible to recover the original tokens from the context in some cases, it is still extremely hard to further predict the rest of the truncated part.
+	\end{itemize}
+\item Optionally syntactic tokens
+	\begin{itemize}
+		\item retweet discourse marker: RT
+		\item URL: http://bit.ly/xyz
+		\item hashtag: \#ACL
+		\item at-mentioned username: @user
+		\item emoticons and emojis: :), :-), $\heart$, etc.
+	\end{itemize}
+\end{itemize}
+
+As optionally syntactic tokens will be treated as syntactic or non-syntactic tokens based on the specific context, for the sake of simplicity, we will only discuss the syntactic and non-syntactic tokens in the following sections.
+
+\subsubsection{Structure Level}
+Besides the token level phenomena of twitter, there are also structural patterns appearing in the twitter.
+
+\begin{itemize}
+\item Retweet structure: {\tt RT @user : \{tweet content\}} is a typical structural pattern when a user is retweeting from other users. 
+\item At-mentioned structure: Except the retweet structure and syntactically at-mentioned username, we think that all of at-mentioned usernames are representing a vocative situation, usually appearing at the beginning or the end of the sentences in tweets.
+\item Paratactic parts without punctuations: We use ``part'' to represent a self-contained clause or phrase, and is independent of the previous and the following part.
+Very often, one tweet is comprised of multiple parts without any delimiting punctuations, such as {\tt \{part 1\} \{part 2\} ...}
+\end{itemize}
+
+We treat retweet structure and at-mention structure as structural patterns and keep their annotations consistent across tweets.
+For parataxis case, we treat each single sentence or phrases independently, and connect them together following the UD conventions.
+
+Consider the following example
+
+\begin{figure}[h]
+\label{ex1}
+\small
+{\tt
+RT @yijialiu : \#ACL2017 heading to Canada for ACL u gim me money rn :) http://url I would love to do it with th $\ldots$ %…
+}
+\caption{Tweet Example 1}
+\label{ex1}
+\end{figure}
+
+From the example, we argue that {\tt u} and {\tt rn} are syntactic tokens.
+{\tt th} is a truncated token and does not have any syntactic function, although we can infer that the {\tt th} could be probably {\tt the}.
+{\tt \#ACL2017}, {\tt :)} and {\tt http://url} are optionally syntactic tokens, and should be all treated as non-syntactic tokens in this example.
+{\tt RT @Yijia :} should be analyzed as the retweet structure, and {\tt heading to Canada for ACL} and {\tt can u gimme some money} should be considered as paratactic clauses without punctuations.
+
+However, consider another example
+\begin{figure}[h]
+\small
+{\tt
+@zypandora u gonna $\heart$ it . \#NAACL will be \#Awesome . Check out our new paper with @nlpnoah on http://url . RT it !!
+}
+\caption{Tweet Example 2}
+\label{ex2}
+\end{figure}
+
+All of the optionally syntactic tokens ({\tt RT}, {\tt http://url}, {\tt \#NAACL}, {\tt \#Awesome}, {\tt @zypandora}, {\tt @nlpnoah} and {\tt $\heart$}) have syntactic functions, and we need to take them into account in the syntactic analysis.
+
+\subsection{POS Tagging}
+We follow the UD V2 morphology guideline and use the Universal POS tags~\cite{PETROV12.274} to tag the tweet tokens.
+For twitter specific linguistic phenomena, we have set different strategies and try to align with the UD conventions and UD\_English as close as possible.\footnote{https://github.com/UniversalDependencies/UD\_English}
+
+In token level phenomena, for non-syntactic tokens, we tag most of them as X (other), except for the emojis and emoticons, which would be tagged as SYM, as same in the UD\_English. 
+For syntactic tokens, we tag them considering their corresponding syntactic function.
+
+In structure level phenomena, we think {\tt RT @user} in retweet structure have no contribution to the tweet syntax and tag both of them as X.
+We tag the at-mentioned username in at-mentioned structure as PROPN as they present the vocative case.
+
+Therefore, in Fig. ~\ref{ex1}, {\tt RT} {\tt @yijialiu}, {\tt \#ACL2017}, {\tt http://url} and {\tt th} are all tagged as X and {\tt :)} is tagged as SYM. 
+{\tt rn} is tagged as ADV and {\tt ima} is tagged as PROPN.
+We should note that multiple tokens are actually included in one non-explicit contraction, and we use one of their tags as the contraction tag according to their dependency relation or semantic priority.
+If there is a hierarchy in the contraction, we use the tag of the head word as the contraction tag.
+``Right'' is the dependent of ``now '' in the dependency of {\tt rn}, so we tag {\tt rn} as ADV.
+Although there is no head word in {\tt im}, we think that the subject is usually more informative than the tense in many downstream tasks such as semantic role labelling, so we use the tag of ``I'', e.g.
+PROPN as the tag of {\tt im}.
+In Fig.
+~\ref{ex2}, {\tt RT} and {\tt $\heart$} would be tagged as VERB, {\tt http://url} as X, {\tt \#Awesome} as ADJ, {\tt \#NAACL}, {\tt @zypandora} and {\tt @nlpnoah} as PROPN.
+One exception is that we tag URLs always as X regardless whether they are syntactic tokens.
+The reason is that we observed, in UD\_English, that the URLs are all tagged as X and we want to conform with the UD dataset, although we think it is not reasonable and should be changed to tags such as PROPN when they are treated as syntactic tokens.
+
+Comparison with Gimpel
+% Tokenization discrepancy
+
+\subsection{Dependency Annotation}
+We follow the UD V2 syntax guideline and the English specific Universal Dependency Relations to annotate our data.
+
+In token level phenomena, we adopt the following rules for non-syntactic tokens, denoted as x:
+
+\begin{itemize}
+\item If the sentence x belongs to has a clear predicate with syntactic function, x should not have any dependent and are attached to this sentence’s predicate;
+\item If the sentence x belongs to consists of only non-syntactic tokens we attach x to the first tokens of the sentence;
+\item In parataxis case, it might be difficult to decide which sentence or phrase x should belong to. In this case, we always attach x to the previous predicate of the paratactic clause or phrase;
+\item x is mostly labelled as \it{discourse}, but URLs are always labelled as \it{list};
+\end{itemize}
+
+The reason we annotate URLs differently is the same as in POS tagging, that UD\_English labelled them as {\it list} when they are non-syntactic tokens and we want to keep the dataset conformed with it.
+
+Syntactic tokens are just normal tokens.
+
+we further adopt the following rules for structure level phenomena:
+
+\begin{itemize}
+\item Retweet structure: we attach {\tt @user} to {\tt RT} and {\tt RT} to the predicate of the following sentence with {\it discourse} as labels.
+\item At-mentioned structure: we attach at-mention username to the predicate of the most relevant sentence with {\it vocative} label.
+If it is hard to decide which sentence would be the most relevant, we attach it to the previous sentence's predicate.
+\item Paratactic parts without punctuations: we follow the UD convention, and set the first part as the main part of the sentence, and set its predicate as the main predicate of the sentence.
+Every predicate of the following parts should attach to the main predicate.
+If the main part and some following part are both phrases, the label is {\it list}, otherwise the label is {\it parataxis}.
+Note that we still have an exception for URLs, conforming with UD, which is URLs are always labelled as {\it list}, regardless of the type of the other part.
+\end{itemize}
+
+Comparison with Kong
+
+\section{Pipeline}
+
+\section{Model}
+
+\section{Experiments}
+
 \section{Related Work}
@@
 
-\section{Data Annotation}
-% Linguistic phenomena
-	% word level
-		% RT
-		% Hashtag
-		% Mention, urls
-		% Emoticons
-		% Partially Elided tokens
-	% twitter level
-		% RT, Answer
-		% Parataxis	
-% POS
-	% Acronym priority	
-% Depenency
-	% Concentrate on NON-UD phenomena
-% Statistics
-	% Scale
-	% Inter-annotator agreement
-	% Proportion
-		% how many hashtags, mentions, ....
-		% how many acornyms
-\subsection{}
-
-\section{Pipeline}
-\subsection{Tokenization}
-We use the UDPipe\footnote{https://github.com/ufal/udpipe} to tokenize the tweets and then detokenize the wrongly tokenized usernames and hashtags.
-
-\subsection{POS Tagging}
-Different from standard sentences, special constructions in tweets exist in both the whole tweet-level and token-level.
-
-\subsubsection{Token-level Unconventional Part-of-Speech}
-In addition to standard language, tweets have the following specific constructions:
-\begin{itemize}
-\item Discourse marker, URL, hashtag, emoticon
-	\begin{itemize}
-		\item RT, http://bit.ly/xyz, \#acl, :-), @user
-	\end{itemize}
-\item Acronym
-	\begin{itemize}
-		\item wtf (what the fuck), smh (shake my hand), mfw (my face when), ima (i am going to), rn (right now), af (as fuck)
-	\end{itemize}
-\item Contraction
-	\begin{itemize}
-		\item Contraction with apostrophe: There’s, he’s, book’ll, buy’em
-		\item Contraction without apostrophe: gonna, tryna, gimme, Iv, im, aint, whatis
-	\end{itemize}
-\item Partially Elided Tokens
-\end{itemize}
-
-Gimpel et al. \shortcite{Gimpel:2011:PTT:2002736.2002747} proposed a set of part-of-speech tags that handles most of these cases. 
-We are inspired by their work but argue that, first different abbreviation can have different syntactic functions. 
+Gimpel et al. \shortcite{Gimpel:2011:PTT:2002736.2002747} proposed a set of twitter POS tags that handle most of token level phenomena of tweets. 
+We believe that the Universal POS tags have some advantages over their tags on syntax analysis.
+The first different abbreviation can have different syntactic functions. 
 Like “mfw” is usually followed by an adverbial clause and “ima” is usually followed by a clausal complement. 
@@
 
-\subsubsection{Tweets-level Special Construction}
-There are several tweet-level constructions which are unconventional to standard text, including:
-
-\begin{itemize}
-\item Retweet: RT @user : $\langle$ sentence $\rangle$
-\item Leading or ending topic marked as hashtag: \#topic \#topic \#topic $\langle$ sentence $\rangle$ \#topic \#topic \#topic
-\item Leading or ending complementary URL:  $\langle$ complementary URL $\rangle$ $\langle$ sentence $\rangle$ $\langle$ complementary URL $\rangle$
-%\item Tokens like the RT mark, @user and URL that usually don’t carry any syntactic functions and can be eliminated from the sentence.
-Kong et al.
-\shortcite{kong-EtAl:2014:EMNLP2014} proposed an additional token selection process to eliminate these non-syntactic tokens
-\end{itemize}
-
-\subsection{Sentence Segmentation}
-
-\section{Model}
-
-\section{Experiments}
-
 \section{Conclusion}

### 2017-07-22 paper.tex
lp pos dependency annotation 1

@@
 Usually they are tokens like URLs ad hashtags that do not participate in the syntax of the tweets, and we treat them as non-syntactic functions by default.
-However, similar in the analysis of Kong et al.
-\shortcite{kong-EtAl:2014:EMNLP2014}, in some cases they are perceived as the arguments or predicates of tweets and therefore have syntactic functions.
+However, similar in the analysis of \newcite{kong-EtAl:2014:EMNLP2014}, in some cases they are perceived as the arguments or predicates of tweets and therefore have syntactic functions.
 In this case we treat them as syntactic tokens.
@@
 
-Comparison with Gimpel
-% Tokenization discrepancy
+\newcite{Gimpel:2011:PTT:2002736.2002747} proposed a twitter POS tagset that handles most of the token level phenomena.
+However, we found that their methods did not conform with UD conventions and our strategies have some advantages over their tagset.
+We discuss the main difference as follows.
+The first difference lies in the tokenizations.
+Gimpel et al. opted not to split contractions or possessives and introduced four new tags (S, Z, L, M) for combined forms: \{nominal, proper noun\} $\times$ \{verb, possessive\}. 
+Major concern of designing such tags is to minimize the effort of tokenization, but it is not comprehensive and far from including all of the possible combinations of POS tags within the contractions.
+What's more, only a small proportion of tokens can be categorized into these tags (2.7 \% in total), which casts a doubt of the usefulness of these tags.
+Instead UD conventions suggest that we put such complexity into the tokenization module and split contractions and possessives, then tag them accordingly.
+Therefore, we do not need extra POS tags for the combined forms.
+The second difference is that although the phrasal abbreviations are not split in both methods, they use tag G for all the other abbreviations that cannot be tokenized, while we use the tag of the head word or the highest hierarchical word in terms of dependencies as the tag of the whole phrasal abbreviations.
+We think it is not reasonable to treat the phrasal abbreviations in the same part of speech because obviously abbreviations can have different syntactic functions and we want to preserver the most useful information for both parser and the downstream tasks.
+For example, {\tt wtf} could be tagged as PRON or INTJ according to the context, and {\tt rn} is usually tagged as ADV.
+Tagging them merely as G will definitely lose much information.
+Third, special tags were designed to handle twitter or online special tokens such as URLs, hashtags and emoticon in \newcite{Gimpel:2011:PTT:2002736.2002747}.
+However, in most cases, as long as theses tokens are non syntactic, they play the same role in tweets hence should be tagged the same.
+In this paper, except for the emoticon, tagged as SYM, we tag all the other non-syntactic tokens as X.
 
@@
 
-Syntactic tokens are just normal tokens.
+For syntactic tokens, they are considered the same as normal tokens in the standard text and we annotate them by just following the UD guidelines.
 
@@
 
-Comparison with Kong
+% unlabelled, Informal
+% exclude non-syntactic tokens, punctuations
+% Annotation conventions
+\newcite{kong-EtAl:2014:EMNLP2014} built a syntactic treebank of tweets called Tweebank using Gimpel et al.'s POS tagset. 
+Apart from the difference in POS tagging, we found the following difference in both methods.
+First, Tweebank is an unlabelled dependency treebank, while we are annotating labelled dependencies.
+There is clearly a doubt about the usefulness of the Tweebank.
+We annotate the labelled dependencies by following the UD annotation guideline.
+Second, most of Tweebank was built in a day by two dozen annotators, most of whom had only cursory training in the annotation scheme~\cite{kong-EtAl:2014:EMNLP2014}.
+We think, after investigation, that despite the speed, the quality of data is still to be improved.
+We follow strictly the UD annotation guideline and only make twitter specific conventions when there is no suitable convention to adopt in UD guideline or no relevant data found in UD\_English.
+Third, \newcite{kong-EtAl:2014:EMNLP2014} developed a first-order sequence model to filter out the non-syntactic tokens and punctuations, and exclude them before parsing.
+It is very different from most of the annotation conventions, especially for UD conventions.
+We believe that every token should be included in the dependency tree, whether they have syntactic functions or are to be evaluated in the end, as in most of the conventions, so we annotate all tokens.
+Last, \newcite{kong-EtAl:2014:EMNLP2014} adopt the ``Yamada-Matsumoto" conventions~\cite{Yamada03statisticaldependency}, where auxiliary verbs are parents of main verbs, and prepositions are parents of their arguments, in contrast to UD conventions, where content words are primary tokens, and dependency relations hold primarily between them, rather than being indirect relations mediated by function words.
 
@@
 \section{Related Work}
-Eisenstein \shortcite{eisenstein:2013:NAACL-HLT} reviewed NLP approaches for analyzing text on social media, especially for tweets and showed that there are two major directions for NLP community to handle the tweets, including normalization and domain adaptation.
+\newcite{eisenstein:2013:NAACL-HLT} reviewed NLP approaches for analyzing text on social media, especially for tweets and showed that there are two major directions for NLP community to handle the tweets, including normalization and domain adaptation.
 He also pointed out that normalization can be problematic because precisely defining the normalization task is difficult.
 
-Kong et al. \shortcite{kong-EtAl:2014:EMNLP2014} argues that the Penn Treebank approach to annotation is poorly suited to more informal genres of text, as some of the annotation challenges for tweets,
+\newcite{kong-EtAl:2014:EMNLP2014} argues that the Penn Treebank approach to annotation is poorly suited to more informal genres of text, as some of the annotation challenges for tweets,
 including token selection, multiword expressions, multiple roots, and structure within noun phrases diverge significantly from conventional approaches. 
@@
 
-Gimpel et al. \shortcite{Gimpel:2011:PTT:2002736.2002747} proposed a set of twitter POS tags that handle most of token level phenomena of tweets. 
-We believe that the Universal POS tags have some advantages over their tags on syntax analysis.
-The first different abbreviation can have different syntactic functions. 
 Like “mfw” is usually followed by an adverbial clause and “ima” is usually followed by a clausal complement. 

### 2017-07-22 paper.tex
lp pos da 2

@@
 %Eisenstan
-As the representative of the web language, different from the standard languages such as newswire, twitter has its own linguistic phenomena, that could be categorized into word level and structure level phenomena, and we will discuss them separately.
+As the representative of the web language, different from the standard languages such as newswire, twitter has its own linguistic phenomena, that could be categorized into token level and structure level phenomena, and we will discuss them separately.
 
@@
 According to the syntactic functions these tokens have in the tweets, we classify them into three types: syntactic tokens, non-syntactic tokens and optionally syntactic tokens.
-Syntactic tokens are tokens that will always have syntactic functions in tweets, but they might not be in their normal orthographic form and we need to do some preprocessing to recover their standard form.
-Then we can treat them just as normal tokens in the standard text.
-Non-syntactic tokens are tokens that will not have syntactic function or semantic meaning in tweets, and they are not considered in the syntax analysis and need to be treated independently.
+Syntactic tokens are just like normal tokens in the standard text. They always have syntactic functions in tweets. They could be orthographic variants or abbreviations that represents a phrase.
+Non-syntactic tokens are tokens that will not have syntactic function in tweets, and they are not considered in the syntax analysis and need to be treated independently.
 Optionally syntactic tokens are tokens that can have either syntactic or non-syntactic functions based on the context.
 Usually they are tokens like URLs ad hashtags that do not participate in the syntax of the tweets, and we treat them as non-syntactic functions by default.
-However, similar in the analysis of \newcite{kong-EtAl:2014:EMNLP2014}, in some cases they are perceived as the arguments or predicates of tweets and therefore have syntactic functions.
+However, similar in the analysis of \newcite{Gimpel:2011:PTT:2002736.2002747} and \newcite{kong-EtAl:2014:EMNLP2014}, in some cases they are perceived as the arguments or predicates of tweets and therefore have syntactic functions.
 In this case we treat them as syntactic tokens.
@@
 		\item truncated tokens: last tokens that are truncated in tweets exceeding twitter character limits.
-It might be possible to recover the original tokens from the context in some cases, it is still extremely hard to further predict the rest of the truncated part.
+Although It might be possible to recover the original tokens from the context in some cases, it is still extremely hard to further predict the rest of the truncated part.
 	\end{itemize}
@@
 
-As optionally syntactic tokens will be treated as syntactic or non-syntactic tokens based on the specific context, for the sake of simplicity, we will only discuss the syntactic and non-syntactic tokens in the following sections.
+As optionally syntactic tokens will be treated as syntactic or non-syntactic tokens based on the specific context, for the sake of simplicity, if not necessary, we will only discuss the syntactic and non-syntactic tokens in the following sections.
 
@@
 \item Retweet structure: {\tt RT @user : \{tweet content\}} is a typical structural pattern when a user is retweeting from other users. 
-\item At-mentioned structure: Except the retweet structure and syntactically at-mentioned username, we think that all of at-mentioned usernames are representing a vocative situation, usually appearing at the beginning or the end of the sentences in tweets.
-\item Paratactic parts without punctuations: We use ``part'' to represent a self-contained clause or phrase, and is independent of the previous and the following part.
+\item At-mentioned structure: Except the retweet structure and syntactically at-mentioned username, we think that all of other at-mentions are vocative case, usually appearing at the beginning or the end of the sentences in tweets.
+\item Paratactic parts without punctuations: We use ``part'' to refer to a self-contained clause or phrase, which is independent of other ``part''.
 Very often, one tweet is comprised of multiple parts without any delimiting punctuations, such as {\tt \{part 1\} \{part 2\} ...}
@@
 
-We treat retweet structure and at-mention structure as structural patterns and keep their annotations consistent across tweets.
-For parataxis case, we treat each single sentence or phrases independently, and connect them together following the UD conventions.
-
-Consider the following example
+We treat retweet structure and at-mentioned structure as structural patterns and keep their annotations consistent across tweets.
+For parataxis case, we treat each single sentence or phrase normally, and connect them together following the UD conventions.
 
@@
 
-From the example, we argue that {\tt u} and {\tt rn} are syntactic tokens.
+From Fig.~\ref{ex1}, we argue that {\tt u} and {\tt rn} are syntactic tokens.
 {\tt th} is a truncated token and does not have any syntactic function, although we can infer that the {\tt th} could be probably {\tt the}.
@@
 We follow the UD V2 morphology guideline and use the Universal POS tags~\cite{PETROV12.274} to tag the tweet tokens.
-For twitter specific linguistic phenomena, we have set different strategies and try to align with the UD conventions and UD\_English as close as possible.\footnote{https://github.com/UniversalDependencies/UD\_English}
+For twitter specific linguistic phenomena, we have set different strategies and try to align with the UD conventions and UD\textunderscore English as close as possible.\footnote{\url{https://github.com/UniversalDependencies/UD\_English}}
 
@@
 In structure level phenomena, we think {\tt RT @user} in retweet structure have no contribution to the tweet syntax and tag both of them as X.
-We tag the at-mentioned username in at-mentioned structure as PROPN as they present the vocative case.
+We tag usernames in at-mentioned structure as PROPN as they present the vocative case.
 
-Therefore, in Fig. ~\ref{ex1}, {\tt RT} {\tt @yijialiu}, {\tt \#ACL2017}, {\tt http://url} and {\tt th} are all tagged as X and {\tt :)} is tagged as SYM. 
-{\tt rn} is tagged as ADV and {\tt ima} is tagged as PROPN.
-We should note that multiple tokens are actually included in one non-explicit contraction, and we use one of their tags as the contraction tag according to their dependency relation or semantic priority.
-If there is a hierarchy in the contraction, we use the tag of the head word as the contraction tag.
-``Right'' is the dependent of ``now '' in the dependency of {\tt rn}, so we tag {\tt rn} as ADV.
-Although there is no head word in {\tt im}, we think that the subject is usually more informative than the tense in many downstream tasks such as semantic role labelling, so we use the tag of ``I'', e.g.
+In Fig.~\ref{ex1}, {\tt RT} {\tt @yijialiu}, {\tt \#ACL2017}, {\tt http://url} and {\tt th} are all tagged as X and {\tt :)} is tagged as SYM. 
+{\tt rn} is tagged as ADV.
+We should note that multiple tokens are actually included in a phrasal abbreviation, and we use one of their tags as the tag of the whole abbreviation according to their dependency relation or semantic priority.
+If there is a hierarchy in the abbreviation, we use the tag of the head word. In UD, ``Right'' is the dependent of ``now '' in the dependency of {\tt rn}, so we tag {\tt rn} as ADV. 
+%Although there is no head word in {\tt im}, we think that the subject is usually more informative than the tense in many downstream tasks such as semantic role labelling, so we use the tag of ``I'', e.g.
 PROPN as the tag of {\tt im}.
-In Fig.
-~\ref{ex2}, {\tt RT} and {\tt $\heart$} would be tagged as VERB, {\tt http://url} as X, {\tt \#Awesome} as ADJ, {\tt \#NAACL}, {\tt @zypandora} and {\tt @nlpnoah} as PROPN.
+In Fig.~\ref{ex2}, {\tt RT} and {\tt $\heart$} would be tagged as VERB, {\tt http://url} as X, {\tt \#Awesome} as ADJ, {\tt \#NAACL}, {\tt @zypandora} and {\tt @nlpnoah} as PROPN.
 One exception is that we tag URLs always as X regardless whether they are syntactic tokens.
-The reason is that we observed, in UD\_English, that the URLs are all tagged as X and we want to conform with the UD dataset, although we think it is not reasonable and should be changed to tags such as PROPN when they are treated as syntactic tokens.
+The reason is that we observed, in UD\_English, that the URLs are all tagged as X and we want to conform with the UD dataset, although we think it is not appropriate and should be changed to tags such as PROPN when they are treated as syntactic tokens.
 
@@
 The first difference lies in the tokenizations.
-Gimpel et al. opted not to split contractions or possessives and introduced four new tags (S, Z, L, M) for combined forms: \{nominal, proper noun\} $\times$ \{verb, possessive\}. 
+\newcite{Gimpel:2011:PTT:2002736.2002747} opted not to split contractions or possessives and introduced four new tags (S, Z, L, M) for combined forms: \{nominal, proper noun\} $\times$ \{verb, possessive\}.
 Major concern of designing such tags is to minimize the effort of tokenization, but it is not comprehensive and far from including all of the possible combinations of POS tags within the contractions.
 What's more, only a small proportion of tokens can be categorized into these tags (2.7 \% in total), which casts a doubt of the usefulness of these tags.
-Instead UD conventions suggest that we put such complexity into the tokenization module and split contractions and possessives, then tag them accordingly.
-Therefore, we do not need extra POS tags for the combined forms.
-The second difference is that although the phrasal abbreviations are not split in both methods, they use tag G for all the other abbreviations that cannot be tokenized, while we use the tag of the head word or the highest hierarchical word in terms of dependencies as the tag of the whole phrasal abbreviations.
-We think it is not reasonable to treat the phrasal abbreviations in the same part of speech because obviously abbreviations can have different syntactic functions and we want to preserver the most useful information for both parser and the downstream tasks.
+Instead UD conventions suggest that we put such complexity into the tokenization module and split contractions and possessives, then tag them accordingly, so that we do not need extra POS tags for the combined forms.
+The second difference is that although the phrasal abbreviations are not split in both methods, they use tag G for all the phrasal abbreviations, while we use the tag of the head word or the highest hierarchical word in terms of dependencies as the tag of the whole phrasal abbreviations.
+We think it is not reasonable to treat the phrasal abbreviations in the same part of speech because obviously abbreviations can have different syntactic functions and we want to preserve the most useful information for both parser and the downstream tasks.
 For example, {\tt wtf} could be tagged as PRON or INTJ according to the context, and {\tt rn} is usually tagged as ADV.
@@
 Third, special tags were designed to handle twitter or online special tokens such as URLs, hashtags and emoticon in \newcite{Gimpel:2011:PTT:2002736.2002747}.
-However, in most cases, as long as theses tokens are non syntactic, they play the same role in tweets hence should be tagged the same.
-In this paper, except for the emoticon, tagged as SYM, we tag all the other non-syntactic tokens as X.
+However, in most cases, as long as theses tokens are non syntactic, they play the same role in tweets, hence should be tagged the same.
+In this paper, except for the emoticon and emoji, tagged as SYM, we tag all the other non-syntactic tokens as X.
 
@@
 \begin{itemize}
-\item If the sentence x belongs to has a clear predicate with syntactic function, x should not have any dependent and are attached to this sentence’s predicate;
-\item If the sentence x belongs to consists of only non-syntactic tokens we attach x to the first tokens of the sentence;
-\item In parataxis case, it might be difficult to decide which sentence or phrase x should belong to. In this case, we always attach x to the previous predicate of the paratactic clause or phrase;
-\item x is mostly labelled as \it{discourse}, but URLs are always labelled as \it{list};
+\item If the sentence x belongs to has a clear predicate with syntactic function, x should not have any dependent and is attached to this sentence’s predicate;
+\item If the sentence x belongs to consists of only non-syntactic tokens we attach x to the first token of the sentence;
+\item In parataxis case, when it is difficult to decide which sentence or phrase x should belong to, we always attach x to the previous predicate of the paratactic clause or phrase;
+\item x is mostly labelled as {\it discourse}, but URLs are always labelled as {\it list};
 \end{itemize}
@@
 
-For syntactic tokens, they are considered the same as normal tokens in the standard text and we annotate them by just following the UD guidelines.
+For syntactic tokens, they are considered the same as normal tokens and we just annotate them by following the UD guidelines.
 
@@
 \item Retweet structure: we attach {\tt @user} to {\tt RT} and {\tt RT} to the predicate of the following sentence with {\it discourse} as labels.
-\item At-mentioned structure: we attach at-mention username to the predicate of the most relevant sentence with {\it vocative} label.
+\item At-mentioned structure: we attach at-mentioned username to the predicate of the most relevant sentence with {\it vocative} label.
 If it is hard to decide which sentence would be the most relevant, we attach it to the previous sentence's predicate.
-\item Paratactic parts without punctuations: we follow the UD convention, and set the first part as the main part of the sentence, and set its predicate as the main predicate of the sentence.
+\item Paratactic parts without punctuations: we follow the UD convention, set the first part as the main part of the sentence, and set its predicate as the main predicate of the sentence.
 Every predicate of the following parts should attach to the main predicate.
 If the main part and some following part are both phrases, the label is {\it list}, otherwise the label is {\it parataxis}.
-Note that we still have an exception for URLs, conforming with UD, which is URLs are always labelled as {\it list}, regardless of the type of the other part.
+Note that we still have an exception for URLs, conforming with UD, which are always labelled as {\it list}, regardless of the type of the other part.
 \end{itemize}
@@
 Apart from the difference in POS tagging, we found the following difference in both methods.
-First, Tweebank is an unlabelled dependency treebank, while we are annotating labelled dependencies.
-There is clearly a doubt about the usefulness of the Tweebank.
-We annotate the labelled dependencies by following the UD annotation guideline.
+First, Tweebank is an unlabelled dependency treebank. There is clearly a doubt about the usefulness of the Tweebank. We annotate the labelled dependencies by following the UD annotation guideline.
 Second, most of Tweebank was built in a day by two dozen annotators, most of whom had only cursory training in the annotation scheme~\cite{kong-EtAl:2014:EMNLP2014}.
@@
 We believe that every token should be included in the dependency tree, whether they have syntactic functions or are to be evaluated in the end, as in most of the conventions, so we annotate all tokens.
-Last, \newcite{kong-EtAl:2014:EMNLP2014} adopt the ``Yamada-Matsumoto" conventions~\cite{Yamada03statisticaldependency}, where auxiliary verbs are parents of main verbs, and prepositions are parents of their arguments, in contrast to UD conventions, where content words are primary tokens, and dependency relations hold primarily between them, rather than being indirect relations mediated by function words.
+Last, \newcite{kong-EtAl:2014:EMNLP2014} adopt the ``Yamada-Matsumoto" conventions~\cite{Yamada03statisticaldependency}, where auxiliary verbs are parents of main verbs, and prepositions are parents of their arguments, in contrast to UD conventions, where content words are put into the primacy, and dependency relations hold primarily between them, rather than being indirect relations mediated by function words.
+Auxiliary verbs and prepositions are all function words, and are attached to the most related content words in UD.
 

### 2017-07-26 paper.tex
Data Acuquisition & basic statistics

@@
 \begin{figure}[h]
-\label{ex1}
 \small
@@
 
+\subsection{Tweebank V2}
+We present Tweebank V2, a version 2 of Tweebank~\cite{kong-EtAl:2014:EMNLP2014}.
+
+%data aquisition/statistics
+The tweet source of Tweebank V2 consists of three parts. 
+The first is the original Tweebank created by~\cite{kong-EtAl:2014:EMNLP2014}, denoted as Tweebank V1.
+There are 639 unique tweets in the training data of Tweebank V1, and 201 unique tweets in the data set.
+All of the unique tweets in Tweebank V1 are included in Tweebank V2.
+The second are 210 tweets from POS-tagged Twitter corpus of~\newcite{Owo13}, denoted as Tweebank V1 Dev. It was initially created as a development set of Tweebank V1 for hyperparameter tuning.
+Tweebank V1 Dev comprises were equally sampled from two data set, OCT27 (tweets sampled from a particular day, October 27, 2010) and DAILY 547 (one random English tweet per day from January 2011 through June 2012, 547 tweets in total).
+We should note that all of the Tweebank V1 tweets were also drawn from OCT27 and DAILY547, and the new tweets we extracted are not in the Tweebank V1.
+The third are 2500 tweets from the Twitter streams from February 2017 to July 2017 from ArchiveTeam,\footnote{https://archive.org} which we call Feb\_Jul\_16 corpus.
+The Twitter streams are in Spritzer version, which provides a 1\% random sample of public tweets everyday, and the tweets are in twitter JSON format.
+There are xxx tweets in all the streams.
+We filtered them with \textit{lang} attribute in \textit{user} and used \textit{langid.py}\footnote{https://github.com/saffsd/langid.py} to pick out English tweets, which ends in xxx tweets in English.
+Then we sampled 2500 tweets roughly equally from these months.
+
+Tweebank V2 contains 3550 tweets in total, split into training set with 1639 tweets, development set with 710 tweets and test set with 1201 tweets. 
+The training set contains all the 639 unique tweets in the training set of Tweebank V1 and another 1000 tweets in feb\_jul\_16 corpus.
+The development set contains 210 tweets of Tweebank V1 Dev and another 500 tweets in feb\_jul\_16 corpus.
+The test set contains all the 201 tweets in the test set of Tweebank V1 and another 1000 tweets in feb\_jul\_16 corpus.
+
+We process all the raw tweets of these corpora from scratch, from tokenization and POS tagging to dependency annotation.
+As Tweebank V1 and the POS-tagged Twitter corpus of~\newcite{Owo13} used a tweet tokenizer~\cite{Krieger10tweetmotif:exploratory} and POS tagger~\cite{Gimpel:2011:PTT:2002736.2002747} that do not conform with UD guidelines, as we discussed before, we did not use any data of the intermediate steps from these corpora.
+The basic statistics of Tweebank V2 is shown in Table~\ref{tab1}.
+
+% tweets, tokens, tokens/tweet, part/tweet, token types.
+\begin{table}[h!]
+\centering
+ \begin{tabular}{l r r r} 
+ \hline
+ 			& 	Train 		& 	Test		&	Dev\\[0.5ex] \hline
+tweets 		&	1639 		&	1201		&	709\\
+tokens 		&			&			&	\\
+types 		&	 		&			&	\\
+utterances 	&	 		&			&	\\ \hline
+\end{tabular}
+ \caption{Statistics of Tweebank}
+ \label{tab1}
+\end{table}
+
+% tokens and its proportions for the previous language phenomena.
+
+%annotation statistics, agreement
+
 \section{Pipeline}

### 2017-07-28 paper.tex
twitter specific statistics table

@@
 \newcommand{\heart}{\ensuremath\heartsuit}
+\usepackage{multirow}
 
@@
 
-\section{Introduction}
+\section{introduction}
 Analyzing the syntax of tweets is challenging for traditional NLP tools because most of the tweet texts are informal and noisy.
@@
 
-\subsection{Linguistic Phenomena of Twitter} \label{introduction}
+\subsection{Linguistic Phenomena of Twitter} \label{lingphen}
 %Eisenstan
@@
 
+\subsubsection{Basic Statistics}
 Tweebank V2 contains 3550 tweets in total, split into training set with 1639 tweets, development set with 710 tweets and test set with 1201 tweets. 
@@
 % tweets, tokens, tokens/tweet, part/tweet, token types.
-\begin{table}[h!]
+\begin{table}[t]
 \centering
@@
  \hline
- 			& 	Train 		& 	Test		&	Dev\\[0.5ex] \hline
-tweets 		&	1639 		&	1201		&	709\\
+ 			& 	Train 		& 	Dev		&	Test\\[0.5ex] \hline
+tweets 		&	1639 		&	709		&	1201\\
 tokens 		&			&			&	\\
 types 		&	 		&			&	\\
-utterances 	&	 		&			&	\\ \hline
+parts		 	&	 		&			&	\\ \hline
 \end{tabular}
- \caption{Statistics of Tweebank}
+ \caption{Basic Statistics of Tweebank}
  \label{tab1}
@@
 % tokens and its proportions for the previous language phenomena.
+\subsubsection{Twitter Specific Statistics}\label{lingphen}
+Following the discussion of the Twitter specific linguistic phenomena, we obtain Table~\ref{tab2}.
 
+\begin{table*}[t]
+\centering
+\small
+ \begin{tabular}{r | l | l | l | r r r r r} 
+ \hline
+\multicolumn{4}{l}{}	&	Train		&	Test	&	Dev	&	All	&	Per\\[0.5ex] \hline\hline
+\multirow{10}{*}{\textit{token}}	&	syntactic						&	\multicolumn{2}{l |}{phrasal abbreviation}				
+			 	&	  		&		&		&		&		\\
+\cline{2-9}
+						&	\multirow{8}{*}{optionally syntactic}	&	\multirow{2}{*}{RT}					&	syntactic	
+			 	&	  		&		&		&		&		\\
+						&								&									&	non-syntactic
+				&	  		&		&		&		&		\\
+\cline{3-9}
+						&								&	\multirow{2}{*}{hashtag}				&	syntactic
+				&	  		&		&		&		&		\\
+						&								&									&	non-syntactic
+				&	  		&		&		&		&		\\
+\cline{3-9}
+						&								&	\multirow{2}{*}{at-mentioned}			&	syntactic
+				&	  		&		&		&		&		\\
+						&								&									&	non-syntactic
+				&	  		&		&		&		&		\\
+\cline{3-9}
+						&								&	\multirow{2}{*}{emoticon/emoji}			&	syntactic
+				&	  		&		&		&		&		\\
+						&								&									&	non-syntactic
+				&	  		&		&		&		&		\\
+\cline{2-9}
+						&	non-syntactic 					&	\multicolumn{2}{l |}{truncated}
+				&	  		&		&		&		&		\\
+
+\hline
+\multirow{3}{*}{\textit{structure}}	& 	\multicolumn{3}{l |}{retweet}
+			 	&	  		&		&		&		&		\\
+						&	\multicolumn{3}{l |}{at-mentioned}
+				&	  		&		&		&		&		\\
+						&	\multicolumn{3}{l |}{parataxis without punctuations}
+				&	  		&		&		&		&		\\
+\hline
+\end{tabular}
+ \caption{Twitter Specific Statistics of Tweebank}
+ \label{tab1}
+\end{table*}
 %annotation statistics, agreement

### 2017-08-13 paper.tex
revise 2.1.1

@@
 \usepackage{multirow}
+\usepackage{xcolor}
+\usepackage{tikz-dependency}
 \usepackage{url}
@@
 \usepackage{multirow}
+
+\newcommand{\yjcomment}[1]{\textcolor{orange}{[$_\mathrm{L}^\mathrm{Y}$\textsc{#1}]}}
 
@@
 
-\section{introduction}
+\section{Introduction}
 Analyzing the syntax of tweets is challenging for traditional NLP tools because most of the tweet texts are informal and noisy.
@@
 \subsection{Linguistic Phenomena of Twitter} \label{lingphen}
-%Eisenstan
-As the representative of the web language, different from the standard languages such as newswire, twitter has its own linguistic phenomena, that could be categorized into token level and structure level phenomena, and we will discuss them separately.
+Twitter, as an extreme example of informal domain, contains a collection of conversational languages (like abbreviation, informal contraction, and variant entity names) and twitter-specified markers (like retweet mark, and username).
+Despite the informal nature of tweets, we argue that they basically follow the same grammar as their formal language counterpart.
+The key issue lies in understanding the specific construction that doesn't carry any syntactic functions.
+In the following section, we studied such constructions from both the token and structure level. \yjcomment{I don't like the name of \textbf{structure level}}
+%As the representative of the web language, different from the standard languages such as newswire, twitter has its own linguistic phenomena, that could be categorized into token level and structure level phenomena, and we will discuss them separately.
 
 \subsubsection{Token Level}
+\paragraph{Informal Syntactic Tokens.}
+Informal tokens like phrase abbreviation (like {\tt mfw}: my face when, {\tt rn}: right now, and etc.) and orthographic variants (like {\tt sooo cooool}) have drawn much attention in previous literals \cite{finin-EtAl:2010:MTURK,eisenstein:2013:NAACL-HLT} \yjcomment{not sure orthographic variants is a good name, need reference.}
+However, in the sense of syntactic functions, they work in the same way as the ordinary words, which makes them requires less specialty in designing annotation conventions.
+%Syntactic tokens are just like normal tokens in the standard text.
+%They always have syntactic functions in tweets.
+%They could be orthographic variants or abbreviations that represents a phrase.
 
-There are special tokens that will appear only or much more frequently in tweets.
-According to the syntactic functions these tokens have in the tweets, we classify them into three types: syntactic tokens, non-syntactic tokens and optionally syntactic tokens.
-Syntactic tokens are just like normal tokens in the standard text. They always have syntactic functions in tweets. They could be orthographic variants or abbreviations that represents a phrase.
-Non-syntactic tokens are tokens that will not have syntactic function in tweets, and they are not considered in the syntax analysis and need to be treated independently.
-Optionally syntactic tokens are tokens that can have either syntactic or non-syntactic functions based on the context.
+\paragraph{Non-syntactic Tokens.}
+
+\begin{figure*}[t]
+	\centering
+	\small
+	\begin{dependency}[edge slant=2, text only label, label style=above]
+		\begin{deptext}
+			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& @coldplay \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl}\\
+			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny X \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \\
+		\end{deptext}
+		\deproot{1}{root}
+		\depedge[edge unit distance=1em]{1}{2}{discourse}
+		\deproot{6}{root}
+		\depedge[edge unit distance=1em]{6}{3}{discourse}
+		\depedge[edge unit distance=1em]{3}{4}{discourse}
+		\depedge[edge unit distance=1em]{3}{5}{punct}
+		\depedge[edge unit distance=1em]{6}{7}{obj}
+		\depedge[edge unit distance=0.8em]{6}{10}{obl}
+		\depedge[edge unit distance=1em]{10}{8}{case}
+		\depedge[edge unit distance=1em]{10}{9}{det}
+		\depedge[edge unit distance=0.8em]{6}{11}{discourse}
+		\depedge[edge unit distance=0.8em]{6}{12}{list}
+	\end{dependency}
+	\caption{A example tweet contains major non-syntactic tokens, with
+		\textcolor{red}{sentiment emoticon},
+		\textcolor{orange}{retweet mark},
+		\textcolor{gray}{topical hashtag}, and
+		\textcolor{blue}{referential URL}.}\label{fig:non-syn-toks}
+\end{figure*}
+
+\begin{figure*}[t]
+	\centering
+	\small
+	\begin{dependency}[edge slant=2, text only label, label style=above]
+		\begin{deptext}
+			its \& \#awesome \& u \& gonna \& $\heart$ \& it \& Chk \& out \& our \& cooool \& project \& on \& http:// \& + \& RT \& pls\\
+			\tiny PRON \& \tiny ADJ \& \tiny PRON \& \tiny VERB \& \tiny VERB \& \tiny PRON \& \tiny VERB \& \tiny ADP \& \tiny PRON \& \tiny ADJ \& \tiny NOUN \& \tiny ADP \& \tiny X \& \tiny SYM \& \tiny VERB\& \tiny INTJ\\
+		\end{deptext}
+		\deproot{2}{root}
+		\depedge[edge unit distance=1em]{2}{1}{nsubj}
+		\deproot{4}{root}
+		\depedge[edge unit distance=1em]{4}{3}{nsubj}
+		\depedge[edge unit distance=1em]{4}{5}{xcomp}
+		\depedge[edge unit distance=1em]{5}{6}{obj}
+		\deproot{7}{root}
+		\depedge[edge unit distance=1em]{7}{8}{compound:prt}
+		\depedge[edge unit distance=0.7em]{7}{11}{obj}
+		\depedge[edge unit distance=1em]{11}{9}{nmod:poss}
+		\depedge[edge unit distance=1em]{11}{10}{amod}
+		\depedge[edge unit distance=1em]{11}{13}{nmod}
+		\depedge[edge unit distance=1em]{13}{12}{case}
+		\depedge[edge unit distance=0.45em]{7}{15}{conj}
+		\depedge[edge unit distance=1em]{15}{14}{cc}
+		\depedge[edge unit distance=0.5em]{7}{16}{discourse}
+	\end{dependency}
+	\caption{}\label{fig:informal-toks}
+\end{figure*}
+
+Besides the informal but syntactic tokens, there are a large collection of tokens that cannot be handled by the syntactic theory designed for standard text.
+A major part of these tokens consists of meta data in tweets, like the sentiment emotion, retweet mark, topical hashtag, and referential URL shown in Figure \ref{tbl:non-syn-toks}.
+
+However, whether a token convey some syntactic function cannot be simply decided by its form.
+For example, besides being a discourse marker, {\tt RT} can also works as a abbreviation of the verb {\tt retweet}.
+Emoticons are sometimes used as a nominal part of the sentence like `I {\tt $\heart$} it.'
+Twitter users have developed a casual habit of using hashtag, even with words expressing exclamation (like {\tt \#lol}).
+Thus, whether a token make a non-syntactic one is highly conditioned on its context.
+
+A kind of token that doesn't carry clearly syntactic functions can be resulted by the 140 characters limits of tweets.
+Since last tokens that exceeding 140 characters limits are truncated in tweets which leaves a broken sentence, it is impossible to fully recover their original form and figure out their syntactics.
+In this paper, we propose to treat these truncated tokens, along with the other 4 kinds of tokens mentioned above, as ones without syntactic functions.
+
+In the sense of dealing with the non-syntactic tokens, \newcite{kong-EtAl:2014:EMNLP2014} proposed an preprocessing step named {\it token selection} to remove non-syntactic tokens from the original tweets.
+However, concrete standard of non-syntactic tokens was not presented in their work.
+What's more, these unselected tokens are absent from downstream processing, including parsing.
+We differ from their work by proposing concrete standard of non-syntactic tokens and we include these non-syntactic tokens in our final analyzed dependencies by adding special attachment to them.
+%There are special tokens that will appear only or much more frequently in tweets.
+%According to the syntactic functions these tokens have in the tweets, we classify them into three types: syntactic tokens, non-syntactic tokens and optionally syntactic tokens. 
+%Non-syntactic tokens are tokens that will not have syntactic function in tweets, and they are not considered in the syntax analysis and need to be treated independently.
+%Optionally syntactic tokens are tokens that can have either syntactic or non-syntactic functions based on the context.
 Usually they are tokens like URLs ad hashtags that do not participate in the syntax of the tweets, and we treat them as non-syntactic functions by default.
@@
 
-Here is a complete list of the special tokens in tweets classified in three types.
+%Here is a complete list of the special tokens in tweets classified in three types.
+%
+%\begin{itemize}
+%\item syntactic tokens
+%	\begin{itemize}
+%		\item phrasal abbreviations: {\tt wtf} (what the fuck), {\tt rn} (right now), etc.
+%		\item orthographic variants: {\tt u} (you), {\tt sooooo}, {\tt dat} (that), etc.
+%	\end{itemize}
+%\item Non-syntactic tokens
+%	\begin{itemize}
+%		\item truncated tokens: last tokens that are truncated in tweets exceeding twitter character limits.
+Although It might be possible to recover the original tokens from the context in some cases, it is still extremely hard to further predict the rest of the truncated part.
+%	\end{itemize}
+%\item Optionally syntactic tokens
+%	\begin{itemize}
+%		\item retweet discourse marker: RT
+%		\item URL: http://bit.ly/xyz
+%		\item hashtag: \#ACL
+%		\item at-mentioned username: @user
+%		\item emoticons and emojis: :), :-), $\heart$, etc.
+%	\end{itemize}
+%\end{itemize}
 
-\begin{itemize}
-\item syntactic tokens
-	\begin{itemize}
-		\item phrasal abbreviations: {\tt wtf} (what the fuck), {\tt rn} (right now), etc.
-		\item orthographic variants: {\tt u} (you), {\tt sooooo}, {\tt dat} (that), etc.
-	\end{itemize}
-\item Non-syntactic tokens
-	\begin{itemize}
-		\item truncated tokens: last tokens that are truncated in tweets exceeding twitter character limits.
-Although It might be possible to recover the original tokens from the context in some cases, it is still extremely hard to further predict the rest of the truncated part.
-	\end{itemize}
-\item Optionally syntactic tokens
-	\begin{itemize}
-		\item retweet discourse marker: RT
-		\item URL: http://bit.ly/xyz
-		\item hashtag: \#ACL
-		\item at-mentioned username: @user
-		\item emoticons and emojis: :), :-), $\heart$, etc.
-	\end{itemize}
-\end{itemize}
-
-As optionally syntactic tokens will be treated as syntactic or non-syntactic tokens based on the specific context, for the sake of simplicity, if not necessary, we will only discuss the syntactic and non-syntactic tokens in the following sections.
+%As optionally syntactic tokens will be treated as syntactic or non-syntactic tokens based on the specific context, for the sake of simplicity, if not necessary, we will only discuss the syntactic and non-syntactic tokens in the following sections.
 
@@
 
-\begin{figure}[h]
-\small
-{\tt
-RT @yijialiu : \#ACL2017 heading to Canada for ACL u gim me money rn :) http://url I would love to do it with th $\ldots$ %…
-}
-\caption{Tweet Example 1}
-\label{ex1}
-\end{figure}
-
 From Fig.~\ref{ex1}, we argue that {\tt u} and {\tt rn} are syntactic tokens.
@@
 
-However, consider another example
-\begin{figure}[h]
-\small
-{\tt
-@zypandora u gonna $\heart$ it . \#NAACL will be \#Awesome . Check out our new paper with @nlpnoah on http://url . RT it !!
-}
-\caption{Tweet Example 2}
-\label{ex2}
-\end{figure}
-
+However, consider another example in Figure \ref{fig:informal-toks}.
 All of the optionally syntactic tokens ({\tt RT}, {\tt http://url}, {\tt \#NAACL}, {\tt \#Awesome}, {\tt @zypandora}, {\tt @nlpnoah} and {\tt $\heart$}) have syntactic functions, and we need to take them into account in the syntactic analysis.
@@
 \subsection{Dependency Annotation}
+
 We follow the UD V2 syntax guideline and the English specific Universal Dependency Relations to annotate our data.
@@
 % tokens and its proportions for the previous language phenomena.
-\subsubsection{Twitter Specific Statistics}\label{lingphen}
+\subsubsection{Twitter Specific Statistics}\label{stats}
 Following the discussion of the Twitter specific linguistic phenomena, we obtain Table~\ref{tab2}.
@@
 
-Like “mfw” is usually followed by an adverbial clause and “ima” is usually followed by a clausal complement. 
+Like ``mfw'' is usually followed by an adverbial clause and ``ima'' is usually followed by a clausal complement. 
 It is not reasonable to treat them in the same part-of-speech. 
@@
 
-\bibliography{tacl}
+\bibliography{shortdb}
 \bibliographystyle{acl2012}

### 2017-08-15 paper.tex
adding previous version pdf
revise 2.1.2

@@
 Despite the informal nature of tweets, we argue that they basically follow the same grammar as their formal language counterpart.
-The key issue lies in understanding the specific construction that doesn't carry any syntactic functions.
+The key issue lies in understanding the specific construction that doesn't carry any syntactic functions, and designed rules to handle the specific constructions in tweets.
 In the following section, we studied such constructions from both the token and structure level. \yjcomment{I don't like the name of \textbf{structure level}}
@@
 		\depedge[edge unit distance=1em]{2}{1}{nsubj}
-		\deproot{4}{root}
+		\depedge[edge unit distance=1em]{2}{4}{parataxis}
 		\depedge[edge unit distance=1em]{4}{3}{nsubj}
@@
 		\depedge[edge unit distance=1em]{5}{6}{obj}
-		\deproot{7}{root}
+		\depedge[edge unit distance=0.7em]{2}{7}{parataxis}
 		\depedge[edge unit distance=1em]{7}{8}{compound:prt}
@@
 		\depedge[edge unit distance=1em]{15}{14}{cc}
-		\depedge[edge unit distance=0.5em]{7}{16}{discourse}
+		\depedge[edge unit distance=0.35em]{2}{16}{discourse}
 	\end{dependency}
-	\caption{}\label{fig:informal-toks}
+	\caption{An example tweet with informal but syntactic tokens.}\label{fig:informal-toks}
 \end{figure*}
@@
 Besides the informal but syntactic tokens, there are a large collection of tokens that cannot be handled by the syntactic theory designed for standard text.
-A major part of these tokens consists of meta data in tweets, like the sentiment emotion, retweet mark, topical hashtag, and referential URL shown in Figure \ref{tbl:non-syn-toks}.
+A major part of these tokens consists of meta data in tweets, like the sentiment emotion, retweet mark, topical hashtag, and referential URL shown in Figure \ref{fig:non-syn-toks}.
 
@@
 For example, besides being a discourse marker, {\tt RT} can also works as a abbreviation of the verb {\tt retweet}.
-Emoticons are sometimes used as a nominal part of the sentence like `I {\tt $\heart$} it.'
-Twitter users have developed a casual habit of using hashtag, even with words expressing exclamation (like {\tt \#lol}).
-Thus, whether a token make a non-syntactic one is highly conditioned on its context.
+Emoticons are sometimes used as a verbal part of the sentence.
+Twitter users have developed a casual habit of using hashtag, and even use hashtag as a adjective.
+The sentence in Figure \ref{fig:informal-toks} gives a comprehensive example of those informal but syntactic tokens.
+It shows whether a token makes a non-syntactic one is highly conditioned on its context.
 
@@
 \subsubsection{Structure Level}
-Besides the token level phenomena of twitter, there are also structural patterns appearing in the twitter.
+The syntactic constructions vary greatly across different tweets.
+Unconventional constructions which frequently occur include ellipsis, irregular word orders, and para-tactic sentences without the segmentation of punctuations \yjcomment{I move the 3rd bullet point here because this construction was handled by UD-guidelines}.
+And these unconventional ones are more or less resolved by the universal dependencies.
+The unresolved cases are mainly resulted by the format of twitter.
+The {\it retweet} and {\it at-mention} are of two major constructions.
+\paragraph{Retweet.} For the {\it retweet} construction (`{\tt RT @coldplay :}' in Figure \ref{fig:non-syn-toks}), although it can be treated as a verbal phrase in which retweet marker works as a verb and the following at-mention is its objective, we argue that such convention lead to a uninformative root word.
+It also increase the difficulty for downstream tasks in figuring out the core predicate and arguments for one certain tweet.
+Thus, we treat the whole construction as a non-syntactic phrase. \yjcomment{correct me if I am wrong.}
+\paragraph{At-mention.} At-mention in the beginning of a tweet is the format of indicating the `reply' action.
+In this paper, we treat the at-mentions as vocative expressions for their connections with the traditional vocative words, rather than treat them as non-syntactic metadata, which increase the complexity for analyzing a tweet.
+\yjcomment{since the original discussion mainly focus on tokens, I move them to the former section.}
+%Besides the token level phenomena of twitter, there are also structural patterns appearing in the twitter.
 
-\begin{itemize}
-\item Retweet structure: {\tt RT @user : \{tweet content\}} is a typical structural pattern when a user is retweeting from other users. 
-\item At-mentioned structure: Except the retweet structure and syntactically at-mentioned username, we think that all of other at-mentions are vocative case, usually appearing at the beginning or the end of the sentences in tweets.
-\item Paratactic parts without punctuations: We use ``part'' to refer to a self-contained clause or phrase, which is independent of other ``part''.
+%\begin{itemize}
+%\item Retweet structure: {\tt RT @user : \{tweet content\}} is a typical structural pattern when a user is retweeting from other users. 
+%\item At-mentioned structure: Except the retweet structure and syntactically at-mentioned username, we think that all of other at-mentions are vocative case, usually appearing at the beginning or the end of the sentences in tweets.
+%\item Paratactic parts without punctuations: We use ``part'' to refer to a self-contained clause or phrase, which is independent of other ``part''.
 Very often, one tweet is comprised of multiple parts without any delimiting punctuations, such as {\tt \{part 1\} \{part 2\} ...}
-\end{itemize}
+%\end{itemize}
 
-We treat retweet structure and at-mentioned structure as structural patterns and keep their annotations consistent across tweets.
+%We treat retweet structure and at-mentioned structure as structural patterns and keep their annotations consistent across tweets.
 For parataxis case, we treat each single sentence or phrase normally, and connect them together following the UD conventions.
 
-From Fig.~\ref{ex1}, we argue that {\tt u} and {\tt rn} are syntactic tokens.
-{\tt th} is a truncated token and does not have any syntactic function, although we can infer that the {\tt th} could be probably {\tt the}.
-{\tt \#ACL2017}, {\tt :)} and {\tt http://url} are optionally syntactic tokens, and should be all treated as non-syntactic tokens in this example.
-{\tt RT @Yijia :} should be analyzed as the retweet structure, and {\tt heading to Canada for ACL} and {\tt can u gimme some money} should be considered as paratactic clauses without punctuations.
-
-However, consider another example in Figure \ref{fig:informal-toks}.
+%From Fig.~\ref{ex1}, we argue that {\tt u} and {\tt rn} are syntactic tokens.
+%{\tt th} is a truncated token and does not have any syntactic function, although we can infer that the {\tt th} could be probably {\tt the}.
+%{\tt \#ACL2017}, {\tt :)} and {\tt http://url} are optionally syntactic tokens, and should be all treated as non-syntactic tokens in this example.
+%{\tt RT @Yijia :} should be analyzed as the retweet structure, and {\tt heading to Canada for ACL} and {\tt can u gimme some money} should be considered as paratactic clauses without punctuations.
+%
+%However, consider another example in Figure \ref{fig:informal-toks}.
 All of the optionally syntactic tokens ({\tt RT}, {\tt http://url}, {\tt \#NAACL}, {\tt \#Awesome}, {\tt @zypandora}, {\tt @nlpnoah} and {\tt $\heart$}) have syntactic functions, and we need to take them into account in the syntactic analysis.
@@
 tweets 		&	1639 		&	709		&	1201\\
-tokens 		&			&			&	\\
-types 		&	 		&			&	\\
-parts		 	&	 		&			&	\\ \hline
+tokens 		&	24753		&	11742	&	19112\\
+types 		&	7579			&	4165		&	6228\\
+parts		 	&	3025 		&	1402		&	2252\\ \hline
 \end{tabular}
- \caption{Basic Statistics of Tweebank}
+ \caption{Basic Statistics of Tweebank V2}
  \label{tab1}
@@
 \end{tabular}
- \caption{Twitter Specific Statistics of Tweebank}
- \label{tab1}
+ \caption{Twitter Specific Statistics of Tweebank V2}
+ \label{tab2}
 \end{table*}

### 2017-08-15 paper.tex
sync.

@@
 			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& @coldplay \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl}\\
-			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny X \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \\
+			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny PROPN \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \\
 		\end{deptext}
@@
 \subsection{POS Tagging}
-We follow the UD V2 morphology guideline and use the Universal POS tags~\cite{PETROV12.274} to tag the tweet tokens.
+We adopt the universal Part-of-Speech (POS) tagset \cite{PETROV12.274} to annotate the tweets.
+The POS annotation of a word in tweets is generally based on its syntactic distribution, which indicates typical nouns can be tagged as verbs in some certain context.
+%We follow the UD V2 morphology guideline and use the Universal POS tags~ to tag the tweet tokens.
 For twitter specific linguistic phenomena, we have set different strategies and try to align with the UD conventions and UD\textunderscore English as close as possible.\footnote{\url{https://github.com/UniversalDependencies/UD\_English}}

### 2017-08-16 paper.tex
revise 2.2

@@
 			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& @coldplay \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl}\\
-			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny PROPN \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \\
+			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny X \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \\
 		\end{deptext}
@@
 		\textcolor{red}{sentiment emoticon},
-		\textcolor{orange}{retweet mark},
+		\textcolor{orange}{retweet marker},
 		\textcolor{gray}{topical hashtag}, and
@@
 
-\subsection{POS Tagging}
+\subsection{Part-of-Speech Annotation}
 We adopt the universal Part-of-Speech (POS) tagset \cite{PETROV12.274} to annotate the tweets.
-The POS annotation of a word in tweets is generally based on its syntactic distribution, which indicates typical nouns can be tagged as verbs in some certain context.
+The POS annotation of a word in tweets is generally based on its syntactic distribution, which indicates that the POS of word changes on different context.
+Sticking to the syntactic distribution makes it possible that a `$\heart$' symbol is tagged as a verb as shown in Figure \ref{fig:non-syn-toks}. \yjcomment{Need a better explanation.}
 %We follow the UD V2 morphology guideline and use the Universal POS tags~ to tag the tweet tokens.
@@
 
-In token level phenomena, for non-syntactic tokens, we tag most of them as X (other), except for the emojis and emoticons, which would be tagged as SYM, as same in the UD\_English. 
-For syntactic tokens, we tag them considering their corresponding syntactic function.
+We need to note that in some certain cases, the distribution criteria doesn't holds.
+For example, the nominal URL in Figure \ref{fig:informal-toks} is tagged as {\it other} ({\tt X}) and the conjunctor {\tt +} symbol is tagged as {\it symbol} ({\tt SYM}) rather than {\it conjunction} ({\tt CCONJ}).
+Such violation is resulted by our attempt of conforming the annotation to the {\it universal dependencies - English dependency treebank} (UD\_English), in which all the URLs are tagged as {\it other} and symbolic conjunctors are tagged as {\it symbol}.\footnote{\url{https://github.com/UniversalDependencies/UD\_English}}
+By conforming our annotation to the UD\_English data, hopefully, the tools we built on tweets can benefit from the dataset on broader domain. \yjcomment{need wording}
 
-In structure level phenomena, we think {\tt RT @user} in retweet structure have no contribution to the tweet syntax and tag both of them as X.
-We tag usernames in at-mentioned structure as PROPN as they present the vocative case.
+Again, there are un-conventional linguistic constructions in tweets that syntactic distribution doesn't handle well.
+One of the cases is the non-syntactic tokens.
+We consider most of them as {\tt X}, except for the sentiment emoticons, which would be tagged as {\tt SYM}, in practice of matching the UD\_English.
+Another case is the retweet construction which is considered as a non-syntactic phrase and both the RT and at-mention are tagged as {\tt X}.
+For the at-mention, we tag them as proper noun ({\tt PROPN}) in spirit of following the vocative example in UD\_English.
+%In token level phenomena, for non-syntactic tokens,  
+%For syntactic tokens, we tag them considering their corresponding syntactic function.
 
-In Fig.~\ref{ex1}, {\tt RT} {\tt @yijialiu}, {\tt \#ACL2017}, {\tt http://url} and {\tt th} are all tagged as X and {\tt :)} is tagged as SYM. 
-{\tt rn} is tagged as ADV.
-We should note that multiple tokens are actually included in a phrasal abbreviation, and we use one of their tags as the tag of the whole abbreviation according to their dependency relation or semantic priority.
-If there is a hierarchy in the abbreviation, we use the tag of the head word. In UD, ``Right'' is the dependent of ``now '' in the dependency of {\tt rn}, so we tag {\tt rn} as ADV. 
+%In structure level phenomena, we think {\tt RT @user} in retweet structure have no contribution to the tweet syntax and tag both of them as X.
+%We tag usernames in at-mentioned structure as PROPN as they present the vocative case.
+
+The informal syntactic tokens can generally be handled by their distribution.
+However, one of the exception is the {\tt phrasal abbreviations} in which one token carries multiple syntactic functions.
+In dealing with such phrases, we propose a routine that first recover their original forms, then, use the POS of their syntactic head word as the POS of the whole phrase.
+Therefore, {\it idk} (I don't care) is a verb because {\it care} is its syntactic head.
+Such routine works for most of the phrasal abbreviations.
+When it falls, we just use the POS of the left-most sub-phrase.
+\footnote{Such failure can be resulted by the mis-match of phrase boundaries between the original form and the definition of `phrase' in UD.
+For example, `mfw' (my face when) doesn't make a phrase because `when' belongs to the subordination that modifies `my face'.}
+
+%In Fig.~\ref{ex1}, {\tt RT} {\tt @yijialiu}, {\tt \#ACL2017}, {\tt http://url} and {\tt th} are all tagged as X and {\tt :)} is tagged as SYM. 
+%{\tt rn} is tagged as ADV.
+%We should note that multiple tokens are actually included in a phrasal abbreviation, and we use one of their tags as the tag of the whole abbreviation according to their dependency relation or semantic priority.
+%If there is a hierarchy in the abbreviation, we use the tag of the head word. In UD, ``Right'' is the dependent of ``now '' in the dependency of {\tt rn}, so we tag {\tt rn} as ADV. 
 %Although there is no head word in {\tt im}, we think that the subject is usually more informative than the tense in many downstream tasks such as semantic role labelling, so we use the tag of ``I'', e.g.
 PROPN as the tag of {\tt im}.
-In Fig.~\ref{ex2}, {\tt RT} and {\tt $\heart$} would be tagged as VERB, {\tt http://url} as X, {\tt \#Awesome} as ADJ, {\tt \#NAACL}, {\tt @zypandora} and {\tt @nlpnoah} as PROPN.
+%In Fig.~\ref{ex2}, {\tt RT} and {\tt $\heart$} would be tagged as VERB, {\tt http://url} as X, {\tt \#Awesome} as ADJ, {\tt \#NAACL}, {\tt @zypandora} and {\tt @nlpnoah} as PROPN.
 One exception is that we tag URLs always as X regardless whether they are syntactic tokens.
@@
 
-\newcite{Gimpel:2011:PTT:2002736.2002747} proposed a twitter POS tagset that handles most of the token level phenomena.
-However, we found that their methods did not conform with UD conventions and our strategies have some advantages over their tagset.
-We discuss the main difference as follows.
-The first difference lies in the tokenizations.
-\newcite{Gimpel:2011:PTT:2002736.2002747} opted not to split contractions or possessives and introduced four new tags (S, Z, L, M) for combined forms: \{nominal, proper noun\} $\times$ \{verb, possessive\}.
-Major concern of designing such tags is to minimize the effort of tokenization, but it is not comprehensive and far from including all of the possible combinations of POS tags within the contractions.
-What's more, only a small proportion of tokens can be categorized into these tags (2.7 \% in total), which casts a doubt of the usefulness of these tags.
-Instead UD conventions suggest that we put such complexity into the tokenization module and split contractions and possessives, then tag them accordingly, so that we do not need extra POS tags for the combined forms.
-The second difference is that although the phrasal abbreviations are not split in both methods, they use tag G for all the phrasal abbreviations, while we use the tag of the head word or the highest hierarchical word in terms of dependencies as the tag of the whole phrasal abbreviations.
-We think it is not reasonable to treat the phrasal abbreviations in the same part of speech because obviously abbreviations can have different syntactic functions and we want to preserve the most useful information for both parser and the downstream tasks.
+Similar to our work, \newcite{gimpel-EtAl:2011:ACL-HLT2011} proposed a course grain twitter POS tagset that handles most of the token level phenomena.
+However, our work diverge theirs in several ways.
+Compared with the Gimpel's work, which assigns different tags to non-syntactic tokens in different categories, we simplify them into the {\tt X} tag.
+At the same time, all the abbreviations in \newcite{gimpel-EtAl:2011:ACL-HLT2011} are tagged with one POS, which doesn't distinguish their syntactic functions.
+We argue that such approach over-simplify the abbreviations.
+One example is that {\it idc} (I don't care) and {\it rn} (right now) carries significantly different syntactic functions and should not be treated as the same.
+In this paper, we stick more to the syntactic distribution when handling such abbreviations and it allows them to function differently in different context.
+
+The last difference between \newcite{gimpel-EtAl:2011:ACL-HLT2011} is resulted by the tokenization process.
+In \newcite{gimpel-EtAl:2011:ACL-HLT2011}, they opted out the tokenization on contractions and possessives and introduce several tags for these un-tokenized words.
+As mentioned above, the goal of conforming our annotation to the UD\_English makes us adopt the same the UD-styled tokenization.
+Thus, these tags for contractions and possessives are not necessary at all in our case.
+What's more, as \newcite{gimpel-EtAl:2011:ACL-HLT2011} mentioned, only a small proportion of tokens can be categorized into these tags (2.7 \% in total), which casts a doubt of the usefulness of these tags.
+%However, we found that their methods did not conform with UD conventions and our strategies have some advantages over their tagset. We discuss the main difference as follows.
+%The first difference lies in the tokenizations.
+%\newcite{Gimpel:2011:PTT:2002736.2002747} opted not to split contractions or possessives and introduced four new tags (S, Z, L, M) for combined forms: \{nominal, proper noun\} $\times$ \{verb, possessive\}.
+%Major concern of designing such tags is to minimize the effort of tokenization, but it is not comprehensive and far from including all of the possible combinations of POS tags within the contractions.
+%What's more, only a small proportion of tokens can be categorized into these tags (2.7 \% in total), which casts a doubt of the usefulness of these tags.
+%Instead UD conventions suggest that we put such complexity into the tokenization module and split contractions and possessives, then tag them accordingly, so that we do not need extra POS tags for the combined forms.
+%The second difference is that although the phrasal abbreviations are not split in both methods, they use tag G for all the phrasal abbreviations, while we use the tag of the head word or the highest hierarchical word in terms of dependencies as the tag of the whole phrasal abbreviations.
+%We think it is not reasonable to treat the phrasal abbreviations in the same part of speech because obviously abbreviations can have different syntactic functions and we want to preserve the most useful information for both parser and the downstream tasks.
 For example, {\tt wtf} could be tagged as PRON or INTJ according to the context, and {\tt rn} is usually tagged as ADV.
 Tagging them merely as G will definitely lose much information.
-Third, special tags were designed to handle twitter or online special tokens such as URLs, hashtags and emoticon in \newcite{Gimpel:2011:PTT:2002736.2002747}.
+%Third, special tags were designed to handle twitter or online special tokens such as URLs, hashtags and emoticon in \newcite{Gimpel:2011:PTT:2002736.2002747}.
 However, in most cases, as long as theses tokens are non syntactic, they play the same role in tweets, hence should be tagged the same.

### 2017-08-16 paper.tex
add statstics

@@
 The Twitter streams are in Spritzer version, which provides a 1\% random sample of public tweets everyday, and the tweets are in twitter JSON format.
-There are xxx tweets in all the streams.
-We filtered them with \textit{lang} attribute in \textit{user} and used \textit{langid.py}\footnote{https://github.com/saffsd/langid.py} to pick out English tweets, which ends in xxx tweets in English.
-Then we sampled 2500 tweets roughly equally from these months.
+There over 2k million tweets in all the streams.
+We filtered them with \textit{lang} attribute in \textit{user} and used \textit{langid.py}\footnote{https://github.com/saffsd/langid.py} to pick out English tweets, and then we sampled 2500 tweets roughly equally from these months.
 
@@
 \multirow{10}{*}{\textit{token}}	&	syntactic						&	\multicolumn{2}{l |}{phrasal abbreviation}				
-			 	&	  		&		&		&		&		\\
+			 	&	 12 		&	12	&	10	&	34	&	0.06\%	\\
 \cline{2-9}
 						&	\multirow{8}{*}{optionally syntactic}	&	\multirow{2}{*}{RT}					&	syntactic	
-			 	&	  		&		&		&		&		\\
+			 	&	 40 		&	19	&	18	&	77	&	0.14\%	\\
 						&								&									&	non-syntactic
-				&	  		&		&		&		&		\\
+				&	600  		&	500	&	286	&	1386	&	2.49\%	\\
 \cline{3-9}
 						&								&	\multirow{2}{*}{hashtag}				&	syntactic
-				&	  		&		&		&		&		\\
+				&	251  		&	212	&	103	&	566	&	1.02 \%	\\
 						&								&									&	non-syntactic
-				&	  		&		&		&		&		\\
+				&	 290 		&	246	&	155	&	691	&	1.24\%	\\
 \cline{3-9}
 						&								&	\multirow{2}{*}{at-mentioned}			&	syntactic
-				&	  		&		&		&		&		\\
+				&	  659		&	420	&	257	&	1336	&	2.40\%	\\
 						&								&									&	non-syntactic
-				&	  		&		&		&		&		\\
+				&	  640		&	519	&	311	&	1470	&	2.64\%	\\
 \cline{3-9}
 						&								&	\multirow{2}{*}{emoticon/emoji}			&	syntactic
-				&	  		&		&		&		&		\\
+				&	  59		&	31	&	24	&	114	&	2.05\%	\\
 						&								&									&	non-syntactic
-				&	  		&		&		&		&		\\
+				&	 233		&	164	&	98	&	495	&	0.89\%	\\
 \cline{2-9}
 						&	non-syntactic 					&	\multicolumn{2}{l |}{truncated}
-				&	  		&		&		&		&		\\
+				&	  111		&	110	&	50	&	271	&	0.49\%	\\
 
@@
 \multirow{3}{*}{\textit{structure}}	& 	\multicolumn{3}{l |}{retweet}
-			 	&	  		&		&		&		&		\\
+			 	&	  596		&	498	&	282	&	1376	&	2.47\%	\\
 						&	\multicolumn{3}{l |}{at-mentioned}
-				&	  		&		&		&		&		\\
-						&	\multicolumn{3}{l |}{parataxis without punctuations}
-				&	  		&		&		&		&		\\
+				&	  485		&	305	&	175	&	965	&	1.74\%	\\
 \hline
@@
 %annotation statistics, agreement
+
+The inter-annotator agreement of POS tagging is 95.02\%, the unlabelled dependency agreement is 88\% and the labelled dependency agreement is 84\%.
 

### 2017-08-16 paper.tex
revise 2.3, leave out the discussion.

--- 2017-08-16 paper.tex
@@
 
-\subsection{Part-of-Speech Annotation}
+\subsection{Part-of-Speech Annotation}\label{sec:pos-anno}
 We adopt the universal Part-of-Speech (POS) tagset \cite{PETROV12.274} to annotate the tweets.
@@
 In dealing with such phrases, we propose a routine that first recover their original forms, then, use the POS of their syntactic head word as the POS of the whole phrase.
-Therefore, {\it idk} (I don't care) is a verb because {\it care} is its syntactic head.
+Therefore, {\it idc} (I don't care) is a verb because {\it care} is its syntactic head.
 Such routine works for most of the phrasal abbreviations.
@@
 
-We follow the UD V2 syntax guideline and the English specific Universal Dependency Relations to annotate our data.
+We adopt universal dependency (UD) \cite{Marneffe2014UniversalSD} v2 guideline to annotate the syntax relations between tokens in tweets.
+UD was designed to handle the variant syntactic phenomenons across different languages and we expect its `context head' principle will bring convenience to the parsing of informal and even ungrammatical tweets.
+\yjcomment{I still feel we should give a reason why we choose UD.
+One example is that twitter users tend to leave out the copula verb and it will be messy for the `function head' principle to deal with this case.
+One observation is that informal tokens/syntax happens more on function words rather than content word.}
+%We follow the UD v2 syntax guideline and the English specific {\it universal dependency relations} to annotate our data.
 
-In token level phenomena, we adopt the following rules for non-syntactic tokens, denoted as x:
-
+%In token level phenomena, we adopt the following rules for non-syntactic tokens, denoted as x: 
+Again, as shown in Section \ref{sec:pos-anno}, the major challenge in adopting UD on tweets lies on dealing with the non-syntactic parts.
+Inspired by the way UD deal with punctuation, we adopt the following rules to obtain relation for the non-syntactic tokens:
 \begin{itemize}
-\item If the sentence x belongs to has a clear predicate with syntactic function, x should not have any dependent and is attached to this sentence’s predicate;
-\item If the sentence x belongs to consists of only non-syntactic tokens we attach x to the first token of the sentence;
-\item In parataxis case, when it is difficult to decide which sentence or phrase x should belong to, we always attach x to the previous predicate of the paratactic clause or phrase;
-\item x is mostly labelled as {\it discourse}, but URLs are always labelled as {\it list};
+\item If a non-syntactic token is within a sentence that has a clear predicate, it will be attached to this predicate;
+\item If the whole sentence is made of a sequence of non-syntactic tokens, we attach all these tokens to the first one;
+%\item In parataxis case, when it is difficult to decide which sentence or phrase x should belong to, we always attach x to the previous predicate of the paratactic clause or phrase;
+\item non-syntactic tokens are mostly labeled as {\it discourse}, but URLs are always labeled as {\it list} in conformation with the UD\_English;
 \end{itemize}
 
-The reason we annotate URLs differently is the same as in POS tagging, that UD\_English labelled them as {\it list} when they are non-syntactic tokens and we want to keep the dataset conformed with it.
-
-For syntactic tokens, they are considered the same as normal tokens and we just annotate them by following the UD guidelines.
-
-we further adopt the following rules for structure level phenomena:
-
-\begin{itemize}
-\item Retweet structure: we attach {\tt @user} to {\tt RT} and {\tt RT} to the predicate of the following sentence with {\it discourse} as labels.
-\item At-mentioned structure: we attach at-mentioned username to the predicate of the most relevant sentence with {\it vocative} label.
-If it is hard to decide which sentence would be the most relevant, we attach it to the previous sentence's predicate.
-\item Paratactic parts without punctuations: we follow the UD convention, set the first part as the main part of the sentence, and set its predicate as the main predicate of the sentence.
+Considering the twitter specific constructions, we will treat the retweet construction as a whole non-syntactic phrase, and the inner structure will always be attaching {\tt at-mention} to {\tt RT} with {\tt discourse}, {\tt :} to {\tt RT} with {\tt punct}.
+The whole construction headed on the {\tt RT} marker modifies the predicate of following sentence.
+For the at-mentioned structure, we attach at-mentioned username to the predicate of the most relevant sentence with {\it vocative} label.
+%If it is hard to decide which sentence would be the most relevant, we attach it to the previous sentence's predicate.
+	%\item Paratactic parts without punctuations: we follow the UD convention, set the first part as the main part of the sentence, and set its predicate as the main predicate of the sentence.
 Every predicate of the following parts should attach to the main predicate.
@@
 Note that we still have an exception for URLs, conforming with UD, which are always labelled as {\it list}, regardless of the type of the other part.
-\end{itemize}
+%\end{itemize}
+
+Besides these non-syntactic and special constructions, the informal but syntactic tokens are treated in the same way with their original form.
+
+%We further adopt the following rules for structure level phenomena:
 
@@
 % Annotation conventions
-\newcite{kong-EtAl:2014:EMNLP2014} built a syntactic treebank of tweets called Tweebank using Gimpel et al.'s POS tagset. 
-Apart from the difference in POS tagging, we found the following difference in both methods.
-First, Tweebank is an unlabelled dependency treebank. There is clearly a doubt about the usefulness of the Tweebank. We annotate the labelled dependencies by following the UD annotation guideline.
-Second, most of Tweebank was built in a day by two dozen annotators, most of whom had only cursory training in the annotation scheme~\cite{kong-EtAl:2014:EMNLP2014}.
+\newcite{kong-EtAl:2014:EMNLP2014} presented a syntactic treebank on Gimpel et al.'s POS tagset.
+Compared with their work which create an unlabeled treebank, we further attach dependency relations and it's expected to be more helpful for the downstream tasks.
+We also provide concrete guidelines on dealing with the special constructions in tweets along with their variant linguistic phenomenon.
+It solve the annotation inconsistency problem in \newcite{kong-EtAl:2014:EMNLP2014}'s treebank.
+Our definition of the non-syntactic tokens is similar in spirit to the token selection process but we further define the concrete cases for such tokens.
+\yjcomment{We can put the ellipsis example in as a comparison of the `function headed' Yamada dependency and `content head' UD dependency.}
+%Second, most of Tweebank was built in a day by two dozen annotators, most of whom had only cursory training in the annotation scheme~\cite{kong-EtAl:2014:EMNLP2014}.
 We think, after investigation, that despite the speed, the quality of data is still to be improved.
 We follow strictly the UD annotation guideline and only make twitter specific conventions when there is no suitable convention to adopt in UD guideline or no relevant data found in UD\_English.
-Third, \newcite{kong-EtAl:2014:EMNLP2014} developed a first-order sequence model to filter out the non-syntactic tokens and punctuations, and exclude them before parsing.
-It is very different from most of the annotation conventions, especially for UD conventions.
+%Third, \newcite{kong-EtAl:2014:EMNLP2014} developed a first-order sequence model to filter out the non-syntactic tokens and punctuations, and exclude them before parsing.
+%It is very different from most of the annotation conventions, especially for UD conventions.
 We believe that every token should be included in the dependency tree, whether they have syntactic functions or are to be evaluated in the end, as in most of the conventions, so we annotate all tokens.
-Last, \newcite{kong-EtAl:2014:EMNLP2014} adopt the ``Yamada-Matsumoto" conventions~\cite{Yamada03statisticaldependency}, where auxiliary verbs are parents of main verbs, and prepositions are parents of their arguments, in contrast to UD conventions, where content words are put into the primacy, and dependency relations hold primarily between them, rather than being indirect relations mediated by function words.
+%Last, \newcite{kong-EtAl:2014:EMNLP2014} adopt the ``Yamada-Matsumoto" conventions~\cite{Yamada03statisticaldependency}, where auxiliary verbs are parents of main verbs, and prepositions are parents of their arguments, in contrast to UD conventions, where content words are put into the primacy, and dependency relations hold primarily between them, rather than being indirect relations mediated by function words.
 Auxiliary verbs and prepositions are all function words, and are attached to the most related content words in UD.
 
-\subsection{Tweebank V2}
-We present Tweebank V2, a version 2 of Tweebank~\cite{kong-EtAl:2014:EMNLP2014}.
+\subsection{Data Collection}
+\yjcomment{This section is un-finished.}
+Following the guideline mentioned above, we create a new annotated Twitter treebank, which we call tweebank v2.
+%We present tweebank v2, a version 2 of tweebank~\cite{kong-EtAl:2014:EMNLP2014}.
 
@@
 \subsubsection{Basic Statistics}
-Tweebank V2 contains 3550 tweets in total, split into training set with 1639 tweets, development set with 710 tweets and test set with 1201 tweets. 
+Tweebank v2 contains 3550 tweets in total, split into training set with 1639 tweets, development set with 710 tweets and test set with 1201 tweets. 
 The training set contains all the 639 unique tweets in the training set of Tweebank V1 and another 1000 tweets in feb\_jul\_16 corpus.

### 2017-08-16 paper.tex

@@
 \end{document}
+
+=======
+%
+% File acl2012.tex
+%
+% Contact: Maggie Li (cswjli@comp.polyu.edu.hk), Michael White (mwhite@ling.osu.edu)
+%%
+%% Based on the style files for ACL2008 by Joakim Nivre and Noah Smith
+%% and that of ACL2010 by Jing-Shin Chang and Philipp Koehn
+
+\documentclass[11pt,letterpaper]{article}
+\usepackage[letterpaper]{geometry}
+\usepackage{acl2012}
+\usepackage{times}
+\usepackage{latexsym}
+\usepackage{amsmath}
+\usepackage{multirow}
+\usepackage{xcolor}
+\usepackage{tikz-dependency}
+\usepackage{url}
+\makeatletter
+\newcommand{\@BIBLABEL}{\@emptybiblabel}
+\newcommand{\@emptybiblabel}[1]{}
+\makeatother
+\usepackage[hidelinks]{hyperref}
+\DeclareMathOperator*{\argmax}{arg\,max}
+\setlength\titlebox{6.5cm}    % Expanding the titlebox
+
+%%%%%%%
+\usepackage{graphicx}
+\newcommand{\heart}{\ensuremath\heartsuit}
+\usepackage{multirow}
+
+\newcommand{\yjcomment}[1]{\textcolor{orange}{[$_\mathrm{L}^\mathrm{Y}$\textsc{#1}]}}
+
+\title{Parsing Tweets into Universal Dependencies}
+
+\author{First Author \\
+  Affiliation / Address line 1 \\
+  Affiliation / Address line 2 \\
+  Affiliation / Address line 3 \\
+  {\tt email@domain} \\\And
+  Second Author \\
+  Affiliation / Address line 1 \\
+  Affiliation / Address line 2 \\
+  Affiliation / Address line 3 \\
+  {\tt email@domain} \\}
+
+\date{}
+
+\begin{document}
+\maketitle
+\begin{abstract}
+
+\end{abstract}
+
+\section{Introduction}
+Analyzing the syntax of tweets is challenging for traditional NLP tools because most of the tweet texts are informal and noisy.
+
+In this paper, we propose to parse the tweets in the convention of universal dependencies and built up the whole pipeline to parse the tweets from the raw text form.
+
+Contribution of this paper includes:
+\begin{itemize}
+\item We create a new version of tweet Treebank Tweebank 2.0
+\item We propose a neural network method to parse tweets into universal dependencies
+\item We study the adaptation of universal dependencies for analyzing tweets
+\end{itemize}
+
+\section{Data}
+% Linguistic phenomena
+	% word level
+		% RT
+		% Hashtag
+		% Mention, urls
+		% Symbols and Emoticons
+		% Truncated tokens
+	% twitter level
+		% RT
+		% Parataxis	
+% POS
+	% Acronym priority
+	% URL tagged as X	
+% Depenency
+	% Concentrate on NON-UD phenomena
+% Statistics
+	% Scale
+	% Inter-annotator agreement
+	% Proportion
+		% how many hashtags, mentions, ....
+		% how many acornyms
+
+\subsection{Linguistic Phenomena of Twitter} \label{lingphen}
+Twitter, as an extreme example of informal domain, contains a collection of conversational languages (like abbreviation, informal contraction, and variant entity names) and twitter-specified markers (like retweet mark, and username).
+Despite the informal nature of tweets, we argue that they basically follow the same grammar as their formal language counterpart.
+The key issue lies in understanding the specific construction that doesn't carry any syntactic functions, and designed rules to handle the specific constructions in tweets.
+In the following section, we studied such constructions from both the token and structure level. \yjcomment{I don't like the name of \textbf{structure level}}
+%As the representative of the web language, different from the standard languages such as newswire, twitter has its own linguistic phenomena, that could be categorized into token level and structure level phenomena, and we will discuss them separately.
+
+\subsubsection{Token Level}
+\paragraph{Informal Syntactic Tokens.}
+Informal tokens like phrase abbreviation (like {\tt mfw}: my face when, {\tt rn}: right now, and etc.) and orthographic variants (like {\tt sooo cooool}) have drawn much attention in previous literals \cite{finin-EtAl:2010:MTURK,eisenstein:2013:NAACL-HLT} \yjcomment{not sure orthographic variants is a good name, need reference.}
+However, in the sense of syntactic functions, they work in the same way as the ordinary words, which makes them requires less specialty in designing annotation conventions.
+%Syntactic tokens are just like normal tokens in the standard text.
+%They always have syntactic functions in tweets.
+%They could be orthographic variants or abbreviations that represents a phrase.
+
+\paragraph{Non-syntactic Tokens.}
+
+\begin{figure*}[t]
+	\centering
+	\small
+	\begin{dependency}[edge slant=2, text only label, label style=above]
+		\begin{deptext}
+			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& @coldplay \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl}\\
+			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny X \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \\
+		\end{deptext}
+		\deproot{1}{root}
+		\depedge[edge unit distance=1em]{1}{2}{discourse}
+		\deproot{6}{root}
+		\depedge[edge unit distance=1em]{6}{3}{discourse}
+		\depedge[edge unit distance=1em]{3}{4}{discourse}
+		\depedge[edge unit distance=1em]{3}{5}{punct}
+		\depedge[edge unit distance=1em]{6}{7}{obj}
+		\depedge[edge unit distance=0.8em]{6}{10}{obl}
+		\depedge[edge unit distance=1em]{10}{8}{case}
+		\depedge[edge unit distance=1em]{10}{9}{det}
+		\depedge[edge unit distance=0.8em]{6}{11}{discourse}
+		\depedge[edge unit distance=0.8em]{6}{12}{list}
+	\end{dependency}
+	\caption{A example tweet contains major non-syntactic tokens, with
+		\textcolor{red}{sentiment emoticon},
+		\textcolor{orange}{retweet marker},
+		\textcolor{gray}{topical hashtag}, and
+		\textcolor{blue}{referential URL}.}\label{fig:non-syn-toks}
+\end{figure*}
+
+\begin{figure*}[t]
+	\centering
+	\small
+	\begin{dependency}[edge slant=2, text only label, label style=above]
+		\begin{deptext}
+			its \& \#awesome \& u \& gonna \& $\heart$ \& it \& Chk \& out \& our \& cooool \& project \& on \& http:// \& + \& RT \& pls\\
+			\tiny PRON \& \tiny ADJ \& \tiny PRON \& \tiny VERB \& \tiny VERB \& \tiny PRON \& \tiny VERB \& \tiny ADP \& \tiny PRON \& \tiny ADJ \& \tiny NOUN \& \tiny ADP \& \tiny X \& \tiny SYM \& \tiny VERB\& \tiny INTJ\\
+		\end{deptext}
+		\deproot{2}{root}
+		\depedge[edge unit distance=1em]{2}{1}{nsubj}
+		\depedge[edge unit distance=1em]{2}{4}{parataxis}
+		\depedge[edge unit distance=1em]{4}{3}{nsubj}
+		\depedge[edge unit distance=1em]{4}{5}{xcomp}
+		\depedge[edge unit distance=1em]{5}{6}{obj}
+		\depedge[edge unit distance=0.7em]{2}{7}{parataxis}
+		\depedge[edge unit distance=1em]{7}{8}{compound:prt}
+		\depedge[edge unit distance=0.7em]{7}{11}{obj}
+		\depedge[edge unit distance=1em]{11}{9}{nmod:poss}
+		\depedge[edge unit distance=1em]{11}{10}{amod}
+		\depedge[edge unit distance=1em]{11}{13}{nmod}
+		\depedge[edge unit distance=1em]{13}{12}{case}
+		\depedge[edge unit distance=0.45em]{7}{15}{conj}
+		\depedge[edge unit distance=1em]{15}{14}{cc}
+		\depedge[edge unit distance=0.35em]{2}{16}{discourse}
+	\end{dependency}
+	\caption{An example tweet with informal but syntactic tokens.}\label{fig:informal-toks}
+\end{figure*}
+
+Besides the informal but syntactic tokens, there are a large collection of tokens that cannot be handled by the syntactic theory designed for standard text.
+A major part of these tokens consists of meta data in tweets, like the sentiment emotion, retweet mark, topical hashtag, and referential URL shown in Figure \ref{fig:non-syn-toks}.
+
+However, whether a token convey some syntactic function cannot be simply decided by its form.
+For example, besides being a discourse marker, {\tt RT} can also works as a abbreviation of the verb {\tt retweet}.
+Emoticons are sometimes used as a verbal part of the sentence.
+Twitter users have developed a casual habit of using hashtag, and even use hashtag as a adjective.
+The sentence in Figure \ref{fig:informal-toks} gives a comprehensive example of those informal but syntactic tokens.
+It shows whether a token makes a non-syntactic one is highly conditioned on its context.
+
+A kind of token that doesn't carry clearly syntactic functions can be resulted by the 140 characters limits of tweets.
+Since last tokens that exceeding 140 characters limits are truncated in tweets which leaves a broken sentence, it is impossible to fully recover their original form and figure out their syntactics.
+In this paper, we propose to treat these truncated tokens, along with the other 4 kinds of tokens mentioned above, as ones without syntactic functions.
+
+In the sense of dealing with the non-syntactic tokens, \newcite{kong-EtAl:2014:EMNLP2014} proposed an preprocessing step named {\it token selection} to remove non-syntactic tokens from the original tweets.
+However, concrete standard of non-syntactic tokens was not presented in their work.
+What's more, these unselected tokens are absent from downstream processing, including parsing.
+We differ from their work by proposing concrete standard of non-syntactic tokens and we include these non-syntactic tokens in our final analyzed dependencies by adding special attachment to them.
+%There are special tokens that will appear only or much more frequently in tweets.
+%According to the syntactic functions these tokens have in the tweets, we classify them into three types: syntactic tokens, non-syntactic tokens and optionally syntactic tokens. 
+%Non-syntactic tokens are tokens that will not have syntactic function in tweets, and they are not considered in the syntax analysis and need to be treated independently.
+%Optionally syntactic tokens are tokens that can have either syntactic or non-syntactic functions based on the context.
+Usually they are tokens like URLs ad hashtags that do not participate in the syntax of the tweets, and we treat them as non-syntactic functions by default.
+However, similar in the analysis of \newcite{Gimpel:2011:PTT:2002736.2002747} and \newcite{kong-EtAl:2014:EMNLP2014}, in some cases they are perceived as the arguments or predicates of tweets and therefore have syntactic functions.
+In this case we treat them as syntactic tokens.
+
+%Here is a complete list of the special tokens in tweets classified in three types.
+%
+%\begin{itemize}
+%\item syntactic tokens
+%	\begin{itemize}
+%		\item phrasal abbreviations: {\tt wtf} (what the fuck), {\tt rn} (right now), etc.
+%		\item orthographic variants: {\tt u} (you), {\tt sooooo}, {\tt dat} (that), etc.
+%	\end{itemize}
+%\item Non-syntactic tokens
+%	\begin{itemize}
+%		\item truncated tokens: last tokens that are truncated in tweets exceeding twitter character limits.
+Although It might be possible to recover the original tokens from the context in some cases, it is still extremely hard to further predict the rest of the truncated part.
+%	\end{itemize}
+%\item Optionally syntactic tokens
+%	\begin{itemize}
+%		\item retweet discourse marker: RT
+%		\item URL: http://bit.ly/xyz
+%		\item hashtag: \#ACL
+%		\item at-mentioned username: @user
+%		\item emoticons and emojis: :), :-), $\heart$, etc.
+%	\end{itemize}
+%\end{itemize}
+
+%As optionally syntactic tokens will be treated as syntactic or non-syntactic tokens based on the specific context, for the sake of simplicity, if not necessary, we will only discuss the syntactic and non-syntactic tokens in the following sections.
+
+\subsubsection{Structure Level}
+The syntactic constructions vary greatly across different tweets.
+Unconventional constructions which frequently occur include ellipsis, irregular word orders, and para-tactic sentences without the segmentation of punctuations \yjcomment{I move the 3rd bullet point here because this construction was handled by UD-guidelines}.
+And these unconventional ones are more or less resolved by the universal dependencies.
+The unresolved cases are mainly resulted by the format of twitter.
+The {\it retweet} and {\it at-mention} are of two major constructions.
+\paragraph{Retweet.} For the {\it retweet} construction (`{\tt RT @coldplay :}' in Figure \ref{fig:non-syn-toks}), although it can be treated as a verbal phrase in which retweet marker works as a verb and the following at-mention is its objective, we argue that such convention lead to a uninformative root word.
+It also increase the difficulty for downstream tasks in figuring out the core predicate and arguments for one certain tweet.
+Thus, we treat the whole construction as a non-syntactic phrase. \yjcomment{correct me if I am wrong.}
+\paragraph{At-mention.} At-mention in the beginning of a tweet is the format of indicating the `reply' action.
+In this paper, we treat the at-mentions as vocative expressions for their connections with the traditional vocative words, rather than treat them as non-syntactic metadata, which increase the complexity for analyzing a tweet.
+\yjcomment{since the original discussion mainly focus on tokens, I move them to the former section.}
+%Besides the token level phenomena of twitter, there are also structural patterns appearing in the twitter.
+
+%\begin{itemize}
+%\item Retweet structure: {\tt RT @user : \{tweet content\}} is a typical structural pattern when a user is retweeting from other users. 
+%\item At-mentioned structure: Except the retweet structure and syntactically at-mentioned username, we think that all of other at-mentions are vocative case, usually appearing at the beginning or the end of the sentences in tweets.
+%\item Paratactic parts without punctuations: We use ``part'' to refer to a self-contained clause or phrase, which is independent of other ``part''.
+Very often, one tweet is comprised of multiple parts without any delimiting punctuations, such as {\tt \{part 1\} \{part 2\} ...}
+%\end{itemize}
+
+%We treat retweet structure and at-mentioned structure as structural patterns and keep their annotations consistent across tweets.
+For parataxis case, we treat each single sentence or phrase normally, and connect them together following the UD conventions.
+
+%From Fig.~\ref{ex1}, we argue that {\tt u} and {\tt rn} are syntactic tokens.
+%{\tt th} is a truncated token and does not have any syntactic function, although we can infer that the {\tt th} could be probably {\tt the}.
+%{\tt \#ACL2017}, {\tt :)} and {\tt http://url} are optionally syntactic tokens, and should be all treated as non-syntactic tokens in this example.
+%{\tt RT @Yijia :} should be analyzed as the retweet structure, and {\tt heading to Canada for ACL} and {\tt can u gimme some money} should be considered as paratactic clauses without punctuations.
+%
+%However, consider another example in Figure \ref{fig:informal-toks}.
+All of the optionally syntactic tokens ({\tt RT}, {\tt http://url}, {\tt \#NAACL}, {\tt \#Awesome}, {\tt @zypandora}, {\tt @nlpnoah} and {\tt $\heart$}) have syntactic functions, and we need to take them into account in the syntactic analysis.
+
+\subsection{Part-of-Speech Annotation}
+We adopt the universal Part-of-Speech (POS) tagset \cite{PETROV12.274} to annotate the tweets.
+The POS annotation of a word in tweets is generally based on its syntactic distribution, which indicates that the POS of word changes on different context.
+Sticking to the syntactic distribution makes it possible that a `$\heart$' symbol is tagged as a verb as shown in Figure \ref{fig:non-syn-toks}. \yjcomment{Need a better explanation.}
+%We follow the UD V2 morphology guideline and use the Universal POS tags~ to tag the tweet tokens.
+For twitter specific linguistic phenomena, we have set different strategies and try to align with the UD conventions and UD\textunderscore English as close as possible.\footnote{\url{https://github.com/UniversalDependencies/UD\_English}}
+
+We need to note that in some certain cases, the distribution criteria doesn't holds.
+For example, the nominal URL in Figure \ref{fig:informal-toks} is tagged as {\it other} ({\tt X}) and the conjunctor {\tt +} symbol is tagged as {\it symbol} ({\tt SYM}) rather than {\it conjunction} ({\tt CCONJ}).
+Such violation is resulted by our attempt of conforming the annotation to the {\it universal dependencies - English dependency treebank} (UD\_English), in which all the URLs are tagged as {\it other} and symbolic conjunctors are tagged as {\it symbol}.\footnote{\url{https://github.com/UniversalDependencies/UD\_English}}
+By conforming our annotation to the UD\_English data, hopefully, the tools we built on tweets can benefit from the dataset on broader domain. \yjcomment{need wording}
+
+Again, there are un-conventional linguistic constructions in tweets that syntactic distribution doesn't handle well.
+One of the cases is the non-syntactic tokens.
+We consider most of them as {\tt X}, except for the sentiment emoticons, which would be tagged as {\tt SYM}, in practice of matching the UD\_English.
+Another case is the retweet construction which is considered as a non-syntactic phrase and both the RT and at-mention are tagged as {\tt X}.
+For the at-mention, we tag them as proper noun ({\tt PROPN}) in spirit of following the vocative example in UD\_English.
+%In token level phenomena, for non-syntactic tokens,  
+%For syntactic tokens, we tag them considering their corresponding syntactic function.
+
+%In structure level phenomena, we think {\tt RT @user} in retweet structure have no contribution to the tweet syntax and tag both of them as X.
+%We tag usernames in at-mentioned structure as PROPN as they present the vocative case.
+
+The informal syntactic tokens can generally be handled by their distribution.
+However, one of the exception is the {\tt phrasal abbreviations} in which one token carries multiple syntactic functions.
+In dealing with such phrases, we propose a routine that first recover their original forms, then, use the POS of their syntactic head word as the POS of the whole phrase.
+Therefore, {\it idk} (I don't care) is a verb because {\it care} is its syntactic head.
+Such routine works for most of the phrasal abbreviations.
+When it falls, we just use the POS of the left-most sub-phrase.
+\footnote{Such failure can be resulted by the mis-match of phrase boundaries between the original form and the definition of `phrase' in UD.
+For example, `mfw' (my face when) doesn't make a phrase because `when' belongs to the subordination that modifies `my face'.}
+
+%In Fig.~\ref{ex1}, {\tt RT} {\tt @yijialiu}, {\tt \#ACL2017}, {\tt http://url} and {\tt th} are all tagged as X and {\tt :)} is tagged as SYM. 
+%{\tt rn} is tagged as ADV.
+%We should note that multiple tokens are actually included in a phrasal abbreviation, and we use one of their tags as the tag of the whole abbreviation according to their dependency relation or semantic priority.
+%If there is a hierarchy in the abbreviation, we use the tag of the head word. In UD, ``Right'' is the dependent of ``now '' in the dependency of {\tt rn}, so we tag {\tt rn} as ADV. 
+%Although there is no head word in {\tt im}, we think that the subject is usually more informative than the tense in many downstream tasks such as semantic role labelling, so we use the tag of ``I'', e.g.
+PROPN as the tag of {\tt im}.
+%In Fig.~\ref{ex2}, {\tt RT} and {\tt $\heart$} would be tagged as VERB, {\tt http://url} as X, {\tt \#Awesome} as ADJ, {\tt \#NAACL}, {\tt @zypandora} and {\tt @nlpnoah} as PROPN.
+One exception is that we tag URLs always as X regardless whether they are syntactic tokens.
+The reason is that we observed, in UD\_English, that the URLs are all tagged as X and we want to conform with the UD dataset, although we think it is not appropriate and should be changed to tags such as PROPN when they are treated as syntactic tokens.
+
+Similar to our work, \newcite{gimpel-EtAl:2011:ACL-HLT2011} proposed a course grain twitter POS tagset that handles most of the token level phenomena.
+However, our work diverge theirs in several ways.
+Compared with the Gimpel's work, which assigns different tags to non-syntactic tokens in different categories, we simplify them into the {\tt X} tag.
+At the same time, all the abbreviations in \newcite{gimpel-EtAl:2011:ACL-HLT2011} are tagged with one POS, which doesn't distinguish their syntactic functions.
+We argue that such approach over-simplify the abbreviations.
+One example is that {\it idc} (I don't care) and {\it rn} (right now) carries significantly different syntactic functions and should not be treated as the same.
+In this paper, we stick more to the syntactic distribution when handling such abbreviations and it allows them to function differently in different context.
+
+The last difference between \newcite{gimpel-EtAl:2011:ACL-HLT2011} is resulted by the tokenization process.
+In \newcite{gimpel-EtAl:2011:ACL-HLT2011}, they opted out the tokenization on contractions and possessives and introduce several tags for these un-tokenized words.
+As mentioned above, the goal of conforming our annotation to the UD\_English makes us adopt the same the UD-styled tokenization.
+Thus, these tags for contractions and possessives are not necessary at all in our case.
+What's more, as \newcite{gimpel-EtAl:2011:ACL-HLT2011} mentioned, only a small proportion of tokens can be categorized into these tags (2.7 \% in total), which casts a doubt of the usefulness of these tags.
+%However, we found that their methods did not conform with UD conventions and our strategies have some advantages over their tagset. We discuss the main difference as follows.
+%The first difference lies in the tokenizations.
+%\newcite{Gimpel:2011:PTT:2002736.2002747} opted not to split contractions or possessives and introduced four new tags (S, Z, L, M) for combined forms: \{nominal, proper noun\} $\times$ \{verb, possessive\}.
+%Major concern of designing such tags is to minimize the effort of tokenization, but it is not comprehensive and far from including all of the possible combinations of POS tags within the contractions.
+%What's more, only a small proportion of tokens can be categorized into these tags (2.7 \% in total), which casts a doubt of the usefulness of these tags.
+%Instead UD conventions suggest that we put such complexity into the tokenization module and split contractions and possessives, then tag them accordingly, so that we do not need extra POS tags for the combined forms.
+%The second difference is that although the phrasal abbreviations are not split in both methods, they use tag G for all the phrasal abbreviations, while we use the tag of the head word or the highest hierarchical word in terms of dependencies as the tag of the whole phrasal abbreviations.
+%We think it is not reasonable to treat the phrasal abbreviations in the same part of speech because obviously abbreviations can have different syntactic functions and we want to preserve the most useful information for both parser and the downstream tasks.
+For example, {\tt wtf} could be tagged as PRON or INTJ according to the context, and {\tt rn} is usually tagged as ADV.
+Tagging them merely as G will definitely lose much information.
+%Third, special tags were designed to handle twitter or online special tokens such as URLs, hashtags and emoticon in \newcite{Gimpel:2011:PTT:2002736.2002747}.
+However, in most cases, as long as theses tokens are non syntactic, they play the same role in tweets, hence should be tagged the same.
+In this paper, except for the emoticon and emoji, tagged as SYM, we tag all the other non-syntactic tokens as X.
+
+\subsection{Dependency Annotation}
+
+We follow the UD V2 syntax guideline and the English specific Universal Dependency Relations to annotate our data.
+
+In token level phenomena, we adopt the following rules for non-syntactic tokens, denoted as x:
+
+\begin{itemize}
+\item If the sentence x belongs to has a clear predicate with syntactic function, x should not have any dependent and is attached to this sentence’s predicate;
+\item If the sentence x belongs to consists of only non-syntactic tokens we attach x to the first token of the sentence;
+\item In parataxis case, when it is difficult to decide which sentence or phrase x should belong to, we always attach x to the previous predicate of the paratactic clause or phrase;
+\item x is mostly labelled as {\it discourse}, but URLs are always labelled as {\it list};
+\end{itemize}
+
+The reason we annotate URLs differently is the same as in POS tagging, that UD\_English labelled them as {\it list} when they are non-syntactic tokens and we want to keep the dataset conformed with it.
+
+For syntactic tokens, they are considered the same as normal tokens and we just annotate them by following the UD guidelines.
+
+we further adopt the following rules for structure level phenomena:
+
+\begin{itemize}
+\item Retweet structure: we attach {\tt @user} to {\tt RT} and {\tt RT} to the predicate of the following sentence with {\it discourse} as labels.
+\item At-mentioned structure: we attach at-mentioned username to the predicate of the most relevant sentence with {\it vocative} label.
+If it is hard to decide which sentence would be the most relevant, we attach it to the previous sentence's predicate.
+\item Paratactic parts without punctuations: we follow the UD convention, set the first part as the main part of the sentence, and set its predicate as the main predicate of the sentence.
+Every predicate of the following parts should attach to the main predicate.
+If the main part and some following part are both phrases, the label is {\it list}, otherwise the label is {\it parataxis}.
+Note that we still have an exception for URLs, conforming with UD, which are always labelled as {\it list}, regardless of the type of the other part.
+\end{itemize}
+
+% unlabelled, Informal
+% exclude non-syntactic tokens, punctuations
+% Annotation conventions
+\newcite{kong-EtAl:2014:EMNLP2014} built a syntactic treebank of tweets called Tweebank using Gimpel et al.'s POS tagset. 
+Apart from the difference in POS tagging, we found the following difference in both methods.
+First, Tweebank is an unlabelled dependency treebank. There is clearly a doubt about the usefulness of the Tweebank. We annotate the labelled dependencies by following the UD annotation guideline.
+Second, most of Tweebank was built in a day by two dozen annotators, most of whom had only cursory training in the annotation scheme~\cite{kong-EtAl:2014:EMNLP2014}.
+We think, after investigation, that despite the speed, the quality of data is still to be improved.
+We follow strictly the UD annotation guideline and only make twitter specific conventions when there is no suitable convention to adopt in UD guideline or no relevant data found in UD\_English.
+Third, \newcite{kong-EtAl:2014:EMNLP2014} developed a first-order sequence model to filter out the non-syntactic tokens and punctuations, and exclude them before parsing.
+It is very different from most of the annotation conventions, especially for UD conventions.
+We believe that every token should be included in the dependency tree, whether they have syntactic functions or are to be evaluated in the end, as in most of the conventions, so we annotate all tokens.
+Last, \newcite{kong-EtAl:2014:EMNLP2014} adopt the ``Yamada-Matsumoto" conventions~\cite{Yamada03statisticaldependency}, where auxiliary verbs are parents of main verbs, and prepositions are parents of their arguments, in contrast to UD conventions, where content words are put into the primacy, and dependency relations hold primarily between them, rather than being indirect relations mediated by function words.
+Auxiliary verbs and prepositions are all function words, and are attached to the most related content words in UD.
+
+\subsection{Tweebank V2}
+We present Tweebank V2, a version 2 of Tweebank~\cite{kong-EtAl:2014:EMNLP2014}.
+
+%data aquisition/statistics
+The tweet source of Tweebank V2 consists of three parts. 
+The first is the original Tweebank created by~\cite{kong-EtAl:2014:EMNLP2014}, denoted as Tweebank V1.
+There are 639 unique tweets in the training data of Tweebank V1, and 201 unique tweets in the data set.
+All of the unique tweets in Tweebank V1 are included in Tweebank V2.
+The second are 210 tweets from POS-tagged Twitter corpus of~\newcite{Owo13}, denoted as Tweebank V1 Dev. It was initially created as a development set of Tweebank V1 for hyperparameter tuning.
+Tweebank V1 Dev comprises were equally sampled from two data set, OCT27 (tweets sampled from a particular day, October 27, 2010) and DAILY 547 (one random English tweet per day from January 2011 through June 2012, 547 tweets in total).
+We should note that all of the Tweebank V1 tweets were also drawn from OCT27 and DAILY547, and the new tweets we extracted are not in the Tweebank V1.
+The third are 2500 tweets from the Twitter streams from February 2017 to July 2017 from ArchiveTeam,\footnote{https://archive.org} which we call Feb\_Jul\_16 corpus.
+The Twitter streams are in Spritzer version, which provides a 1\% random sample of public tweets everyday, and the tweets are in twitter JSON format.
+There over 2k million tweets in all the streams.
+We filtered them with \textit{lang} attribute in \textit{user} and used \textit{langid.py}\footnote{https://github.com/saffsd/langid.py} to pick out English tweets, and then we sampled 2500 tweets roughly equally from these months.
+
+\subsubsection{Basic Statistics}
+Tweebank V2 contains 3550 tweets in total, split into training set with 1639 tweets, development set with 710 tweets and test set with 1201 tweets. 
+The training set contains all the 639 unique tweets in the training set of Tweebank V1 and another 1000 tweets in feb\_jul\_16 corpus.
+The development set contains 210 tweets of Tweebank V1 Dev and another 500 tweets in feb\_jul\_16 corpus.
+The test set contains all the 201 tweets in the test set of Tweebank V1 and another 1000 tweets in feb\_jul\_16 corpus.
+
+We process all the raw tweets of these corpora from scratch, from tokenization and POS tagging to dependency annotation.
+As Tweebank V1 and the POS-tagged Twitter corpus of~\newcite{Owo13} used a tweet tokenizer~\cite{Krieger10tweetmotif:exploratory} and POS tagger~\cite{Gimpel:2011:PTT:2002736.2002747} that do not conform with UD guidelines, as we discussed before, we did not use any data of the intermediate steps from these corpora.
+The basic statistics of Tweebank V2 is shown in Table~\ref{tab1}.
+
+% tweets, tokens, tokens/tweet, part/tweet, token types.
+\begin{table}[t]
+\centering
+ \begin{tabular}{l r r r} 
+ \hline
+ 			& 	Train 		& 	Dev		&	Test\\[0.5ex] \hline
+tweets 		&	1639 		&	709		&	1201\\
+tokens 		&	24753		&	11742	&	19112\\
+types 		&	7579			&	4165		&	6228\\
+parts		 	&	3025 		&	1402		&	2252\\ \hline
+\end{tabular}
+ \caption{Basic Statistics of Tweebank V2}
+ \label{tab1}
+\end{table}
+
+% tokens and its proportions for the previous language phenomena.
+\subsubsection{Twitter Specific Statistics}\label{stats}
+Following the discussion of the Twitter specific linguistic phenomena, we obtain Table~\ref{tab2}.
+
+\begin{table*}[t]
+\centering
+\small
+ \begin{tabular}{r | l | l | l | r r r r r} 
+ \hline
+\multicolumn{4}{l}{}	&	Train		&	Test	&	Dev	&	All	&	Per\\[0.5ex] \hline\hline
+\multirow{10}{*}{\textit{token}}	&	syntactic						&	\multicolumn{2}{l |}{phrasal abbreviation}				
+			 	&	 12 		&	12	&	10	&	34	&	0.06\%	\\
+\cline{2-9}
+						&	\multirow{8}{*}{optionally syntactic}	&	\multirow{2}{*}{RT}					&	syntactic	
+			 	&	 40 		&	19	&	18	&	77	&	0.14\%	\\
+						&								&									&	non-syntactic
+				&	600  		&	500	&	286	&	1386	&	2.49\%	\\
+\cline{3-9}
+						&								&	\multirow{2}{*}{hashtag}				&	syntactic
+				&	251  		&	212	&	103	&	566	&	1.02 \%	\\
+						&								&									&	non-syntactic
+				&	 290 		&	246	&	155	&	691	&	1.24\%	\\
+\cline{3-9}
+						&								&	\multirow{2}{*}{at-mentioned}			&	syntactic
+				&	  659		&	420	&	257	&	1336	&	2.40\%	\\
+						&								&									&	non-syntactic
+				&	  640		&	519	&	311	&	1470	&	2.64\%	\\
+\cline{3-9}
+						&								&	\multirow{2}{*}{emoticon/emoji}			&	syntactic
+				&	  59		&	31	&	24	&	114	&	2.05\%	\\
+						&								&									&	non-syntactic
+				&	 233		&	164	&	98	&	495	&	0.89\%	\\
+\cline{2-9}
+						&	non-syntactic 					&	\multicolumn{2}{l |}{truncated}
+				&	  111		&	110	&	50	&	271	&	0.49\%	\\
+
+\hline
+\multirow{3}{*}{\textit{structure}}	& 	\multicolumn{3}{l |}{retweet}
+			 	&	  596		&	498	&	282	&	1376	&	2.47\%	\\
+						&	\multicolumn{3}{l |}{at-mentioned}
+				&	  485		&	305	&	175	&	965	&	1.74\%	\\
+\hline
+\end{tabular}
+ \caption{Twitter Specific Statistics of Tweebank V2}
+ \label{tab2}
+\end{table*}
+%annotation statistics, agreement
+
+The inter-annotator agreement of POS tagging is 95.02\%, the unlabelled dependency agreement is 88\% and the labelled dependency agreement is 84\%.
+
+\section{Pipeline}
+
+\section{Model}
+
+\section{Experiments}
+
+\section{Related Work}
+\newcite{eisenstein:2013:NAACL-HLT} reviewed NLP approaches for analyzing text on social media, especially for tweets and showed that there are two major directions for NLP community to handle the tweets, including normalization and domain adaptation.
+He also pointed out that normalization can be problematic because precisely defining the normalization task is difficult.
+
+\newcite{kong-EtAl:2014:EMNLP2014} argues that the Penn Treebank approach to annotation is poorly suited to more informal genres of text, as some of the annotation challenges for tweets,
+including token selection, multiword expressions, multiple roots, and structure within noun phrases diverge significantly from conventional approaches. 
+They believe that rapid, small scale annotation efforts performed by imperfectly-trained annotators should provide enough evidence to train an effective parser, given the rapidly changing nature of tweets~\cite{eisenstein:2013:NAACL-HLT}, the attested difficulties of domain adaptation for parsing~\cite{dred07}, and the expense of creating Penn Treebank-style annotations~\cite{penn93}.
+Therefore, they build a new corpus of tweets (Tweebank), with conventions informed by the domain, using new syntactic annotations that can tackle all the forementioned problems annotated in a day by two dozen annotators, most of whom had only cursory training in the annotation scheme.
+Then, they modify the decoder of the TurboParser, a graph-based dependency parser, which is open-source and has been found to perform well on a range of parsing problems in different languages~\cite{turbo13} to adapt to the Tweebank dataset, and incorporate new features such as Brown Clusters and Penn Treebank features and changes to specification
+in the output space into TurboParser.
+
+Like ``mfw'' is usually followed by an adverbial clause and ``ima'' is usually followed by a clausal complement. 
+It is not reasonable to treat them in the same part-of-speech. 
+In this paper, when annotating the POS tagging for abbreviations, we first try to recover their original forms, then use the POS of the core-word as the POS for the abbreviation.
+Second, four special POS tags (S, L, M, Y) were designed to handle contraction words in Gimpel et al.
+\shortcite{Gimpel:2011:PTT:2002736.2002747}.
+Major concern of designing such tags is to minimize the effort of tokenization.
+However, contractions of common nouns and pronouns are casted into the same category which increase the difficulty of distinguishing their syntactic function (say, there's and book'll are treated with the same syntactic function).
+What's more, only a small proportion of words can be categorized into these tags (2.7 \% in total), which cast a doubt of the usefulness of these certain tags.
+In this paper, we believe such contraction can be properly handled by tokenization module, so we suggest to tokenize the contraction word and annotate POS tag accordingly.
+Besides the contraction that be conventionally tokenized, tweets also witness a set of unconventional contraction like iv (I've), whatis (what is).
+In this paper, we follow the same idea of annotation abbreviation to handle the unconventional contractions and use the POS of core word of the original form as their POS.
+Third, special POS was designed to handle emoticon in Gimpel et al.
+\shortcite{Gimpel:2011:PTT:2002736.2002747}.
+However, in most cases, emoticon plays the same role as most of the symbolic tokens.
+In this paper, we follow the UD guideline to annotate the emoticon as symbol (SYM).
+At last, it’s arguable that some of the hashtags, URLs can work as a nominal in tweets.
+Whether treating them as the same part-of-speech or different ones according to their context is an open question.
+A preliminary survey on the standard UD English data shows that URL, email address are all tagged as the foreign language (X), so we also tag them as X and leave the disambiguation of their syntactic function to the annotation of parse tree.
+
+\section{Conclusion}
+
+\bibliography{shortdb}
+\bibliographystyle{acl2012}
+\end{document}

### 2017-08-16 paper.tex
resolve conflict and add stat.

--- 2017-08-16 paper.tex
@@
 All of the unique tweets in Tweebank V1 are included in Tweebank V2.
-The second are 210 tweets from POS-tagged Twitter corpus of~\newcite{Owo13}, denoted as Tweebank V1 Dev. It was initially created as a development set of Tweebank V1 for hyperparameter tuning.
+The second are 210 tweets from POS-tagged Twitter corpus of \newcite{owoputi-EtAl:2013:NAACL-HLT}, denoted as Tweebank V1 Dev.
+It was initially created as a development set of Tweebank V1 for hyperparameter tuning.
 Tweebank V1 Dev comprises were equally sampled from two data set, OCT27 (tweets sampled from a particular day, October 27, 2010) and DAILY 547 (one random English tweet per day from January 2011 through June 2012, 547 tweets in total).
@@
 \subsubsection{Basic Statistics}
-Tweebank v2 contains 3550 tweets in total, split into training set with 1639 tweets, development set with 710 tweets and test set with 1201 tweets. 
+Tweebank V2 contains 3550 tweets in total, split into training set with 1639 tweets, development set with 710 tweets and test set with 1201 tweets. 
 The training set contains all the 639 unique tweets in the training set of Tweebank V1 and another 1000 tweets in feb\_jul\_16 corpus.
@@
 We process all the raw tweets of these corpora from scratch, from tokenization and POS tagging to dependency annotation.
-As Tweebank V1 and the POS-tagged Twitter corpus of~\newcite{Owo13} used a tweet tokenizer~\cite{Krieger10tweetmotif:exploratory} and POS tagger~\cite{Gimpel:2011:PTT:2002736.2002747} that do not conform with UD guidelines, as we discussed before, we did not use any data of the intermediate steps from these corpora.
+As Tweebank V1 and the POS-tagged Twitter corpus of \newcite{gimpel-EtAl:2011:ACL-HLT2011} used a tweet tokenizer~\cite{ICWSM101540} that do not conform with UD guidelines, as we discussed before, we did not use any data of the intermediate steps from these corpora.
 The basic statistics of Tweebank V2 is shown in Table~\ref{tab1}.
@@
 		\multirow{10}{*}{\textit{token}}	&	syntactic						&	\multicolumn{2}{l |}{phrasal abbreviation}				
-			 	&	  		&		&		&		&		\\
+		&	 12 		&	12	&	10	&	34	&	0.06\%	\\
 		\cline{2-9}
 		&	\multirow{8}{*}{optionally syntactic}	&	\multirow{2}{*}{RT}					&	syntactic	
-			 	&	  		&		&		&		&		\\
+		&	 40 		&	19	&	18	&	77	&	0.14\%	\\
 		&								&									&	non-syntactic
-				&	  		&		&		&		&		\\
+		&	600  		&	500	&	286	&	1386	&	2.49\%	\\
 		\cline{3-9}
 		&								&	\multirow{2}{*}{hashtag}				&	syntactic
-				&	  		&		&		&		&		\\
+		&	251  		&	212	&	103	&	566	&	1.02 \%	\\
 		&								&									&	non-syntactic
-				&	  		&		&		&		&		\\
+		&	 290 		&	246	&	155	&	691	&	1.24\%	\\
 		\cline{3-9}
 		&								&	\multirow{2}{*}{at-mentioned}			&	syntactic
-				&	  		&		&		&		&		\\
+		&	  659		&	420	&	257	&	1336	&	2.40\%	\\
 		&								&									&	non-syntactic
-				&	  		&		&		&		&		\\
+		&	  640		&	519	&	311	&	1470	&	2.64\%	\\
 		\cline{3-9}
 		&								&	\multirow{2}{*}{emoticon/emoji}			&	syntactic
-				&	  		&		&		&		&		\\
+		&	  59		&	31	&	24	&	114	&	2.05\%	\\
 		&								&									&	non-syntactic
-				&	  		&		&		&		&		\\
+		&	 233		&	164	&	98	&	495	&	0.89\%	\\
 		\cline{2-9}
 		&	non-syntactic 					&	\multicolumn{2}{l |}{truncated}
-				&	  		&		&		&		&		\\
+		&	  111		&	110	&	50	&	271	&	0.49\%	\\
 
@@
 		\multirow{3}{*}{\textit{structure}}	& 	\multicolumn{3}{l |}{retweet}
-			 	&	  		&		&		&		&		\\
+		&	  596		&	498	&	282	&	1376	&	2.47\%	\\
 		&	\multicolumn{3}{l |}{at-mentioned}
-				&	  		&		&		&		&		\\
-						&	\multicolumn{3}{l |}{parataxis without punctuations}
-				&	  		&		&		&		&		\\
+		&	  485		&	305	&	175	&	965	&	1.74\%	\\
 		\hline

### 2017-08-20 paper.tex
Noah

@@
 \newcommand{\yjcomment}[1]{\textcolor{orange}{[$_\mathrm{L}^\mathrm{Y}$\textsc{#1}]}}
+\newcommand{\nascomment}[1]{\textcolor{blue}{[#1 ---\textsc{nas}]}}
 
@@
 
-In this paper, we propose to parse the tweets in the convention of universal dependencies and built up the whole pipeline to parse the tweets from the raw text form.
+In this paper, we propose to parse the tweets in the convention of
+universal dependencies and built up the whole pipeline to parse the
+tweets from the raw text form.
+
+Motivation notes:  explain why UD is attractive (and more attractive
+than what previous work used, which was based on YM).  one reason is
+that it might allow sharing of texts annotated in different genres (or
+even languages, cite Waleed).  but universal annotation schemes are
+challenging!  this paper contends with the challenges of
+applying UD to social media texts.
+
+\nascomment{Points that were in older text that I want to keep around:}
+\begin{itemize}
+\item Despite the informal nature of tweets, we argue that they basically follow the same grammar as their formal language counterpart.
+\item UD was designed to handle the variant syntactic phenomenons across different languages and we expect its `context head' principle will bring convenience to the parsing of informal and even ungrammatical tweets.
+\yjcomment{I still feel we should give a reason why we choose UD. One
+  example is that twitter users tend to leave out the copula verb and
+  it will be messy for the `function head' principle to deal with this
+  case. One observation is that informal tokens/syntax happens more on
+  function words rather than content word.} \nascomment{maybe we could
+  argue that, if UD is designed to work for many languages, it should
+  also be able to work for dialects, including AAVE, and informal
+  registers.  YM was not designed for cross-linguistic applicability.}
+
+\end{itemize}
 
@@
 
-\section{Data}
+\nascomment{not clear to me:  did we reannotate the POS corpus?  was
+  that automatic or manual?  I wasn't sure what to do with the POS
+  section below.}
+
+\section{Annotation}
+
+\nascomment{need to introduce this section and explain the structure.
+I'm not crazy about what I have now, but I like it better than what
+we had before, which seemed to keep repeating the same ideas in
+different contexts.  the flow still seems wrong; we start by talking
+about dependencies, then take a detour to POS, then come back to
+dependencies.}
+\subsection{Background:  \textsc{Tweebank}}
+
+The annotation effort we describe stands in contrast to previous work
+by \newcite{kong-EtAl:2014:EMNLP2014}.  Their aim was the rapid
+development of a dependency parser for tweets, and to that end they
+contributed a new annotated corpus, \textsc{Tweebank}, consisting of
+929 tweets.  Their annotations added a layer to a portion of the data
+annotated with part-of-speech tags by
+\newcite{gimpel-EtAl:2011:ACL-HLT2011} and
+\newcite{owoputi-EtAl:2013:NAACL-HLT}.  They also contributed a system
+for parsing;
+we defer discussion of their parser to \S\ref{sec:parsing}.
+
+Kong et al.'s rapid, small-scale annotation effort was heavily constrained.  It was
+carried out mostly by non-native speakers, in a very short amount of
+time (a day).  Driven both by the style of the text they sought to annotate
+and by exigency, some of their annotation conventions included:
+\begin{itemize}
+\item Allowing an annotator to exclude tokens from the dependency
+  tree.  A clear criterion for exclusion was not given, but many
+  tokens were excluded because they were deemed ``non-syntactic.''
+\item Allowing an annotator to merge a multiword expression into a
+  single node in the dependency tree, with no internal structure.
+  Annotators were allowed to take the same step with noun phrases.
+\item Allowing multiple roots, since a single tweet might contain more
+  than one sentence.
+\end{itemize}
+These conventions were justified on the grounds of making the
+annotation easier for non-experts, but they must be revisited in our
+effort to apply UD to tweets.
+
+\subsection{Part-of-Speech Annotation}\label{sec:pos-anno}
+
+Before turning to UD annotations, we (re)annotated the data with 
+part-of-speech, for consistency with other UD efforts,
+which adopt the universal POS tagset of \newcite{PETROV12.274}.
+% The POS annotation of a word in tweets is generally based on its syntactic distribution, which indicates that the POS of word changes on different context.
+% Sticking to the syntactic distribution makes it possible that a `$\heart$' symbol is tagged as a verb as shown in Figure \ref{fig:non-syn-toks}. \yjcomment{Need a better explanation.}
+%We follow the UD V2 morphology guideline and use the Universal POS tags~ to tag the tweet tokens.
+For twitter specific linguistic phenomena, we have set different strategies and try to align with the UD conventions and UD\textunderscore English as close as possible.\footnote{\url{https://github.com/UniversalDependencies/UD\_English}}
+
+In some cases, conflicts arose between the UD English 
+treebank conventions (UD\_English)
+\footnote{\url{https://github.com/UniversalDependencies/UD_English}}
+\nascomment{add cite}
+and the conventions of \newcite{gimpel-EtAl:2011:ACL-HLT2011} and
+\newcite{owoputi-EtAl:2013:NAACL-HLT}.  In these cases, we always
+conformed to UD, enabling consistency (e.g., when we exploit the
+existing UD English treebank in our parser for tweets, \S\ref{???}).  For example,  
+the nominal URL in Figure \ref{fig:informal-toks} is tagged as {\it
+  other} ({\tt X}) and {\tt +} is tagged as {\it symbol} ({\tt SYM})
+rather than {\it conjunction} ({\tt CCONJ}).  
+% Such violation is resulted by our attempt of conforming the annotation to the {\it universal dependencies - English dependency treebank} (UD\_English), in which all the URLs are tagged as {\it other} and symbolic conjunctors are tagged as {\it symbol}.
+% By conforming our annotation to the UD\_English data, hopefully, the tools we built on tweets can benefit from the dataset on broader domain. \yjcomment{need wording}
+
+Tokens that do not have a syntactic function (discussed at greater
+length in the next section) were usually annotated as \emph{other}
+(\texttt{X}), except for emoticons, which are tagged as \emph{symbol}
+(\texttt{SYM}), following UD\_English.
+
+% Again, there are un-conventional linguistic constructions in tweets that syntactic distribution doesn't handle well.
+% One of the cases is the non-syntactic tokens.
+% We consider most of them as {\tt X}, except for the sentiment emoticons, which would be tagged as {\tt SYM}, in practice of matching the UD\_English.
+% Another case is the retweet construction which is considered as a non-syntactic phrase and both the RT and at-mention are tagged as {\tt X}.
+% For the at-mention, we tag them as proper noun ({\tt PROPN}) in spirit of following the vocative example in UD\_English.
+%In token level phenomena, for non-syntactic tokens,  
+%For syntactic tokens, we tag them considering their corresponding syntactic function.
+
+%In structure level phenomena, we think {\tt RT @user} in retweet structure have no contribution to the tweet syntax and tag both of them as X.
+%We tag usernames in at-mentioned structure as PROPN as they present the vocative case.
+
+Tokens that abbreviate multiple words, such as \emph{idc} (``I don't
+care'') are resolved to the POS of the syntactic head of the
+expression, following UD conventions (in this example, the head \emph{care} is
+a verb, so \emph{idc} is tagged as a verb).
+% The informal syntactic tokens can generally be handled by their distribution.
+% However, one of the exception is the {\tt phrasal abbreviations} in which one token carries multiple syntactic functions.
+% In dealing with such phrases, we propose a routine that first recover their original forms, then, use the POS of their syntactic head word as the POS of the whole phrase.
+% Therefore, {\it idc} (I don't care) is a verb because {\it care} is its syntactic head.
+% Such routine works for most of the phrasal abbreviations.
+When the token is not phrasal, we use the POS of the left-most
+sub-phrase.  For example, \emph{mfw} (``my face when'') is tagged as a
+noun (for \emph{face}).
+% \footnote{Such failure can be resulted by the mis-match of phrase boundaries between the original form and the definition of `phrase' in UD.
+For example, `mfw' (my face when) doesn't make a phrase because `when' belongs to the subordination that modifies `my face'.}
+
+%In Fig.~\ref{ex1}, {\tt RT} {\tt @yijialiu}, {\tt \#ACL2017}, {\tt http://url} and {\tt th} are all tagged as X and {\tt :)} is tagged as SYM. 
+%{\tt rn} is tagged as ADV.
+%We should note that multiple tokens are actually included in a phrasal abbreviation, and we use one of their tags as the tag of the whole abbreviation according to their dependency relation or semantic priority.
+%If there is a hierarchy in the abbreviation, we use the tag of the head word. In UD, ``Right'' is the dependent of ``now '' in the dependency of {\tt rn}, so we tag {\tt rn} as ADV. 
+%Although there is no head word in {\tt im}, we think that the subject is usually more informative than the tense in many downstream tasks such as semantic role labelling, so we use the tag of ``I'', e.g.
+PROPN as the tag of {\tt im}.
+%In Fig.~\ref{ex2}, {\tt RT} and {\tt $\heart$} would be tagged as VERB, {\tt http://url} as X, {\tt \#Awesome} as ADJ, {\tt \#NAACL}, {\tt @zypandora} and {\tt @nlpnoah} as PROPN.
+One exception is that we tag URLs always as X regardless whether they are syntactic tokens.
+The reason is that we observed, in UD\_English, that the URLs are all tagged as X and we want to conform with the UD dataset, although we think it is not appropriate and should be changed to tags such as PROPN when they are treated as syntactic tokens.
+
+Compared to coarse-grained part-of-speech tagging effort of
+\newcite{gimpel-EtAl:2011:ACL-HLT2011}, our approach simplifies some
+matters.  For example, if a token is not considered syntactic by UD
+conventions, it gets an \emph{other} (\texttt{X}) tag (Gimpel et
+al.~had more extensive conventions).  Other phenomena, like
+abbreviations, are more complicated for us, as discussed above;
+Gimpel et al.~used a single part of speech for such expressions.
+
+%  proposed a course grain twitter POS tagset that handles most of the token level phenomena.
+% However, our work diverge theirs in several ways.
+% Compared with the Gimpel's work, which assigns different tags to non-syntactic tokens in different categories, we simplify them into the {\tt X} tag.
+% At the same time, all the abbreviations in \newcite{gimpel-EtAl:2011:ACL-HLT2011} are tagged with one POS, which doesn't distinguish their syntactic functions.
+% We argue that such approach over-simplify the abbreviations.
+% One example is that {\it idc} (I don't care) and {\it rn} (right now) carries significantly different syntactic functions and should not be treated as the same.
+% In this paper, we stick more to the syntactic distribution when handling such abbreviations and it allows them to function differently in different context.
+
+Another important difference is in tokenization.  UD calls for more
+aggressive tokenization than that used by
+\newcite{gimpel-EtAl:2011:ACL-HLT2011}, which followed
+\newcite{oconnor-2010}.  In particular, they opted out of tokenizing
+contractions and possessives, introducing new parts of speech
+instead.\footnote{These tags only accounted for 2.7\% of tokens,
+  leading to concerns about data sparseness in tagging and all
+  downstream analyses.}  For us, these tokens must be split, but
+universal parts of speech can be applied.
+
+%  is resulted by the tokenization process.
+% In \newcite{gimpel-EtAl:2011:ACL-HLT2011}, they opted out the tokenization on contractions and possessives and introduce several tags for these un-tokenized words.
+% As mentioned above, the goal of conforming our annotation to the UD\_English makes us adopt the same the UD-styled tokenization.
+% Thus, these tags for contractions and possessives are not necessary at all in our case.
+% What's more, as \newcite{gimpel-EtAl:2011:ACL-HLT2011} mentioned, only a small proportion of tokens can be categorized into these tags (2.7 \% in total), which casts a doubt of the usefulness of these tags.
+% %However, we found that their methods did not conform with UD conventions and our strategies have some advantages over their tagset. We discuss the main difference as follows.
+% %The first difference lies in the tokenizations.
+% %\newcite{Gimpel:2011:PTT:2002736.2002747} opted not to split contractions or possessives and introduced four new tags (S, Z, L, M) for combined forms: \{nominal, proper noun\} $\times$ \{verb, possessive\}.
+% %Major concern of designing such tags is to minimize the effort of tokenization, but it is not comprehensive and far from including all of the possible combinations of POS tags within the contractions.
+% %What's more, only a small proportion of tokens can be categorized into these tags (2.7 \% in total), which casts a doubt of the usefulness of these tags.
+% %Instead UD conventions suggest that we put such complexity into the tokenization module and split contractions and possessives, then tag them accordingly, so that we do not need extra POS tags for the combined forms.
+% %The second difference is that although the phrasal abbreviations are not split in both methods, they use tag G for all the phrasal abbreviations, while we use the tag of the head word or the highest hierarchical word in terms of dependencies as the tag of the whole phrasal abbreviations.
+% %We think it is not reasonable to treat the phrasal abbreviations in the same part of speech because obviously abbreviations can have different syntactic functions and we want to preserve the most useful information for both parser and the downstream tasks.
+For example, {\tt wtf} could be tagged as PRON or INTJ according to the context, and {\tt rn} is usually tagged as ADV.
+Tagging them merely as G will definitely lose much information.
+% %Third, special tags were designed to handle twitter or online special tokens such as URLs, hashtags and emoticon in \newcite{Gimpel:2011:PTT:2002736.2002747}.
+However, in most cases, as long as theses tokens are non syntactic, they play the same role in tweets, hence should be tagged the same.
+In this paper, except for the emoticon and emoji, tagged as SYM, we tag all the other non-syntactic tokens as X.
+
+\subsection{Universal Dependencies Applied to Tweets}
+
+We adopt UD version 2 
+\cite{Marneffe2014UniversalSD} guidelines to annotate the syntax of tweets.
+In applying UD annotation conventions to tweets, the choices of 
+\newcite{kong-EtAl:2014:EMNLP2014} must be revisited.  We consider the
+key questions that arose in our annotation effort, and how we resolved them.
+
+\nascomment{for each thing we talk about here, might be nice to
+  quantify it in our annotated corpus}
+
 % Linguistic phenomena
@@
 
-\subsection{Linguistic Phenomena of Twitter} \label{lingphen}
-Twitter, as an extreme example of informal domain, contains a collection of conversational languages (like abbreviation, informal contraction, and variant entity names) and twitter-specified markers (like retweet mark, and username).
-Despite the informal nature of tweets, we argue that they basically follow the same grammar as their formal language counterpart.
-The key issue lies in understanding the specific construction that doesn't carry any syntactic functions, and designed rules to handle the specific constructions in tweets.
-In the following section, we studied such constructions from both the token and structure level. \yjcomment{I don't like the name of \textbf{structure level}}
-%As the representative of the web language, different from the standard languages such as newswire, twitter has its own linguistic phenomena, that could be categorized into token level and structure level phenomena, and we will discuss them separately.
+%\subsection{Linguistic Phenomena of Twitter} \label{lingphen}
+% Twitter, as an extreme example of informal domain, contains a collection of conversational languages (like abbreviation, informal contraction, and variant entity names) and twitter-specified markers (like retweet mark, and username).
+% The key issue lies in understanding the specific construction that doesn't carry any syntactic functions, and designed rules to handle the specific constructions in tweets.
+% In the following section, we studied such constructions from both the token and structure level. \yjcomment{I don't like the name of \textbf{structure level}}
+% %As the representative of the web language, different from the standard languages such as newswire, twitter has its own linguistic phenomena, that could be categorized into token level and structure level phenomena, and we will discuss them separately.
 
-\subsubsection{Token Level}
-\paragraph{Informal Syntactic Tokens.}
-Informal tokens like phrase abbreviation (like {\tt mfw}: my face when, {\tt rn}: right now, and etc.) and orthographic variants (like {\tt sooo cooool}) have drawn much attention in previous literals \cite{finin-EtAl:2010:MTURK,eisenstein:2013:NAACL-HLT} \yjcomment{not sure orthographic variants is a good name, need reference.}
-However, in the sense of syntactic functions, they work in the same way as the ordinary words, which makes them requires less specialty in designing annotation conventions.
-%Syntactic tokens are just like normal tokens in the standard text.
-%They always have syntactic functions in tweets.
-%They could be orthographic variants or abbreviations that represents a phrase.
+\paragraph{Acronym abbreviations.}  How should we syntactically
+analyze acronym tokens like \emph{mfw}
+(abbreviating ``my face when'') and \emph{rn} (``right now'')?  Should
+they be decomposed into their component words, and if so should those
+words be ``normalized'' into explicitly spelled out intermediate
+forms?  \nascomment{explain what we do, and include how this is
+  similar to or different from Kong et al}
 
-\paragraph{Non-syntactic Tokens.}
+\nascomment{maybe we owe citations to
+  \cite{finin-EtAl:2010:MTURK,eisenstein:2013:NAACL-HLT} here?  maybe
+  better papers to cite}
+
+\paragraph{Non-syntactic tokens.}  
+Figure \ref{fig:non-syn-toks} illustrates examples of tokens that have
+no syntactic function.  Note that these generally have the
+\emph{other} (\texttt{X}) part of speech.
+
+It is important to note that these types may, in some
+contexts, have syntactic functions.
+For example, besides being a discourse marker, \emph{RT} can
+abbreviate the verb {\tt retweet}, and emoticons and hashtags may be
+used as content words within a sentence; see  Figure
+\ref{fig:informal-toks}.  Therefore, the criteria for annotating a
+token as non-syntactic must be context-dependent.
+To our knowledge, this issue has not previously been addressed in UD
+annotation efforts \nascomment{check!}.
+
+\nascomment{I'm confused about (1) how we define non-syntactic tokens
+  (what are the criteria) and (2) whether this is something we kick
+  over to POS annotation}
+
+Inspired by the way UD deals with \emph{punctuation} (which is
+canonically non-syntactic), we adopt the following
+conventions:
+\begin{itemize}
+\item If a non-syntactic token is within a sentence that has a clear predicate, it will be attached to this predicate;
+\item If the whole sentence is made of a sequence of non-syntactic tokens, we attach all these tokens to the first one;
+%\item In parataxis case, when it is difficult to decide which sentence or phrase x should belong to, we always attach x to the previous predicate of the paratactic clause or phrase;
+\item non-syntactic tokens are mostly labeled as {\it discourse}, but
+  URLs are always labeled as {\it list}, following the UD\_English dataset.
+\end{itemize}
+
+\nascomment{explain our conventions and how
+  they relate to Kong and to UD.  in the draft before, we said that we
+had conventions, and Kong didn't, but we didn't really say what ours were.}
+
+% \subsubsection{Token Level}
+% \paragraph{Informal Syntactic Tokens.}
+% Informal tokens like phrase abbreviation (like {\tt mfw}: my face when, {\tt rn}: right now, and etc.) and orthographic variants (like {\tt sooo cooool}) have drawn much attention in previous literals \cite{finin-EtAl:2010:MTURK,eisenstein:2013:NAACL-HLT} \yjcomment{not sure orthographic variants is a good name, need reference.}
+% However, in the sense of syntactic functions, they work in the same way as the ordinary words, which makes them requires less specialty in designing annotation conventions.
+% %Syntactic tokens are just like normal tokens in the standard text.
+% %They always have syntactic functions in tweets.
+% %They could be orthographic variants or abbreviations that represents a phrase.
+
+% \paragraph{Non-syntactic Tokens.}
 
@@
 
-Besides the informal but syntactic tokens, there are a large collection of tokens that cannot be handled by the syntactic theory designed for standard text.
-A major part of these tokens consists of meta data in tweets, like the sentiment emotion, retweet mark, topical hashtag, and referential URL shown in Figure \ref{fig:non-syn-toks}.
+% Besides the informal but syntactic tokens, there are a large collection of tokens that cannot be handled by the syntactic theory designed for standard text.
+% A major part of these tokens consists of meta data in tweets, like the sentiment emotion, retweet mark, topical hashtag, and referential URL shown in Figure \ref{fig:non-syn-toks}.
 
-However, whether a token convey some syntactic function cannot be simply decided by its form.
-For example, besides being a discourse marker, {\tt RT} can also works as a abbreviation of the verb {\tt retweet}.
-Emoticons are sometimes used as a verbal part of the sentence.
-Twitter users have developed a casual habit of using hashtag, and even use hashtag as a adjective.
-The sentence in Figure \ref{fig:informal-toks} gives a comprehensive example of those informal but syntactic tokens.
-It shows whether a token makes a non-syntactic one is highly conditioned on its context.
+% However, whether a token convey some syntactic function cannot be simply decided by its form.
+% For example, besides being a discourse marker, {\tt RT} can also works as a abbreviation of the verb {\tt retweet}.
+% Emoticons are sometimes used as a verbal part of the sentence.
+% Twitter users have developed a casual habit of using hashtag, and even use hashtag as a adjective.
+% The sentence in Figure \ref{fig:informal-toks} gives a comprehensive example of those informal but syntactic tokens.
+% It shows whether a token makes a non-syntactic one is highly conditioned on its context.
 
-A kind of token that doesn't carry clearly syntactic functions can be resulted by the 140 characters limits of tweets.
-Since last tokens that exceeding 140 characters limits are truncated in tweets which leaves a broken sentence, it is impossible to fully recover their original form and figure out their syntactics.
-In this paper, we propose to treat these truncated tokens, along with the other 4 kinds of tokens mentioned above, as ones without syntactic functions.
+\nascomment{in latex source I've commented out a paragraph about
+  truncated content.  it's not clear to me what the nonsyntactic
+  tokens are, when that happens}
+% A kind of token that doesn't carry clearly syntactic functions can be resulted by the 140 characters limits of tweets.
+% Since last tokens that exceeding 140 characters limits are truncated in tweets which leaves a broken sentence, it is impossible to fully recover their original form and figure out their syntactics.
+% In this paper, we propose to treat these truncated tokens, along with the other 4 kinds of tokens mentioned above, as ones without syntactic functions.
 
-In the sense of dealing with the non-syntactic tokens, \newcite{kong-EtAl:2014:EMNLP2014} proposed an preprocessing step named {\it token selection} to remove non-syntactic tokens from the original tweets.
-However, concrete standard of non-syntactic tokens was not presented in their work.
-What's more, these unselected tokens are absent from downstream processing, including parsing.
-We differ from their work by proposing concrete standard of non-syntactic tokens and we include these non-syntactic tokens in our final analyzed dependencies by adding special attachment to them.
+\newcite{kong-EtAl:2014:EMNLP2014} proposed an additional
+preprocessing step, \emph{token selection}, to remove non-syntactic
+tokens before parsing.  \nascomment{confusing.  were they removed or
+  just labeled as non-syntactic and then excluded from the tree?  I
+  think they were not actually removed, and were still available,
+  e.g., for defining features of the input for parsing}  In order to
+keep our annotation conventions in line with UD norms, we include
+non-syntactic tokens in the dependency analysis, with a special label
+\nascomment{say what it is, and what they attach to, and clarify that
+  the annotators didn't do this manually (I think)}
+
+%In the sense of dealing with the non-syntactic tokens, \newcite{kong-EtAl:2014:EMNLP2014} proposed an preprocessing step named {\it token selection} to remove non-syntactic tokens from the original tweets.
+%However, concrete standard of non-syntactic tokens was not presented in their work.
+%What's more, these unselected tokens are absent from downstream processing, including parsing.
+%We differ from their work by proposing concrete standard of non-syntactic tokens and we include these non-syntactic tokens in our final analyzed dependencies by adding special attachment to them.
 %There are special tokens that will appear only or much more frequently in tweets.
@@
 
-\subsubsection{Structure Level}
-The syntactic constructions vary greatly across different tweets.
-Unconventional constructions which frequently occur include ellipsis, irregular word orders, and para-tactic sentences without the segmentation of punctuations \yjcomment{I move the 3rd bullet point here because this construction was handled by UD-guidelines}.
-And these unconventional ones are more or less resolved by the universal dependencies.
-The unresolved cases are mainly resulted by the format of twitter.
-The {\it retweet} and {\it at-mention} are of two major constructions.
-\paragraph{Retweet.} For the {\it retweet} construction (`{\tt RT @coldplay :}' in Figure \ref{fig:non-syn-toks}), although it can be treated as a verbal phrase in which retweet marker works as a verb and the following at-mention is its objective, we argue that such convention lead to a uninformative root word.
-It also increase the difficulty for downstream tasks in figuring out the core predicate and arguments for one certain tweet.
-Thus, we treat the whole construction as a non-syntactic phrase. \yjcomment{correct me if I am wrong.}
-\paragraph{At-mention.} At-mention in the beginning of a tweet is the format of indicating the `reply' action.
-In this paper, we treat the at-mentions as vocative expressions for their connections with the traditional vocative words, rather than treat them as non-syntactic metadata, which increase the complexity for analyzing a tweet.
-\yjcomment{since the original discussion mainly focus on tokens, I move them to the former section.}
-%Besides the token level phenomena of twitter, there are also structural patterns appearing in the twitter.
+\paragraph{Retweet construction.} Figure \ref{fig:non-syn-toks} shows
+an example of the retweet construction (\emph{RT @coldplay :}).  This
+might be treated as a verb phrase, with \emph{RT} as a verb and the
+at-mention as its object.  This solution would lead to an uninformative root
+word and, since this expression is idiomatic to Twitter, might create
+unnecessary confusion for downstream applications aiming to identify
+the main predicate(s) of a tweet.  We therefore treat the whole
+expression as non-syntactic, including assigning the \emph{other}
+(\texttt{X}) part of speech to both \emph{RT} and \emph{@coldplay},
+attaching the at-mention to \emph{RT} with the \emph{discourse}
+label and the colon to \emph{RT} with the \emph{punct}(uation) label,
+and attaching \emph{RT} to the predicate of the following sentence.
+
+% \nascomment{smooth this in: } Considering the twitter specific constructions, we will treat the retweet construction as a whole non-syntactic phrase, and the inner structure will always be attaching {\tt at-mention} to {\tt RT} with {\tt discourse}, {\tt :} to {\tt RT} with {\tt punct}.
+% The whole construction headed on the {\tt RT} marker modifies the predicate of following sentence.
+% For the at-mentioned structure, we attach at-mentioned username to the predicate of the most relevant sentence with {\it vocative} label.
+
+\paragraph{Constructions handled by UD.}  A number of constructions
+that are especially common in tweets are well handled by UD
+conventions:  ellipsis, irregular word orders, and paratactic sentences
+not explicitly delineated by punctuation.
+
+% \subsubsection{Structure Level}
+% The syntactic constructions vary greatly across different tweets.
+% Unconventional constructions which frequently occur include ellipsis, irregular word orders, and para-tactic sentences without the segmentation of punctuations \yjcomment{I move the 3rd bullet point here because this construction was handled by UD-guidelines}.
+% And these unconventional ones are more or less resolved by the universal dependencies.
+% The unresolved cases are mainly resulted by the format of twitter.
+% The {\it retweet} and {\it at-mention} are of two major constructions.
+% \paragraph{Retweet.} For the {\it retweet} construction (`{\tt RT @coldplay :}' in Figure \ref{fig:non-syn-toks}), although it can be treated as a verbal phrase in which retweet marker works as a verb and the following at-mention is its objective, we argue that such convention lead to a uninformative root word.
+% It also increase the difficulty for downstream tasks in figuring out the core predicate and arguments for one certain tweet.
+% Thus, we treat the whole construction as a non-syntactic phrase. \yjcomment{correct me if I am wrong.}
+
+\paragraph{Vocative at-mentions.}  Another idiomatic construction on
+Twitter is an at-mention (followed by a colon \nascomment{?}) as a
+sign that a tweet is a reply to a tweet by the mentioned user.  We
+treat these at-mentions as vocative expressions, labeling them as
+\emph{proper noun} (\texttt{PROPN}) and attaching them to the
+following predicate with the label \emph{vocative}.  \nascomment{need an example.}
+
+% \paragraph{At-mention.} At-mention in the beginning of a tweet is the format of indicating the `reply' action.
+% In this paper, we treat the at-mentions as vocative expressions for their connections with the traditional vocative words, rather than treat them as non-syntactic metadata, which increase the complexity for analyzing a tweet.
+% \yjcomment{since the original discussion mainly focus on tokens, I move them to the former section.}
+% %Besides the token level phenomena of twitter, there are also structural patterns appearing in the twitter.
 
@@
 
-\subsection{Part-of-Speech Annotation}\label{sec:pos-anno}
-We adopt the universal Part-of-Speech (POS) tagset \cite{PETROV12.274} to annotate the tweets.
-The POS annotation of a word in tweets is generally based on its syntactic distribution, which indicates that the POS of word changes on different context.
-Sticking to the syntactic distribution makes it possible that a `$\heart$' symbol is tagged as a verb as shown in Figure \ref{fig:non-syn-toks}. \yjcomment{Need a better explanation.}
-%We follow the UD V2 morphology guideline and use the Universal POS tags~ to tag the tweet tokens.
-For twitter specific linguistic phenomena, we have set different strategies and try to align with the UD conventions and UD\textunderscore English as close as possible.\footnote{\url{https://github.com/UniversalDependencies/UD\_English}}
+% \subsection{Dependency Annotation}
 
-We need to note that in some certain cases, the distribution criteria doesn't holds.
-For example, the nominal URL in Figure \ref{fig:informal-toks} is tagged as {\it other} ({\tt X}) and the conjunctor {\tt +} symbol is tagged as {\it symbol} ({\tt SYM}) rather than {\it conjunction} ({\tt CCONJ}).
-Such violation is resulted by our attempt of conforming the annotation to the {\it universal dependencies - English dependency treebank} (UD\_English), in which all the URLs are tagged as {\it other} and symbolic conjunctors are tagged as {\it symbol}.\footnote{\url{https://github.com/UniversalDependencies/UD\_English}}
-By conforming our annotation to the UD\_English data, hopefully, the tools we built on tweets can benefit from the dataset on broader domain. \yjcomment{need wording}
-
-Again, there are un-conventional linguistic constructions in tweets that syntactic distribution doesn't handle well.
-One of the cases is the non-syntactic tokens.
-We consider most of them as {\tt X}, except for the sentiment emoticons, which would be tagged as {\tt SYM}, in practice of matching the UD\_English.
-Another case is the retweet construction which is considered as a non-syntactic phrase and both the RT and at-mention are tagged as {\tt X}.
-For the at-mention, we tag them as proper noun ({\tt PROPN}) in spirit of following the vocative example in UD\_English.
-%In token level phenomena, for non-syntactic tokens,  
-%For syntactic tokens, we tag them considering their corresponding syntactic function.
-
-%In structure level phenomena, we think {\tt RT @user} in retweet structure have no contribution to the tweet syntax and tag both of them as X.
-%We tag usernames in at-mentioned structure as PROPN as they present the vocative case.
-
-The informal syntactic tokens can generally be handled by their distribution.
-However, one of the exception is the {\tt phrasal abbreviations} in which one token carries multiple syntactic functions.
-In dealing with such phrases, we propose a routine that first recover their original forms, then, use the POS of their syntactic head word as the POS of the whole phrase.
-Therefore, {\it idc} (I don't care) is a verb because {\it care} is its syntactic head.
-Such routine works for most of the phrasal abbreviations.
-When it falls, we just use the POS of the left-most sub-phrase.
-\footnote{Such failure can be resulted by the mis-match of phrase boundaries between the original form and the definition of `phrase' in UD.
-For example, `mfw' (my face when) doesn't make a phrase because `when' belongs to the subordination that modifies `my face'.}
-
-%In Fig.~\ref{ex1}, {\tt RT} {\tt @yijialiu}, {\tt \#ACL2017}, {\tt http://url} and {\tt th} are all tagged as X and {\tt :)} is tagged as SYM. 
-%{\tt rn} is tagged as ADV.
-%We should note that multiple tokens are actually included in a phrasal abbreviation, and we use one of their tags as the tag of the whole abbreviation according to their dependency relation or semantic priority.
-%If there is a hierarchy in the abbreviation, we use the tag of the head word. In UD, ``Right'' is the dependent of ``now '' in the dependency of {\tt rn}, so we tag {\tt rn} as ADV. 
-%Although there is no head word in {\tt im}, we think that the subject is usually more informative than the tense in many downstream tasks such as semantic role labelling, so we use the tag of ``I'', e.g.
-PROPN as the tag of {\tt im}.
-%In Fig.~\ref{ex2}, {\tt RT} and {\tt $\heart$} would be tagged as VERB, {\tt http://url} as X, {\tt \#Awesome} as ADJ, {\tt \#NAACL}, {\tt @zypandora} and {\tt @nlpnoah} as PROPN.
-One exception is that we tag URLs always as X regardless whether they are syntactic tokens.
-The reason is that we observed, in UD\_English, that the URLs are all tagged as X and we want to conform with the UD dataset, although we think it is not appropriate and should be changed to tags such as PROPN when they are treated as syntactic tokens.
-
-Similar to our work, \newcite{gimpel-EtAl:2011:ACL-HLT2011} proposed a course grain twitter POS tagset that handles most of the token level phenomena.
-However, our work diverge theirs in several ways.
-Compared with the Gimpel's work, which assigns different tags to non-syntactic tokens in different categories, we simplify them into the {\tt X} tag.
-At the same time, all the abbreviations in \newcite{gimpel-EtAl:2011:ACL-HLT2011} are tagged with one POS, which doesn't distinguish their syntactic functions.
-We argue that such approach over-simplify the abbreviations.
-One example is that {\it idc} (I don't care) and {\it rn} (right now) carries significantly different syntactic functions and should not be treated as the same.
-In this paper, we stick more to the syntactic distribution when handling such abbreviations and it allows them to function differently in different context.
-
-The last difference between \newcite{gimpel-EtAl:2011:ACL-HLT2011} is resulted by the tokenization process.
-In \newcite{gimpel-EtAl:2011:ACL-HLT2011}, they opted out the tokenization on contractions and possessives and introduce several tags for these un-tokenized words.
-As mentioned above, the goal of conforming our annotation to the UD\_English makes us adopt the same the UD-styled tokenization.
-Thus, these tags for contractions and possessives are not necessary at all in our case.
-What's more, as \newcite{gimpel-EtAl:2011:ACL-HLT2011} mentioned, only a small proportion of tokens can be categorized into these tags (2.7 \% in total), which casts a doubt of the usefulness of these tags.
-%However, we found that their methods did not conform with UD conventions and our strategies have some advantages over their tagset. We discuss the main difference as follows.
-%The first difference lies in the tokenizations.
-%\newcite{Gimpel:2011:PTT:2002736.2002747} opted not to split contractions or possessives and introduced four new tags (S, Z, L, M) for combined forms: \{nominal, proper noun\} $\times$ \{verb, possessive\}.
-%Major concern of designing such tags is to minimize the effort of tokenization, but it is not comprehensive and far from including all of the possible combinations of POS tags within the contractions.
-%What's more, only a small proportion of tokens can be categorized into these tags (2.7 \% in total), which casts a doubt of the usefulness of these tags.
-%Instead UD conventions suggest that we put such complexity into the tokenization module and split contractions and possessives, then tag them accordingly, so that we do not need extra POS tags for the combined forms.
-%The second difference is that although the phrasal abbreviations are not split in both methods, they use tag G for all the phrasal abbreviations, while we use the tag of the head word or the highest hierarchical word in terms of dependencies as the tag of the whole phrasal abbreviations.
-%We think it is not reasonable to treat the phrasal abbreviations in the same part of speech because obviously abbreviations can have different syntactic functions and we want to preserve the most useful information for both parser and the downstream tasks.
-For example, {\tt wtf} could be tagged as PRON or INTJ according to the context, and {\tt rn} is usually tagged as ADV.
-Tagging them merely as G will definitely lose much information.
-%Third, special tags were designed to handle twitter or online special tokens such as URLs, hashtags and emoticon in \newcite{Gimpel:2011:PTT:2002736.2002747}.
-However, in most cases, as long as theses tokens are non syntactic, they play the same role in tweets, hence should be tagged the same.
-In this paper, except for the emoticon and emoji, tagged as SYM, we tag all the other non-syntactic tokens as X.
-
-\subsection{Dependency Annotation}
-
-We adopt universal dependency (UD) \cite{Marneffe2014UniversalSD} v2 guideline to annotate the syntax relations between tokens in tweets.
-UD was designed to handle the variant syntactic phenomenons across different languages and we expect its `context head' principle will bring convenience to the parsing of informal and even ungrammatical tweets.
-\yjcomment{I still feel we should give a reason why we choose UD.
-One example is that twitter users tend to leave out the copula verb and it will be messy for the `function head' principle to deal with this case.
-One observation is that informal tokens/syntax happens more on function words rather than content word.}
 %We follow the UD v2 syntax guideline and the English specific {\it universal dependency relations} to annotate our data.
@@
 %In token level phenomena, we adopt the following rules for non-syntactic tokens, denoted as x: 
-Again, as shown in Section \ref{sec:pos-anno}, the major challenge in adopting UD on tweets lies on dealing with the non-syntactic parts.
-Inspired by the way UD deal with punctuation, we adopt the following rules to obtain relation for the non-syntactic tokens:
-\begin{itemize}
-\item If a non-syntactic token is within a sentence that has a clear predicate, it will be attached to this predicate;
-\item If the whole sentence is made of a sequence of non-syntactic tokens, we attach all these tokens to the first one;
-%\item In parataxis case, when it is difficult to decide which sentence or phrase x should belong to, we always attach x to the previous predicate of the paratactic clause or phrase;
-\item non-syntactic tokens are mostly labeled as {\it discourse}, but URLs are always labeled as {\it list} in conformation with the UD\_English;
-\end{itemize}
+%Again, as shown in Section \ref{sec:pos-anno}, the major challenge in adopting UD on tweets lies on dealing with the non-syntactic parts.
 
-Considering the twitter specific constructions, we will treat the retweet construction as a whole non-syntactic phrase, and the inner structure will always be attaching {\tt at-mention} to {\tt RT} with {\tt discourse}, {\tt :} to {\tt RT} with {\tt punct}.
-The whole construction headed on the {\tt RT} marker modifies the predicate of following sentence.
-For the at-mentioned structure, we attach at-mentioned username to the predicate of the most relevant sentence with {\it vocative} label.
 %If it is hard to decide which sentence would be the most relevant, we attach it to the previous sentence's predicate.
@@
 
-Besides these non-syntactic and special constructions, the informal but syntactic tokens are treated in the same way with their original form.
+% Besides these non-syntactic and special constructions, the informal but syntactic tokens are treated in the same way with their original form.
 
@@
 % Annotation conventions
-\newcite{kong-EtAl:2014:EMNLP2014} presented a syntactic treebank on Gimpel et al.'s POS tagset.
-Compared with their work which create an unlabeled treebank, we further attach dependency relations and it's expected to be more helpful for the downstream tasks.
-We also provide concrete guidelines on dealing with the special constructions in tweets along with their variant linguistic phenomenon.
-It solve the annotation inconsistency problem in \newcite{kong-EtAl:2014:EMNLP2014}'s treebank.
-Our definition of the non-syntactic tokens is similar in spirit to the token selection process but we further define the concrete cases for such tokens.
-\yjcomment{We can put the ellipsis example in as a comparison of the `function headed' Yamada dependency and `content head' UD dependency.}
+%\newcite{kong-EtAl:2014:EMNLP2014} presented a syntactic treebank on Gimpel et al.'s POS tagset.
+%Compared with their work which create an unlabeled treebank, we further attach dependency relations and it's expected to be more helpful for the downstream tasks.
+%We also provide concrete guidelines on dealing with the special constructions in tweets along with their variant linguistic phenomenon.
+% It solve the annotation inconsistency problem in \newcite{kong-EtAl:2014:EMNLP2014}'s treebank.
+%Our definition of the non-syntactic tokens is similar in spirit to the token selection process but we further define the concrete cases for such tokens.
+%\yjcomment{We can put the ellipsis example in as a comparison of the `function headed' Yamada dependency and `content head' UD dependency.}
 %Second, most of Tweebank was built in a day by two dozen annotators, most of whom had only cursory training in the annotation scheme~\cite{kong-EtAl:2014:EMNLP2014}.
@@
 Auxiliary verbs and prepositions are all function words, and are attached to the most related content words in UD.
+
+\nascomment{I didn't touch anything below here}
 
@@
 \section{Pipeline} 
+\label{sec:parsing}
 

### 2017-09-11 paper.tex
switch to naacl 2018 template

@@
 
-\documentclass[11pt,letterpaper]{article}
-\usepackage[letterpaper]{geometry}
-\usepackage{acl2012}
+\documentclass[11pt,a4paper]{article}
+\usepackage[hyperref]{naaclhlt2018}
 \usepackage{times}
@@
 \usepackage{url}
-\makeatletter
-\newcommand{\@BIBLABEL}{\@emptybiblabel}
-\newcommand{\@emptybiblabel}[1]{}
-\makeatother
-\usepackage[hidelinks]{hyperref}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\setlength\titlebox{6.5cm}    % Expanding the titlebox
+\usepackage{multirow}
+\newcommand\BibTeX{B{\sc ib}\TeX}
 
@@
 \newcommand{\heart}{\ensuremath\heartsuit}
-\usepackage{multirow}
 
@@
 conformed to UD, enabling consistency (e.g., when we exploit the
-existing UD English treebank in our parser for tweets, \S\ref{???}).  For example,  
+existing UD English treebank in our parser for tweets, \S\ref{sec:parsing}).  For example,  
 the nominal URL in Figure \ref{fig:informal-toks} is tagged as {\it
@@
 
-\subsection{Data Collection}
-\yjcomment{This section is un-finished.}
-Following the guideline mentioned above, we create a new annotated Twitter treebank, which we call tweebank v2.
-%We present tweebank v2, a version 2 of tweebank~\cite{kong-EtAl:2014:EMNLP2014}.
+\subsection{\sc Tweebank v2}
+Following the guideline mentioned above, we create a new annotated Twitter treebank, which we call {\sc Tweebank v2}.
 
-%data aquisition/statistics
-The tweet source of Tweebank V2 consists of three parts. 
-The first is the original Tweebank created by~\cite{kong-EtAl:2014:EMNLP2014}, denoted as Tweebank V1.
+\subsubsection{Data Collection}
+{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1} (Kong et al., 2014, 639 tweets), along with additional 201 tweets sampled from \newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled  from the Twitter stream from Feb.
+2017 to Jul.
+2017.
+The latter data source consists 147.4M English tweets which are filtered by {\it lang} attribute in the tweet JSON and {\it langid.py}\footnote{\url{https://github.com/saffsd/langid.py}} toolkit.
+%The tweet source of Tweebank V2 consists of three parts. 
+%The first is the original Tweebank created by~\cite{kong-EtAl:2014:EMNLP2014}, denoted as Tweebank V1.
 There are 639 unique tweets in the training data of Tweebank V1, and 201 unique tweets in the data set.
 All of the unique tweets in Tweebank V1 are included in Tweebank V2.
-The second are 210 tweets from POS-tagged Twitter corpus of \newcite{owoputi-EtAl:2013:NAACL-HLT}, denoted as Tweebank V1 Dev.
+%The second are 210 tweets from POS-tagged Twitter corpus of \newcite{owoputi-EtAl:2013:NAACL-HLT}, denoted as Tweebank V1 Dev.
 It was initially created as a development set of Tweebank V1 for hyperparameter tuning.
-Tweebank V1 Dev comprises were equally sampled from two data set, OCT27 (tweets sampled from a particular day, October 27, 2010) and DAILY 547 (one random English tweet per day from January 2011 through June 2012, 547 tweets in total).
+%Tweebank V1 Dev comprises were equally sampled from two data set, OCT27 (tweets sampled from a particular day, October 27, 2010) and DAILY 547 (one random English tweet per day from January 2011 through June 2012, 547 tweets in total).
 We should note that all of the Tweebank V1 tweets were also drawn from OCT27 and DAILY547, and the new tweets we extracted are not in the Tweebank V1.
-The third are 2500 tweets from the Twitter streams from February 2017 to July 2017 from ArchiveTeam,\footnote{https://archive.org} which we call Feb\_Jul\_16 corpus.
+%The third are 2500 tweets from the Twitter streams from February 2017 to July 2017 from ArchiveTeam,\footnote{https://archive.org} which we call Feb\_Jul\_16 corpus.
 The Twitter streams are in Spritzer version, which provides a 1\% random sample of public tweets everyday, and the tweets are in twitter JSON format.
-There are xxx tweets in all the streams.
+%There are xxx tweets in all the streams.
 We filtered them with \textit{lang} attribute in \textit{user} and used \textit{langid.py}\footnote{https://github.com/saffsd/langid.py} to pick out English tweets, which ends in xxx tweets in English.
@@
 
-\subsubsection{Basic Statistics}
+\subsubsection{Annotation Process}
+The whole annotation process contains their stages.
+In the first stage, 18 researchers worked on the {\sc Tweebank v1} proportion and created the initial annotation in one day.
+This annotation was further refined by the authors of this paper to solve inconsistency between different annotators.
+In the second stage, a postagger and parser are trained on the annotated data from the first stage, and automatically analyze the sampled 2,500 tweets and the authors of this paper manually correct these automatically annotated.
+Finally, an extra layer of word-level normalization was manually annotated.
+
+We report the inter-annotator agreement between the annotators in the second stage.
+The agreement on POS is 95.16\%, the unlabeled dependency agreement is 88.43\% and the labeled dependency agreement is 83.89\%.
+Further analysis shows the major disagreement on POS happens.
+
+\subsubsection{Statistics}
+\yjcomment{this part is not finished}
 Tweebank V2 contains 3550 tweets in total, split into training set with 1639 tweets, development set with 710 tweets and test set with 1201 tweets. 
@@
 		& 	Train 		& 	Dev		&	Test\\[0.5ex] \hline
-		tweets 		&	1639 		&	709		&	1201\\
-		tokens 		&	24753		&	11742	&	19112\\
-		types 		&	7579			&	4165		&	6228\\
-		parts		 	&	3025 		&	1402		&	2252\\ \hline
+		tweets 		&	1,639 		&	709		&	1,201\\
+		tokens 		&	24,753		&	11,742	&	19,112\\
+		types 		&	7,579			&	4,165		&	6,228\\
+		parts		 	&	3,025 		&	1,402		&	2,252\\ \hline
 	\end{tabular}
@@
 \end{table*}
-%annotation statistics, agreement
-
-The inter-annotator agreement of POS tagging is 95.02\%, the unlabelled dependency agreement is 88\% and the labelled dependency agreement is 84\%.
 
@@
 
-\section{Model}
+We present a pipeline model to parse tweets into universal dependency.
+
+\subsection{Tokenizer}
+Tokenization is non-trivial for Twitter domain \cite{ICWSM101540}.
+Due to the informal nature, tweets present cases which are unconventional for traditional toeknization module, like hashtags, at-mentions and emoticons.
+Some of them are even ambiguous without understanding their contexts.
+For example, the asterisk in {\it 4*3} works as a symbol for times and indicates to segment this token into {\it 4 * 3} but that in {\it SH*T} works as a mask and {\it SH*T} should not be segmented.
+
+Instead of manually crafting rules, we propose to deal with tweets tokenization with a character-level bidirectional LSTM (bi-LSTM) sequence-labeling model.
+Our model takes the raw sentence and tag each character in this sentence as whether it is the beginning of a word.
+
+%Our experimental results show that
+\subsection{POS-Tagger}
+
+We use the postagger of \newcite{owoputi-EtAl:2013:NAACL-HLT}.
+In our preliminary experiments, neural model didn't show superiority over the rich-feature linear model.
+
+\subsection{Parser}
+
+Time is a major concern on
+
+\subsection{Exploiting UD\_English}
+
+%\section{Model}
+%We propose a new model
 
@@
 
+\subsection{Tokenization Result}
+
+\begin{table}[t]
+	\centering
+	\small
+	\begin{tabular}{rc}
+		\hline
+		\it System & F \\
+		\hline
+		Stanford Tokenizer & 96.6 \\
+		Twokenizer & 94.4 \\
+		UD pipe v1.2 & 94.7 \\
+		UD pipe v1.2 (re-trained) & 97.3 \\
+		Our Tokenizer & \bf 98.3 \\
+		\hline
+	\end{tabular}
+	\caption{The tokenization result.}\label{tbl:tok-result}
+\end{table}
+
+The tokenization results are shown in Table \ref{tbl:tok-result}.
+
+\subsection{POS tagging Result}
+
+\begin{table}[t]
+	\centering
+	\small
+	\begin{tabular}{rc}
+		\hline
+		\it System & P \\
+		\hline
+		Stanford Postagger & 65.6 \\
+		UD pipe v1.2 & 78.7 \\
+		UD pipe v1.2 (re-trained) & 83.8 \\
+		Our bi-LSTM & 91.8 \\
+		\newcite{owoputi-EtAl:2013:NAACL-HLT} & \bf 95.1 \\
+		\hline
+	\end{tabular}
+	\caption{The POS tagging result on gold tokenization.}\label{tbl:pos-result}
+\end{table}
+
+\begin{table}[t]
+	\centering
+	\small
+	\begin{tabular}{rc}
+		\hline
+		\it System & F \\
+		\hline
+		Stanford Tokenizer & 92.0 \\
+		Our Tokenizer & 93.6 \\
+		\hline
+	\end{tabular}
+	\caption{The POS tagging result on automatic tokenization. The POS-tagger we used is from Owoput et al., 2013.}\label{tbl:pos-result-vs-tok}
+\end{table}
+
+The POS-tagging results are shown in Table \ref{tbl:pos-result}.
+
+We also study the influence of tokenization on POS-tagging by evaluating the model's performance on automatically tokenized data.
+This result is shown in Table \ref{tbl:pos-result-vs-tok}.
+
+\subsection{Parsing Result}
+
+\begin{table}[t]
+	\centering
+	\small
+	\begin{tabular}{rcc}
+		\hline
+		\it System & UAS & LAS \\
+		\hline
+		Our Parser & & \\
+		\hline
+	\end{tabular}
+	\caption{The POS tagging result.}\label{tbl:parse-result}
+\end{table}
+
 \section{Related Work}
+\yjcomment{related word is not finished.}
 \newcite{eisenstein:2013:NAACL-HLT} reviewed NLP approaches for analyzing text on social media, especially for tweets and showed that there are two major directions for NLP community to handle the tweets, including normalization and domain adaptation.
@@
 \bibliography{shortdb}
-\bibliographystyle{acl2012}
+\bibliographystyle{acl_natbib}
 \end{document}

### 2017-09-14 paper.tex
add figure.

@@
 \begin{itemize}
-\item We create a new version of tweet Treebank Tweebank 2.0
-\item We propose a neural network method to parse tweets into universal dependencies
-\item We study the adaptation of universal dependencies for analyzing tweets
+\item We create a new annotated tweet dependency treebank ({\sc Tweebank v2}) following the UD convention.
+This annotation contains 3,549 tweets.
+Tokenization, part-of-speech tag, and dependencies of these tweets are annotated in this data.
+
+\item We propose to use the transition-based neural parser \cite{ballesteros-EtAl:2016:EMNLP2016} with consideration of the speed in processing social media data.
+To achieve a more accurate parser, we propose to train the parser with a distillation of an ensemble 20 parser and this achieve an improvement of 3 point LAS over the baseline.
 \end{itemize}
+
+We release our parser at.
 
@@
 
-%Our experimental results show that
-\subsection{POS-Tagger}
-
-We use the postagger of \newcite{owoputi-EtAl:2013:NAACL-HLT}.
-In our preliminary experiments, neural model didn't show superiority over the rich-feature linear model.
-
-\subsection{Parser}
-
-Time is a major concern on
-
-\subsection{Exploiting UD\_English}
-
-%\section{Model}
-%We propose a new model
-
-\section{Experiments}
-
-\subsection{Tokenization Result}
+\paragraph{Experimental Results}
 
@@
 
-The tokenization results are shown in Table \ref{tbl:tok-result}.
+We test our tokenizer on Tweebank v2 test set.
+F-score was used to evaluate the tokenization accuracy.
+Our model was trained on a merge of UD\_English and Tweebank v2 training data.
+Table \ref{tbl:tok-result} shows the tokenization results along with comparison with other tokenizers.
+Our bi-LSTM tokenizer achieves the best accuracy among all these tokenizers.
+By comparing the rule-based group to the model-based group, we can see the model-based ones generally outperform the rule-based tokenizers, which shows the necessity of using statistical model for tweet tokenization.
 
-\subsection{POS tagging Result}
+%Our experimental results show that
+\subsection{POS-Tagger}
+
+We use the postagger of \newcite{owoputi-EtAl:2013:NAACL-HLT}.
+%In our preliminary experiments, neural model didn't show superiority over the rich-feature linear model.
+
+\paragraph{Experimental Results}
 
@@
 		Stanford Postagger & 65.6 \\
+		Stanford Postagger (re-train) & 90.37 \\
 		UD pipe v1.2 & 78.7 \\
@@
 	\end{tabular}
-	\caption{The POS tagging result on automatic tokenization. The POS-tagger we used is from Owoput et al., 2013.}\label{tbl:pos-result-vs-tok}
+	\caption{The POS tagging result on automatic tokenization. The POS tagger we used is from Owoput et al., 2013.}\label{tbl:pos-result-vs-tok}
 \end{table}
 
-The POS-tagging results are shown in Table \ref{tbl:pos-result}.
-
+We test several different POS taggers on Tweebank v2.
 We also study the influence of tokenization on POS-tagging by evaluating the model's performance on automatically tokenized data.
@@
 
-\subsection{Parsing Result}
+\subsection{Parser}
+
+%Time is a major concern on
+Social media applications usually require processing tones of data.
+Speed becomes important under such circumstance.
+In this paper, we use the neural greedy parser by \newcite{ballesteros-EtAl:2016:EMNLP2016}, which can parse a sentence in linear time and harness the useful character representations.
+To further improve the parsing accuracy, we propose a new method to distill an ensemble of 20 differently initialized parsers into one greedy parser.
+
+Distilling a smaller classifier from a single large neural network was explored in \newcite{DBLP:journals/corr/HintonVD15} and \newcite{kim-rush:2016:EMNLP2016}.
+In these works, the predicted distribution from the larger model serves as a soft target for training the small classifier.
+Training the smaller classifier is delivered by training with a interpolate between two losses:
+\begin{equation}\label{eq:distill}
+\mathcal{L}=(1-\alpha)\mathcal{L}_{NNL} + \alpha\mathcal{L}_{KD}
+\end{equation}
+where $\mathcal{L}_{NNL}$ is the traditional log-likelihood loss and $\mathcal{L}_{KD}$ is the loss from soft target.
+
+\newcite{kuncoro-16} was inspired by the distillation idea and proposed to incorporate the knowledge from an ensemble of 20 parsers into one single graph-based parser by adapting the soft target into a structure loss.
+However, as \newcite{kuncoro-16} pointed out, it's not straight-forward to incorporate the structure loss into a transition-based parser.
+Considering the efficiency advantage of transition-based parser over its graph-based counterpart, it's worth study distillation of an ensemble of different parsers.
+
+In this paper, we follow \newcite{DBLP:journals/corr/HintonVD15} and \newcite{kim-rush:2016:EMNLP2016} and distill one single parser from 20 parsers trained with different initialization.
+Training a transition-based greedy parser includes generating a transition sequence from the data and learning the classifier from the states in the sequence.
+And it also holds for training the ensemble parser.
+%We first study the necessity of log-likelihood loss (the first term in Equation \ref{eq:distill}).
+
+\paragraph{Effect of $\alpha$}
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=\columnwidth]{graphics/alpha}
+	\caption{The effect of $\alpha$ in distillation.}\label{fig:effect-alpha}
+\end{figure}
+
+We show the effect of $\alpha$ in Figure \ref{fig:effect-alpha}.
+This figure shows that a larger $\alpha$
+
+%\paragraph{Effect of $\mathcal{T}$}
+%
+%\begin{figure}[t]
+%	\centering
+%	\includegraphics[width=\columnwidth]{graphics/temperature}
+%	\caption{The effect of temperature $\alpha$.}\label{fig:effect-temp}
+%\end{figure}
+
+\paragraph{Results}
 
@@
 		\hline
-		Our Parser & & \\
+		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 79.25 & 74.17 \\
+		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & & \\
+		Ensemble 20 & 82.80 & 78.69 \\
+		Distill & & \\
+
 		\hline
@@
 
+%\subsection{Exploiting UD\_English}
+
+%UD\_English as an important source of training data.
+%\section{Model}
+%We propose a new model
+
 \section{Related Work}
-\yjcomment{related word is not finished.}
-\newcite{eisenstein:2013:NAACL-HLT} reviewed NLP approaches for analyzing text on social media, especially for tweets and showed that there are two major directions for NLP community to handle the tweets, including normalization and domain adaptation.
+%\yjcomment{related word is not finished.}
+%\newcite{eisenstein:2013:NAACL-HLT} reviewed NLP approaches for analyzing text on social media, especially for tweets and showed that there are two major directions for NLP community to handle the tweets, including normalization and domain adaptation.
 He also pointed out that normalization can be problematic because precisely defining the normalization task is difficult.
-
-\newcite{kong-EtAl:2014:EMNLP2014} argues that the Penn Treebank approach to annotation is poorly suited to more informal genres of text, as some of the annotation challenges for tweets,
-including token selection, multiword expressions, multiple roots, and structure within noun phrases diverge significantly from conventional approaches. 
-They believe that rapid, small scale annotation efforts performed by imperfectly-trained annotators should provide enough evidence to train an effective parser, given the rapidly changing nature of tweets~\cite{eisenstein:2013:NAACL-HLT}, the attested difficulties of domain adaptation for parsing~\cite{dred07}, and the expense of creating Penn Treebank-style annotations~\cite{penn93}.
-Therefore, they build a new corpus of tweets (Tweebank), with conventions informed by the domain, using new syntactic annotations that can tackle all the forementioned problems annotated in a day by two dozen annotators, most of whom had only cursory training in the annotation scheme.
+%
+%\newcite{kong-EtAl:2014:EMNLP2014} argues that the Penn Treebank approach to annotation is poorly suited to more informal genres of text, as some of the annotation challenges for tweets,
+%including token selection, multiword expressions, multiple roots, and structure within noun phrases diverge significantly from conventional approaches. 
+%They believe that rapid, small scale annotation efforts performed by imperfectly-trained annotators should provide enough evidence to train an effective parser, given the rapidly changing nature of tweets~\cite{eisenstein:2013:NAACL-HLT}, the attested difficulties of domain adaptation for parsing~\cite{dred07}, and the expense of creating Penn Treebank-style annotations~\cite{penn93}.
+%Therefore, they build a new corpus of tweets (Tweebank), with conventions informed by the domain, using new syntactic annotations that can tackle all the forementioned problems annotated in a day by two dozen annotators, most of whom had only cursory training in the annotation scheme.
 Then, they modify the decoder of the TurboParser, a graph-based dependency parser, which is open-source and has been found to perform well on a range of parsing problems in different languages~\cite{turbo13} to adapt to the Tweebank dataset, and incorporate new features such as Brown Clusters and Penn Treebank features and changes to specification
-in the output space into TurboParser.
-
-Like ``mfw'' is usually followed by an adverbial clause and ``ima'' is usually followed by a clausal complement. 
-It is not reasonable to treat them in the same part-of-speech. 
-In this paper, when annotating the POS tagging for abbreviations, we first try to recover their original forms, then use the POS of the core-word as the POS for the abbreviation.
-Second, four special POS tags (S, L, M, Y) were designed to handle contraction words in Gimpel et al.
+%in the output space into TurboParser.
+%
+%Like ``mfw'' is usually followed by an adverbial clause and ``ima'' is usually followed by a clausal complement. 
+%It is not reasonable to treat them in the same part-of-speech. 
+%In this paper, when annotating the POS tagging for abbreviations, we first try to recover their original forms, then use the POS of the core-word as the POS for the abbreviation.
+%Second, four special POS tags (S, L, M, Y) were designed to handle contraction words in Gimpel et al.
 \shortcite{Gimpel:2011:PTT:2002736.2002747}.
 Major concern of designing such tags is to minimize the effort of tokenization.
-However, contractions of common nouns and pronouns are casted into the same category which increase the difficulty of distinguishing their syntactic function (say, there's and book'll are treated with the same syntactic function).
+%However, contractions of common nouns and pronouns are casted into the same category which increase the difficulty of distinguishing their syntactic function (say, there's and book'll are treated with the same syntactic function).
 What's more, only a small proportion of words can be categorized into these tags (2.7 \% in total), which cast a doubt of the usefulness of these certain tags.
 In this paper, we believe such contraction can be properly handled by tokenization module, so we suggest to tokenize the contraction word and annotate POS tag accordingly.
-Besides the contraction that be conventionally tokenized, tweets also witness a set of unconventional contraction like iv (I've), whatis (what is).
+%Besides the contraction that be conventionally tokenized, tweets also witness a set of unconventional contraction like iv (I've), whatis (what is).
 In this paper, we follow the same idea of annotation abbreviation to handle the unconventional contractions and use the POS of core word of the original form as their POS.
-Third, special POS was designed to handle emoticon in Gimpel et al.
+%Third, special POS was designed to handle emoticon in Gimpel et al.
 \shortcite{Gimpel:2011:PTT:2002736.2002747}.
@@
 In this paper, we follow the UD guideline to annotate the emoticon as symbol (SYM).
-At last, it’s arguable that some of the hashtags, URLs can work as a nominal in tweets.
+%At last, it’s arguable that some of the hashtags, URLs can work as a nominal in tweets.
 Whether treating them as the same part-of-speech or different ones according to their context is an open question.

### 2017-09-14 graphics/alpha.r

@@ -1,0 +1,35 @@
+library("ggplot2")
+
+lines1 <- "alpha,las
+1.0,76.98
+0.9,76.99
+0.8,76.75
+0.7,76.68
+0.6,76.10
+0.5,76.24
+0.4,75.31
+0.3,76.09
+0.2,74.57
+0.1,74.57
+0.0,74.17"
+
+result1 <- read.table(text=lines1, sep=",", header=TRUE)
+names(result1) <- c("alpha", "las")
+
+#result1 <- melt(result1, id=c("alpha"))
+#print(result1$alpha)
+#print(result1$las)
+
+# two plots
+p1 <- ggplot(result1, aes(x=alpha, y=las, label=las)) +
+    geom_line() +
+    geom_point() +
+    geom_text(vjust=-1) +
+    scale_x_continuous(breaks=result1$alpha) + 
+    ylim(NA, 77.5) +
+    theme_bw()
+
+# extract gtable
+#g1 <- ggplot_gtable(ggplot_build(p1))
+
+ggsave("alpha.pdf", height=4, width = 8)

### 2017-09-22 paper.tex
sync

@@
 
-\newcommand{\yjcomment}[1]{\textcolor{orange}{[$_\mathrm{L}^\mathrm{Y}$\textsc{#1}]}}
+\newcommand{\yjcomment}[1]{\textcolor{orange}{[$_\mathrm{L}^\mathrm{Y}$#1]}}
 \newcommand{\nascomment}[1]{\textcolor{blue}{[#1 ---\textsc{nas}]}}
@@
 \section{Introduction}
-Analyzing the syntax of tweets is challenging for traditional NLP tools because most of the tweet texts are informal and noisy.
+Analyzing the syntax of tweets is challenging. The challenges not
+only come from the difficulty of adapting the parser trained on the
+standard text to the Twitter domain, but also comes from creating
+reasonable dataset for training and evaluating tweet parsers. 
+\citet{AAAIW113912} pioneered in this research direction by
+annotating Penn Treebank \citep[PTB]{Marcus93buildinga}
+constituencies to a set of tweets which contains 7,630 tokens. 
+Stanford dependencies were converted afterwards. 
+\citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
+annotating tweets and presented a tweets treebank ({\sc Tweebank})
+which has 12,149 tokens and was created using the 
+\citet{Yamada03statisticaldependency} dependencies. Both these
+annotation efforts were highly influenced by the PTB whose guideline
+has a good grammatical coverage on newswire. However, when it comes
+to the noisy and informal user generated text, it's questionable
+whether such good coverage holds.
+%Motivation notes:  explain why UD is attractive (and more attractive
+%than what previous work used, which was based on YM).  one reason is
+%that it might allow sharing of texts annotated in different genres (or
+%even languages, cite Waleed).  but universal annotation schemes are
+%challenging!  this paper contends with the challenges of
+%applying UD to social media texts.
 
-In this paper, we propose to parse the tweets in the convention of
-universal dependencies and built up the whole pipeline to parse the
-tweets from the raw text form.
+%In this paper, we propose to parse the tweets in the convention of
+%universal dependencies and built up the whole pipeline to parse the
+%tweets from the raw text form.
 
-Motivation notes:  explain why UD is attractive (and more attractive
-than what previous work used, which was based on YM).  one reason is
-that it might allow sharing of texts annotated in different genres (or
-even languages, cite Waleed).  but universal annotation schemes are
-challenging!  this paper contends with the challenges of
-applying UD to social media texts.
+Universal dependencies \citep[UD]{NIVRE16.348} was created to delivery
+consistent annotation across different languages. To allow such
+consistency, UD was designed to be adaptive to different genres and languages
+\cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. It's promising that analyzing
+the syntax of tweets can benefit from such adaptability. In this paper,
+we create a new tweets treebank of 55,607 tokens by following the UD
+guidelines but also contending the domain-specific challenges which wasn't
+covered by UD guidelines. Our annotation includes a whole pipeline of
+tokenization, part-of-speech (POS) tags and universal dependencies.
 
-\nascomment{Points that were in older text that I want to keep around:}
-\begin{itemize}
-\item Despite the informal nature of tweets, we argue that they basically follow the same grammar as their formal language counterpart.
-\item UD was designed to handle the variant syntactic phenomenons across different languages and we expect its `context head' principle will bring convenience to the parsing of informal and even ungrammatical tweets.
-\yjcomment{I still feel we should give a reason why we choose UD. One
-  example is that twitter users tend to leave out the copula verb and
-  it will be messy for the `function head' principle to deal with this
-  case. One observation is that informal tokens/syntax happens more on
-  function words rather than content word.} \nascomment{maybe we could
-  argue that, if UD is designed to work for many languages, it should
-  also be able to work for dialects, including AAVE, and informal
-  registers.  YM was not designed for cross-linguistic applicability.}
+%\nascomment{Points that were in older text that I want to keep around:}
+%\begin{itemize}
+%\item Despite the informal nature of tweets, we argue that they basically follow the same grammar as their formal language counterpart.
+%\item UD was designed to handle the variant syntactic phenomenons across different languages and we expect its `context head' principle will bring convenience to the parsing of informal and even ungrammatical tweets.
+%\yjcomment{I still feel we should give a reason why we choose UD. One
+%  example is that twitter users tend to leave out the copula verb and
+%  it will be messy for the `function head' principle to deal with this
+%  case. One observation is that informal tokens/syntax happens more on
+%  function words rather than content word.} \nascomment{maybe we could
+%  argue that, if UD is designed to work for many languages, it should
+%  also be able to work for dialects, including AAVE, and informal
+%  registers.  YM was not designed for cross-linguistic applicability.}
+%\end{itemize}
 
-\end{itemize}
+Based on these annotations, we built up a whole pipeline to parse the
+raw tweet text into universal dependencies. Our pipeline includes: a
+bidirectional LSTM (bi-LSTM) tokenizer, a word cluster enhanced POS
+tagger \cite{owoputi-EtAl:2013:NAACL-HLT}, and stack-lstm parser
+with character representation \cite{ballesteros-dyer-smith:2015:EMNLP}.
+
+To achieve better performance without sacrificing efficiency, we propose
+a new method to train the parser with the distillation 
+\cite{DBLP:journals/corr/HintonVD15} of 20 parsers ensemble.
+We show that learning from the exploration of the ensemble parser
+can be more beneficial than just learning from the gold standard
+transition sequence in the sense of training a transition-based
+distilling parser. Experimental results show an improvement of more
+than 3 points in LAS over baseline parser can be achieved with our
+distillation method.
 
@@
 \begin{itemize}
-\item We create a new annotated tweet dependency treebank ({\sc Tweebank v2}) following the UD convention.
-This annotation contains 3,549 tweets.
-Tokenization, part-of-speech tag, and dependencies of these tweets are annotated in this data.
+\item We study the challenges of annotating tweets in UD (\S\ref{sec:anno})
+and create a new tweet treebank ({\sc Tweebank v2}), which includes 
+tokenization, part-of-speech tagging, and dependencies annotation.
 
-\item We propose to use the transition-based neural parser \cite{ballesteros-EtAl:2016:EMNLP2016} with consideration of the speed in processing social media data.
-To achieve a more accurate parser, we propose to train the parser with a distillation of an ensemble 20 parser and this achieve an improvement of 3 point LAS over the baseline.
+\item We built up a whole pipeline to parse the raw tweet text into
+universal dependencies (\S\ref{sec:parsing}). We propose a new distillation
+method in training the parser in our pipeline which achieve 3 points improvement
+without sacrificing efficiency.
 \end{itemize}
 
-We release our parser at.
+We release our system at.
 
@@
   section below.}
+\yjcomment{we re-annotated the POS. In one way, Gimple's POS is not very
+consistent with UD POS. In another way, 2,500 new tweets were annotated
+from scratch and they didn't have Gimple's tags.}
 
-\section{Annotation}
+\section{Annotation}\label{sec:anno}
 
@@
 \newcite{gimpel-EtAl:2011:ACL-HLT2011}, which followed
-\newcite{oconnor-2010}.  In particular, they opted out of tokenizing
+\newcite{ICWSM101540}.  In particular, they opted out of tokenizing
 contractions and possessives, introducing new parts of speech
@@
 	\end{tabular}
-	\caption{The tokenization result.}\label{tbl:tok-result}
+	\caption{The tokenization results.}\label{tbl:tok-result}
 \end{table}
@@
 
-%Our experimental results show that
 \subsection{POS-Tagger}
 
+Part-of-Speech tagging for tweets has been studied in previous literals \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}.
 We use the postagger of \newcite{owoputi-EtAl:2013:NAACL-HLT}.
-%In our preliminary experiments, neural model didn't show superiority over the rich-feature linear model.
 
@@
 		Stanford Postagger & 65.6 \\
-		Stanford Postagger (re-train) & 90.37 \\
+		Stanford Postagger (re-train) & 90.4 \\
 		UD pipe v1.2 & 78.7 \\
 		UD pipe v1.2 (re-trained) & 83.8 \\
-		Our bi-LSTM & 91.8 \\
-		\newcite{owoputi-EtAl:2013:NAACL-HLT} & \bf 95.1 \\
+		bi-LSTM & 91.8 \\
+		ARK Tagger & \bf 95.1 \\
 		\hline
@@
 We show the effect of $\alpha$ in Figure \ref{fig:effect-alpha}.
-This figure shows that a larger $\alpha$
+This figure shows that parsers with larger $\alpha$ achieves better performance than that with smaller $\alpha$.
+This result shows that learning from the hard target in unnecessary.
 
@@
 		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 79.25 & 74.17 \\
-		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & & \\
+		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.90 & 72.95 \\
 		Ensemble 20 & 82.80 & 78.69 \\
-		Distill & & \\
-
+		Distill expert ($\alpha$=0.)& 81.22 & 76.98 \\
+		Distill boltzmann ($\mathcal{T}$=1) & 81.55 & 77.32 \\
 		\hline

### 2017-09-25 paper.tex
sync.

@@
 
-Universal dependencies \citep[UD]{NIVRE16.348} was created to delivery
+Universal dependencies \citep[UD]{NIVRE16.348} was created to deliver
 consistent annotation across different languages. To allow such
@@
 
-We adopt UD version 2 
-\cite{Marneffe2014UniversalSD} guidelines to annotate the syntax of tweets.
+We adopt UD version 2 guidelines to annotate the syntax of tweets.
 In applying UD annotation conventions to tweets, the choices of 
@@
 \paragraph{Acronym abbreviations.}  How should we syntactically
-analyze acronym tokens like \emph{mfw}
-(abbreviating ``my face when'') and \emph{rn} (``right now'')?  Should
+analyze acronym tokens like \emph{idc}
+(abbreviating ``I don't care'') and \emph{rn} (``right now'')?  Should
 they be decomposed into their component words, and if so should those
 words be ``normalized'' into explicitly spelled out intermediate
-forms?  \nascomment{explain what we do, and include how this is
-  similar to or different from Kong et al}
+forms? We follow \citet{kong-EtAl:2014:EMNLP2014} and annotate their
+syntax as a single word without normalization. Their syntactic functions
+are decided according to their context.
+\nascomment{explain what we do, and include how this is
+	similar to or different from Kong et al}\yjcomment{done.}
 
+\citet{eisenstein:2013:NAACL-HLT} studied the necessity of normalization
+in social media text and pointed that such normalization is problematic.
+Our solution to the syntax of abbreviations is in the same spirit with
+his work. Further study shows that the abbreviations which clearly carry
+syntactic functions only make 0.06\% tokens in our dataset, which
+also indicates it's unnecessary to normalize text in social media.
 \nascomment{maybe we owe citations to
@@
 \paragraph{Non-syntactic tokens.}  
-Figure \ref{fig:non-syn-toks} illustrates examples of tokens that have
-no syntactic function.  Note that these generally have the
-\emph{other} (\texttt{X}) part of speech.
+\begin{table}
+\centering
+\small
+\begin{tabular}{rcc}
+\% & syntactic & non-syntactic \\ \hline
+emoticons & 0.25 & 0.95 \\
+RT & 0.14 & 2.49\\
+hashtag & 1.02 & 1.24 \\
+URL & 0.67 & 2.38 \\
+truncated words & 0 & 0.49 \\
+ \hline
+ sum & 2.08 & 7.55 \\
+\end{tabular}
+\caption{Proportion of non-syntactic tokens in the annotation.}\label{tbl:non-synt-prop}
+\end{table}
+The major characteristic that distinguishes tweets from standard texts is that
+there are large proportion of tokens that don't carry any syntactic functions.
+In our annotation, there are five types of non-syntactic tokens which include
+sentiment emoticons, retweet markers, topical hashtags, referential URLs, and
+truncated words. Figure \ref{fig:non-syn-toks} illustrates examples of
+these non-syntactic tokens. In the sense of part of speech, emoticons are tagged
+as \emph{symbol} ({\tt SYM}) by following the UD guidelines. For other 4 types of
+non-syntactic tokens, they generally have the \emph{other} (\texttt{X})
+part of speech. In our annotation, these five types of tokens make more than
+7.5\% of all tokens and detailed statistics can be found in Table \ref{tbl:non-synt-prop}.
+\nascomment{in latex source I've commented out a paragraph about
+	truncated content.  it's not clear to me what the nonsyntactic
+	tokens are, when that happens}\yjcomment{i've put truncated words here.}
 
@@
 token as non-syntactic must be context-dependent.
-To our knowledge, this issue has not previously been addressed in UD
-annotation efforts \nascomment{check!}.
+%To our knowledge, this issue has not previously been addressed in UD
+%annotation efforts \nascomment{check!}\yjcomment{it's not safe to claim that.}.
 
@@
   over to POS annotation}
+\yjcomment{I've put the definition of non-syntactic tokens there.}
 
@@
 had conventions, and Kong didn't, but we didn't really say what ours were.}
+\yjcomment{The bullet points describe our convention for non-syntactic tokens.}
 
@@
 		\begin{deptext}
-			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& @coldplay \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl}\\
-			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny X \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \\
+			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& @coldplay \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl} \& Nice \& \textcolor{cyan}{\bf p} \& ...\\
+			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny X \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \& \tiny ADJ \& \tiny X \& \tiny PUNCT \\
 		\end{deptext}
@@
 		\depedge[edge unit distance=0.8em]{6}{12}{list}
+		\deproot{13}{root}		
+		\depedge[edge unit distance=0.8em]{13}{14}{discourse}
+		\depedge[edge unit distance=0.8em]{13}{15}{punct}
 	\end{dependency}
@@
 		\textcolor{orange}{retweet marker},
-		\textcolor{gray}{topical hashtag}, and
-		\textcolor{blue}{referential URL}.}\label{fig:non-syn-toks}
+		\textcolor{gray}{topical hashtag},
+		\textcolor{blue}{referential URL}, and
+		\textcolor{cyan}{truncated word}.}\label{fig:non-syn-toks}
 \end{figure*}
@@
 		\begin{deptext}
-			its \& \#awesome \& u \& gonna \& $\heart$ \& it \& Chk \& out \& our \& cooool \& project \& on \& http:// \& + \& RT \& pls\\
-			\tiny PRON \& \tiny ADJ \& \tiny PRON \& \tiny VERB \& \tiny VERB \& \tiny PRON \& \tiny VERB \& \tiny ADP \& \tiny PRON \& \tiny ADJ \& \tiny NOUN \& \tiny ADP \& \tiny X \& \tiny SYM \& \tiny VERB\& \tiny INTJ\\
+			@username \& its \& \#awesome \& u \& gonna \& $\heart$ \& it \& Chk \& out \& our \& cooool \& project \& on \& http:// \& + \& RT \& pls\\
+			\tiny PROPN \& \tiny PRON \& \tiny ADJ \& \tiny PRON \& \tiny VERB \& \tiny VERB \& \tiny PRON \& \tiny VERB \& \tiny ADP \& \tiny PRON \& \tiny ADJ \& \tiny NOUN \& \tiny ADP \& \tiny X \& \tiny SYM \& \tiny VERB\& \tiny INTJ\\
 		\end{deptext}
-		\deproot{2}{root}
-		\depedge[edge unit distance=1em]{2}{1}{nsubj}
-		\depedge[edge unit distance=1em]{2}{4}{parataxis}
-		\depedge[edge unit distance=1em]{4}{3}{nsubj}
-		\depedge[edge unit distance=1em]{4}{5}{xcomp}
-		\depedge[edge unit distance=1em]{5}{6}{obj}
-		\depedge[edge unit distance=0.7em]{2}{7}{parataxis}
-		\depedge[edge unit distance=1em]{7}{8}{compound:prt}
-		\depedge[edge unit distance=0.7em]{7}{11}{obj}
-		\depedge[edge unit distance=1em]{11}{9}{nmod:poss}
-		\depedge[edge unit distance=1em]{11}{10}{amod}
-		\depedge[edge unit distance=1em]{11}{13}{nmod}
-		\depedge[edge unit distance=1em]{13}{12}{case}
-		\depedge[edge unit distance=0.45em]{7}{15}{conj}
-		\depedge[edge unit distance=1em]{15}{14}{cc}
-		\depedge[edge unit distance=0.35em]{2}{16}{discourse}
+		\deproot{3}{root}
+		\depedge[edge unit distance=1em]{3}{1}{vocative}
+		\depedge[edge unit distance=1em]{3}{2}{nsubj}
+		\depedge[edge unit distance=1em]{3}{5}{parataxis}
+		\depedge[edge unit distance=1em]{5}{4}{nsubj}
+		\depedge[edge unit distance=1em]{5}{6}{xcomp}
+		\depedge[edge unit distance=1em]{6}{7}{obj}
+		\depedge[edge unit distance=0.7em]{3}{8}{parataxis}
+		\depedge[edge unit distance=1em]{8}{9}{compound:prt}
+		\depedge[edge unit distance=0.7em]{8}{12}{obj}
+		\depedge[edge unit distance=1em]{12}{10}{nmod:poss}
+		\depedge[edge unit distance=1em]{12}{11}{amod}
+		\depedge[edge unit distance=1em]{12}{14}{nmod}
+		\depedge[edge unit distance=1em]{14}{13}{case}
+		\depedge[edge unit distance=0.45em]{8}{16}{conj}
+		\depedge[edge unit distance=1em]{16}{15}{cc}
+		\depedge[edge unit distance=0.35em]{3}{17}{discourse}
 	\end{dependency}
@@
 
-\nascomment{in latex source I've commented out a paragraph about
-  truncated content.  it's not clear to me what the nonsyntactic
-  tokens are, when that happens}
 % A kind of token that doesn't carry clearly syntactic functions can be resulted by the 140 characters limits of tweets.
@@
 \newcite{kong-EtAl:2014:EMNLP2014} proposed an additional
-preprocessing step, \emph{token selection}, to remove non-syntactic
-tokens before parsing.  \nascomment{confusing.  were they removed or
-  just labeled as non-syntactic and then excluded from the tree?  I
-  think they were not actually removed, and were still available,
-  e.g., for defining features of the input for parsing}  In order to
-keep our annotation conventions in line with UD norms, we include
-non-syntactic tokens in the dependency analysis, with a special label
+preprocessing step, \emph{token selection}, in their annotation process.
+They required the annotators to first select the non-syntactic
+tokens and exclude them from the final dependencies annotation.
+%  \nascomment{confusing.  were they removed or
+%  just labeled as non-syntactic and then excluded from the tree?  I
+%  think they were not actually removed, and were still available,
+%  e.g., for defining features of the input for parsing}
+In order to keep our annotation conventions in line with UD norms,
+we include non-syntactic tokens in our annotation following the
+convention above. Compared with \citet{kong-EtAl:2014:EMNLP2014},
+we also gave a clear definition of non-syntactic tokens, which help
+us avoid confusion.
 \nascomment{say what it is, and what they attach to, and clarify that
@@
 \paragraph{Vocative at-mentions.}  Another idiomatic construction on
-Twitter is an at-mention (followed by a colon \nascomment{?}) as a
-sign that a tweet is a reply to a tweet by the mentioned user.  We
+Twitter is an at-mention %(followed by a colon \nascomment{?})
+as a sign that a tweet is a reply to a tweet by the mentioned user.  We
 treat these at-mentions as vocative expressions, labeling them as
 \emph{proper noun} (\texttt{PROPN}) and attaching them to the
-following predicate with the label \emph{vocative}.  \nascomment{need an example.}
+following predicate with the label \emph{vocative} (see Figure \ref{fig:informal-toks} for an example).  \nascomment{need an example.} \yjcomment{done.}
 
@@
 
-\nascomment{I didn't touch anything below here}
+%\nascomment{I didn't touch anything below here}
 
@@
 \subsubsection{Annotation Process}
-The whole annotation process contains their stages.
-In the first stage, 18 researchers worked on the {\sc Tweebank v1} proportion and created the initial annotation in one day.
-This annotation was further refined by the authors of this paper to solve inconsistency between different annotators.
-In the second stage, a postagger and parser are trained on the annotated data from the first stage, and automatically analyze the sampled 2,500 tweets and the authors of this paper manually correct these automatically annotated.
-Finally, an extra layer of word-level normalization was manually annotated.
+The whole annotation process contains three stages.
+In the first stage, 18 researchers worked on the {\sc Tweebank v1}
+proportion and created the initial annotation in one day
+following our guideline. Both the guideline and annotation
+were further refined by the authors of this paper to increase
+the coverage of our guideline and solve inconsistency between
+different annotators. In the second stage, a postagger and
+parser are trained on the annotated data from the first stage,
+and automatically analyze the sampled 2,500 tweets and the authors
+of this paper manually correct the parsed data. Finally, an extra
+layer of word-level normalization was manually annotated.
 
-We report the inter-annotator agreement between the annotators in the second stage.
-The agreement on POS is 95.16\%, the unlabeled dependency agreement is 88.43\% and the labeled dependency agreement is 83.89\%.
-Further analysis shows the major disagreement on POS happens.
-
-\subsubsection{Statistics}
-\yjcomment{this part is not finished}
-Tweebank V2 contains 3550 tweets in total, split into training set with 1639 tweets, development set with 710 tweets and test set with 1201 tweets. 
-The training set contains all the 639 unique tweets in the training set of Tweebank V1 and another 1000 tweets in feb\_jul\_16 corpus.
-The development set contains 210 tweets of Tweebank V1 Dev and another 500 tweets in feb\_jul\_16 corpus.
-The test set contains all the 201 tweets in the test set of Tweebank V1 and another 1000 tweets in feb\_jul\_16 corpus.
-
-We process all the raw tweets of these corpora from scratch, from tokenization and POS tagging to dependency annotation.
-As Tweebank V1 and the POS-tagged Twitter corpus of \newcite{gimpel-EtAl:2011:ACL-HLT2011} used a tweet tokenizer~\cite{ICWSM101540} that do not conform with UD guidelines, as we discussed before, we did not use any data of the intermediate steps from these corpora.
-The basic statistics of Tweebank V2 is shown in Table~\ref{tab1}.
-
-% tweets, tokens, tokens/tweet, part/tweet, token types.
-\begin{table}[t]
-	\centering
-	\begin{tabular}{l r r r} 
-		\hline
-		& 	Train 		& 	Dev		&	Test\\[0.5ex] \hline
-		tweets 		&	1,639 		&	709		&	1,201\\
-		tokens 		&	24,753		&	11,742	&	19,112\\
-		types 		&	7,579			&	4,165		&	6,228\\
-		parts		 	&	3,025 		&	1,402		&	2,252\\ \hline
-	\end{tabular}
-	\caption{Basic Statistics of Tweebank V2}
-	\label{tab1}
-\end{table}
-
-% tokens and its proportions for the previous language phenomena.
-\subsubsection{Twitter Specific Statistics}\label{stats}
-Following the discussion of the Twitter specific linguistic phenomena, we obtain Table~\ref{tab2}.
-
-\begin{table*}[t]
+\begin{figure}
 \centering
 \small
-	\begin{tabular}{r | l | l | l | r r r r r} 
-		\hline
-		\multicolumn{4}{l}{}	&	Train		&	Test	&	Dev	&	All	&	Per\\[0.5ex] \hline\hline
-		\multirow{10}{*}{\textit{token}}	&	syntactic						&	\multicolumn{2}{l |}{phrasal abbreviation}				
-		&	 12 		&	12	&	10	&	34	&	0.06\%	\\
-		\cline{2-9}
-		&	\multirow{8}{*}{optionally syntactic}	&	\multirow{2}{*}{RT}					&	syntactic	
-		&	 40 		&	19	&	18	&	77	&	0.14\%	\\
-		&								&									&	non-syntactic
-		&	600  		&	500	&	286	&	1386	&	2.49\%	\\
-		\cline{3-9}
-		&								&	\multirow{2}{*}{hashtag}				&	syntactic
-		&	251  		&	212	&	103	&	566	&	1.02 \%	\\
-		&								&									&	non-syntactic
-		&	 290 		&	246	&	155	&	691	&	1.24\%	\\
-		\cline{3-9}
-		&								&	\multirow{2}{*}{at-mentioned}			&	syntactic
-		&	  659		&	420	&	257	&	1336	&	2.40\%	\\
-		&								&									&	non-syntactic
-		&	  640		&	519	&	311	&	1470	&	2.64\%	\\
-		\cline{3-9}
-		&								&	\multirow{2}{*}{emoticon/emoji}			&	syntactic
-		&	  59		&	31	&	24	&	114	&	2.05\%	\\
-		&								&									&	non-syntactic
-		&	 233		&	164	&	98	&	495	&	0.89\%	\\
-		\cline{2-9}
-		&	non-syntactic 					&	\multicolumn{2}{l |}{truncated}
-		&	  111		&	110	&	50	&	271	&	0.49\%	\\
+\begin{dependency}[edge slant=2, text only label, label style=above]
+	\begin{deptext}
+		Olympic \& gold \& medallist \& whipped \& by \& John \& Fisher \\
+	\end{deptext}
+	\deproot{3}{root}
+	\depedge[edge unit distance=1em]{3}{1}{amod}
+    \depedge[edge unit distance=1em]{3}{2}{compound}
+    \depedge[edge unit distance=1em]{3}{4}{acl}
+    \depedge[edge unit distance=1em]{4}{6}{obl}
+    \depedge[edge unit distance=1em]{6}{5}{case}
+    \depedge[edge unit distance=1em]{6}{7}{flat}
+	\deproot[edge below]{4}{root}
+%	\depedge[edge below, edge unit distance=1em]{3}{1}{amod}
+%	\depedge[edge below, edge unit distance=1em]{3}{2}{compound}
+	\depedge[edge below, edge unit distance=1em]{4}{3}{nsubj}
+%	\depedge[edge below, edge unit distance=1em]{4}{6}{obl}
+%	\depedge[edge below, edge unit distance=1em]{6}{5}{case}
+%	\depedge[edge below, edge unit distance=1em]{6}{7}{flat}
+\end{dependency}
+\caption{An example of disagreement when annotating tweets with ellipsis.}\label{fig:disagree}
+\end{figure}
 
-		\hline
-		\multirow{3}{*}{\textit{structure}}	& 	\multicolumn{3}{l |}{retweet}
-		&	  596		&	498	&	282	&	1376	&	2.47\%	\\
-		&	\multicolumn{3}{l |}{at-mentioned}
-		&	  485		&	305	&	175	&	965	&	1.74\%	\\
-		\hline
-	\end{tabular}
-	\caption{Twitter Specific Statistics of Tweebank V2}
-	\label{tab2}
-\end{table*}
+We report the inter-annotator agreement between the annotators
+in the second stage. The agreement on POS is 96.61\%, the unlabeled
+dependency agreement is 88.75\% and the labeled dependency agreement
+is 84.31\%. Further analysis shows the major disagreements on POS
+involve entity names (30.57\%) and topical hashtags (18.11\%).
+Taking the example in Figure \ref{fig:non-syn-toks}, ``Fix you'' can
+be understood as a verbal phrase but also as the name of the Coldplay's
+single and tagged as proper noun. The disagreements on dependencies
+annotation come in several different ways. One of these disagreements
+is resulted by the ellipsis as shown in Figure \ref{fig:disagree}.
+Due to the absence of auxiliary verb, this tweet can either be treated
+as a nominal phrase modified by a clause or a sentence with auxiliary
+verb missing.
+
+%\subsubsection{Statistics}
+%\yjcomment{this part is not finished}
+%Tweebank V2 contains 3550 tweets in total, split into training set with 1639 tweets, development set with 710 tweets and test set with 1201 tweets. 
+%The training set contains all the 639 unique tweets in the training set of Tweebank V1 and another 1000 tweets in feb\_jul\_16 corpus.
+%The development set contains 210 tweets of Tweebank V1 Dev and another 500 tweets in feb\_jul\_16 corpus.
+%The test set contains all the 201 tweets in the test set of Tweebank V1 and another 1000 tweets in feb\_jul\_16 corpus.
+%
+%We process all the raw tweets of these corpora from scratch, from tokenization and POS tagging to dependency annotation.
+%As Tweebank V1 and the POS-tagged Twitter corpus of \newcite{gimpel-EtAl:2011:ACL-HLT2011} used a tweet tokenizer~\cite{ICWSM101540} that do not conform with UD guidelines, as we discussed before, we did not use any data of the intermediate steps from these corpora.
+The basic statistics of Tweebank V2 is shown in Table~\ref{tab1}.
+%
+%% tweets, tokens, tokens/tweet, part/tweet, token types.
+%\begin{table}[t]
+%	\centering
+%	\begin{tabular}{l r r r} 
+%		\hline
+%		& 	Train 		& 	Dev		&	Test\\[0.5ex] \hline
+%		tweets 		&	1,639 		&	709		&	1,201\\
+%		tokens 		&	24,753		&	11,742	&	19,112\\
+%		types 		&	7,579			&	4,165		&	6,228\\
+%		parts		 	&	3,025 		&	1,402		&	2,252\\ \hline
+%	\end{tabular}
+%	\caption{Basic Statistics of Tweebank V2}
+%	\label{tab1}
+%\end{table}
+%
+%% tokens and its proportions for the previous language phenomena.
+%\subsubsection{Twitter Specific Statistics}\label{stats}
+%Following the discussion of the Twitter specific linguistic phenomena, we obtain Table~\ref{tab2}.
+%
+%
+%\begin{table*}[t]
+%	\centering
+%	\small
+%	\begin{tabular}{r | l | l | l | r r r r r} 
+%		\hline
+%		\multicolumn{4}{l}{}	&	Train		&	Test	&	Dev	&	All	&	Per\\[0.5ex] \hline\hline
+%		\multirow{10}{*}{\textit{token}}	&	syntactic						&	\multicolumn{2}{l |}{phrasal abbreviation}				
+%		&	 12 		&	12	&	10	&	34	&	0.06\%	\\
+%		\cline{2-9}
+%		&	\multirow{8}{*}{optionally syntactic}	&	\multirow{2}{*}{RT}					&	syntactic	
+%		&	 40 		&	19	&	18	&	77	&	0.14\%	\\
+%		&								&									&	non-syntactic
+%		&	600  		&	500	&	286	&	1386	&	2.49\%	\\
+%		\cline{3-9}
+%		&								&	\multirow{2}{*}{hashtag}				&	syntactic
+%		&	251  		&	212	&	103	&	566	&	1.02 \%	\\
+%		&								&									&	non-syntactic
+%		&	 290 		&	246	&	155	&	691	&	1.24\%	\\
+%		\cline{3-9}
+%		&								&	\multirow{2}{*}{at-mentioned}			&	syntactic
+%		&	  659		&	420	&	257	&	1336	&	2.40\%	\\
+%		&								&									&	non-syntactic
+%		&	  640		&	519	&	311	&	1470	&	2.64\%	\\
+%		\cline{3-9}
+%		&								&	\multirow{2}{*}{emoticon/emoji}			&	syntactic
+%		&	  59		&	31	&	24	&	114	&	2.05\%	\\
+%		&								&									&	non-syntactic
+%		&	 233		&	164	&	98	&	495	&	0.89\%	\\
+%		\cline{2-9}
+%		&	non-syntactic 					&	\multicolumn{2}{l |}{truncated}
+%		&	  111		&	110	&	50	&	271	&	0.49\%	\\
+%		
+%		\hline
+%		\multirow{3}{*}{\textit{structure}}	& 	\multicolumn{3}{l |}{retweet}
+%		&	  596		&	498	&	282	&	1376	&	2.47\%	\\
+%		&	\multicolumn{3}{l |}{at-mentioned}
+%		&	  485		&	305	&	175	&	965	&	1.74\%	\\
+%		\hline
+%	\end{tabular}
+%	\caption{Twitter Specific Statistics of Tweebank V2}
+%	\label{tab2}
+%\end{table*}
 
@@
 
-We present a pipeline model to parse tweets into universal dependency.
+We present a pipeline system to parse tweets into universal dependency.
 
 \subsection{Tokenizer}
-Tokenization is non-trivial for Twitter domain \cite{ICWSM101540}.
-Due to the informal nature, tweets present cases which are unconventional for traditional toeknization module, like hashtags, at-mentions and emoticons.
-Some of them are even ambiguous without understanding their contexts.
-For example, the asterisk in {\it 4*3} works as a symbol for times and indicates to segment this token into {\it 4 * 3} but that in {\it SH*T} works as a mask and {\it SH*T} should not be segmented.
+Tokenization, as the initial step of many NLP tasks, is non-trivial for
+Twitter domain \cite{ICWSM101540}. Due to the informal nature, tweets
+present several cases which are unconventional for traditional
+toeknization module, like hashtags, at-mentions and emoticons. Some of
+them are even ambiguous without understanding their contexts. For example,
+the asterisk (*) in {\it 4*3} works as a symbol of multiplying and
+delimiter of tokens {\it 4 * 3}; but for the asterisk (*) in {\it SH*T}
+works as a mask for censorship, should not be treated as a delimiter.
 
-Instead of manually crafting rules, we propose to deal with tweets tokenization with a character-level bidirectional LSTM (bi-LSTM) sequence-labeling model.
-Our model takes the raw sentence and tag each character in this sentence as whether it is the beginning of a word.
+Considering the complexity of tweets tokenization, instead of manually
+crafting rules, we propose to deal with tweets tokenization with a 
+character-level bidirectional LSTM (bi-LSTM) sequence-labeling model.
+Our model takes the raw sentence and tag each character in this 
+sentence as whether it is the beginning of a word.
 

### 2017-09-26 paper.tex
sync

@@
 \usepackage{multirow}
+\usepackage{graphicx}
+\usepackage{subcaption}
+\usepackage{arydshln}
 \newcommand\BibTeX{B{\sc ib}\TeX}
@@
 		\depedge[edge unit distance=1em]{12}{11}{amod}
-		\depedge[edge unit distance=1em]{12}{14}{nmod}
+		\depedge[edge unit distance=0.6em]{8}{14}{obl}
 		\depedge[edge unit distance=1em]{14}{13}{case}
-		\depedge[edge unit distance=0.45em]{8}{16}{conj}
+		\depedge[edge unit distance=0.55em]{8}{16}{conj}
 		\depedge[edge unit distance=1em]{16}{15}{cc}
-		\depedge[edge unit distance=0.35em]{3}{17}{discourse}
+		\depedge[edge unit distance=0.37em]{3}{17}{discourse}
 	\end{dependency}
@@
 		Twokenizer & 94.4 \\
-		UD pipe v1.2 & 94.7 \\
-		UD pipe v1.2 (re-trained) & 97.3 \\
-		Our Tokenizer & \bf 98.3 \\
+% 		UD pipe v1.2 & 94.7 \\
+		UD pipe v1.2 & 97.3 \\
+		Our bi-LSTM tokenizer & \bf 98.3 \\
 		\hline
@@
 
-We test our tokenizer on Tweebank v2 test set.
-F-score was used to evaluate the tokenization accuracy.
-Our model was trained on a merge of UD\_English and Tweebank v2 training data.
-Table \ref{tbl:tok-result} shows the tokenization results along with comparison with other tokenizers.
+We test our tokenizer on Tweebank v2 test set. F-score was used to evaluate
+the tokenization accuracy. Our model was trained on a merge of UD\_English
+and Tweebank v2 training data. Table \ref{tbl:tok-result} shows the
+tokenization results along with comparison with other tokenizers. UD pipe v1.2
+\cite{straka-strakova:2017:K17-3} model was re-trained on the same data.
 Our bi-LSTM tokenizer achieves the best accuracy among all these tokenizers.
-By comparing the rule-based group to the model-based group, we can see the model-based ones generally outperform the rule-based tokenizers, which shows the necessity of using statistical model for tweet tokenization.
+From this table, we can also see that the model-based tokenizers
+generally outperform the rule-based tokenizers, which shows the necessity of
+using statistical model for tweet tokenization.
 
@@
 Part-of-Speech tagging for tweets has been studied in previous literals \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}.
-We use the postagger of \newcite{owoputi-EtAl:2013:NAACL-HLT}.
+The goal is to give a fair comparison of these models on our annotation.
+We are especially interested in finding out the can neural network
+models win against the model enhanced by carefully crafted features.
 
@@
 		\hline
-		Stanford Postagger & 65.6 \\
-		Stanford Postagger (re-train) & 90.4 \\
-		UD pipe v1.2 & 78.7 \\
-		UD pipe v1.2 (re-trained) & 83.8 \\
-		bi-LSTM & 91.8 \\
-		ARK Tagger & \bf 95.1 \\
+%		Stanford Postagger & 65.6 \\
+		Stanford Postagger & 90.4 \\
+%		UD pipe v1.2 & 78.7 \\
+		ARK tagger (greedy) & 94.2 \\
+		ARK Tagger (CRF) & \bf 95.1 \\
+		\hdashline
+%		UD pipe v1.2 & 83.8 \\
+		\newcite{ma-hovy:2016:P16-1} & \\
+		Our word bi-LSTM & 89.1 \\
+		Our char bi-LSTM + word bi-LSTM & 91.4 \\
 		\hline
@@
 	\end{tabular}
-	\caption{The POS tagging result on automatic tokenization. The POS tagger we used is from Owoput et al., 2013.}\label{tbl:pos-result-vs-tok}
+	\caption{The POS tagging result on automatic tokenization.}\label{tbl:pos-result-vs-tok}
 \end{table}
 
-We test several different POS taggers on Tweebank v2.
-We also study the influence of tokenization on POS-tagging by evaluating the model's performance on automatically tokenized data.
-This result is shown in Table \ref{tbl:pos-result-vs-tok}.
+We test the POS taggers on Tweebank v2 test set and the results are shown in
+Table \ref{tbl:pos-result}. All the comparison systems were re-trained on
+the merge of UD\_English and Tweebank v2 training set.
+Gold tokenization was used. This table shows that carefully feature engineer
+POS tagger \cite{owoputi-EtAl:2013:NAACL-HLT} outperform the neural network
+models.
+
+We also study the influence of tokenization on POS tagging
+by evaluating the model's performance on automatically
+tokenized data. We use the best performed POS tagger \cite{owoputi-EtAl:2013:NAACL-HLT}
+on gold tokenization as our POS tagger. The results are
+shown in Table \ref{tbl:pos-result-vs-tok}. Table \ref{tbl:pos-result-vs-tok}
+shows that tokenization errors propagate to POS tagging but these
+errors didn't significant influence the tagging decisions.
 
@@
 Social media applications usually require processing tones of data.
-Speed becomes important under such circumstance.
-In this paper, we use the neural greedy parser by \newcite{ballesteros-EtAl:2016:EMNLP2016}, which can parse a sentence in linear time and harness the useful character representations.
-To further improve the parsing accuracy, we propose a new method to distill an ensemble of 20 differently initialized parsers into one greedy parser.
-
-Distilling a smaller classifier from a single large neural network was explored in \newcite{DBLP:journals/corr/HintonVD15} and \newcite{kim-rush:2016:EMNLP2016}.
-In these works, the predicted distribution from the larger model serves as a soft target for training the small classifier.
-Training the smaller classifier is delivered by training with a interpolate between two losses:
+Speed becomes important under such circumstance. In this paper, we
+use the neural greedy parser by \newcite{ballesteros-EtAl:2016:EMNLP2016},
+which can parse a sentence in linear time and harness the useful
+character representations. To further improve the parsing accuracy,
+we propose a new method to distill an ensemble of 20 differently
+initialized parsers into one parser.
+
+Distilling a simple and fast {\it student model} from the accurate but
+slow {\it teacher model} was explored in \newcite{DBLP:journals/corr/HintonVD15}
+and \newcite{kim-rush:2016:EMNLP2016}. In their works, the predicted
+distribution from the teacher model serves as a soft target for
+training the student model by minimizing
+\begin{equation}
+\mathcal{L}_{KD} = \sum_k q(y=k|x) p(y=k|x)
+\end{equation} where $q(y=k|x)$ is the probability distribution
+predicted by the teacher model. Training the student model is
+delivered by training with a interpolate between two losses:
 \begin{equation}\label{eq:distill}
@@
 \end{equation}
-where $\mathcal{L}_{NNL}$ is the traditional log-likelihood loss and $\mathcal{L}_{KD}$ is the loss from soft target.
-
-\newcite{kuncoro-16} was inspired by the distillation idea and proposed to incorporate the knowledge from an ensemble of 20 parsers into one single graph-based parser by adapting the soft target into a structure loss.
-However, as \newcite{kuncoro-16} pointed out, it's not straight-forward to incorporate the structure loss into a transition-based parser.
-Considering the efficiency advantage of transition-based parser over its graph-based counterpart, it's worth study distillation of an ensemble of different parsers.
-
-In this paper, we follow \newcite{DBLP:journals/corr/HintonVD15} and \newcite{kim-rush:2016:EMNLP2016} and distill one single parser from 20 parsers trained with different initialization.
-Training a transition-based greedy parser includes generating a transition sequence from the data and learning the classifier from the states in the sequence.
-And it also holds for training the ensemble parser.
+where $\mathcal{L}_{NNL}$ is the negative log-likelihood loss.
+
+\newcite{kuncoro-16} was inspired by the distillation idea and
+proposed to incorporate the knowledge from an ensemble of 20
+parsers into one single graph-based parser by adapting the soft
+target into a structure loss. However, as \newcite{kuncoro-16}
+pointed out, it's not straight-forward to incorporate the structure
+loss into a transition-based parser. Considering the efficiency
+advantage of transition-based parser over its graph-based counterpart,
+it's worth study distillation of an ensemble of different parsers.
+
+The generic algorithm for training a transition-based greedy parser
+usually includes 1) generating a sequence of transitions from the 
+training data with ``oracle'' and 2) learning the classifier from
+the transitions. One natural adoption of the distillation will be replacing
+$\mathcal{L}_{NLL}$ with the distillation objective (Equation \ref{eq:distill})
+in the second step. We name such method as {\it distill expert}. 
+We adopt such distilling method in our preliminary experiments.
+
+\paragraph{Preliminary Results}
+In our preliminary experiments, we train our parser on the merge of UD\_English
+and Tweebank v2 training set. Automatic POS tags are assigned with 5-fold
+jackknifing. Hyper-parameters including the value of $\alpha$ in Equation \ref{eq:distill}
+are tuned on Tweebank v2 development set. The 20 parsers are trained with
+different random seeds and ensembled by averaging their output probability
+distribution. The ensemble parser achieves a LAS of 78.8, which is more 
+than 3 points higher than the baseline single parser. Distilling from this
+parser leads to a single parser of 77.0 LAS.
 %We first study the necessity of log-likelihood loss (the first term in Equation \ref{eq:distill}).
@@
 
-We show the effect of $\alpha$ in Figure \ref{fig:effect-alpha}.
-This figure shows that parsers with larger $\alpha$ achieves better performance than that with smaller $\alpha$.
-This result shows that learning from the hard target in unnecessary.
-
-%\paragraph{Effect of $\mathcal{T}$}
-%
-%\begin{figure}[t]
-%	\centering
-%	\includegraphics[width=\columnwidth]{graphics/temperature}
-%	\caption{The effect of temperature $\alpha$.}\label{fig:effect-temp}
-%\end{figure}
-
-\paragraph{Results}
-
+We further study the effect of $\alpha$ by varying it from 0 to 1 and
+the results are shown in Figure \ref{fig:effect-alpha}. From this figure,
+we can see that distilling parsers with larger $\alpha$ achieves better
+performance, which means the model should pay more attention to learn
+from the teacher model. And the changes of $\alpha$ from 0.9 to 1.0
+didn't significantly influence the final result, which casts a doubt on
+the necessity of learning from $\mathcal{L}_{NNL}$.
+
+\paragraph{Learning from Exploration} We further set $\alpha$ to 1.0
+and this enable us to get rid of the ``oracle'' in the first step in generic
+transition-based parser training algorithm. Instead of generating
+training instances from the oracle, we generate them by random sampling
+transition from the teacher model's output distribution and follow the
+trajectory of these transitions. We name such method as {\it distill explore}.
+
+\paragraph{Final Results}
 \begin{table}[t]
@@
 		\hline
-		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 79.25 & 74.17 \\
-		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.90 & 72.95 \\
-		Ensemble 20 & 82.80 & 78.69 \\
-		Distill expert ($\alpha$=0.)& 81.22 & 76.98 \\
-		Distill boltzmann ($\mathcal{T}$=1) & 81.55 & 77.32 \\
+		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.2 & 75.4 \\
+%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
+		Ensemble 20x & 83.0 & 78.8 \\
+		Distill 20x expert ($\alpha$=1.0) & 81.2 & 76.7 \\
+		Distill 20x expert ($\alpha$=0.9) & 81.4 & 77.0 \\		
+		Distill 20x explore & 82.2 & 77.9 \\
 		\hline
 	\end{tabular}
-	\caption{The POS tagging result.}\label{tbl:parse-result}
+	\caption{The parsing results on automatic POS tags.}\label{tbl:parse-result}
 \end{table}
 
-%\subsection{Exploiting UD\_English}
-
-%UD\_English as an important source of training data.
-%\section{Model}
-%We propose a new model
+\begin{table}[t]
+	\centering
+	\small
+	\begin{tabular}{rcc}
+		\hline
+		\it System & UAS & LAS \\
+		\hline
+		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 93.0 & 90.9 \\
+		%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
+		Ensemble 20x & 94.5 & 92.6 \\
+		Distill 20x expert ($\alpha$=1.0) & 93.8 & 91.7 \\
+		Distill 20x explore & 94.1 & 92.0 \\
+		\hline
+		\newcite{kuncoro-16} & 94.3 & 92.1 \\
+		\hline
+	\end{tabular}
+	\caption{Distillation on PTB.}\label{tbl:parse-result-PTB}
+\end{table}
+
+Our final parsing experiments are shown in Table \ref{tbl:parse-result},
+in which we can see that distilling from exploration significant outperform
+distilling from expert by achieving one more point LAS improvement.
+Additional experiments on the Penn Treebank data are performed following
+the setting of \newcite{dyer-EtAl:2015:ACL-IJCNLP} and similar trend are
+witnessed. We address this improvement to the fact that learning
+from exploration enables the single parser to learn from the ensemble on
+states of different qualities.
+
+\subsection{Final Evaluation}
+Finally, we evaluate the tweet parsing in a pipeline manner.
 

### 2017-09-26 graphics/alpha.r

@@ -1,17 +1,17 @@
 library("ggplot2")
 
 lines1 <- "alpha,las
-1.0,76.98
-0.9,76.99
-0.8,76.75
-0.7,76.68
-0.6,76.10
-0.5,76.24
-0.4,75.31
-0.3,76.09
-0.2,74.57
-0.1,74.57
-0.0,74.17"
+1.0,76.81
+0.9,76.85
+0.8,76.24
+0.7,76.28
+0.6,76.03
+0.5,76.37
+0.4,76.15
+0.3,76.00
+0.2,74.98
+0.1,75.11
+0.0,74.74"
 
 result1 <- read.table(text=lines1, sep=",", header=TRUE)
 names(result1) <- c("alpha", "las")

### 2017-09-30 paper.tex
Noah

--- 2017-09-25 paper.tex
@@
 
-We release our system at.
-
-\nascomment{not clear to me:  did we reannotate the POS corpus?  was
-  that automatic or manual?  I wasn't sure what to do with the POS
-  section below.}
-\yjcomment{we re-annotated the POS. In one way, Gimple's POS is not very
-consistent with UD POS. In another way, 2,500 new tweets were annotated
-from scratch and they didn't have Gimple's tags.}
+We release our dataset and our system as open-source software at
+\url{http://anonymized}.
+
+\nascomment{I didn't do anything significant to the intro.  for every
+  example, make clear whether it's ``real'' or contrived.}
 
@@
 
-\nascomment{need to introduce this section and explain the structure.
-I'm not crazy about what I have now, but I like it better than what
-we had before, which seemed to keep repeating the same ideas in
-different contexts.  the flow still seems wrong; we start by talking
-about dependencies, then take a detour to POS, then come back to
-dependencies.}
+\nascomment{need to introduce this section and explain the structure.}
+
 \subsection{Background: \textsc{Tweebank}}
@@
 aggressive tokenization than that used by
-\newcite{gimpel-EtAl:2011:ACL-HLT2011}, which followed
+\newcite{gimpel-EtAl:2011:ACL-HLT2011}, which followed the rule-based
+system  introduced by 
 \newcite{ICWSM101540}.  In particular, they opted out of tokenizing
@@
 are decided according to their context.
-\nascomment{explain what we do, and include how this is
-	similar to or different from Kong et al}\yjcomment{done.}
 
@@
 in social media text and pointed that such normalization is problematic.
-Our solution to the syntax of abbreviations is in the same spirit with
-his work. Further study shows that the abbreviations which clearly carry
-syntactic functions only make 0.06\% tokens in our dataset, which
-also indicates it's unnecessary to normalize text in social media.
+Our solution to the syntax of abbreviations follows the spirit of his argument. Because abbreviations which clearly carry
+syntactic functions only constitute 0.06\% of the tokens in our
+dataset, we believe that normalization is an unnecessarily complicated step.
 \nascomment{maybe we owe citations to
@@
 \centering
-\small
-\begin{tabular}{rcc}
-\% & syntactic & non-syntactic \\ \hline
+\begin{tabular}{lrr}
+\multicolumn{2}{r}{syntactic (\%)} & non-syntactic (\%)\\ \hline
 emoticons & 0.25 & 0.95 \\
@@
 URL & 0.67 & 2.38 \\
-truncated words & 0 & 0.49 \\
- \hline
- sum & 2.08 & 7.55 \\
+truncated words & 0.00 & 0.49 \\
+ \hline
+ total & 2.08 & 7.55 \\
 \end{tabular}
@@
 The major characteristic that distinguishes tweets from standard texts is that
-there are large proportion of tokens that don't carry any syntactic functions.
-In our annotation, there are five types of non-syntactic tokens which include
+there are large proportion of tokens that don't carry any syntactic function.
+In our annotation, there are five types of non-syntactic tokens: 
 sentiment emoticons, retweet markers, topical hashtags, referential URLs, and
 truncated words. Figure \ref{fig:non-syn-toks} illustrates examples of
-these non-syntactic tokens. In the sense of part of speech, emoticons are tagged
-as \emph{symbol} ({\tt SYM}) by following the UD guidelines. For other 4 types of
-non-syntactic tokens, they generally have the \emph{other} (\texttt{X})
-part of speech. In our annotation, these five types of tokens make more than
-7.5\% of all tokens and detailed statistics can be found in Table \ref{tbl:non-synt-prop}.
-\nascomment{in latex source I've commented out a paragraph about
-	truncated content.  it's not clear to me what the nonsyntactic
-	tokens are, when that happens}\yjcomment{i've put truncated words here.}
+these non-syntactic tokens.  As discussed above, these are generally
+tagged with the \emph{other} (\texttt{X}) part of speech, except
+emoticons, which are tagged as \emph{symbol} (\texttt{SYM}).  In our annotation, 
+7.5\% of all tokens are non-syntactic; detailed statistics can be found in Table \ref{tbl:non-synt-prop}.
 
@@
 %annotation efforts \nascomment{check!}\yjcomment{it's not safe to claim that.}.
-
-\nascomment{I'm confused about (1) how we define non-syntactic tokens
-  (what are the criteria) and (2) whether this is something we kick
-  over to POS annotation}
-\yjcomment{I've put the definition of non-syntactic tokens there.}
 
@@
 \end{itemize}
-
-\nascomment{explain our conventions and how
-  they relate to Kong and to UD.  in the draft before, we said that we
-had conventions, and Kong didn't, but we didn't really say what ours were.}
-\yjcomment{The bullet points describe our convention for non-syntactic tokens.}
 
@@
 	\end{dependency}
-	\caption{A example tweet contains major non-syntactic tokens, with
+	\caption{An example tweet that contains non-syntactic tokens:
 		\textcolor{red}{sentiment emoticon},
@@
 convention above. Compared with \citet{kong-EtAl:2014:EMNLP2014},
-we also gave a clear definition of non-syntactic tokens, which help
-us avoid confusion.
-\nascomment{say what it is, and what they attach to, and clarify that
-  the annotators didn't do this manually (I think)}
+we also gave a clear definition of non-syntactic tokens, which helped
+us avoid confusion during annotation.
 
@@
 \emph{proper noun} (\texttt{PROPN}) and attaching them to the
-following predicate with the label \emph{vocative} (see Figure \ref{fig:informal-toks} for an example).  \nascomment{need an example.} \yjcomment{done.}
+following predicate with the label \emph{vocative} (see Figure \ref{fig:informal-toks} for an example).
 
@@
 \subsection{\sc Tweebank v2}
-Following the guideline mentioned above, we create a new annotated Twitter treebank, which we call {\sc Tweebank v2}.
+Following the guidelines mentioned above, we create a new annotated Twitter treebank, which we call {\sc Tweebank v2}.
 
 \subsubsection{Data Collection}
-{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1} (Kong et al., 2014, 639 tweets), along with additional 201 tweets sampled from \newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled  from the Twitter stream from Feb.
-2017 to Jul.
-2017.
+{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1} (Kong et al., 2014, 639 tweets), along with additional 201 tweets sampled from \newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled  from the Twitter stream from February 2017 to July 2017.
 The latter data source consists 147.4M English tweets which are filtered by {\it lang} attribute in the tweet JSON and {\it langid.py}\footnote{\url{https://github.com/saffsd/langid.py}} toolkit.
@@
 \subsubsection{Annotation Process}
-The whole annotation process contains three stages.
+Our annotation process was conducted in three stages.
 In the first stage, 18 researchers worked on the {\sc Tweebank v1}
-proportion and created the initial annotation in one day
-following our guideline. Both the guideline and annotation
+proportion and created the initial annotations in one day.
+\nascomment{Check:} Before annotating, they were given a tutorial overview of the UD
+annotation conventions and our guidelines.
+Both the guidelines and annotation
 were further refined by the authors of this paper to increase
 the coverage of our guideline and solve inconsistency between
-different annotators. In the second stage, a postagger and
-parser are trained on the annotated data from the first stage,
-and automatically analyze the sampled 2,500 tweets and the authors
-of this paper manually correct the parsed data. Finally, an extra
+different annotators during this exercise. In the second stage, a POS tagger and
+parser were trained on the annotated data from the first stage,
+and used to automatically analyze the sampled 2,500 tweets.  Authors 
+of this paper manually corrected the parsed data. \nascomment{this is
+  a little weird:  don't you have to do this before you parse?} Finally, an extra
 layer of word-level normalization was manually annotated.
@@
 \end{dependency}
-\caption{An example of disagreement when annotating tweets with ellipsis.}\label{fig:disagree}
+\caption{An example of disagreement; one annotator's parse is shown above, disagreeing arcs from the other
+  annotator are shown below.}\label{fig:disagree}
 \end{figure}
@@
 be understood as a verbal phrase but also as the name of the Coldplay's
-single and tagged as proper noun. The disagreements on dependencies
-annotation come in several different ways. One of these disagreements
-is resulted by the ellipsis as shown in Figure \ref{fig:disagree}.
-Due to the absence of auxiliary verb, this tweet can either be treated
-as a nominal phrase modified by a clause or a sentence with auxiliary
-verb missing.
+single and tagged as proper noun. An example of a disagreement on
+dependencies is shown in Figure \ref{fig:disagree}.  Depending on
+whether this is an example of an empty auxiliary verb, or a clause-modified
+noun, both annotations are reasonable.
 
@@
 
-We present a pipeline system to parse tweets into universal dependency.
-
-\subsection{Tokenizer}
+We present a pipeline system to parse tweets into universal
+dependencies.  We evaluate each component individually, and the system
+as a whole.
+
+\subsection{Tokenizer} \label{sec:tok}
 Tokenization, as the initial step of many NLP tasks, is non-trivial for
-Twitter domain \cite{ICWSM101540}. Due to the informal nature, tweets
-present several cases which are unconventional for traditional
-toeknization module, like hashtags, at-mentions and emoticons. Some of
-them are even ambiguous without understanding their contexts. For example,
-the asterisk (*) in {\it 4*3} works as a symbol of multiplying and
-delimiter of tokens {\it 4 * 3}; but for the asterisk (*) in {\it SH*T}
-works as a mask for censorship, should not be treated as a delimiter.
-
-Considering the complexity of tweets tokenization, instead of manually
-crafting rules, we propose to deal with tweets tokenization with a 
-character-level bidirectional LSTM (bi-LSTM) sequence-labeling model.
-Our model takes the raw sentence and tag each character in this 
+informal tweets, which include hashtags, at-mentions, and emoticons
+\cite{ICWSM101540}.  Context is often required for tokenization
+decisions; for example,
+the asterisk (*) in {\it 4*3} is a separate token signifying
+multiplication, but for the asterisk (*) in {\it sh*t}
+works as a mask for censorship and should not be segmented.
+
+We introduce a new
+character-level bidirectional LSTM (bi-LSTM) sequence-labeling model
+\nascomment{add cite for this kind of model}
+for tokenization.
+Our model takes the raw sentence and tags each character in this 
 sentence as whether it is the beginning of a word.
-
-\paragraph{Experimental Results}
+\nascomment{check:} It is trained on the training portion of
+\textsc{Tweebank v2} combined with the UD\_English training dataset.
+
+\paragraph{Experimental results.}
 
@@
 	\centering
-	\small
 	\begin{tabular}{rc}
 		\hline
-		\it System & F \\
-		\hline
-		Stanford Tokenizer & 96.6 \\
+		\it System & $F_1$ \\
+		\hline
+		Stanford CoreNLP & 96.6 \\
 		Twokenizer & 94.4 \\
-		UD pipe v1.2 & 94.7 \\
-		UD pipe v1.2 (re-trained) & 97.3 \\
-		Our Tokenizer & \bf 98.3 \\
+% 		UD pipe v1.2 & 94.7 \\
+		UD pipe v1.2 (same training data) & 97.3 \\
+		Our bi-LSTM tokenizer & \bf 98.3 \\
 		\hline
 	\end{tabular}
-	\caption{The tokenization results.}\label{tbl:tok-result}
+	\caption{Tokenizer comparison on the \textsc{Tweebank v2} test set.}\label{tbl:tok-result}
 \end{table}
 
-We test our tokenizer on Tweebank v2 test set.
-F-score was used to evaluate the tokenization accuracy.
-Our model was trained on a merge of UD\_English and Tweebank v2 training data.
-Table \ref{tbl:tok-result} shows the tokenization results along with comparison with other tokenizers.
-Our bi-LSTM tokenizer achieves the best accuracy among all these tokenizers.
-By comparing the rule-based group to the model-based group, we can see the model-based ones generally outperform the rule-based tokenizers, which shows the necessity of using statistical model for tweet tokenization.
-
-\subsection{POS-Tagger}
-
-Part-of-Speech tagging for tweets has been studied in previous literals \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}.
-We use the postagger of \newcite{owoputi-EtAl:2013:NAACL-HLT}.
-
-\paragraph{Experimental Results}
+We tested our tokenizer on the \textsc{Tweebank v2} test set. 
+We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
+tokenization results, compared to  other available tokenizers. 
+\nascomment{Check:}  The Stanford \nascomment{cite}  and Twokenizer
+\nascomment{cite} systems are rule-based systems and were not adapted
+to the UD tokenization scheme.
+The UD pipe v1.2
+\cite{straka-strakova:2017:K17-3} model was re-trained on the same
+data as our system.
+Our bi-LSTM tokenizer achieves the best accuracy among all these
+tokenizers.  These results indicate the value of statistical modeling
+in tokenization for informal texts.
+
+\subsection{Part-of-Speech Tagger}
+
+Part-of-speech tagging for tweets has been extensively studied \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}.
+On the annotation scheme designed in \S\ref{sec:pos-anno}, based on UD and adapted for
+Twitter, we compared several existing systems and also two bi-LSTM systems similar
+to \citet{??} \nascomment{add cite}, one using word vectors and the
+other using word and character vectors.   All systems were re-trained on
+the combination of the UD\_English and \textsc{Tweebank v2} training sets.
+
+\nascomment{I wonder if we ought to give more detail about our biLSTM
+  systems, here and under tokenization?  will reviewers want to know details?}
+
+\paragraph{Experimental results.}
 
@@
 	\centering
-	\small
 	\begin{tabular}{rc}
 		\hline
-		\it System & P \\
-		\hline
-		Stanford Postagger & 65.6 \\
-		Stanford Postagger (re-train) & 90.4 \\
-		UD pipe v1.2 & 78.7 \\
-		UD pipe v1.2 (re-trained) & 83.8 \\
-		bi-LSTM & 91.8 \\
-		ARK Tagger & \bf 95.1 \\
+		\it System & \it Precision \\
+		\hline
+%		Stanford Postagger & 65.6 \\
+		Stanford CoreNLP & 90.4 \\
+%		UD pipe v1.2 & 78.7 \\
+		\citealp{owoputi-EtAl:2013:NAACL-HLT} (greedy) & 94.2 \\
+		\citealp{owoputi-EtAl:2013:NAACL-HLT} (CRF) & \bf 95.1 \\
+		\hdashline
+%		UD pipe v1.2 & 83.8 \\
+		\citealp{ma-hovy:2016:P16-1} & \\
+		our word bi-LSTM & 89.1 \\
+		our character + word bi-LSTMs & 91.4 \\
 		\hline
 	\end{tabular}
-	\caption{The POS tagging result on gold tokenization.}\label{tbl:pos-result}
+	\caption{POS tagger comparison on gold-standard tokens in the
+          \textsc{Tweebank v2} test set. \label{tbl:pos-result}
+          \nascomment{to do:  fill in Ma/Hovy}}
 \end{table}
@@
 	\centering
-	\small
 	\begin{tabular}{rc}
 		\hline
-		\it System & F \\
-		\hline
-		Stanford Tokenizer & 92.0 \\
-		Our Tokenizer & 93.6 \\
+		\it System & $F_1$ \\
+		\hline
+		Stanford CoreNLP & 92.0 \\
+		our tokenizer (\S\ref{sec:tok}) & 93.6 \\
 		\hline
 	\end{tabular}
-	\caption{The POS tagging result on automatic tokenization. The POS tagger we used is from Owoput et al., 2013.}\label{tbl:pos-result-vs-tok}
+	\caption{\citet{owoputi-EtAl:2013:NAACL-HLT} POS tagging performance with automatic tokenization on
+          the \textsc{Tweebank v2} test set. \label{tbl:pos-result-vs-tok}}
 \end{table}
 
-We test several different POS taggers on Tweebank v2.
-We also study the influence of tokenization on POS-tagging by evaluating the model's performance on automatically tokenized data.
-This result is shown in Table \ref{tbl:pos-result-vs-tok}.
+We tested the POS taggers on \textsc{Tweebank v2} test set.  Results
+with gold-standard tokenization are shown in
+Table \ref{tbl:pos-result}. The careful feature engineering in the 
+POS tagger  of \citet{owoputi-EtAl:2013:NAACL-HLT} outperforms our neural network
+models.  (That tagger also makes use of \citet{Brown} clusters derived
+from a large collection of unannotated tweets.  Those clusters did not
+improve the performance of our bi-LSTM models.)
+
+Results of the \citet{owoputi-EtAl:2013:NAACL-HLT}  with non-greedy
+inference \nascomment{check} on automatically tokenized data
+are shown in  Table \ref{tbl:pos-result-vs-tok}.  We see that errors
+in tokenization do propagate, but tagging performance is above 93\%
+with our tokenizer.
 
@@
 %Time is a major concern on
-Social media applications usually require processing tones of data.
-Speed becomes important under such circumstance.
-In this paper, we use the neural greedy parser by \newcite{ballesteros-EtAl:2016:EMNLP2016}, which can parse a sentence in linear time and harness the useful character representations.
-To further improve the parsing accuracy, we propose a new method to distill an ensemble of 20 differently initialized parsers into one greedy parser.
-
-Distilling a smaller classifier from a single large neural network was explored in \newcite{DBLP:journals/corr/HintonVD15} and \newcite{kim-rush:2016:EMNLP2016}.
-In these works, the predicted distribution from the larger model serves as a soft target for training the small classifier.
-Training the smaller classifier is delivered by training with a interpolate between two losses:
+Social media applications teypically require processing large volumes
+of data, making speed an important criterion. We therefore 
+use the neural greedy parser introduced by \newcite{ballesteros-EtAl:2016:EMNLP2016},
+which can parse a sentence in linear time and harnesses 
+character representations, which should help mitigate the challenge of
+spelling variation. To further improve the parsing accuracy,
+we propose a new method to distill an ensemble of 20 differently
+initialized parsers into one parser.  To our knowledge, this is the
+first attempt to distill an ensemble of greedy transition-based
+parsers \nascomment{check}.
+
+Distilling a simple and fast {\it student model} from the accurate but
+slow {\it teacher model} was explored by \newcite{DBLP:journals/corr/HintonVD15}
+and \newcite{kim-rush:2016:EMNLP2016}. In their works, the predicted
+distribution from the teacher model serves as a soft target for
+training the student model by minimizing
+\begin{equation}
+\mathcal{L}_{\mathit{KD}} = \sum_k q(y=k\mid x) p(y=k\mid x)
+\end{equation} where $q(y=k\mid x)$ is the probability distribution
+predicted by the teacher model. Training the parameters of the student model ($p$) is
+accomplished by interpolating between two losses:
 \begin{equation}\label{eq:distill}
-\mathcal{L}=(1-\alpha)\mathcal{L}_{NNL} + \alpha\mathcal{L}_{KD}
+\mathcal{L}=(1-\alpha)\mathcal{L}_{\mathit{NNL}} + \alpha\mathcal{L}_{\mathit{KD}}
 \end{equation}
-where $\mathcal{L}_{NNL}$ is the traditional log-likelihood loss and $\mathcal{L}_{KD}$ is the loss from soft target.
-
-\newcite{kuncoro-16} was inspired by the distillation idea and proposed to incorporate the knowledge from an ensemble of 20 parsers into one single graph-based parser by adapting the soft target into a structure loss.
-However, as \newcite{kuncoro-16} pointed out, it's not straight-forward to incorporate the structure loss into a transition-based parser.
-Considering the efficiency advantage of transition-based parser over its graph-based counterpart, it's worth study distillation of an ensemble of different parsers.
-
-In this paper, we follow \newcite{DBLP:journals/corr/HintonVD15} and \newcite{kim-rush:2016:EMNLP2016} and distill one single parser from 20 parsers trained with different initialization.
-Training a transition-based greedy parser includes generating a transition sequence from the data and learning the classifier from the states in the sequence.
-And it also holds for training the ensemble parser.
+where $\mathcal{L}_{\mathit{NNL}}$ is the negative log-likelihood loss.
+
+\newcite{kuncoro-16} were inspired by the distillation idea and
+proposed to incorporate the knowledge from an ensemble of 20 greedy transition-based
+parsers into one single \emph{graph-based} parser by adapting the soft
+target into a structured loss. However, as \newcite{kuncoro-16}
+pointed out, it is not straightforward to incorporate the structure
+loss into a \emph{transition-based} parser. Considering the efficiency
+advantage of greedy transition-based parsers over their graph-based counterparts,
+it is worth considering distillation of an ensemble into a greedy parser.
+
+The generic algorithm for training a transition-based greedy parser
+usually includes 1) generating a sequence of transitions from the 
+training data, called the ``oracle'' and 2) learning the classifier from
+the oracle transitions. One natural adaptation of the distillation will be interpolating
+$\mathcal{L}_{\mathit{NLL}}$ with the distillation objective (Equation \ref{eq:distill})
+in the second step. We name this method \textsc{distill expert}.
+
+\paragraph{Preliminary results.}
+In our preliminary experiments, we train our parser on the combination of UD\_English
+and \textsc{Tweebank v2} training sets. \nascomment{are we using
+  gold-standard tokenization or automatic, here?} Automatic POS tags are assigned with 5-fold
+jackknifing. Hyperparameters, including the value of $\alpha$ in Equation \ref{eq:distill},
+are tuned on the \textsc{Tweebank v2} development set. 20 parsers are trained with
+different random seeds and ensembled by averaging their output probability
+distributions over transitions. The ensemble parser achieves a LAS of 78.8, which is more 
+than 3 points higher than the baseline single parser. Distilling from this
+parser leads to a single parser with  77.0 LAS.
 %We first study the necessity of log-likelihood loss (the first term in Equation \ref{eq:distill}).
 
-\paragraph{Effect of $\alpha$}
+\paragraph{Effect of $\alpha$.}
 
@@
 	\includegraphics[width=\columnwidth]{graphics/alpha}
-	\caption{The effect of $\alpha$ in distillation.}\label{fig:effect-alpha}
+	\caption{The effect of $\alpha$ on distillation.}\label{fig:effect-alpha}
 \end{figure}
 
-We show the effect of $\alpha$ in Figure \ref{fig:effect-alpha}.
-This figure shows that parsers with larger $\alpha$ achieves better performance than that with smaller $\alpha$.
-This result shows that learning from the hard target in unnecessary.
-
-%\paragraph{Effect of $\mathcal{T}$}
-%
-%\begin{figure}[t]
-%	\centering
-%	\includegraphics[width=\columnwidth]{graphics/temperature}
-%	\caption{The effect of temperature $\alpha$.}\label{fig:effect-temp}
-%\end{figure}
-
-\paragraph{Results}
-
+We further study the effect of the interpolation hyperparameter $\alpha$ by varying it from 0 to 1.
+The results are shown in Figure \ref{fig:effect-alpha}. We can see that distilling parsers with larger $\alpha$ achieves better
+performance, which means the model should pay more attention to learning
+from the teacher model.  Indeed, the negligible difference between the
+best performance at $\alpha = 0.9$ and $\alpha=1.0$ casts doubt on the
+necessity of including $\mathcal{L}_{NNL}$ in the training objective
+at all. \nascomment{check my rewording}
+
+\paragraph{Learning from exploration.} We further set $\alpha$ to 1.0,
+eliminating the oracle from the usual transition-based parser
+training algorithm.  Instead of generating
+training instances from the oracle, we generate them by random sampling
+transitions from the teacher (ensemble \nascomment{check}) model's output distribution and follow the
+trajectory of these transitions. We name this method \textsc{distill explore}.
+
+\paragraph{Final results.}
 \begin{table}[t]
 	\centering
-	\small
 	\begin{tabular}{rcc}
@@
 		\hline
-		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 79.25 & 74.17 \\
-		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.90 & 72.95 \\
-		Ensemble 20 & 82.80 & 78.69 \\
-		Distill expert ($\alpha$=0.)& 81.22 & 76.98 \\
-		Distill boltzmann ($\mathcal{T}$=1) & 81.55 & 77.32 \\
+		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.2 & 75.4 \\
+%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
+		Ensemble (20) & 83.0 & 78.8 \\
+		\textsc{distill expert} ($\alpha$=1.0) & 81.2 & 76.7 \\
+		\textsc{distill expert} ($\alpha$=0.9) & 81.4 & 77.0 \\		
+		\textsc{distill explore} & 82.2 & 77.9 \\
 		\hline
 	\end{tabular}
-	\caption{The POS tagging result.}\label{tbl:parse-result}
+	\caption{Dependency parser comparison on \textsc{Tweebank v2},
+           with automatic POS tags. \label{tbl:parse-result}}
 \end{table}
 
-%\subsection{Exploiting UD\_English}
-
-%UD\_English as an important source of training data.
-%\section{Model}
-%We propose a new model
+\begin{table}[t]
+	\centering
+	\begin{tabular}{rcc}
+		\hline
+		\it System & UAS & LAS \\
+		\hline
+		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 93.0 & 90.9 \\
+		%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
+		Ensemble (20) & 94.5 & 92.6 \\
+		\textsc{distill expert} ($\alpha$=1.0) & 93.8 & 91.7 \\
+		\textsc{distill explore} & 94.1 & 92.0 \\
+		\hline
+		\newcite{kuncoro-16} & 94.3 & 92.1 \\
+		\hline
+	\end{tabular}
+	\caption{Dependency parser comparison on PTB test set.}\label{tbl:parse-result-PTB}
+\end{table}
+
+Our final parsing experiments are shown in Table \ref{tbl:parse-result},
+in which we can see that \textsc{distill explore} significant
+outperforms \textsc{distill expert}, gaining one more point in LAS improvement.
+Additional experiments on the Penn Treebank were performed following
+the setting of \newcite{dyer-EtAl:2015:ACL-IJCNLP};
+Table~\ref{tbl:parse-result-PTB} shows a similar trend, and we achieve
+performance close to that of the graph-based parser of \citet{kuncoro-16}.
+We attribute the improvements of \textsc{distill explore} over
+\textsc{distill expert} to the former's exploration of
+ensemble-sanctioned parser states
+of different qualities.
+
+\subsection{Final Evaluation}
+Finally, we evaluate our full pipeline.
 

### 2017-10-26 paper.tex
Noah
fix some errors

@@
 annotating tweets and presented a tweets treebank ({\sc Tweebank})
-which has 12,149 tokens and was created using the 
+which has 12,149 tokens and largely followed the conventions
+suggested by \citet{schneider-EtAl:2013:LAW7-ID} that are close to 
 \citet{Yamada03statisticaldependency} dependencies. Both these
@@
 		\begin{deptext}
-			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& @coldplay \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl} \& Nice \& \textcolor{cyan}{\bf p} \& ...\\
+			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& \textcolor{green}{\bf @coldplay} \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl} \& Nice \& \textcolor{cyan}{\bf p} \& ...\\
 			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny X \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \& \tiny ADJ \& \tiny X \& \tiny PUNCT \\
@@
 		\textcolor{orange}{retweet marker},
+		\textcolor{green}{user at-mention}
 		\textcolor{gray}{topical hashtag},
@@
 \subsubsection{Data Collection}
-{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1} (Kong et al., 2014, 639 tweets), along with additional 201 tweets sampled from \newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled  from the Twitter stream from February 2017 to July 2017.
+{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1} (Kong et al., 2014, 639 tweets), along with additional 201 tweets sampled from \newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled  from the Twitter stream from February 2016 to July 2016.
 The latter data source consists 147.4M English tweets which are filtered by {\it lang} attribute in the tweet JSON and {\it langid.py}\footnote{\url{https://github.com/saffsd/langid.py}} toolkit.
@@
 	\includegraphics[width=\columnwidth]{graphics/alpha}
-	\caption{The effect of $\alpha$ on distillation.}\label{fig:effect-alpha}
+	\caption{The effect of $\alpha$ on
+          distillation. \nascomment{to do:  please make the font in
+            the graphic readable}}\label{fig:effect-alpha}
 \end{figure}

### 2017-10-27 paper.tex
fix minor error
minor error on statstics of v1 tweebank

@@
 		\textcolor{orange}{retweet marker},
-		\textcolor{green}{user at-mention}
+		\textcolor{green}{retweet at-mention},
 		\textcolor{gray}{topical hashtag},
@@
 \subsubsection{Data Collection}
-{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1} (Kong et al., 2014, 639 tweets), along with additional 201 tweets sampled from \newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled  from the Twitter stream from February 2016 to July 2016.
+{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1} (Kong et al., 2014, 840 unique tweets, including training and test set), along with additional 201 tweets sampled from \newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled from the Twitter stream from February 2016 to July 2016.
 The latter data source consists 147.4M English tweets which are filtered by {\it lang} attribute in the tweet JSON and {\it langid.py}\footnote{\url{https://github.com/saffsd/langid.py}} toolkit.

### 2017-11-09 paper.tex
update result, add motivation for ensemble, add abstract

@@
 \begin{abstract}
-
+In this paper, we study the problem of analyzing tweets with
+universal dependencies \citep[UD]{NIVRE16.348}. We extend the UD guidelines to cover
+special constructions in tweets. Under such guidelines, we create
+a new tweet treebank which has 55,607 tokens and it's more than 4 times
+larger than the {\sc Tweebank v1}. We characterize the disagreements
+among our annotation and show that it is challenging to deliver
+consistent annotation due to the ambiguities in ways of
+understanding and explaining the tweets. Over the new treebank,
+we build a pipeline system to parse tweets into UD. To conquer the
+annotation noise without sacrificing efficiency, we propose a new
+method to distill an ensemble of 20 parsers into a single one. Our
+method achieve an improvement of 2.3 in LAS over the baseline.
 \end{abstract}
@@
 tokenization, part-of-speech (POS) tags and universal dependencies.
+We characterize the disagreement among our annotations and show that
+consistent annotation is still challenging to deliver even with
+the extended guidelines.
 
@@
 
-To achieve better performance without sacrificing efficiency, we propose
-a new method to train the parser with the distillation 
+To conquer the noise in our annotation and achieve better performance
+without sacrificing efficiency, we propose a new method to
+train the parser with the distillation 
 \cite{DBLP:journals/corr/HintonVD15} of 20 parsers ensemble.
@@
 		\textcolor{blue}{referential URL}, and
-		\textcolor{cyan}{truncated word}.}\label{fig:non-syn-toks}
+		\textcolor{cyan}{truncated word}.
+		This example tweet is a concatenation of three real tweets.
+	}\label{fig:non-syn-toks}
 \end{figure*}
@@
 	\end{dependency}
-	\caption{An example tweet with informal but syntactic tokens.}\label{fig:informal-toks}
+	\caption{An example tweet with informal but syntactic tokens.
+	This is an artificial tweets inspired by several tweets.}\label{fig:informal-toks}
 \end{figure*}
@@
 
-\subsection{\sc Tweebank v2}
+\subsection{\sc Tweebank v2}\label{sec:anno-process}
 Following the guidelines mentioned above, we create a new annotated Twitter treebank, which we call {\sc Tweebank v2}.
@@
 proportion and created the initial annotations in one day.
-\nascomment{Check:} Before annotating, they were given a tutorial overview of the UD
+Before annotating, they were given a tutorial overview of the UD
 annotation conventions and our guidelines.
@@
 different annotators during this exercise. In the second stage, a POS tagger and
-parser were trained on the annotated data from the first stage,
+parser were trained on the annotated data from the first stage (1,041 tweets in total),
 and used to automatically analyze the sampled 2,500 tweets.  Authors 
@@
   a little weird:  don't you have to do this before you parse?} Finally, an extra
-layer of word-level normalization was manually annotated.
+layer of word-level normalization was manually annotated for data
+analysis purposes.
 
@@
 \caption{An example of disagreement; one annotator's parse is shown above, disagreeing arcs from the other
-  annotator are shown below.}\label{fig:disagree}
+  annotator are shown below. This is a real example in our annotation.}\label{fig:disagree}
 \end{figure}
@@
 
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=\columnwidth,trim={0 0 13cm 9cm},clip]{graphics/bilstm_tokenizer}
+	\caption{The bi-LSTM tokenizer model that segments `its gonna be' into `it s gon na be'.}\label{fig:tok-model}
+\end{figure}
 We introduce a new
 character-level bidirectional LSTM (bi-LSTM) sequence-labeling model
-\nascomment{add cite for this kind of model}
+\cite{DBLP:journals/corr/HuangXY15,ma-hovy:2016:P16-1}
 for tokenization.
 Our model takes the raw sentence and tags each character in this 
-sentence as whether it is the beginning of a word.
-\nascomment{check:} It is trained on the training portion of
-\textsc{Tweebank v2} combined with the UD\_English training dataset.
+sentence as whether it is the beginning of a word (1 as the beginning and 0 otherwise).
+Figure \ref{fig:tok-model} shows our tokenization model.
+Space is treated as an input but consistently assigned a special tag \$.
 
@@
 
-We tested our tokenizer on the \textsc{Tweebank v2} test set. 
+We trained our tokenizer on the training portion of
+\textsc{Tweebank v2} combined with the UD\_English training dataset
+and tested on the \textsc{Tweebank v2} test set. 
 We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
 tokenization results, compared to  other available tokenizers. 
-\nascomment{Check:}  The Stanford \nascomment{cite}  and Twokenizer
-\nascomment{cite} systems are rule-based systems and were not adapted
+The Stanford \cite{manning-EtAl:2014:P14-5} and Twokenizer
+\cite{ICWSM101540} systems are rule-based systems and were not adapted
 to the UD tokenization scheme.
@@
 
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=\columnwidth,trim={0 0 13cm 3cm},clip]{graphics/bilstm_postagger}
+	\caption{The bi-LSTM postagger model that tags `it s gon na be' as {\tt PRON AUX VERB PART AUX}.}\label{fig:pos-model}
+\end{figure}
+
 Part-of-speech tagging for tweets has been extensively studied \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}.
@@
 Twitter, we compared several existing systems and also two bi-LSTM systems similar
-to \citet{??} \nascomment{add cite}, one using word vectors and the
-other using word and character vectors.   All systems were re-trained on
-the combination of the UD\_English and \textsc{Tweebank v2} training sets.
+to \citet{DBLP:journals/corr/HuangXY15} and \citet{lample-EtAl:2016:N16-1}, one using
+word vectors and the other using word and character vectors (see Figure \ref{fig:pos-model}).
+All systems were re-trained on the combination of the UD\_English and 
+\textsc{Tweebank v2} training sets. We use the twitter specific glove embedding released by
+\citet{pennington-socher-manning:2014:EMNLP2014} as the word embeeding in all the neural tagger
+and parser\footnote{\url{http://nlp.stanford.edu/data/glove.twitter.27B.zip}}.
 
@@
 %		UD pipe v1.2 & 83.8 \\
-		\citealp{ma-hovy:2016:P16-1} & \\
-		our word bi-LSTM & 89.1 \\
-		our character + word bi-LSTMs & 91.4 \\
+		\citealp{ma-hovy:2016:P16-1} & 91.8 \\
+		our word bi-LSTM & 89.2 \\
+		our character + word bi-LSTMs & 91.5 \\
 		\hline
@@
 	\caption{POS tagger comparison on gold-standard tokens in the
-          \textsc{Tweebank v2} test set. \label{tbl:pos-result}
-          \nascomment{to do:  fill in Ma/Hovy}}
+          \textsc{Tweebank v2} test set. \label{tbl:pos-result}}
 \end{table}
@@
 POS tagger of \citet{owoputi-EtAl:2013:NAACL-HLT} outperforms our neural network
-models.  (That tagger also makes use of \citet{Brown} clusters derived
+models.  (That tagger also makes use of \citet{Brown:1992:CNG:176313.176316} clusters derived
 from a large collection of unannotated tweets.  Those clusters did not
@@
 Results of the \citet{owoputi-EtAl:2013:NAACL-HLT}  with non-greedy
-inference \nascomment{check} on automatically tokenized data
+inference on automatically tokenized data
 are shown in  Table \ref{tbl:pos-result-vs-tok}.  We see that errors
@@
 
-%Time is a major concern on
-Social media applications teypically require processing large volumes
+Social media applications typically require processing large volumes
 of data, making speed an important criterion. We therefore 
@@
 character representations, which should help mitigate the challenge of
-spelling variation. To further improve the parsing accuracy,
-we propose a new method to distill an ensemble of 20 differently
-initialized parsers into one parser.  To our knowledge, this is the
-first attempt to distill an ensemble of greedy transition-based
-parsers \nascomment{check}.
+spelling variation. We encourage the reader to refer their paper for
+more details about the model.
+
+Section \ref{sec:anno-process} shows that severe ambiguities
+exist when we create {\sc Tweebank v2}, which makes the training data
+of the parser very noisy. \citet{Frnay2014ClassificationIT} suggested
+that most of losses are shown to be not robust to 
+classification noise, including the log-likelihood loss used in
+\citet{ballesteros-dyer-smith:2015:EMNLP}. To conquer the noisy
+data and further improve the parsing accuracy, we followed the
+empirical study of \citet{Dietterich2000} and ensemble of 20 differently
+initialized parsers. To make it still parses in linear time, we
+propose a new method to distill the ensemble of 20 parsers into one parser.
+To our knowledge, this is the first attempt to distill an
+ensemble of greedy transition-based
+parsers.% \nascomment{check}.
 
@@
 In our preliminary experiments, we train our parser on the combination of UD\_English
-and \textsc{Tweebank v2} training sets. \nascomment{are we using
-  gold-standard tokenization or automatic, here?} Automatic POS tags are assigned with 5-fold
+and \textsc{Tweebank v2} training sets. Gold-standard tokenization and automatic POS
+tags are used. Automatic POS tags are assigned with 5-fold
 jackknifing. Hyperparameters, including the value of $\alpha$ in Equation \ref{eq:distill},
-are tuned on the \textsc{Tweebank v2} development set. 20 parsers are trained with
-different random seeds and ensembled by averaging their output probability
-distributions over transitions. The ensemble parser achieves a LAS of 78.8, which is more 
+are tuned on the \textsc{Tweebank v2} development set. Unlabeled attachment score and
+labeled attachment score including punctuations are used to evaluate parsing performance.
+
+\citet{reimers-gurevych:2017:EMNLP2017} pointed out that the training process for neural networks are highly
+non-deterministic and largely depends on the seed value for pseduo-random number generator.
+Our preliminary experiments confirm this finding by witnessing a gap of 1 LAS on development set
+between the best (75.8) and worst (74.8) runs. To eliminate the effect of random number, for each
+hyperparameter setting, we conduct 5 runs with different seeds and report the averaged score.
+
+Our 20 parsers are ensembled by averaging their output probability
+distributions over transitions. The ensemble parser achieves a LAS of 79.4, which is more 
 than 3 points higher than the baseline single parser. Distilling from this
-parser leads to a single parser with  77.0 LAS.
+parser leads to a single parser with 78.1 LAS.
 %We first study the necessity of log-likelihood loss (the first term in Equation \ref{eq:distill}).
@@
 	\centering
-	\includegraphics[width=\columnwidth]{graphics/alpha}
-	\caption{The effect of $\alpha$ on
-          distillation. \nascomment{to do:  please make the font in
-            the graphic readable}}\label{fig:effect-alpha}
+	\includegraphics[width=\columnwidth,trim={0.3cm 0 0 0},clip]{graphics/alpha}
+	\caption{The effect of $\alpha$ on \textsc{expert distillation}.}\label{fig:effect-alpha}
 \end{figure}
@@
 necessity of including $\mathcal{L}_{NNL}$ in the training objective
-at all. \nascomment{check my rewording}
+at all.% \nascomment{check my rewording}
 
@@
 training instances from the oracle, we generate them by random sampling
-transitions from the teacher (ensemble \nascomment{check}) model's output distribution and follow the
+transitions from the teacher (ensemble) model's output distribution and follow the
 trajectory of these transitions. We name this method \textsc{distill explore}.
@@
 		\hline
-		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.2 & 75.4 \\
+		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.4 & 75.8 \\
 %		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
-		Ensemble (20) & 83.0 & 78.8 \\
-		\textsc{distill expert} ($\alpha$=1.0) & 81.2 & 76.7 \\
-		\textsc{distill expert} ($\alpha$=0.9) & 81.4 & 77.0 \\		
-		\textsc{distill explore} & 82.2 & 77.9 \\
+		Ensemble (20) & 83.5 & 79.4 \\
+		\textsc{distill expert} ($\alpha$=1.0) & 82.2 & 78.0 \\
+		\textsc{distill expert} ($\alpha$=0.9) & 82.4 & 78.1 \\		
+		\textsc{distill explore} & 82.5 & 78.4 \\
 		\hline

### 2017-11-09 graphics/alpha.r

@@ -1,19 +1,20 @@
 library("ggplot2")
 
 lines1 <- "alpha,las
-1.0,76.81
-0.9,76.85
-0.8,76.24
-0.7,76.28
-0.6,76.03
-0.5,76.37
-0.4,76.15
-0.3,76.00
-0.2,74.98
-0.1,75.11
-0.0,74.74"
+1.0,78.0
+0.9,78.1
+0.8,77.6
+0.7,77.4
+0.6,77.4
+0.5,76.6
+0.4,77.1
+0.3,76.3
+0.2,76.2
+0.1,75.7
+0.0,75.8"
 
 result1 <- read.table(text=lines1, sep=",", header=TRUE)
+print(result1)
 names(result1) <- c("alpha", "las")
 
 #result1 <- melt(result1, id=c("alpha"))
@@ -24,10 +25,10 @@ names(result1) <- c("alpha", "las")
 p1 <- ggplot(result1, aes(x=alpha, y=las, label=las)) +
     geom_line() +
     geom_point() +
-    geom_text(vjust=-1) +
+    geom_text(vjust=-1, size=5) +
     scale_x_continuous(breaks=result1$alpha) + 
-    ylim(NA, 77.5) +
-    theme_bw()
+    ylim(NA, 78.3) +
+    theme_bw(base_size=18)
 
 # extract gtable
 #g1 <- ggplot_gtable(ggplot_build(p1))

### 2017-11-11 paper.tex
add kong and dozat's parsing comparsion and final result.

@@
 method to distill an ensemble of 20 parsers into a single one. Our
-method achieve an improvement of 2.3 in LAS over the baseline.
+parser achieves an improvement of 2.3 in LAS over the baseline
+and outperforms other state-of-the-art parsers.
 \end{abstract}
@@
 distilling parser. Experimental results show an improvement of more
-than 3 points in LAS over baseline parser can be achieved with our
-distillation method.
+than 2.3 points in LAS over baseline parser can be achieved with our
+distillation method and it outperforms other state-of-the-art parsers.
 
@@
 tokenization, part-of-speech tagging, and dependencies annotation.
+We also characterize the difficulties of creating such annotation.
 
@@
 universal dependencies (\S\ref{sec:parsing}). We propose a new distillation
-method in training the parser in our pipeline which achieve 3 points improvement
-without sacrificing efficiency.
+method in training the parser in our pipeline which achieve 2.3 points improvement
+without sacrificing efficiency and outperform other state-of-the-art parsers
+in our comparison.
 \end{itemize}
@@
   example, make clear whether it's ``real'' or contrived.}
-
+\yjcomment{I've add the source of our example in the figure caption.}
 \section{Annotation}\label{sec:anno}
 
+In this section, we first review {\sc Tweebank v1} of \citet{kong-EtAl:2014:EMNLP2014},
+which is the largest twitter dependencies annotation in previous literals (\S\ref{sec:tweebank}).
+Then we introduce the difference in our part-of-speech (re)annotation with 
+\citet{gimpel-EtAl:2011:ACL-HLT2011} which {\sc Tweebank v1} was built 
+on (\S\ref{sec:pos-anno}). Then, we move to our efford of adopting the
+UD convention to cover tweets specific constructions. At last, we describ
+our process of creating new tweet treebank and characterize
+the difficulties in reaching consistent annotations.
 \nascomment{need to introduce this section and explain the structure.}
-
-\subsection{Background: \textsc{Tweebank}}
+\yjcomment{done.}
+
+\subsection{Background: \textsc{Tweebank}}\label{sec:tweebank}
 
@@
 In some cases, conflicts arose between the UD English 
-treebank conventions (UD\_English)
+treebank conventions \cite[UD\_English]{Marneffe2014UniversalSD}
 \footnote{\url{https://github.com/UniversalDependencies/UD_English}}
-\nascomment{add cite}
 and the conventions of \newcite{gimpel-EtAl:2011:ACL-HLT2011} and
@@
 \end{table}
-The major characteristic that distinguishes tweets from standard texts is that
-there are large proportion of tokens that don't carry any syntactic function.
-In our annotation, there are five types of non-syntactic tokens: 
-sentiment emoticons, retweet markers, topical hashtags, referential URLs, and
-truncated words. Figure \ref{fig:non-syn-toks} illustrates examples of
-these non-syntactic tokens.  As discussed above, these are generally
-tagged with the \emph{other} (\texttt{X}) part of speech, except
-emoticons, which are tagged as \emph{symbol} (\texttt{SYM}).  In our annotation, 
-7.5\% of all tokens are non-syntactic; detailed statistics can be found in Table \ref{tbl:non-synt-prop}.
-
-It is important to note that these types may, in some
-contexts, have syntactic functions.
-For example, besides being a discourse marker, \emph{RT} can
-abbreviate the verb {\tt retweet}, and emoticons and hashtags may be
-used as content words within a sentence; see  Figure
-\ref{fig:informal-toks}.  Therefore, the criteria for annotating a
-token as non-syntactic must be context-dependent.
-%To our knowledge, this issue has not previously been addressed in UD
-%annotation efforts \nascomment{check!}\yjcomment{it's not safe to claim that.}.
-
-Inspired by the way UD deals with \emph{punctuation} (which is
-canonically non-syntactic), we adopt the following
-conventions:
-\begin{itemize}
-\item If a non-syntactic token is within a sentence that has a clear predicate, it will be attached to this predicate;
-\item If the whole sentence is made of a sequence of non-syntactic tokens, we attach all these tokens to the first one;
-%\item In parataxis case, when it is difficult to decide which sentence or phrase x should belong to, we always attach x to the previous predicate of the paratactic clause or phrase;
-\item non-syntactic tokens are mostly labeled as {\it discourse}, but
-  URLs are always labeled as {\it list}, following the UD\_English dataset.
-\end{itemize}
-
-% \subsubsection{Token Level}
-% \paragraph{Informal Syntactic Tokens.}
-% Informal tokens like phrase abbreviation (like {\tt mfw}: my face when, {\tt rn}: right now, and etc.) and orthographic variants (like {\tt sooo cooool}) have drawn much attention in previous literals \cite{finin-EtAl:2010:MTURK,eisenstein:2013:NAACL-HLT} \yjcomment{not sure orthographic variants is a good name, need reference.}
-% However, in the sense of syntactic functions, they work in the same way as the ordinary words, which makes them requires less specialty in designing annotation conventions.
-% %Syntactic tokens are just like normal tokens in the standard text.
-% %They always have syntactic functions in tweets.
-% %They could be orthographic variants or abbreviations that represents a phrase.
-
-% \paragraph{Non-syntactic Tokens.}
 
@@
 
+The major characteristic that distinguishes tweets from standard texts is that
+there are large proportion of tokens that don't carry any syntactic function.
+In our annotation, there are five types of non-syntactic tokens: 
+sentiment emoticons, retweet markers, topical hashtags, referential URLs, and
+truncated words. Figure \ref{fig:non-syn-toks} illustrates examples of
+these non-syntactic tokens.  As discussed above, these are generally
+tagged with the \emph{other} (\texttt{X}) part of speech, except
+emoticons, which are tagged as \emph{symbol} (\texttt{SYM}).  In our annotation, 
+7.5\% of all tokens are non-syntactic; detailed statistics can be found in Table \ref{tbl:non-synt-prop}.
+
+It is important to note that these types may, in some
+contexts, have syntactic functions.
+For example, besides being a discourse marker, \emph{RT} can
+abbreviate the verb {\tt retweet}, and emoticons and hashtags may be
+used as content words within a sentence; see  Figure
+\ref{fig:informal-toks}.  Therefore, the criteria for annotating a
+token as non-syntactic must be context-dependent.
+%To our knowledge, this issue has not previously been addressed in UD
+%annotation efforts \nascomment{check!}\yjcomment{it's not safe to claim that.}.
+
+Inspired by the way UD deals with \emph{punctuation} (which is
+canonically non-syntactic), we adopt the following
+conventions:
+\begin{itemize}
+\item If a non-syntactic token is within a sentence that has a clear predicate, it will be attached to this predicate;
+\item If the whole sentence is made of a sequence of non-syntactic tokens, we attach all these tokens to the first one;
+%\item In parataxis case, when it is difficult to decide which sentence or phrase x should belong to, we always attach x to the previous predicate of the paratactic clause or phrase;
+\item non-syntactic tokens are mostly labeled as {\it discourse}, but
+  URLs are always labeled as {\it list}, following the UD\_English dataset.
+\end{itemize}
+
+% \subsubsection{Token Level}
+% \paragraph{Informal Syntactic Tokens.}
+% Informal tokens like phrase abbreviation (like {\tt mfw}: my face when, {\tt rn}: right now, and etc.) and orthographic variants (like {\tt sooo cooool}) have drawn much attention in previous literals \cite{finin-EtAl:2010:MTURK,eisenstein:2013:NAACL-HLT} \yjcomment{not sure orthographic variants is a good name, need reference.}
+% However, in the sense of syntactic functions, they work in the same way as the ordinary words, which makes them requires less specialty in designing annotation conventions.
+% %Syntactic tokens are just like normal tokens in the standard text.
+% %They always have syntactic functions in tweets.
+% %They could be orthographic variants or abbreviations that represents a phrase.
+
+% \paragraph{Non-syntactic Tokens.}
+
 % Besides the informal but syntactic tokens, there are a large collection of tokens that cannot be handled by the syntactic theory designed for standard text.
@@
 of this paper manually corrected the parsed data. \nascomment{this is
-  a little weird:  don't you have to do this before you parse?} Finally, an extra
+  a little weird:  don't you have to do this before you parse?}\yjcomment{we were actually correcting the auto-analyzed 2,500 tweets.} Finally, an extra
 layer of word-level normalization was manually annotated for data
@@
   systems, here and under tokenization?  will reviewers want to know details?}
+\yjcomment{I add figure to illustrat our model.}
 
@@
 		\hline
+		\citet{kong-EtAl:2014:EMNLP2014} &81.6 & 77.2 \\
+		\citet{DBLP:journals/corr/DozatM16} & 81.9 &  77.7 \\
+		\hdashline
+%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
 		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.4 & 75.8 \\
-%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
 		Ensemble (20) & 83.5 & 79.4 \\
@@
 		\hline
+		\newcite{kuncoro-16} & 94.3 & 92.1 \\
+		\citet{DBLP:journals/corr/DozatM16} & 95.7 & 94.1 \\
+		\hdashline
 		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 93.0 & 90.9 \\		
@@
 		\hline
-		\newcite{kuncoro-16} & 94.3 & 92.1 \\
-		\hline
 	\end{tabular}
@@
 
-Our final parsing experiments are shown in Table \ref{tbl:parse-result},
-in which we can see that \textsc{distill explore} significant
-outperforms \textsc{distill expert}, gaining one more point in LAS improvement.
-Additional experiments on the Penn Treebank were performed following
+Our final parsing experiments are shown in Table \ref{tbl:parse-result}.
+We also compare our model with the {\sc TweeboParser} 
+of \citet{kong-EtAl:2014:EMNLP2014} and the state-of-the-art parser
+ \cite{DBLP:journals/corr/DozatM16} in CoNLL 2017.
+Both the compared systems are re-trained on the same data as our system.
+From Table \ref{tbl:parse-result}, our baseline system is 1.9 point behind the
+state-of-the-art parsing systems. However, through distilling, our baseline
+parser catched up and outperform that of \citet{DBLP:journals/corr/DozatM16} and 
+\textsc{distill explore} further outperforms \textsc{distill expert}, gaining 0.4
+point in LAS improvement. We attribute the improvements of \textsc{distill explore} over
+\textsc{distill expert} to the former's exploration of 
+ensemble-sanctioned parser states of different qualities.
+
+We also perform additional experiments on the Penn Treebank were performed following
 the setting of \newcite{dyer-EtAl:2015:ACL-IJCNLP};
@@
 performance close to that of the graph-based parser of \citet{kuncoro-16}.
-We attribute the improvements of \textsc{distill explore} over
-\textsc{distill expert} to the former's exploration of
-ensemble-sanctioned parser states
-of different qualities.
+However, our model is still way behind \citet{DBLP:journals/corr/DozatM16}.
+We address this to the intrastic differences between transition-based and graph-based
+parsing algorithm.
 
 \subsection{Final Evaluation}
-Finally, we evaluate our full pipeline.
-
-\section{Related Work}
+\begin{table}[t]
+	\centering
+	\begin{tabular}{rc}
+		\hline
+		\it Pipeline & F-score \\
+		\hline
+		Tokenization & 98.3 \\		
+		POS tagging & 93.7 \\
+		Dependencies & 74.1 \\
+		\hline
+	\end{tabular}
+	\caption{Evaluating our model in pipeline manner.}\label{tbl:pipline}
+\end{table}
+
+Finally, we evaluate the problem of parsing tweets into UD in a pipeline manner.
+The results are shown in Table \ref{tbl:pipline}. From this result, we can see
+that in the whole pipeline, every component plays an important role. Without
+gold segmentation, the parsing performance drops more than 4 points.
+
+%\section{Related Work}
 %\yjcomment{related word is not finished.}
@@
 \section{Conclusion}
+In this paper, we study the problem of parsing tweets into universal dependencies.
+We adopt the UD guidelines to cover 
+special constructions in tweets and create
+the {\sc Tweebank v2} which has 55,607 tokens. We characterize the disagreements
+among our annotations and show that it is challenging to deliver
+consistent annotation due to the ambiguities in ways of
+understanding and explaining the tweets. On this new treebank,
+we build a pipeline system to parse tweets into UD. We 
+propose a new method to distill an ensemble of 20 parsers into a single one
+to conquer the annotation noise without sacrificing efficiency.
+Our parser achieves an improvement of 2.3 in LAS over the baseline
+and outperforms other state-of-the-art parsers.
 

### 2017-11-13 paper.tex
mention 280 char limit, minor change in abstract

@@
 \newcommand{\nascomment}[1]{\textcolor{blue}{[#1 ---\textsc{nas}]}}
+\newcommand{\yicomment}[1]{\textcolor{red}{[#1 ---\textsc{nas}]}}
 
@@
 special constructions in tweets. Under such guidelines, we create
-a new tweet treebank which has 55,607 tokens and it's more than 4 times
-larger than the {\sc Tweebank v1}. We characterize the disagreements
+a new tweet treebank ({\sc Tweebank v2}), which has 55,607 tokens with labelled attachements. 
+It is more than 4 times larger than the unlabelled {\sc Tweebank v1} \citep{kong-EtAl:2014:EMNLP2014}. We characterize the disagreements
 among our annotation and show that it is challenging to deliver
@@
 understanding and explaining the tweets. Over the new treebank,
-we build a pipeline system to parse tweets into UD. To conquer the
+we build a pipeline system to parse raw tweets into UD. To conquer the
 annotation noise without sacrificing efficiency, we propose a new
@@
 sentiment emoticons, retweet markers, topical hashtags, referential URLs, and
-truncated words. Figure \ref{fig:non-syn-toks} illustrates examples of
+truncated words \footnote{Tweets we analyze have 140 character limits.
+Although Twitter has now doubled the tweet limit to 280 characters, we believe this type of tokens will still remain.}.
+Figure \ref{fig:non-syn-toks} illustrates examples of
 these non-syntactic tokens.  As discussed above, these are generally
@@
 emoticons, which are tagged as \emph{symbol} (\texttt{SYM}).  In our annotation, 
-7.5\% of all tokens are non-syntactic; detailed statistics can be found in Table \ref{tbl:non-synt-prop}.
+7.5\% of all tokens are non-syntactic; detailed statistics can be found in Table \ref{tbl:non-synt-prop}\footnote{The statistics are obtained on 140 character limit tweets.}.
 

### 2017-11-26 paper.tex
add tokenization section

@@
 \newcommand{\nascomment}[1]{\textcolor{blue}{[#1 ---\textsc{nas}]}}
-\newcommand{\yicomment}[1]{\textcolor{red}{[#1 ---\textsc{nas}]}}
+\newcommand{\yicomment}[1]{\textcolor{green}{[#1 ---\textsc{Yi}]}}
 
@@
 special constructions in tweets. Under such guidelines, we create
-a new tweet treebank ({\sc Tweebank v2}), which has 55,607 tokens with labelled attachements. 
-It is more than 4 times larger than the unlabelled {\sc Tweebank v1} \citep{kong-EtAl:2014:EMNLP2014}. We characterize the disagreements
+a new tweet treebank ({\sc Tweebank v2}), which has 55,607 tokens with labelled attachments.\yicomment{labelled attachments}
+It is more than 4 times larger than the unlabelled {\sc Tweebank v1} \citep{kong-EtAl:2014:EMNLP2014}. \yicomment{unlabelled attachments for the original Tweebank}
+We characterize the disagreements
 among our annotation and show that it is challenging to deliver
@@
 \citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
-annotating tweets and presented a tweets treebank ({\sc Tweebank})
+annotating tweets and presented a tweet treebank ({\sc Tweebank})
 which has 12,149 tokens and largely followed the conventions
 suggested by \citet{schneider-EtAl:2013:LAW7-ID} that are close to 
-\citet{Yamada03statisticaldependency} dependencies. Both these
-annotation efforts were highly influenced by the PTB whose guideline
+\citet{Yamada03statisticaldependency} dependencies. 
+Both annotation efforts were highly influenced by the PTB, whose guideline
 has a good grammatical coverage on newswire. However, when it comes
@@
 the syntax of tweets can benefit from such adaptability. In this paper,
-we create a new tweets treebank of 55,607 tokens by following the UD
-guidelines but also contending the domain-specific challenges which wasn't
+we create a new tweet treebank of 55,607 tokens by following the UD
+guidelines but also contending the domain-specific challenges which were not
 covered by UD guidelines. Our annotation includes a whole pipeline of
@@
 transition sequence in the sense of training a transition-based
-distilling parser. Experimental results show an improvement of more
+distilling parser. Experimental results show that an improvement of more
 than 2.3 points in LAS over baseline parser can be achieved with our
@@
 \begin{itemize}
-\item We study the challenges of annotating tweets in UD (\S\ref{sec:anno})
-and create a new tweet treebank ({\sc Tweebank v2}), which includes 
+\item We studied the challenges of annotating tweets in UD (\S\ref{sec:anno})
+and created a new tweet treebank ({\sc Tweebank v2}), which includes 
 tokenization, part-of-speech tagging, and dependencies annotation.
-We also characterize the difficulties of creating such annotation.
+We also characterized the difficulties of creating such annotation.
 
 \item We built up a whole pipeline to parse the raw tweet text into
-universal dependencies (\S\ref{sec:parsing}). We propose a new distillation
-method in training the parser in our pipeline which achieve 2.3 points improvement
-without sacrificing efficiency and outperform other state-of-the-art parsers
-in our comparison.
+universal dependencies (\S\ref{sec:parsing}). We proposed a new distillation
+method in training the parser in our pipeline which achieve 2.3 points improvement in LAS
+without sacrificing efficiency and outperformed other state-of-the-art parsers
+in our comparison. \yicomment{change verbs to past tense}
 \end{itemize}
@@
 \section{Annotation}\label{sec:anno}
-
+\yicomment{Maybe we should contrast UD and kong's annotation strategy during each stage, because UD has also annotation guideline for every stage.}
 In this section, we first review {\sc Tweebank v1} of \citet{kong-EtAl:2014:EMNLP2014},
 which is the largest twitter dependencies annotation in previous literals (\S\ref{sec:tweebank}).
-Then we introduce the difference in our part-of-speech (re)annotation with 
-\citet{gimpel-EtAl:2011:ACL-HLT2011} which {\sc Tweebank v1} was built 
-on (\S\ref{sec:pos-anno}). Then, we move to our efford of adopting the
-UD convention to cover tweets specific constructions. At last, we describ
-our process of creating new tweet treebank and characterize
+Then we introduce the difference in our tokenization and part-of-speech (re)annotation with \citet{ICWSM101540} and 
+\citet{gimpel-EtAl:2011:ACL-HLT2011} on which {\sc Tweebank v1} was built (\S\ref{sec:pos-anno}). \yicomment{add tok} 
+Then, we move to our effort of adopting the
+UD conventions to cover tweet specific constructions. 
+At last, we describe our process of creating new tweet treebank and characterize
 the difficulties in reaching consistent annotations.
@@
 contributed a new annotated corpus, \textsc{Tweebank}, consisting of
-929 tweets.  Their annotations added a layer to a portion of the data
-annotated with part-of-speech tags by
+929 tweets.  Their annotations added dependencies to a portion of the data
+annotated with POS tags by 
 \newcite{gimpel-EtAl:2011:ACL-HLT2011} and
-\newcite{owoputi-EtAl:2013:NAACL-HLT}.  They also contributed a system
-for parsing;
-we defer discussion of their parser to \S\ref{sec:parsing}.
-
-Kong et al.'s rapid, small-scale annotation effort was heavily constrained.  It was
+\newcite{owoputi-EtAl:2013:NAACL-HLT} after tokenization \citep{ICWSM101540} \yicomment{add tok}.  
+They also contributed a system for parsing;
+we defer the discussion of their parser to \S\ref{sec:parsing}.
+
+\citet{kong-EtAl:2014:EMNLP2014}'s rapid, small-scale annotation effort was heavily constrained.  It was
 carried out mostly by non-native speakers, in a very short amount of
@@
 
-\subsection{Part-of-Speech Annotation}\label{sec:pos-anno}
+\subsection{Tokenization}\label{sec:tok-anno}
+Our tokenization strategy is in the middle of the strategy of \citet{ICWSM101540} and that of UD. 
+We want to fit Twitter texts better in UD dependencies while preserving the original tweets as much as possible.
+
+\citet{ICWSM101540} preserve most of non-informal tokens including 
+the hashtags, at-mentions, emoticons \& emojis and unicode glyphs. 
+They also treat contractions and acronyms as whole tokens and do not split them.
+UD tokenization\footnote{http://universaldependencies.org/u/overview/tokenization.html\yicomment{is it ok?
+no paper reference but webpage reference}} , in order to serve better dependency annotation, treat each syntactic word as token.
+They take more aggressive strategy, including splitting off clitics from contractions or multi-word expressions ({\it gonna}) and combine several orthographic tokens into a single syntactic word.
+\yicomment{does UD support normalization for acronyms?
+Did not see it from website, need to check.
+related to ``idc''}
+
+We do not touch any non-informal token in tweets and leave them as in the original tweets. 
+Then we mainly follow UD tokenization.
+We tokenize contractions and multi-word expressions into their syntactic components, but do not combine tokens that have been already split in the original tweets back anymore.
+For example, words like {\it gonna} or {\it can't} will be tokenized to {\it gon na} and {\it ca n't}, and parts like {\it Y O} and {\it R E T W E E T} will be not connected back to single words\footnote{Such tokens only accounts for 0.067\%, and we use {\it goeswith} relation to resolve it.}.
+
+\subsection{Part-of-speech Annotation}\label{sec:pos-anno}
 
 Before turning to UD annotations, we (re)annotated the data with 
-part-of-speech, for consistency with other UD efforts,
+POS, for consistency with other UD efforts,
 which adopt the universal POS tagset of \newcite{PETROV12.274}.
@@
 
-Compared to coarse-grained part-of-speech tagging effort of
+Compared to coarse-grained POS tagging effort of
 \newcite{gimpel-EtAl:2011:ACL-HLT2011}, our approach simplifies some
@@
 contractions and possessives, introducing new parts of speech
-instead.\footnote{These tags only accounted for 2.7\% of tokens,
+instead.\footnote{These tags only account for 2.7\% of tokens,
   leading to concerns about data sparseness in tagging and all
@@
 analyze acronym tokens like \emph{idc}
-(abbreviating ``I don't care'') and \emph{rn} (``right now'')?  Should
+(abbreviating ``I don't care'') \yicomment{`idc' should be discussed in tokenization section, and actually it is already implied from POS section that it should be treated as a single word.}
+ and \emph{rn} (``right now'')?  Should
 they be decomposed into their component words, and if so should those
@@
 syntax as a single word without normalization. Their syntactic functions
-are decided according to their context.
+are decided according to their context.\yicomment{again we should also mention UD tokenization, so might be worth adding a tokenization section}
 
@@
 \subsection{\sc Tweebank v2}\label{sec:anno-process}
+\yicomment{I think it should move to another section, just as in Kong's paper.}
 Following the guidelines mentioned above, we create a new annotated Twitter treebank, which we call {\sc Tweebank v2}.
@@
 \subsubsection{Data Collection}
-{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1} (Kong et al., 2014, 840 unique tweets, including training and test set), along with additional 201 tweets sampled from \newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled from the Twitter stream from February 2016 to July 2016.
-The latter data source consists 147.4M English tweets which are filtered by {\it lang} attribute in the tweet JSON and {\it langid.py}\footnote{\url{https://github.com/saffsd/langid.py}} toolkit.
+{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1} (840 unique tweets, 639/201 for training/test set), along with additional 210\yicomment{changed to 210} tweets sampled from \newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled from the Twitter stream from February 2016 to July 2016\footnote{Data downloaded from \url{https://archive.org/}}.
+The latter data source consists of 147.4M English tweets after being filtered by {\it lang} attribute in the tweet JSON and {\it langid.py}\footnote{\url{https://github.com/saffsd/langid.py}} toolkit.
+
 %The tweet source of Tweebank V2 consists of three parts. 
@@
 	\includegraphics[width=\columnwidth,trim={0 0 13cm 3cm},clip]{graphics/bilstm_postagger}
-	\caption{The bi-LSTM postagger model that tags `it s gon na be' as {\tt PRON AUX VERB PART AUX}.}\label{fig:pos-model}
+	\caption{The bi-LSTM POS tagger model that tags `it s gon na be' as {\tt PRON AUX VERB PART AUX}.}\label{fig:pos-model}
+	\yicomment{i'm a little confused by the pic, need discussion}
 \end{figure}

### 2017-11-27 paper.tex
N - worked on intro

@@
 \begin{abstract}
-In this paper, we study the problem of analyzing tweets with
-universal dependencies \citep[UD]{NIVRE16.348}. We extend the UD guidelines to cover
-special constructions in tweets. Under such guidelines, we create
-a new tweet treebank ({\sc Tweebank v2}), which has 55,607 tokens with labelled attachments.\yicomment{labelled attachments}
-It is more than 4 times larger than the unlabelled {\sc Tweebank v1} \citep{kong-EtAl:2014:EMNLP2014}. \yicomment{unlabelled attachments for the original Tweebank}
+We study the problem of analyzing tweets with
+universal dependencies \citep[UD;][]{NIVRE16.348}. We extend the UD guidelines to cover
+special constructions in tweets. Using the extended guidelines, we create
+a new tweet treebank ({\sc Tweebank v2}), which has 55,607 tokens with
+labeled attachments. 
+It is more than four times larger than the (unlabeled) {\sc Tweebank
+  v1} introduced by \citet{kong-EtAl:2014:EMNLP2014}. 
 We characterize the disagreements
 among our annotation and show that it is challenging to deliver
-consistent annotation due to the ambiguities in ways of
-understanding and explaining the tweets. Over the new treebank,
+consistent annotation due to ambiguity in
+understanding and explaining tweets. Using the new treebank,
 we build a pipeline system to parse raw tweets into UD. To conquer the
-annotation noise without sacrificing efficiency, we propose a new
+annotation noise without sacrificing computational efficiency, we propose a new
 method to distill an ensemble of 20 parsers into a single one. Our
-parser achieves an improvement of 2.3 in LAS over the baseline
-and outperforms other state-of-the-art parsers.
+parser achieves an improvement of 2.3 in LAS over \nascomment{which?} the baseline
+and outperforms parsers that are state-of-the-art on other treebanks.
 \end{abstract}
@@
 \section{Introduction}
-Analyzing the syntax of tweets is challenging. The challenges not
-only come from the difficulty of adapting the parser trained on the
-standard text to the Twitter domain, but also comes from creating
-reasonable dataset for training and evaluating tweet parsers. 
-\citet{AAAIW113912} pioneered in this research direction by
-annotating Penn Treebank \citep[PTB]{Marcus93buildinga}
-constituencies to a set of tweets which contains 7,630 tokens. 
-Stanford dependencies were converted afterwards. 
+NLP for social media messages is challenging, both because domain
+adaptation is required, but also because creating annotated datasets
+(e.g., treebanks)
+for training and evaluation is hard. 
+Pioneering work by \citet{AAAIW113912} 
+annotated 7,630 tokens' worth of tweets according to the
+phrase-structure conventions of the Penn Treebank \citep[PTB]{Marcus93buildinga}.
+Stanford dependencies were converted afterwards \nascomment{by who?}. 
 \citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
-annotating tweets and presented a tweet treebank ({\sc Tweebank})
-which has 12,149 tokens and largely followed the conventions
-suggested by \citet{schneider-EtAl:2013:LAW7-ID} that are close to 
-\citet{Yamada03statisticaldependency} dependencies. 
-Both annotation efforts were highly influenced by the PTB, whose guideline
-has a good grammatical coverage on newswire. However, when it comes
-to the noisy and informal user generated text, it's questionable
-whether such good coverage holds.
+annotating tweets and presented a tweet treebank ({\sc Tweebank}),
+consisting of 12,149 tokens and largely following conventions
+suggested by \citet{schneider-EtAl:2013:LAW7-ID}, fairly close to 
+\citet{Yamada03statisticaldependency} dependencies (without labels). 
+Both annotation efforts were highly influenced by the PTB, whose guidelines
+have  good grammatical coverage on newswire. However, when it comes
+to informal, unedited, user-generated text, the guidelines may leave
+many annotation decisions unspecified.
 %Motivation notes:  explain why UD is attractive (and more attractive
@@
 
-Universal dependencies \citep[UD]{NIVRE16.348} was created to deliver
+Universal dependencies \citep[UD]{NIVRE16.348} were introduced to enable
 consistent annotation across different languages. To allow such
-consistency, UD was designed to be adaptive to different genres and languages
-\cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. It's promising that analyzing
+consistency, UD was designed to be adaptable to different genres and languages
+\cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. We propose that analyzing
 the syntax of tweets can benefit from such adaptability. In this paper,
-we create a new tweet treebank of 55,607 tokens by following the UD
-guidelines but also contending the domain-specific challenges which were not
-covered by UD guidelines. Our annotation includes a whole pipeline of
-tokenization, part-of-speech (POS) tags and universal dependencies.
-We characterize the disagreement among our annotations and show that
+we introduce a new tweet treebank of 55,607 tokens that follows the UD
+guidelines, but also contends with social media-specific challenges that were not
+covered by UD guidelines. Our annotation includes 
+tokenization, part-of-speech (POS) tags, and (labeled) universal dependencies.
+We characterize the disagreement among our annotations and find that
 consistent annotation is still challenging to deliver even with
@@
 
-Based on these annotations, we built up a whole pipeline to parse the
-raw tweet text into universal dependencies. Our pipeline includes: a
-bidirectional LSTM (bi-LSTM) tokenizer, a word cluster enhanced POS
-tagger \cite{owoputi-EtAl:2013:NAACL-HLT}, and stack-lstm parser
-with character representation \cite{ballesteros-dyer-smith:2015:EMNLP}.
-
-To conquer the noise in our annotation and achieve better performance
-without sacrificing efficiency, we propose a new method to
+Based on these annotations, we designed a pipeline to parse 
+raw tweets into universal dependencies. Our pipeline includes: a
+bidirectional LSTM (bi-LSTM) tokenizer, a word cluster-enhanced POS
+tagger \citep[following][]{owoputi-EtAl:2013:NAACL-HLT}, and a stack LSTM parser
+with character-based word representations
+\cite{ballesteros-dyer-smith:2015:EMNLP}, which we refer to as our
+``baseline'' parser.
+
+To overcome the noise in our annotated data and achieve better performance
+without sacrificing computational efficiency, we propose a new method to
 train the parser with the distillation 
-\cite{DBLP:journals/corr/HintonVD15} of 20 parsers ensemble.
+\cite{DBLP:journals/corr/HintonVD15} of a 20-parser
+ensemble. \nascomment{return to this and clarify}
 We show that learning from the exploration of the ensemble parser
@@
 distilling parser. Experimental results show that an improvement of more
-than 2.3 points in LAS over baseline parser can be achieved with our
+than 2.3 points in LAS over the baseline parser can be achieved with our
 distillation method and it outperforms other state-of-the-art parsers.
 
-Contribution of this paper includes:
+The contributions of this paper include:
 \begin{itemize}
-\item We studied the challenges of annotating tweets in UD (\S\ref{sec:anno})
+\item We study the challenges of annotating tweets in UD (\S\ref{sec:anno})
 and created a new tweet treebank ({\sc Tweebank v2}), which includes 
-tokenization, part-of-speech tagging, and dependencies annotation.
-We also characterized the difficulties of creating such annotation.
-
-\item We built up a whole pipeline to parse the raw tweet text into
-universal dependencies (\S\ref{sec:parsing}). We proposed a new distillation
-method in training the parser in our pipeline which achieve 2.3 points improvement in LAS
+tokenization, part-of-speech tagging, and labeled universal dependencies annotation.
+We also characterize the difficulties of creating such annotation.
+
+\item We introduce and evaluate a system to parse the raw tweet text into
+universal dependencies (\S\ref{sec:parsing}).  \nascomment{say it
+  performs better than existing systems?}
+\item We propose a new distillation
+method for training the parser in our pipeline,  which achieves 2.3 points improvement in LAS
 without sacrificing efficiency and outperformed other state-of-the-art parsers
-in our comparison. \yicomment{change verbs to past tense}
+in our comparison. \nascomment{clean up, remove redundancies with
+  previous paragraph}
 \end{itemize}
@@
 
-\nascomment{I didn't do anything significant to the intro.  for every
-  example, make clear whether it's ``real'' or contrived.}
 \yjcomment{I've add the source of our example in the figure caption.}

### 2017-11-27 paper.tex
N - worked on sec2

@@
 \yicomment{Maybe we should contrast UD and kong's annotation strategy during each stage, because UD has also annotation guideline for every stage.}
-In this section, we first review {\sc Tweebank v1} of \citet{kong-EtAl:2014:EMNLP2014},
-which is the largest twitter dependencies annotation in previous literals (\S\ref{sec:tweebank}).
-Then we introduce the difference in our tokenization and part-of-speech (re)annotation with \citet{ICWSM101540} and 
-\citet{gimpel-EtAl:2011:ACL-HLT2011} on which {\sc Tweebank v1} was built (\S\ref{sec:pos-anno}). \yicomment{add tok} 
-Then, we move to our effort of adopting the
-UD conventions to cover tweet specific constructions. 
-At last, we describe our process of creating new tweet treebank and characterize
-the difficulties in reaching consistent annotations.
-\nascomment{need to introduce this section and explain the structure.}
-\yjcomment{done.}
+
+We first review {\sc Tweebank v1} of \citet{kong-EtAl:2014:EMNLP2014},
+which is the largest Twitter dependencies annotation
+(\S\ref{sec:tweebank}).
+Then we introduce the differences in our tokenization
+(\S\ref{sec:tok-anno}) and part-of-speech (\S\ref{sec:pos-anno}) (re)annotation with \citet{ICWSM101540} and 
+\citet{gimpel-EtAl:2011:ACL-HLT2011}, respectively, on which {\sc Tweebank v1} was built. 
+We describe our effort of adapting the
+UD conventions to cover tweet-specific constructions (\S\ref{sec:ud-tweet}). 
+Finally, we present our process of creating a new tweet treebank, {\sc
+  Tweebank v2}, and characterize
+the difficulties in reaching consistent annotations (\S\ref{sec:anno-process}).
 
@@
 \newcite{gimpel-EtAl:2011:ACL-HLT2011} and
-\newcite{owoputi-EtAl:2013:NAACL-HLT} after tokenization \citep{ICWSM101540} \yicomment{add tok}.  
-They also contributed a system for parsing;
+\newcite{owoputi-EtAl:2013:NAACL-HLT} after rule-based tokenization \citep{ICWSM101540}.
+Kong et al.~also contributed a system for parsing;
 we defer the discussion of their parser to \S\ref{sec:parsing}.
 
-\citet{kong-EtAl:2014:EMNLP2014}'s rapid, small-scale annotation effort was heavily constrained.  It was
-carried out mostly by non-native speakers, in a very short amount of
+Kong et al.'s rapid, small-scale annotation effort was heavily constrained.  It was
+carried out mostly by nonnative speakers, in a very short amount of
 time (a day).  Driven both by the style of the text they sought to annotate
@@
 \subsection{Tokenization}\label{sec:tok-anno}
-Our tokenization strategy is in the middle of the strategy of \citet{ICWSM101540} and that of UD. 
-We want to fit Twitter texts better in UD dependencies while preserving the original tweets as much as possible.
-
-\citet{ICWSM101540} preserve most of non-informal tokens including 
-the hashtags, at-mentions, emoticons \& emojis and unicode glyphs. 
+Our tokenization strategy lies between the strategy of
+\citet{ICWSM101540} and that of UD.
+There is a significant tradeoff  between preservation of original tweet content and respecting
+the UD guidelines.
+
+The regex-based tokenizer of \citet{ICWSM101540}---which was 
+originally designed for an exploratory search interface called
+TweetMotif, not for NLP---preserves most whitespace-delimited tokens, including 
+hashtags, at-mentions, emoticons,  emojis, and unicode glyphs. 
 They also treat contractions and acronyms as whole tokens and do not split them.
-UD tokenization\footnote{http://universaldependencies.org/u/overview/tokenization.html\yicomment{is it ok?
-no paper reference but webpage reference}} , in order to serve better dependency annotation, treat each syntactic word as token.
-They take more aggressive strategy, including splitting off clitics from contractions or multi-word expressions ({\it gonna}) and combine several orthographic tokens into a single syntactic word.
-\yicomment{does UD support normalization for acronyms?
-Did not see it from website, need to check.
-related to ``idc''}
-
-We do not touch any non-informal token in tweets and leave them as in the original tweets. 
-Then we mainly follow UD tokenization.
-We tokenize contractions and multi-word expressions into their syntactic components, but do not combine tokens that have been already split in the original tweets back anymore.
-For example, words like {\it gonna} or {\it can't} will be tokenized to {\it gon na} and {\it ca n't}, and parts like {\it Y O} and {\it R E T W E E T} will be not connected back to single words\footnote{Such tokens only accounts for 0.067\%, and we use {\it goeswith} relation to resolve it.}.
-
-\subsection{Part-of-speech Annotation}\label{sec:pos-anno}
+UD
+tokenization,\footnote{\url{http://universaldependencies.org/u/overview/tokenization.html}}
+in order to better serve dependency annotation, treats each syntactic word as token.
+They therefore take a more aggressive strategy, including splitting
+clitics from contractions or multiword expressions (e.g., {\it
+  gonna}), and sometimes combining several orthographic tokens into a
+single syntactic word. \yicomment{does UD support normalization for
+  acronyms? Did not see it from website, need to check. related to
+  ``idc''} \nascomment{unless we make a change, I think we need to say
+  here that acronyms like \emph{idc} are left as a single token}
+
+In our manual tokenization, we do not modify any non-informal \nascomment{is this defined?} token in tweets and leave them as in the original tweets. 
+Then we mainly follow UD tokenization. We tokenize contractions and
+multiword expressions into their syntactic components, but do not
+combine tokens that appear as split in the original tweet.
+For example, words like {\it gonna} or {\it can't} will be tokenized
+to {\it gon na} and {\it ca n't}, and sequences like {\it Y O} and
+{\it R E T W E E T} will be not combined back into single
+words.\footnote{Such tokens only account for 0.067\%; we use the UD
+  {\it goeswith} relation to resolve these cases in the syntax.}
+
+\subsection{Part-of-Speech Annotation}\label{sec:pos-anno}
 
@@
 For twitter specific linguistic phenomena, we have set different strategies and try to align with the UD conventions and UD\textunderscore English as close as possible.\footnote{\url{https://github.com/UniversalDependencies/UD\_English}}
-
 In some cases, conflicts arose between the UD English 
-treebank conventions \cite[UD\_English]{Marneffe2014UniversalSD}
-\footnote{\url{https://github.com/UniversalDependencies/UD_English}}
+treebank conventions \cite[][UD\_English]{Marneffe2014UniversalSD}\footnote{\url{https://github.com/UniversalDependencies/UD_English}}
 and the conventions of \newcite{gimpel-EtAl:2011:ACL-HLT2011} and
@@
 conformed to UD, enabling consistency (e.g., when we exploit the
-existing UD English treebank in our parser for tweets, \S\ref{sec:parsing}).  For example,  
+existing UD\_English treebank in our parser for tweets, \S\ref{sec:parsing}).  For example,  
 the nominal URL in Figure \ref{fig:informal-toks} is tagged as {\it
@@
 
-Compared to coarse-grained POS tagging effort of
+Compared to the coarse-grained POS tagging effort of
 \newcite{gimpel-EtAl:2011:ACL-HLT2011}, our approach simplifies some
@@
 
-Another important difference is in tokenization.  UD calls for more
+Another important difference follows from the difference in
+tokenization.  As discussed above, UD calls for more
 aggressive tokenization than that used by
-\newcite{gimpel-EtAl:2011:ACL-HLT2011}, which followed the rule-based
-system  introduced by 
-\newcite{ICWSM101540}.  In particular, they opted out of tokenizing
+\newcite{gimpel-EtAl:2011:ACL-HLT2011}.  In particular, Gimpel et al.~opted out of tokenizing
 contractions and possessives, introducing new parts of speech
@@
 
-\subsection{Universal Dependencies Applied to Tweets}
+\subsection{Universal Dependencies Applied to Tweets} \label{sec:ud-tweet}
 
@@
 key questions that arose in our annotation effort, and how we resolved them.
-
-\nascomment{for each thing we talk about here, might be nice to
-  quantify it in our annotated corpus}
 
@@
 \citet{eisenstein:2013:NAACL-HLT} studied the necessity of normalization
-in social media text and pointed that such normalization is problematic.
+in social media text and argued that such normalization is problematic.
 Our solution to the syntax of abbreviations follows the spirit of his argument. Because abbreviations which clearly carry
@@
 dataset, we believe that normalization is an unnecessarily complicated step.
-\nascomment{maybe we owe citations to
-  \cite{finin-EtAl:2010:MTURK,eisenstein:2013:NAACL-HLT} here?  maybe
-  better papers to cite}
+% \nascomment{maybe we owe citations to
+%   \cite{finin-EtAl:2010:MTURK,eisenstein:2013:NAACL-HLT} here?  maybe
+%   better papers to cite}
 
@@
 \end{tabular}
-\caption{Proportion of non-syntactic tokens in the annotation.}\label{tbl:non-synt-prop}
+\caption{Proportions of non-syntactic tokens in our annotation.
+These  statistics are obtained on 140 character-limited tweets. \label{tbl:non-synt-prop}}
 \end{table}
@@
 	\caption{An example tweet with informal but syntactic tokens.
-		This is an artificial tweets inspired by several tweets.}\label{fig:informal-toks}
+		This is a contrived example inspired by several tweets.}\label{fig:informal-toks}
 \end{figure*}
@@
 The major characteristic that distinguishes tweets from standard texts is that
-there are large proportion of tokens that don't carry any syntactic function.
+a large proportion of tokens don't carry any syntactic function.
 In our annotation, there are five types of non-syntactic tokens: 
 sentiment emoticons, retweet markers, topical hashtags, referential URLs, and
-truncated words \footnote{Tweets we analyze have 140 character limits.
-Although Twitter has now doubled the tweet limit to 280 characters, we believe this type of tokens will still remain.}.
-Figure \ref{fig:non-syn-toks} illustrates examples of
+truncated words.\footnote{The tweets we analyze have at most 140
+  characters. Although Twitter has doubled the tweet length limit to
+  280 characters since our analysis, we believe this type of token
+  will still remain.}  Figure \ref{fig:non-syn-toks} illustrates examples of
 these non-syntactic tokens.  As discussed above, these are generally
@@
 emoticons, which are tagged as \emph{symbol} (\texttt{SYM}).  In our annotation, 
-7.5\% of all tokens are non-syntactic; detailed statistics can be found in Table \ref{tbl:non-synt-prop}\footnote{The statistics are obtained on 140 character limit tweets.}.
+7.5\% of all tokens are non-syntactic; detailed statistics can be found in Table \ref{tbl:non-synt-prop}.
 
@@
 %\item In parataxis case, when it is difficult to decide which sentence or phrase x should belong to, we always attach x to the previous predicate of the paratactic clause or phrase;
-\item non-syntactic tokens are mostly labeled as {\it discourse}, but
+\item Non-syntactic tokens are mostly labeled as {\it discourse}, but
   URLs are always labeled as {\it list}, following the UD\_English dataset.
@@
 we include non-syntactic tokens in our annotation following the
-convention above. Compared with \citet{kong-EtAl:2014:EMNLP2014},
+conventions above. Compared with \citet{kong-EtAl:2014:EMNLP2014},
 we also gave a clear definition of non-syntactic tokens, which helped
@@
 \subsection{\sc Tweebank v2}\label{sec:anno-process}
-\yicomment{I think it should move to another section, just as in Kong's paper.}
-Following the guidelines mentioned above, we create a new annotated Twitter treebank, which we call {\sc Tweebank v2}.
+Following the guidelines presented above, we create a new annotated Twitter treebank, which we call {\sc Tweebank v2}.
 
 \subsubsection{Data Collection}
-{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1} (840 unique tweets, 639/201 for training/test set), along with additional 210\yicomment{changed to 210} tweets sampled from \newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled from the Twitter stream from February 2016 to July 2016\footnote{Data downloaded from \url{https://archive.org/}}.
-The latter data source consists of 147.4M English tweets after being filtered by {\it lang} attribute in the tweet JSON and {\it langid.py}\footnote{\url{https://github.com/saffsd/langid.py}} toolkit.
+{\sc Tweebank v2} is built on the original data of {\sc Tweebank v1}
+(840 unique tweets, 639/201 for training/test set), along with an 
+additional 210 tweets sampled from the POS-tagged dataset of \newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled from the Twitter stream from February 2016 to July 2016.\footnote{Data downloaded from \url{https://archive.org/}.}
+The latter data source consists of 147.4M English tweets after being
+filtered by the {\it lang} attribute in the tweet JSON and {\it
+  langid.py} toolkit.\footnote{\url{https://github.com/saffsd/langid.py}}
 
@@
 annotation conventions and our guidelines.
-Both the guidelines and annotation
+Both the guidelines and annotations
 were further refined by the authors of this paper to increase
-the coverage of our guideline and solve inconsistency between
+the coverage of our guidelines and solve inconsistencies between
 different annotators during this exercise. In the second stage, a POS tagger and
@@
 and used to automatically analyze the sampled 2,500 tweets.  Authors 
-of this paper manually corrected the parsed data. \nascomment{this is
-  a little weird:  don't you have to do this before you parse?}\yjcomment{we were actually correcting the auto-analyzed 2,500 tweets.} Finally, an extra
+of this paper manually corrected the parsed data. Finally, an extra
 layer of word-level normalization was manually annotated for data
@@
 whether this is an example of an empty auxiliary verb, or a clause-modified
-noun, both annotations are reasonable.
+noun, either annotation is plausible.
 

### 2017-11-27 paper.tex
Noah done for now

@@
 method to distill an ensemble of 20 parsers into a single one. Our
-parser achieves an improvement of 2.3 in LAS over \nascomment{which?} the baseline
+parser achieves an improvement of 2.3 in LAS over \nascomment{which
+  comparison is this?} the baseline
 and outperforms parsers that are state-of-the-art on other treebanks.
@@
 To overcome the noise in our annotated data and achieve better performance
-without sacrificing computational efficiency, we propose a new method to
-train the parser with the distillation 
-\cite{DBLP:journals/corr/HintonVD15} of a 20-parser
-ensemble. \nascomment{return to this and clarify}
-We show that learning from the exploration of the ensemble parser
-can be more beneficial than just learning from the gold standard
-transition sequence in the sense of training a transition-based
-distilling parser. Experimental results show that an improvement of more
-than 2.3 points in LAS over the baseline parser can be achieved with our
-distillation method and it outperforms other state-of-the-art parsers.
+without sacrificing computational efficiency, we 
+distill a 20-parser ensemble into a single greedy  parser 
+\cite{DBLP:journals/corr/HintonVD15}.
+We show further  that learning directly from the exploration of the ensemble parser
+is more beneficial than learning from the gold standard ``oracle''
+transition sequence. Experimental results show that an improvement of more
+than 2.3 points \nascomment{again, not sure what this is quoting} in LAS over the baseline parser can be achieved with our
+distillation method and that it outperforms other state-of-the-art parsers.
 
@@
 \item We propose a new distillation
-method for training the parser in our pipeline,  which achieves 2.3 points improvement in LAS
-without sacrificing efficiency and outperformed other state-of-the-art parsers
-in our comparison. \nascomment{clean up, remove redundancies with
-  previous paragraph}
+method for training a greedy parser, leading to better performance
+than existing methods and without efficiency sacrifices.
 \end{itemize}
@@
 
-\yjcomment{I've add the source of our example in the figure caption.}
 \section{Annotation}\label{sec:anno}
@@
 decisions; for example,
-the asterisk (*) in {\it 4*3} is a separate token signifying
-multiplication, but for the asterisk (*) in {\it sh*t}
-works as a mask for censorship and should not be segmented.
+the asterisk in {\it 4*3} is a separate token signifying
+multiplication, but for the asterisk in {\it sh*t}
+works as a mask to evoke censorship and should not be segmented.
 
@@
 	\centering
-	\begin{tabular}{rc}
+	\begin{tabular}{lr}
 		\hline
@@
 % 		UD pipe v1.2 & 94.7 \\
-		UD pipe v1.2 (same training data) & 97.3 \\
-		Our bi-LSTM tokenizer & \bf 98.3 \\
+		UD pipe v1.2 & 97.3 \\
+	 	our bi-LSTM tokenizer & \bf 98.3 \\
 		\hline
@@
 tokenization results, compared to  other available tokenizers. 
-The Stanford \cite{manning-EtAl:2014:P14-5} and Twokenizer
+ Stanford CoreNLP \cite{manning-EtAl:2014:P14-5} and Twokenizer
 \cite{ICWSM101540} systems are rule-based systems and were not adapted
@@
 \cite{straka-strakova:2017:K17-3} model was re-trained on the same
-data as our system.
+data as our system. \nascomment{we need to say what their model was;
+  why does ours work better?  from their paper, it seems that they
+  used a GRU instead of an LSTM ... is that all?  do we win because of
+better tuning, or what?}
 Our bi-LSTM tokenizer achieves the best accuracy among all these
@@
 All systems were re-trained on the combination of the UD\_English and 
-\textsc{Tweebank v2} training sets. We use the twitter specific glove embedding released by
-\citet{pennington-socher-manning:2014:EMNLP2014} as the word embeeding in all the neural tagger
-and parser\footnote{\url{http://nlp.stanford.edu/data/glove.twitter.27B.zip}}.
-
-\nascomment{I wonder if we ought to give more detail about our biLSTM
-  systems, here and under tokenization?  will reviewers want to know details?}
-\yjcomment{I add figure to illustrat our model.}
+\textsc{Tweebank v2} training sets. We use Twitter-specific glove embeddings released by
+\citet{pennington-socher-manning:2014:EMNLP2014} in all neural taggers
+and parsers.\footnote{\url{http://nlp.stanford.edu/data/glove.twitter.27B.zip}}
 
@@
 
-We tested the POS taggers on \textsc{Tweebank v2} test set.  Results
+We tested the POS taggers on the \textsc{Tweebank v2} test set.  Results
 with gold-standard tokenization are shown in
@@
 Social media applications typically require processing large volumes
-of data, making speed an important criterion. We therefore 
-use the neural greedy parser introduced by \newcite{ballesteros-EtAl:2016:EMNLP2016},
+of data, making speed an important desideratum. We therefore 
+begin with the neural greedy stack LSTM parser introduced by \newcite{ballesteros-EtAl:2016:EMNLP2016},
 which can parse a sentence in linear time and harnesses 
@@
 
-Section \ref{sec:anno-process} shows that severe ambiguities
-exist when we create {\sc Tweebank v2}, which makes the training data
-of the parser very noisy. \citet{Frnay2014ClassificationIT} suggested
-that most of losses are shown to be not robust to 
-classification noise, including the log-likelihood loss used in
-\citet{ballesteros-dyer-smith:2015:EMNLP}. To conquer the noisy
-data and further improve the parsing accuracy, we followed the
-empirical study of \citet{Dietterich2000} and ensemble of 20 differently
-initialized parsers. To make it still parses in linear time, we
-propose a new method to distill the ensemble of 20 parsers into one parser.
-To our knowledge, this is the first attempt to distill an
-ensemble of greedy transition-based
-parsers.% \nascomment{check}.
-
-Distilling a simple and fast {\it student model} from the accurate but
-slow {\it teacher model} was explored by \newcite{DBLP:journals/corr/HintonVD15}
-and \newcite{kim-rush:2016:EMNLP2016}. In their works, the predicted
-distribution from the teacher model serves as a soft target for
-training the student model by minimizing
-\begin{equation}
-\mathcal{L}_{\mathit{KD}} = \sum_k q(y=k\mid x) p(y=k\mid x)
-\end{equation} where $q(y=k\mid x)$ is the probability distribution
-predicted by the teacher model. Training the parameters of the student model ($p$) is
-accomplished by interpolating between two losses:
-\begin{equation}\label{eq:distill}
-\mathcal{L}=(1-\alpha)\mathcal{L}_{\mathit{NNL}} + \alpha\mathcal{L}_{\mathit{KD}}
-\end{equation}
-where $\mathcal{L}_{\mathit{NNL}}$ is the negative log-likelihood loss.
-
-\newcite{kuncoro-16} were inspired by the distillation idea and
-proposed to incorporate the knowledge from an ensemble of 20 greedy transition-based
-parsers into one single \emph{graph-based} parser by adapting the soft
-target into a structured loss. However, as \newcite{kuncoro-16}
-pointed out, it is not straightforward to incorporate the structure
-loss into a \emph{transition-based} parser. Considering the efficiency
-advantage of greedy transition-based parsers over their graph-based counterparts,
-it is worth considering distillation of an ensemble into a greedy parser.
-
-The generic algorithm for training a transition-based greedy parser
-usually includes 1) generating a sequence of transitions from the 
-training data, called the ``oracle'' and 2) learning the classifier from
-the oracle transitions. One natural adaptation of the distillation will be interpolating
-$\mathcal{L}_{\mathit{NLL}}$ with the distillation objective (Equation \ref{eq:distill})
-in the second step. We name this method \textsc{distill expert}.
-
-\paragraph{Preliminary results.}
 In our preliminary experiments, we train our parser on the combination of UD\_English
@@
 tags are used. Automatic POS tags are assigned with 5-fold
-jackknifing. Hyperparameters, including the value of $\alpha$ in Equation \ref{eq:distill},
+jackknifing. Hyperparameters %, including the value of $\alpha$ in Equation \ref{eq:distill},
 are tuned on the \textsc{Tweebank v2} development set. Unlabeled attachment score and
-labeled attachment score including punctuations are used to evaluate parsing performance.
-
-\citet{reimers-gurevych:2017:EMNLP2017} pointed out that the training process for neural networks are highly
-non-deterministic and largely depends on the seed value for pseduo-random number generator.
-Our preliminary experiments confirm this finding by witnessing a gap of 1 LAS on development set
-between the best (75.8) and worst (74.8) runs. To eliminate the effect of random number, for each
-hyperparameter setting, we conduct 5 runs with different seeds and report the averaged score.
-
-Our 20 parsers are ensembled by averaging their output probability
-distributions over transitions. The ensemble parser achieves a LAS of 79.4, which is more 
-than 3 points higher than the baseline single parser. Distilling from this
-parser leads to a single parser with 78.1 LAS.
-%We first study the necessity of log-likelihood loss (the first term in Equation \ref{eq:distill}).
-
-\paragraph{Effect of $\alpha$.}
-
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=\columnwidth,trim={0.3cm 0 0 0},clip]{graphics/alpha}
-	\caption{The effect of $\alpha$ on \textsc{expert distillation}.}\label{fig:effect-alpha}
-\end{figure}
-
-We further study the effect of the interpolation hyperparameter $\alpha$ by varying it from 0 to 1.
-The results are shown in Figure \ref{fig:effect-alpha}. We can see that distilling parsers with larger $\alpha$ achieves better
-performance, which means the model should pay more attention to learning
-from the teacher model.  Indeed, the negligible difference between the
-best performance at $\alpha = 0.9$ and $\alpha=1.0$ casts doubt on the
-necessity of including $\mathcal{L}_{NNL}$ in the training objective
-at all.% \nascomment{check my rewording}
-
-\paragraph{Learning from exploration.} We further set $\alpha$ to 1.0,
-eliminating the oracle from the usual transition-based parser
-training algorithm.  Instead of generating
-training instances from the oracle, we generate them by random sampling
-transitions from the teacher (ensemble) model's output distribution and follow the
-trajectory of these transitions. We name this method \textsc{distill explore}.
-
-\paragraph{Final results.}
+labeled attachment score (including punctuation) are reported.
+
+\citet{reimers-gurevych:2017:EMNLP2017} and others have
+pointed out that neural network training is 
+nondeterministic and depends on the seed for the random
+number generator.
+Our preliminary experiments confirm this finding, with a gap of 1 LAS on development data
+between the best (75.8) and worst (74.8) runs. To control for this
+effect, we report the average of five differently-seeded runs, for
+each model. \nascomment{please check! we did this for all systems,
+  not just ours, right?}
+
+%%%
+
 \begin{table}[t]
@@
 		\citet{DBLP:journals/corr/DozatM16} & 81.9 &  77.7 \\
-		\hdashline
 %		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
 		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.4 & 75.8 \\
+		\hdashline
 		Ensemble (20) & 83.5 & 79.4 \\
-		\textsc{distill expert} ($\alpha$=1.0) & 82.2 & 78.0 \\
-		\textsc{distill expert} ($\alpha$=0.9) & 82.4 & 78.1 \\		
-		\textsc{distill explore} & 82.5 & 78.4 \\
+		Distillation ($\alpha =1.0$) & 82.2 & 78.0 \\
+		Distillation ($\alpha =0.9$) & 82.4 & 78.1 \\		
+		Distillation with exploration & 82.5 & 78.4 \\
 		\hline
@@
 \end{table}
+
+\paragraph{Initial results.}  The first section of Table~\ref{tbl:parse-result} compares
+the stack LSTM with {\sc TweeboParser} (the system 
+of \citealp{kong-EtAl:2014:EMNLP2014}) and the state-of-the-art parser
+in the CoNLL 2017 evaluations, due to
+ \citet{DBLP:journals/corr/DozatM16}, both of which are graph-based
+ parsers requiring superlinear runtime. \nascomment{can we quantify
+   how much time each one takes, either in tweets parsed per second or
+   seconds per tweet?}
+Both of the comparison systems are re-trained on the same data as our
+system.
+Our system lags behind by nearly two LAS
+points.
+
+\paragraph{Ensemble.}  Due both to ambiguity in the training
+data---which most loss functions are not robust to \citep{Frnay2014ClassificationIT}, including the log loss we use, following
+\citet{ballesteros-dyer-smith:2015:EMNLP}---and due to the instability
+of neural network training, we follow \citet{Dietterich2000} and
+consider an ensemble of twenty parsers trained using different random
+initialization.  To parse at test time, the transition probabilities of the twenty
+members of the ensemble are averaged.  The result achieves LAS of
+79.4, outperforming all three systems above (Table~\ref{tbl:parse-result}).
+
+\paragraph{Distillation.}  The shortcoming of the 20-parser ensemble is, of
+course, that it requires twenty times the runtime of a single greedy
+parser.  \newcite{kuncoro-16} proposed the distillation of 20
+greedy transition-based parser into a single \emph{graph-based}
+parser; they transformed the votes of the ensemble into a structured
+loss function.  However, as Kuncoro et al.~pointed out, 
+it is not straightforward to use a structured
+loss in a \emph{transition-based} parsing algorithm.  Because fast
+runtime is so important for NLP on social media, we
+introduce a new way to distill our greedy ensemble into a single
+transition-based parser (the first such attempt, to our knowledge).
+
+Our approach follows \newcite{DBLP:journals/corr/HintonVD15}
+and \newcite{kim-rush:2016:EMNLP2016}.  
+Note that training a transition-based parser typically involves the
+transformation of the training data into a sequence of ``oracle'' state-action
+pairs.
+Let $q(a \mid s)$ denote the distilled model's
+probability of an action $a$ given parser state $s$; let $p(a \mid s)$ be the probability under the
+ensemble (i.e., the average of the 20 separately-trained ensemble
+members) \nascomment{check}.
+To train the distilled model, we minimize the interpolation between
+their distillation loss and the conventional log loss:
+\begin{align}
+\min_q \quad  & \alpha \sum_i \underbrace{\sum_{a} q(a \mid s_i) \cdot p(a
+  \mid s_i)}_{\text{distillation loss}} \\
+& +\ (1 - \alpha) \sum_i \underbrace{- \log q(a_i \mid
+  s_i)}_{\text{log loss}} \nonumber
+\end{align}
+
+Distilling from this 
+parser leads to a single greedy transition-based parser with 78.1
+LAS---better than past systems but worse than our more expensive ensemble.
+The effect of $\alpha$ is illustrated in
+Figure~\ref{fig:effect-alpha}; generally paying closer attention to
+the ensemble, rather than the conventional log loss objective, leads
+to better performance.
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=\columnwidth,trim={0.3cm 0 0 0},clip]{graphics/alpha}
+	\caption{The effect of $\alpha$ on distillation. \label{fig:effect-alpha}}
+\end{figure}
+
+\paragraph{Learning from exploration.} When we set $\alpha =1$, we
+eliminate the oracle from the estimation procedure (for the distilled
+model).  This presents an opportunity to learn with \emph{exploration}, by
+randomly sampling transitions from the ensemble, found useful
+in recent methods for training greedy models that use dynamic oracles
+\citep{ballesteros-EtAl:2016:EMNLP2016}.  
+We find that this
+approach outperforms the  conventional distillation model, coming in
+only one point behind the ensemble (last line of Table~\ref{tbl:parse-result}).
 
@@
 		Ensemble (20) & 94.5 & 92.6 \\
-		\textsc{distill expert} ($\alpha$=1.0) & 93.8 & 91.7 \\
-		\textsc{distill explore} & 94.1 & 92.0 \\
+		Distillation ($\alpha =1.0$) & 93.8 & 91.7 \\
+		Distillation with exploration  & 94.1 & 92.0 \\
 		\hline
@@
 
-Our final parsing experiments are shown in Table \ref{tbl:parse-result}.
-We also compare our model with the {\sc TweeboParser} 
-of \citet{kong-EtAl:2014:EMNLP2014} and the state-of-the-art parser
- \cite{DBLP:journals/corr/DozatM16} in CoNLL 2017.
-Both the compared systems are re-trained on the same data as our system.
-From Table \ref{tbl:parse-result}, our baseline system is 1.9 point behind the
-state-of-the-art parsing systems. However, through distilling, our baseline
-parser catched up and outperform that of \citet{DBLP:journals/corr/DozatM16} and 
-\textsc{distill explore} further outperforms \textsc{distill expert}, gaining 0.4
-point in LAS improvement. We attribute the improvements of \textsc{distill explore} over
-\textsc{distill expert} to the former's exploration of 
-ensemble-sanctioned parser states of different qualities.
-
-We also perform additional experiments on the Penn Treebank were performed following
-the setting of \newcite{dyer-EtAl:2015:ACL-IJCNLP};
+\nascomment{need to clarify:  is this UD?} We perform additional experiments on the Penn Treebank, following
+the settings of \newcite{dyer-EtAl:2015:ACL-IJCNLP};
 Table~\ref{tbl:parse-result-PTB} shows a similar trend, and we achieve
 performance close to that of the graph-based parser of \citet{kuncoro-16}.
-However, our model is still way behind \citet{DBLP:journals/corr/DozatM16}.
-We address this to the intrastic differences between transition-based and graph-based
-parsing algorithm.
-
-\subsection{Final Evaluation}
+However, this greedy approach still lags behind the very strong
+graph-based system of \citet{DBLP:journals/corr/DozatM16}.
+
 \begin{table}[t]
@@
 		\hline
-		\it Pipeline & F-score \\
+		\it Pipeline & $F_1$\\
 		\hline
@@
 		POS tagging & 93.7 \\
-		Dependencies & 74.1 \\
+		Universal dependencies & 74.1 \\
 		\hline
 	\end{tabular}
-	\caption{Evaluating our model in pipeline manner.}\label{tbl:pipline}
+	\caption{Evaluating our model in pipeline
+          manner. \nascomment{should this be ``F1''?  shouldn't the
+            last line be LAS?}\label{tbl:pipline} }
 \end{table}
 
-Finally, we evaluate the problem of parsing tweets into UD in a pipeline manner.
-The results are shown in Table \ref{tbl:pipline}. From this result, we can see
-that in the whole pipeline, every component plays an important role. Without
-gold segmentation, the parsing performance drops more than 4 points.
+\paragraph{Pipeline evaluation.} Finally, we report  our full
+pipeline's performance in  Table \ref{tbl:pipline}. We see the
+importance of segmentation:  without gold segmentation, UD parsing
+performance drops by more than four points.
 
@@
 \section{Conclusion}
-In this paper, we study the problem of parsing tweets into universal dependencies.
-We adopt the UD guidelines to cover 
+We study the problem of parsing tweets into universal dependencies.
+We adapt the UD guidelines to cover 
 special constructions in tweets and create
-the {\sc Tweebank v2} which has 55,607 tokens. We characterize the disagreements
-among our annotations and show that it is challenging to deliver
-consistent annotation due to the ambiguities in ways of
-understanding and explaining the tweets. On this new treebank,
-we build a pipeline system to parse tweets into UD. We 
-propose a new method to distill an ensemble of 20 parsers into a single one
-to conquer the annotation noise without sacrificing efficiency.
-Our parser achieves an improvement of 2.3 in LAS over the baseline
+the {\sc Tweebank v2}, which has 55,607 tokens. We characterize the disagreements
+among our annotations and argue that inherent ambiguity in this genre
+makes
+consistent annotaiton a challenge.  Using this new treebank,
+we build a pipeline system to parse tweets into UD. We also 
+propose a new method to distill an ensemble of 20 greedy parsers into a single one
+to overcome annotation noise without sacrificing efficiency.
+Our parser achieves an improvement of 2.3  \nascomment{which
+  comparison are you quoting here?} in LAS over a strong baseline
 and outperforms other state-of-the-art parsers.

### 2017-11-27 paper.tex
revise tokenization, add speed comparison, final evaluation comparison TBD.

@@
 understanding and explaining tweets. Using the new treebank,
-we build a pipeline system to parse raw tweets into UD. To conquer the
+we build a pipeline system to parse raw tweets into UD. To overcome the
 annotation noise without sacrificing computational efficiency, we propose a new
-method to distill an ensemble of 20 parsers into a single one. Our
+method to distill an ensemble of 20 transition-based parsers into a single one. Our
 parser achieves an improvement of 2.3 in LAS over \nascomment{which
-  comparison is this?} the baseline
+  comparison is this?} the singlely trained baseline
 and outperforms parsers that are state-of-the-art on other treebanks.
@@
 phrase-structure conventions of the Penn Treebank \citep[PTB]{Marcus93buildinga}.
-Stanford dependencies were converted afterwards \nascomment{by who?}. 
+Stanford dependencies were converted afterwards in their work  \nascomment{by who?}. 
 \citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
@@
 consistent annotation across different languages. To allow such
-consistency, UD was designed to be adaptable to different genres and languages
-\cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. We propose that analyzing
+consistency, UD was designed to be adaptable to different genres \cite{wang-EtAl:2017:Long6} 
+and languages \cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. We propose that analyzing
 the syntax of tweets can benefit from such adaptability. In this paper,
@@
 ``baseline'' parser.
-
 To overcome the noise in our annotated data and achieve better performance
@@
 \section{Annotation}\label{sec:anno}
-\yicomment{Maybe we should contrast UD and kong's annotation strategy during each stage, because UD has also annotation guideline for every stage.}
+%\yicomment{Maybe we should contrast UD and kong's annotation strategy during each stage, because UD has also annotation guideline for every stage.}
 
@@
 TweetMotif, not for NLP---preserves most whitespace-delimited tokens, including 
-hashtags, at-mentions, emoticons,  emojis, and unicode glyphs. 
+hashtags, at-mentions, emoticons, and unicode glyphs. 
 They also treat contractions and acronyms as whole tokens and do not split them.
@@
 in order to better serve dependency annotation, treats each syntactic word as token.
-They therefore take a more aggressive strategy, including splitting
-clitics from contractions or multiword expressions (e.g., {\it
-  gonna}), and sometimes combining several orthographic tokens into a
-single syntactic word. \yicomment{does UD support normalization for
+They therefore more aggressively split
+clitics from contractions (e.g., {\it  gonna} is tokenized as {\it gon} and {\it na}; {\it its}
+is tokenized as {\it it} and {\it s} when {\it s} is a copula). But acronyms is not touched
+in the UD tokenization guidelines. Thus, we follow the UD tokenization for contractions
+and left acronyms like {\em idc} as a single token.
+\yicomment{does UD support normalization for
   acronyms? Did not see it from website, need to check. related to
@@
   here that acronyms like \emph{idc} are left as a single token}
-
-In our manual tokenization, we do not modify any non-informal \nascomment{is this defined?} token in tweets and leave them as in the original tweets. 
-Then we mainly follow UD tokenization. We tokenize contractions and
-multiword expressions into their syntactic components, but do not
-combine tokens that appear as split in the original tweet.
-For example, words like {\it gonna} or {\it can't} will be tokenized
-to {\it gon na} and {\it ca n't}, and sequences like {\it Y O} and
-{\it R E T W E E T} will be not combined back into single
-words.\footnote{Such tokens only account for 0.067\%; we use the UD
-  {\it goeswith} relation to resolve these cases in the syntax.}
+\yjcomment{mentioned acronymns, we don't have the problem of normalization, cause
+normalization was just annotated for data study.}
+
+In the different direction of splitting tokens, UD guidelines also suggest to merge
+{\it multi-token words} (e.g. {\it 20 000}) into one single token in some special
+cases. We witnessed a small number of tweets that contain mult-token words
+(e.g. {\it Y O}, and {\it R E T W E E T}) but didn't combine them due to simplification.
+Such tokens only account for 0.067\% and we use the UD
+  {\it goeswith} relation to resolve these cases in the dependency annotations.
 
@@
 analyze acronym tokens like \emph{idc}
-(abbreviating ``I don't care'') \yicomment{`idc' should be discussed in tokenization section, and actually it is already implied from POS section that it should be treated as a single word.}
+(abbreviating ``I don't care'')
  and \emph{rn} (``right now'')?  Should
@@
 syntax as a single word without normalization. Their syntactic functions
-are decided according to their context.\yicomment{again we should also mention UD tokenization, so might be worth adding a tokenization section}
-
-\citet{eisenstein:2013:NAACL-HLT} studied the necessity of normalization
+are decided according to their context. \citet{eisenstein:2013:NAACL-HLT} studied the necessity of normalization
 in social media text and argued that such normalization is problematic.
@@
 (840 unique tweets, 639/201 for training/test set), along with an 
-additional 210 tweets sampled from the POS-tagged dataset of \newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled from the Twitter stream from February 2016 to July 2016.\footnote{Data downloaded from \url{https://archive.org/}.}
+additional 210 tweets sampled from the POS-tagged dataset of
+\newcite{gimpel-EtAl:2011:ACL-HLT2011} and 2,500 tweets sampled
+from the Twitter stream from February 2016 to July 2016.\footnote{Data downloaded from \url{https://archive.org/}.}
 The latter data source consists of 147.4M English tweets after being
@@
 	\centering
-	\includegraphics[width=\columnwidth,trim={0 0 13cm 9cm},clip]{graphics/bilstm_tokenizer}
+	\includegraphics[width=\columnwidth,trim={0 0 11cm 9cm},clip]{graphics/bilstm_tokenizer}
 	\caption{The bi-LSTM tokenizer model that segments `its gonna be' into `it s gon na be'.}\label{fig:tok-model}
@@
 		\hline
-		\it System & $F_1$ \\
+		\it System & \it F1 \\
 		\hline
@@
 	\centering
-	\includegraphics[width=\columnwidth,trim={0 0 13cm 3cm},clip]{graphics/bilstm_postagger}
+	\includegraphics[width=\columnwidth,trim={0 0 11cm 3cm},clip]{graphics/bilstm_postagger}
 	\caption{The bi-LSTM POS tagger model that tags `it s gon na be' as {\tt PRON AUX VERB PART AUX}.}\label{fig:pos-model}
-	\yicomment{i'm a little confused by the pic, need discussion}
+	%\yicomment{i'm a little confused by the pic, need discussion}
 \end{figure}
@@
 labeled attachment score (including punctuation) are reported.
+All the experiments were ran on a Xeon E5-2670 2.6 GHz machine.
 
@@
 effect, we report the average of five differently-seeded runs, for
-each model. \nascomment{please check! we did this for all systems,
-  not just ours, right?}
+each model and the compared one. %\nascomment{please check! we did this for all systems,
+%  not just ours, right?}
 
@@
 	\centering
-	\begin{tabular}{rcc}
-		\hline
-		\it System & UAS & LAS \\
-		\hline
-		\citet{kong-EtAl:2014:EMNLP2014} &81.6 & 77.2 \\
-		\citet{DBLP:journals/corr/DozatM16} & 81.9 &  77.7 \\
+	\begin{tabular}{rccc}
+		\hline
+		\it System & UAS & LAS & SP \\
+		\hline
+		\citet{kong-EtAl:2014:EMNLP2014} &81.6 & 77.2 & 0.3 \\
+		\citet{DBLP:journals/corr/DozatM16} & 81.9 &  77.7 & 1.7 \\
 %		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
-		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.4 & 75.8 \\
+		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.4 & 75.8 & 2.3 \\
 		\hdashline
-		Ensemble (20) & 83.5 & 79.4 \\
-		Distillation ($\alpha =1.0$) & 82.2 & 78.0 \\
-		Distillation ($\alpha =0.9$) & 82.4 & 78.1 \\		
-		Distillation with exploration & 82.5 & 78.4 \\
+		Ensemble (20) & 83.5 & 79.4 & 0.2 \\
+		Distillation ($\alpha =1.0$) & 82.2 & 78.0 & 2.3 \\
+		Distillation ($\alpha =0.9$) & 82.4 & 78.1 & 2.3 \\		
+		Distillation w/ exploration & 82.5 & 78.4 & 2.3 \\
 		\hline
@@
 	\caption{Dependency parser comparison on \textsc{Tweebank v2},
-           with automatic POS tags. \label{tbl:parse-result}}
+           with automatic POS tags. The {\it SP} column shows
+           the parsing speed evaluated by the number of thousand tokens
+           the model processed per second. For fair comparison, we limit the
+           number of CPU used in \citet{DBLP:journals/corr/DozatM16} experiments to 1.
+            \label{tbl:parse-result}}
 \end{table}
@@
  \citet{DBLP:journals/corr/DozatM16}, both of which are graph-based
- parsers requiring superlinear runtime. \nascomment{can we quantify
-   how much time each one takes, either in tweets parsed per second or
-   seconds per tweet?}
+ parsers requiring superlinear runtime. %\nascomment{can we quantify
+%   how much time each one takes, either in tweets parsed per second or
+%   seconds per tweet?}
 Both of the comparison systems are re-trained on the same data as our
@@
 Our system lags behind by nearly two LAS
-points.
+points but runs faster than both of them.
+
+\begin{table*}[t]
+	\centering
+	\begin{tabular}{rrcc}
+		\hline
+		\it Pipeline & Metrics & Our & SOTA stack\\
+		\hline
+		Tokenization & \it F1 & 98.3 & \\		
+		POS tagging &  \it Precision F1 & 93.7 & \\
+		Universal dependencies & \it LAS F1 & 74.1 & \\
+		\hline
+	\end{tabular}
+	\caption{Evaluating our model in pipeline
+		manner. \nascomment{should this be ``F1''?  shouldn't the
+			last line be LAS?}\label{tbl:pipline} }
+\end{table*}
 
@@
 79.4, outperforming all three systems above (Table~\ref{tbl:parse-result}).
+However, ensembling 20 parsers also significantly slows down the parsing
+speed and leads to the slowest system in our comparison.
 
@@
 ensemble (i.e., the average of the 20 separately-trained ensemble
-members) \nascomment{check}.
+members) \nascomment{check} \yjcomment{checked}.
 To train the distilled model, we minimize the interpolation between
@@
 \begin{align}
-\min_q \quad  & \alpha \sum_i \underbrace{\sum_{a} q(a \mid s_i) \cdot p(a
+{\arg\,\min}_q \quad  & \alpha \sum_i \underbrace{\sum_{a} q(a \mid s_i) \cdot p(a
   \mid s_i)}_{\text{distillation loss}} \\
@@
 
-\begin{table}[t]
-	\centering
-	\begin{tabular}{rcc}
-		\hline
-		\it System & UAS & LAS \\
-		\hline
-		\newcite{kuncoro-16} & 94.3 & 92.1 \\
-		\citet{DBLP:journals/corr/DozatM16} & 95.7 & 94.1 \\
-		\hdashline
-		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 93.0 & 90.9 \\		
-		%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
-		Ensemble (20) & 94.5 & 92.6 \\
-		Distillation ($\alpha =1.0$) & 93.8 & 91.7 \\
-		Distillation with exploration  & 94.1 & 92.0 \\
-		\hline
-	\end{tabular}
-	\caption{Dependency parser comparison on PTB test set.}\label{tbl:parse-result-PTB}
-\end{table}
-
-\nascomment{need to clarify:  is this UD?} We perform additional experiments on the Penn Treebank, following
-the settings of \newcite{dyer-EtAl:2015:ACL-IJCNLP};
-Table~\ref{tbl:parse-result-PTB} shows a similar trend, and we achieve
-performance close to that of the graph-based parser of \citet{kuncoro-16}.
-However, this greedy approach still lags behind the very strong
-graph-based system of \citet{DBLP:journals/corr/DozatM16}.
-
-\begin{table}[t]
-	\centering
-	\begin{tabular}{rc}
-		\hline
-		\it Pipeline & $F_1$\\
-		\hline
-		Tokenization & 98.3 \\		
-		POS tagging & 93.7 \\
-		Universal dependencies & 74.1 \\
-		\hline
-	\end{tabular}
-	\caption{Evaluating our model in pipeline
-          manner. \nascomment{should this be ``F1''?  shouldn't the
-            last line be LAS?}\label{tbl:pipline} }
-\end{table}
+%
+%\begin{table}[t]
+%	\centering
+%	\begin{tabular}{rcc}
+%		\hline
+%		\it System & UAS & LAS \\
+%		\hline
+%		\newcite{kuncoro-16} & 94.3 & 92.1 \\
+%		\citet{DBLP:journals/corr/DozatM16} & 95.7 & 94.1 \\
+%		\hdashline
+%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 93.0 & 90.9 \\		
+%		%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
+%		Ensemble (20) & 94.5 & 92.6 \\
+%		Distillation ($\alpha =1.0$) & 93.8 & 91.7 \\
+%		Distillation with exploration  & 94.1 & 92.0 \\
+%		\hline
+%	\end{tabular}
+%	\caption{Dependency parser comparison on PTB test set.}\label{tbl:parse-result-PTB}
+%\end{table}
+
+%\nascomment{need to clarify:  is this UD?} We perform additional experiments on the Penn Treebank, following
+%the settings of \newcite{dyer-EtAl:2015:ACL-IJCNLP};
+%Table~\ref{tbl:parse-result-PTB} shows a similar trend, and we achieve
+%performance close to that of the graph-based parser of \citet{kuncoro-16}.
+%However, this greedy approach still lags behind the very strong
+%graph-based system of \citet{DBLP:journals/corr/DozatM16}.
 
 \paragraph{Pipeline evaluation.} Finally, we report  our full
-pipeline's performance in  Table \ref{tbl:pipline}. We see the
+pipeline's performance in  Table \ref{tbl:pipline}.
+We see the
 importance of segmentation:  without gold segmentation, UD parsing
-performance drops by more than four points.
+performance drops by more than four points. We also compare
+our model with a stack of the state-of-the-art system: Stanford Tokenizer,
+ARK tagger, and \citet{DBLP:journals/corr/DozatM16}'s parser. \yjcomment{tbd}
 

### 2017-11-28 paper.tex
add speed comparison, add sota-stack comparison in pipeline eval. 2.3->2.6, remove incoherent ptb result.

@@
 \newcommand{\yicomment}[1]{\textcolor{green}{[#1 ---\textsc{Yi}]}}
+%\newcommand{\yjcomment}[1]{}
+%\newcommand{\nascomment}[1]{}
+%\newcommand{\yicomment}[1]{}
 
@@
 method to distill an ensemble of 20 transition-based parsers into a single one. Our
-parser achieves an improvement of 2.3 in LAS over \nascomment{which
-  comparison is this?} the singlely trained baseline
-and outperforms parsers that are state-of-the-art on other treebanks.
+parser achieves an improvement of 2.6 in LAS over \nascomment{which
+  comparison is this?}\yjcomment{my bad, it was fixed.} the baseline
+and outperforms parsers that are state-of-the-art on other treebanks in both accuracy and speed.
 \end{abstract}
@@
 phrase-structure conventions of the Penn Treebank \citep[PTB]{Marcus93buildinga}.
-Stanford dependencies were converted afterwards in their work  \nascomment{by who?}. 
+Stanford dependencies were converted afterwards in their work  \nascomment{by who?}\yjcomment{by themselves}. 
 \citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
@@
 transition sequence. Experimental results show that an improvement of more
-than 2.3 points \nascomment{again, not sure what this is quoting} in LAS over the baseline parser can be achieved with our
-distillation method and that it outperforms other state-of-the-art parsers.
+than 2.6 points \nascomment{again, not sure what this is quoting}\yjcomment{fixed} in LAS over the
+baseline parser can be achieved with our distillation method and that it outperforms
+other state-of-the-art parsers in both accuracy and running speed.
 
@@
 \item We introduce and evaluate a system to parse the raw tweet text into
-universal dependencies (\S\ref{sec:parsing}).  \nascomment{say it
-  performs better than existing systems?}
+universal dependencies (\S\ref{sec:parsing}).  Experimental results show
+it performs better than a stack of the state-of-the-art alternatives.
+\nascomment{say it
+  performs better than existing systems?}\yjcomment{added.}
+
 \item We propose a new distillation
@@
 We report the inter-annotator agreement between the annotators
-in the second stage. The agreement on POS is 96.61\%, the unlabeled
-dependency agreement is 88.75\% and the labeled dependency agreement
-is 84.31\%. Further analysis shows the major disagreements on POS
-involve entity names (30.57\%) and topical hashtags (18.11\%).
+in the second stage. The agreement on POS is 96.6\%, the unlabeled
+dependency agreement is 88.8\% and the labeled dependency agreement
+is 84.3\%. Further analysis shows the major disagreements on POS
+involve entity names (30.6\%) and topical hashtags (18.1\%).
 Taking the example in Figure \ref{fig:non-syn-toks}, ``Fix you'' can
@@
 	\centering
-	\begin{tabular}{lr}
+	\begin{tabular}{rc}
 		\hline
@@
 \cite{straka-strakova:2017:K17-3} model was re-trained on the same
-data as our system. \nascomment{we need to say what their model was;
+data as our system. Compared with the UD pipe, we use LSTM
+instead of GRU in our model and we also use a larger size of hidden units (64 against 20),
+which has stronger representation power. \nascomment{we need to say what their model was;
   why does ours work better?  from their paper, it seems that they
   used a GRU instead of an LSTM ... is that all?  do we win because of
-better tuning, or what?}
+better tuning, or what?}\yjcomment{done.}
 Our bi-LSTM tokenizer achieves the best accuracy among all these
@@
 		\hline
-		Stanford CoreNLP & 92.0 \\
-		our tokenizer (\S\ref{sec:tok}) & 93.6 \\
+		Stanford CoreNLP & 92.1 \\
+		our bi-LSTM tokenizer (\S\ref{sec:tok}) & 93.6 \\
 		\hline
@@
 effect, we report the average of five differently-seeded runs, for
-each model and the compared one. %\nascomment{please check! we did this for all systems,
-%  not just ours, right?}
-
-%%%
+each of our models and the compared ones. \nascomment{please check! we did this for all systems,
+  not just ours, right?}\yjcomment{yes. added}
 
@@
  \citet{DBLP:journals/corr/DozatM16}, both of which are graph-based
- parsers requiring superlinear runtime. %\nascomment{can we quantify
-%   how much time each one takes, either in tweets parsed per second or
-%   seconds per tweet?}
+ parsers requiring superlinear runtime. \nascomment{can we quantify
+   how much time each one takes, either in tweets parsed per second or
+   seconds per tweet?}\yjcomment{done.}
 Both of the comparison systems are re-trained on the same data as our
@@
 		\hline
-		\it Pipeline & Metrics & Our & SOTA stack\\
-		\hline
-		Tokenization & \it F1 & 98.3 & \\		
-		POS tagging &  \it Precision F1 & 93.7 & \\
-		Universal dependencies & \it LAS F1 & 74.1 & \\
+		\it Pipeline & Metrics & ours & SOTA stack\\
+		\hline
+		Tokenization & \it F1 & 98.3 & 96.6 \\		
+		POS tagging &  \it Precision F1 & 93.7 & 92.1 \\
+		Universal dependencies & \it LAS F1 & 74.1 & 70.3 \\
 		\hline
@@
 		manner. \nascomment{should this be ``F1''?  shouldn't the
-			last line be LAS?}\label{tbl:pipline} }
+			last line be LAS?}\yjcomment{added metrics column}\label{tbl:pipline} }
 \end{table*}
@@
 \paragraph{Pipeline evaluation.} Finally, we report  our full
-pipeline's performance in  Table \ref{tbl:pipline}.
-We see the
+pipeline's performance in  Table \ref{tbl:pipline}. We also compare
+our model with a stack of the state-of-the-art systems (named as the {\it SOTA stack}):
+Stanford CoreNLP tokenizer,
+\citet{owoputi-EtAl:2013:NAACL-HLT}'s tagger, and \citet{DBLP:journals/corr/DozatM16}'s parser.
+Our system differs with the SOTA stack in the tokenization and parser components.
+From Table \ref{tbl:pipline}, our system outperforms the SOTA stack when
+evaluated in pipeline manner.
+The results also emphasize the
 importance of segmentation:  without gold segmentation, UD parsing
-performance drops by more than four points. We also compare
-our model with a stack of the state-of-the-art system: Stanford Tokenizer,
-ARK tagger, and \citet{DBLP:journals/corr/DozatM16}'s parser. \yjcomment{tbd}
+performance drops by more than four points.
 
@@
 to overcome annotation noise without sacrificing efficiency.
-Our parser achieves an improvement of 2.3  \nascomment{which
-  comparison are you quoting here?} in LAS over a strong baseline
-and outperforms other state-of-the-art parsers.
+Our parser achieves an improvement of 2.6  \nascomment{which
+  comparison are you quoting here?}\yjcomment{fixed} in LAS over a strong baseline
+and outperforms other state-of-the-art parsers in both accuracy and speed.
 

### 2017-11-30 paper.tex
fix equ.
revise p1 - p3

@@
 \newcommand\BibTeX{B{\sc ib}\TeX}
+\DeclareMathOperator*{\argmin}{argmin}
 
@@
 universal dependencies \citep[UD;][]{NIVRE16.348}. We extend the UD guidelines to cover
-special constructions in tweets. Using the extended guidelines, we create
+special constructions in tweets.
+Using the extended guidelines \yicomment{including tokenization, POS tagging and parsing?
+(need to mention the annotation process/pipeline system not only consists parsing in abstract)}, we create
 a new tweet treebank ({\sc Tweebank v2}), which has 55,607 tokens with
@@
 \section{Introduction}
-NLP for social media messages is challenging, both because domain
-adaptation is required, but also because creating annotated datasets
+NLP for social media messages \yicomment{texts?} is challenging, both \yicomment{not only} because domain
+adaptation is required, but also because \yicomment{delete `because' ?} creating annotated datasets
 (e.g., treebanks)
@@
 consistency, UD was designed to be adaptable to different genres \cite{wang-EtAl:2017:Long6} 
-and languages \cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. We propose that analyzing
+and languages \cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. We propose \yicomment{believe?} that analyzing
 the syntax of tweets can benefit from such adaptability. In this paper,
@@
 covered by UD guidelines. Our annotation includes 
-tokenization, part-of-speech (POS) tags, and (labeled) universal dependencies.
-We characterize the disagreement among our annotations and find that
-consistent annotation is still challenging to deliver even with
+tokenization, part-of-speech (POS) tags, and (labeled) \yicomment{no need for parenthesis} universal dependencies.
+We characterize the disagreement among our annotations \yicomment{annotation(s) and disagreement(s).
+check abstract, same sentence, different singularity/plurality.
+I think should be `disagreement' and `annotations'} and find that
+consistent annotation \yicomment{again, it needs to be the same all the time at least for me.} is still challenging to deliver even with
 the extended guidelines.
@@
 raw tweets into universal dependencies. Our pipeline includes: a
-bidirectional LSTM (bi-LSTM) tokenizer, a word cluster-enhanced POS
-tagger \citep[following][]{owoputi-EtAl:2013:NAACL-HLT}, and a stack LSTM parser
+bidirectional LSTM (bi-LSTM)\yicomment{need cite lstm/bi-lstm here?} tokenizer, a word cluster-enhanced POS
+tagger \citep[following][]{owoputi-EtAl:2013:NAACL-HLT} \yicomment{no need for parenthesis?}, and a stack LSTM parser
 with character-based word representations
@@
 than 2.6 points \nascomment{again, not sure what this is quoting}\yjcomment{fixed} in LAS over the
-baseline parser can be achieved with our distillation method and that it outperforms
+baseline parser can be achieved with our distillation method and that \yicomment{delete `that'?} it outperforms
 other state-of-the-art parsers in both accuracy and running speed.
@@
 and created a new tweet treebank ({\sc Tweebank v2}), which includes 
-tokenization, part-of-speech tagging, and labeled universal dependencies annotation.
+tokenization, part-of-speech \yicomment{POS} tagging, and labeled universal dependencies annotation.
 We also characterize the difficulties of creating such annotation.
 
-\item We introduce and evaluate a system to parse the raw tweet text into
+\item We introduce and evaluate a \yicomment{pipeline} system to parse the raw tweet text into
 universal dependencies (\S\ref{sec:parsing}).  Experimental results show
@@
 
-We release our dataset and our system as open-source software at
+We release our dataset and our \yicomment{delete `our'} system as open-source software \yicomment{delete `as open-source software'?} at
 \url{http://anonymized}.
@@
 We first review {\sc Tweebank v1} of \citet{kong-EtAl:2014:EMNLP2014},
-which is the largest Twitter dependencies annotation
+which is \yicomment{was} the largest \yicomment{unlabelled} Twitter dependencies annotation
 (\S\ref{sec:tweebank}).
@@
 
-The annotation effort we describe stands in contrast to previous work
+The annotation effort we describe stands in contrast to \yicomment{the?} previous work
 by \newcite{kong-EtAl:2014:EMNLP2014}.  Their aim was the rapid
@@
 contributed a new annotated corpus, \textsc{Tweebank}, consisting of
-929 tweets.  Their annotations added dependencies to a portion of the data
+929 tweets.  Their annotations added \yicomment{unlabelled} dependencies to a portion of the data
 annotated with POS tags by 
@@
 Kong et al.'s rapid, small-scale annotation effort was heavily constrained.  It was
-carried out mostly by nonnative speakers, in a very short amount of
+carried out mostly by nonnative speakers \yicomment{should not emphasize non-native speakers (v2 also built by non-native speakers), but emphasize annotators with only cursory training, no clear annotation guidelines, no consensus/agreement on controversial cases, allow annotators to underspecify part of the tree and allow multiple different trees for the same tweets}, in a very short amount of
 time (a day).  Driven both by the style of the text they sought to annotate
@@
   tree.  A clear criterion for exclusion was not given, but many
-  tokens were excluded because they were deemed ``non-syntactic.''
+  tokens were excluded because they were deemed ``non-syntactic''\yicomment{(e.g. retweet sign, topical hashtags, ...)}.
 \item Allowing an annotator to merge a multiword expression into a
@@
 \citet{ICWSM101540} and that of UD.
-There is a significant tradeoff  between preservation of original tweet content and respecting
+There is a significant \yicomment{significant? not really} tradeoff between preservation of original tweet content and respecting
 the UD guidelines.
@@
 tokenization,\footnote{\url{http://universaldependencies.org/u/overview/tokenization.html}}
-in order to better serve dependency annotation, treats each syntactic word as token.
+in order to better serve dependency annotation, treats each syntactic word as a token.
 They therefore more aggressively split
 clitics from contractions (e.g., {\it  gonna} is tokenized as {\it gon} and {\it na}; {\it its}
-is tokenized as {\it it} and {\it s} when {\it s} is a copula). But acronyms is not touched
+is tokenized as {\it it} and {\it s} when {\it s} is a copula)\yicomment{I think the examples are not contractions (can't), is there a name for such words?}. But acronyms are not touched
 in the UD tokenization guidelines. Thus, we follow the UD tokenization for contractions
-and left acronyms like {\em idc} as a single token.
-\yicomment{does UD support normalization for
-  acronyms? Did not see it from website, need to check. related to
-  ``idc''} \nascomment{unless we make a change, I think we need to say
+and left acronyms like {\em idc} as a single token. \nascomment{unless we make a change, I think we need to say
   here that acronyms like \emph{idc} are left as a single token}
@@
 
-In the different direction of splitting tokens, UD guidelines also suggest to merge
+In the different direction of splitting tokens, UD guidelines also suggest to merge \yicomment{suggest merging?}
 {\it multi-token words} (e.g. {\it 20 000}) into one single token in some special
@@
 
-Before turning to UD annotations, we (re)annotated the data with 
-POS, for consistency with other UD efforts,
+Before turning to UD \yicomment{dependencies} annotations, we (re)annotated the data with 
+POS \yicomment{tags}, for consistency with other UD efforts,
 which adopt the universal POS tagset of \newcite{PETROV12.274}.
@@
 and the conventions of \newcite{gimpel-EtAl:2011:ACL-HLT2011} and
-\newcite{owoputi-EtAl:2013:NAACL-HLT}.  In these cases, we always
+\newcite{owoputi-EtAl:2013:NAACL-HLT}.
+\yicomment{The conflicts should refer to a {\bf noncorresponding tag} from that of gimpel to UDEnglish, cuz they dont have the same tagset.} In these cases, we always
 conformed to UD, enabling consistency (e.g., when we exploit the
@@
 
-Compared to the coarse-grained POS tagging effort of
+Compared to the coarse-grained \yicomment{fine-grained?}POS tagging effort of
 \newcite{gimpel-EtAl:2011:ACL-HLT2011}, our approach simplifies some
@@
 Another important difference follows from the difference in
-tokenization.  As discussed above, UD calls for more
+tokenization.  As discussed in \S\ref{sec:tok-anno}, UD calls for more
 aggressive tokenization than that used by 
-\newcite{gimpel-EtAl:2011:ACL-HLT2011}.  In particular, Gimpel et al.~opted out of tokenizing
+\newcite{gimpel-EtAl:2011:ACL-HLT2011} [YICOMMENT: should be OCONNOR's paper? TOKENIZATION?]. In particular, Gimpel et al.~[YICOMMENT: SAME HERE] opted out of tokenizing
 contractions and possessives, introducing new parts of speech
@@
 \begin{align}
-{\arg\,\min}_q \quad  & \alpha \sum_i \underbrace{\sum_{a} q(a \mid s_i) \cdot p(a
-  \mid s_i)}_{\text{distillation loss}} \\
+{\argmin}_q \quad  & \alpha \sum_i \underbrace{\sum_{a} -p(a
+	\mid s_i) \cdot \log q(a \mid s_i)}_{\text{distillation loss}} \\
 & +\ (1 - \alpha) \sum_i \underbrace{- \log q(a_i \mid
@@
 pipeline's performance in  Table \ref{tbl:pipline}. We also compare
-our model with a stack of the state-of-the-art systems (named as the {\it SOTA stack}):
+our model with a stack of the state-of-the-art systems (namely, the {\it SOTA stack}):
 Stanford CoreNLP tokenizer,

### 2017-11-30 paper.tex
.

@@
 {\it multi-token words} (e.g. {\it 20 000}) into one single token in some special
-cases. We witnessed a small number of tweets that contain mult-token words
+cases. We witnessed a small number of tweets that contain multi-token words
 (e.g. {\it Y O}, and {\it R E T W E E T}) but didn't combine them due to simplification.
@@
 aggressive tokenization than that used by 
-\newcite{gimpel-EtAl:2011:ACL-HLT2011} [YICOMMENT: should be OCONNOR's paper? TOKENIZATION?]. In particular, Gimpel et al.~[YICOMMENT: SAME HERE] opted out of tokenizing
+\newcite{gimpel-EtAl:2011:ACL-HLT2011} \yicomment{YICOMMENT: should be OCONNOR's paper? TOKENIZATION?}. In particular, Gimpel et al.~\yicomment{SAME HERE} opted out of tokenizing
 contractions and possessives, introducing new parts of speech

### 2017-11-30 paper.tex
revise p3 - p5

@@
 words be ``normalized'' into explicitly spelled out intermediate
-forms? We follow \citet{kong-EtAl:2014:EMNLP2014} and annotate their
+forms? \yicomment{this sentence should be deleted} \yicomment{As we already know from previous sections, \emph{idc} is not tokenized and tagged as verb, we follow ...}
+We follow \citet{kong-EtAl:2014:EMNLP2014} and annotate their
 syntax as a single word without normalization. Their syntactic functions
@@
 syntactic functions only constitute 0.06\% of the tokens in our
-dataset, we believe that normalization is an unnecessarily complicated step.
+dataset, we believe that normalization is an unnecessarily complicated step.\yicomment{this should be moved to tokenization section, but we can mention again here for emphasizing.}
 % \nascomment{maybe we owe citations to
@@
 \end{tabular}
-\caption{Proportions of non-syntactic tokens in our annotation.
+\caption{Proportions of non-syntactic tokens in our annotation. \yicomment{should add also retweet at-mentions}
 These statistics are obtained on 140 character-limited tweets. \label{tbl:non-synt-prop}}
@@
 a large proportion of tokens don't carry any syntactic function.
-In our annotation, there are five types of non-syntactic tokens: 
+In our annotation, there are five \yicomment{six} types of non-syntactic tokens: 
 sentiment emoticons, retweet markers, topical hashtags, referential URLs, and
-truncated words.\footnote{The tweets we analyze have at most 140
+truncated words \yicomment{and retweet at-mentions}.\footnote{The tweets we analyze have at most 140
   characters. Although Twitter has doubled the tweet length limit to
@@
 emoticons, which are tagged as \emph{symbol} (\texttt{SYM}).  In our annotation, 
-7.5\% of all tokens are non-syntactic; detailed statistics can be found in Table \ref{tbl:non-synt-prop}.
+7.5\% \yicomment{should change according to tab1} of all tokens are non-syntactic; detailed statistics can be found in Table \ref{tbl:non-synt-prop}.
 
@@
 abbreviate the verb {\tt retweet}, and emoticons and hashtags may be
-used as content words within a sentence; see  Figure
-\ref{fig:informal-toks}.  Therefore, the criteria for annotating a
+used as content words within a sentence\yicomment{at-mentions can be a normal vocative proper noun}; see Figure
+\ref{fig:informal-toks}.  Therefore, the criteria for \yicomment{whether} annotating a
 token as non-syntactic must be context-dependent.
@@
 canonically non-syntactic), we adopt the following
-conventions:
+conventions:\yicomment{shall we mention how we segment sentences? Seems relevant here}
 \begin{itemize}
@@
   URLs are always labeled as {\it list}, following the UD\_English dataset.
+\\ \yicomment{For retweet at-mention case, we attach the retweet at-mentions to the RT sign, so that the retweet action and the people whose tweet is being retweeted could be connected.\footnote{We can also follow the first convention to attach the retweet at-mention to its predicate, but we think it is better for downstream tasks.}}
 \end{itemize}
@@
 %  e.g., for defining features of the input for parsing}
-In order to keep our annotation conventions in line with UD norms,
+In order to keep our annotation conventions in line with UD norms \yicomment{and preserve the original tweets as much as possible},
 we include non-syntactic tokens in our annotation following the
 conventions above. Compared with \citet{kong-EtAl:2014:EMNLP2014},
-we also gave a clear definition of non-syntactic tokens, which helped
+we also gave a clear\yicomment{much clearer} definition of non-syntactic tokens, which helped
 us avoid confusion during annotation.
@@
 label and the colon to \emph{RT} with the \emph{punct}(uation) label,
-and attaching \emph{RT} to the predicate of the following sentence.
+and attaching \emph{RT} to the predicate of the following sentence\yicomment{since we have introduced retweet at-mentions in the non-syntactic tokens, here we can just briefly justify our choice.}.
 
@@
 that are especially common in tweets are well handled by UD
-conventions:  ellipsis, irregular word orders, and paratactic sentences
+conventions: ellipsis, irregular word orders, and paratactic sentences \yicomment{or phrases/component}
 not explicitly delineated by punctuation.
@@
 Twitter is an at-mention %(followed by a colon \nascomment{?})
-as a sign that a tweet is a reply to a tweet by the mentioned user.  We
+as a sign that a tweet is a reply to a tweet by the mentioned user\yicomment{not necessary, can be just mentioning somebody.
+should be careful to say it.
+We can say this construction include 1.
+reply;  2.
+mention sb.
+Both cases are similar to general vocative proper noun case in standard texts}.
+We
 treat these at-mentions as vocative expressions, labeling them as
-\emph{proper noun} (\texttt{PROPN}) and attaching them to the
-following predicate with the label \emph{vocative} (see Figure \ref{fig:informal-toks} for an example).
+\emph{proper noun} (\texttt{PROPN})[YI COMMENT: here is confusing that PROPN could be a label in dependencies.
+We can say in POS sections that the decisions on some twitter specific tokens can be made only analyzing syntax together.] and attaching them to the
+following predicate with the label \emph{vocative} (see Figure \ref{fig:informal-toks} for an example) \yicomment{just as UD guidelines}.
 

### 2017-12-01 paper.tex
finish section 2

@@
 treat these at-mentions as vocative expressions, labeling them as
-\emph{proper noun} (\texttt{PROPN})[YI COMMENT: here is confusing that PROPN could be a label in dependencies.
-We can say in POS sections that the decisions on some twitter specific tokens can be made only analyzing syntax together.] and attaching them to the
+\emph{proper noun} (\texttt{PROPN})\yicomment{here is confusing that PROPN could be a label in dependencies.
+We can say in POS sections that the decisions on some twitter specific tokens can be made only analyzing syntax together.} and attaching them to the
 following predicate with the label \emph{vocative} (see Figure \ref{fig:informal-toks} for an example) \yicomment{just as UD guidelines}.
@@
 \subsection{\sc Tweebank v2}\label{sec:anno-process}
-Following the guidelines presented above, we create a new annotated Twitter treebank, which we call {\sc Tweebank v2}.
+Following the guidelines presented above, we create a new annotated\yicomment{del?} Twitter \yicomment{Twitter dependency} treebank, which we call {\sc Tweebank v2}.
 
@@
 proportion and created the initial annotations in one day.
-Before annotating, they were given a tutorial overview of the UD
-annotation conventions and our guidelines.
+Before annotating, they were given a tutorial overview of the \yicomment{general} UD
+annotation conventions and our guidelines \yicomment{specifically for annotating tweets}.
 Both the guidelines and annotations
@@
 different annotators during this exercise. In the second stage, a POS tagger and
-parser were trained on the annotated data from the first stage (1,041 tweets in total),
-and used to automatically analyze the sampled 2,500 tweets.  Authors 
+parser were trained on the annotated data from the first stage (1,050\yicomment{changed to 1050} tweets in total),
+and \yicomment{were?}used to automatically analyze the sampled 2,500 tweets.  Authors 
 of this paper manually corrected the parsed data. Finally, an extra
-layer of word-level normalization was manually annotated for data
-analysis purposes.
+layer of word-level normalization\yicomment{see 10 th col of conllu data, also mention we could recover the original tweets also from this col (tokenization)} was manually annotated for data
+analysis purposes.\yicomment{should mention tokenization process, say we tokenize V1 and train tokenizer for V2 data, then manually correct them. Good story :)}
 
@@
 We report the inter-annotator agreement between the annotators
-in the second stage. The agreement on POS is 96.6\%, the unlabeled
+in the second stage\yicomment{tokenization is easier, did not do inter-annotator agreement}. The agreement on POS is 96.6\%, the unlabeled
 dependency agreement is 88.8\% and the labeled dependency agreement
 is 84.3\%. Further analysis shows the major disagreements on POS
-involve entity names (30.6\%) and topical hashtags (18.1\%).
-Taking the example in Figure \ref{fig:non-syn-toks}, ``Fix you'' can
+involve entity names (30.6\%) \yicomment{noun phrases or proper noun phrases, do we need example here?} and topical hashtags (18.1\%).
+Taking the example in Figure \ref{fig:non-syn-toks}, ``Fix you'' \yicomment{need to relate to previous error analysis, entity names maybe?}can
 be understood as a verbal phrase but also as the name of the Coldplay's
-single and tagged as proper noun. An example of a disagreement on
+single and tagged as proper noun.
+\yicomment{need to say the reason why dependency inter-annotator agreement is low?
+1.
+POS disagreement lead to big difference in understanding the semantics.
+2.
+Some special constructions like ellipsis lead to different view of tweets.
+Fig3 is an example of 2.}An example of a disagreement on
 dependencies is shown in Figure \ref{fig:disagree}.  Depending on

### 2017-12-03 paper.tex
when discussing non-syn tokens, merge @-mention in rt construction and rt marker.

@@
 \newcommand{\nascomment}[1]{\textcolor{blue}{[#1 ---\textsc{nas}]}}
-\newcommand{\yicomment}[1]{\textcolor{green}{[#1 ---\textsc{Yi}]}}
+\newcommand{\yicomment}[1]{\textcolor{gray}{[#1 ---\textsc{Yi}]}}
 %\newcommand{\yjcomment}[1]{}
@@
   v1} introduced by \citet{kong-EtAl:2014:EMNLP2014}. 
-We characterize the disagreements
-among our annotation and show that it is challenging to deliver
+We characterize the disagreement
+among our annotations and show that it is challenging to deliver
 consistent annotation due to ambiguity in
@@
 raw tweets into universal dependencies. Our pipeline includes: a
-bidirectional LSTM (bi-LSTM)\yicomment{need cite lstm/bi-lstm here?} tokenizer, a word cluster-enhanced POS
-tagger \citep[following][]{owoputi-EtAl:2013:NAACL-HLT} \yicomment{no need for parenthesis?}, and a stack LSTM parser
+bidirectional LSTM (bi-LSTM) tokenizer, a word cluster-enhanced POS
+tagger \citep[following][]{owoputi-EtAl:2013:NAACL-HLT}, and a stack LSTM parser
 with character-based word representations
@@
 than 2.6 points \nascomment{again, not sure what this is quoting}\yjcomment{fixed} in LAS over the
-baseline parser can be achieved with our distillation method and that \yicomment{delete `that'?} it outperforms
+baseline parser can be achieved with our distillation method and it outperforms
 other state-of-the-art parsers in both accuracy and running speed.
@@
 and created a new tweet treebank ({\sc Tweebank v2}), which includes 
-tokenization, part-of-speech \yicomment{POS} tagging, and labeled universal dependencies annotation.
+tokenization, part-of-speech tagging, and labeled universal dependencies annotation.
 We also characterize the difficulties of creating such annotation.
@@
   tree.  A clear criterion for exclusion was not given, but many
-  tokens were excluded because they were deemed ``non-syntactic''\yicomment{(e.g. retweet sign, topical hashtags, ...)}.
+  tokens were excluded because they were deemed ``non-syntactic''.
 \item Allowing an annotator to merge a multiword expression into a
@@
 %We should note that multiple tokens are actually included in a phrasal abbreviation, and we use one of their tags as the tag of the whole abbreviation according to their dependency relation or semantic priority.
-%If there is a hierarchy in the abbreviation, we use the tag of the head word. In UD, ``Right'' is the dependent of ``now '' in the dependency of {\tt rn}, so we tag {\tt rn} as ADV. 
+%aIf there is a hierarchy in the abbreviation, we use the tag of the head word. In UD, ``Right'' is the dependent of ``now '' in the dependency of {\tt rn}, so we tag {\tt rn} as ADV. 
 %Although there is no head word in {\tt im}, we think that the subject is usually more informative than the tense in many downstream tasks such as semantic role labelling, so we use the tag of ``I'', e.g.
@@
 
-Compared to the coarse-grained \yicomment{fine-grained?}POS tagging effort of
+Compared to the effort of
 \newcite{gimpel-EtAl:2011:ACL-HLT2011}, our approach simplifies some
@@
 tokenization.  As discussed in \S\ref{sec:tok-anno}, UD calls for more
-aggressive tokenization than that used by 
-\newcite{gimpel-EtAl:2011:ACL-HLT2011} \yicomment{YICOMMENT: should be OCONNOR's paper? TOKENIZATION?}. In particular, Gimpel et al.~\yicomment{SAME HERE} opted out of tokenizing
-contractions and possessives, introducing new parts of speech
+aggressive tokenization than that of \citet{ICWSM101540} which opted
+out of tokenizing contractions and possessives and it was used by 
+\citet{gimpel-EtAl:2011:ACL-HLT2011}. As a consequence, 
+Gimpel et al. introduced new parts of speech for these cases
 instead.\footnote{These tags only account for 2.7\% of tokens,
@@
 \end{tabular}
-\caption{Proportions of non-syntactic tokens in our annotation. \yicomment{should add also retweet at-mentions}
+\caption{Proportions of non-syntactic tokens in our annotation. %\yicomment{should add also retweet at-mentions}
 These statistics are obtained on 140 character-limited tweets. \label{tbl:non-synt-prop}}
@@
 		\begin{deptext}
-			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& \textcolor{green}{\bf @coldplay} \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl} \& Nice \& \textcolor{cyan}{\bf p} \& ...\\
+			Perfect \& \textcolor{red}{\bf $\heart$} \& \textcolor{orange}{\bf RT} \& \textcolor{orange}{\bf @coldplay} \& : \& Fix \& You \& from \& the \& back \& \textcolor{gray}{\bf \#ColdplayMinneapolis} \& \textcolor{blue}{\bf http://bit.ly/2dj2WCl} \& Nice \& \textcolor{cyan}{\bf p} \& ...\\
 			\tiny ADJ \&\tiny SYM \&\tiny X \&\tiny X \&\tiny PUNCT \&\tiny VERB \&\tiny NOUN \&\tiny ADP \&\tiny DET \&\tiny NOUN \&\tiny X \&\tiny X \& \tiny ADJ \& \tiny X \& \tiny PUNCT \\
@@
 		\textcolor{red}{sentiment emoticon},
-		\textcolor{orange}{retweet marker},
-		\textcolor{green}{retweet at-mention},
+		\textcolor{orange}{retweet marker and its following at-mention},
 		\textcolor{gray}{topical hashtag},
@@
 a large proportion of tokens don't carry any syntactic function.
-In our annotation, there are five \yicomment{six} types of non-syntactic tokens: 
-sentiment emoticons, retweet markers, topical hashtags, referential URLs, and
-truncated words \yicomment{and retweet at-mentions}.\footnote{The tweets we analyze have at most 140
+In our annotation, there are five types of non-syntactic tokens: 
+sentiment emoticons, retweet markers and their following at-mentions, topical hashtags, referential URLs, and
+truncated words.\footnote{The tweets we analyze have at most 140
   characters. Although Twitter has doubled the tweet length limit to
@@
 emoticons, which are tagged as \emph{symbol} (\texttt{SYM}).  In our annotation, 
-7.5\% \yicomment{should change according to tab1} of all tokens are non-syntactic; detailed statistics can be found in Table \ref{tbl:non-synt-prop}.
+7.55\% of all tokens are non-syntactic; detailed statistics can be found in Table \ref{tbl:non-synt-prop}.
+\yjcomment{I've merged retweet marker and retweet at-mention into one.}
 
@@
 conventions:\yicomment{shall we mention how we segment sentences? Seems relevant here}
+
 \begin{itemize}
-\item If a non-syntactic token is within a sentence that has a clear predicate, it will be attached to this predicate;
-\item If the whole sentence is made of a sequence of non-syntactic tokens, we attach all these tokens to the first one;
+\item For the at-mentions in retweet constructions, we attach them to their retweet markers. We will discuss our choice in the following paragraph;
+\item For the rest non-syntactic tokens, if one token is within a sentence that has a clear predicate, it will be attached to this predicate.
+If the whole sentence is made of a sequence of non-syntactic tokens, we attach all these tokens to the first one;
 %\item In parataxis case, when it is difficult to decide which sentence or phrase x should belong to, we always attach x to the previous predicate of the paratactic clause or phrase;
@@
   URLs are always labeled as {\it list}, following the UD\_English dataset.
-\\ \yicomment{For retweet at-mention case, we attach the retweet at-mentions to the RT sign, so that the retweet action and the people whose tweet is being retweeted could be connected.\footnote{We can also follow the first convention to attach the retweet at-mention to its predicate, but we think it is better for downstream tasks.}}
+%\\ \yicomment{For retweet at-mention case, we attach the retweet at-mentions to the RT sign, so that the retweet action and the people whose tweet is being retweeted could be connected.\footnote{We can also follow the first convention to attach the retweet at-mention to its predicate, but we think it is better for downstream tasks.}}
 \end{itemize}
@@
 conventions above. Compared with \citet{kong-EtAl:2014:EMNLP2014},
-we also gave a clear\yicomment{much clearer} definition of non-syntactic tokens, which helped
+we also gave a clear %\yicomment{much clearer}
+definition of non-syntactic tokens, which helped
 us avoid confusion during annotation.
@@
 the coverage of our guidelines and solve inconsistencies between
-different annotators during this exercise. In the second stage, a POS tagger and
-parser were trained on the annotated data from the first stage (1,050\yicomment{changed to 1050} tweets in total),
-and \yicomment{were?}used to automatically analyze the sampled 2,500 tweets.  Authors 
+different annotators during this exercise. In the second stage, a tokenizer, a POS tagger, and
+parser were trained on the annotated data from the first stage (1,050 tweets in total),
+and used to automatically analyze the sampled 2,500 tweets.  Authors 
 of this paper manually corrected the parsed data. Finally, an extra
 layer of word-level normalization\yicomment{see 10 th col of conllu data, also mention we could recover the original tweets also from this col (tokenization)} was manually annotated for data
-analysis purposes.\yicomment{should mention tokenization process, say we tokenize V1 and train tokenizer for V2 data, then manually correct them. Good story :)}
+analysis purposes. For example, ``idc'' is annotated as
+`I\_don't\_care' and `4 my FAM' is as `for my familiy'.
+Such normalization doesn't change our tokenization annotation.
+\yicomment{should mention tokenization process, say we tokenize V1 and train tokenizer for V2 data, then manually correct them.
+Good story :)}\yjcomment{add ``a tokenizer''}
 
@@
 We report the inter-annotator agreement between the annotators
-in the second stage\yicomment{tokenization is easier, did not do inter-annotator agreement}. The agreement on POS is 96.6\%, the unlabeled
+in the second stage. There is few disagreement on the tokenization annotation.
+The agreement on POS is 96.6\%, the unlabeled
 dependency agreement is 88.8\% and the labeled dependency agreement
 is 84.3\%. Further analysis shows the major disagreements on POS
-involve entity names (30.6\%) \yicomment{noun phrases or proper noun phrases, do we need example here?} and topical hashtags (18.1\%).
+involve entity names (30.6\%) \yicomment{noun phrases or proper noun phrases, do we need example here?}\yjcomment{i wasn't counting PROPN and NOUN confusion, but any type of confusion related with PROPN} and topical hashtags (18.1\%).
 Taking the example in Figure \ref{fig:non-syn-toks}, ``Fix you'' \yicomment{need to relate to previous error analysis, entity names maybe?}can

### 2017-12-03 paper.tex
revise all, change some comments

@@
 (need to mention the annotation process/pipeline system not only consists parsing in abstract)}, we create
-a new tweet treebank ({\sc Tweebank v2}), which has 55,607 tokens with
+a new tweet treebank ({\sc Tweebank v2}), which has 3,550 tweets\yicomment{add tweet \#} and 55,607 tokens with
 labeled attachments. 
@@
 \section{Introduction}
-NLP for social media messages \yicomment{texts?} is challenging, both \yicomment{not only} because domain
-adaptation is required, but also because \yicomment{delete `because' ?} creating annotated datasets
+NLP for social media messages is challenging, both because domain
+adaptation is required, but also because creating annotated datasets
 (e.g., treebanks)
@@
 consistency, UD was designed to be adaptable to different genres \cite{wang-EtAl:2017:Long6} 
-and languages \cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. We propose \yicomment{believe?} that analyzing
+and languages \cite{guo-EtAl:2015:ACL-IJCNLP2,TACL892}. We propose that analyzing
 the syntax of tweets can benefit from such adaptability. In this paper,
@@
 covered by UD guidelines. Our annotation includes 
-tokenization, part-of-speech (POS) tags, and (labeled) \yicomment{no need for parenthesis} universal dependencies.
+tokenization, part-of-speech (POS) tags, and (labeled) universal dependencies.
 We characterize the disagreement among our annotations \yicomment{annotation(s) and disagreement(s).
@@
 I think should be `disagreement' and `annotations'} and find that
-consistent annotation \yicomment{again, it needs to be the same all the time at least for me.} is still challenging to deliver even with
+consistent annotation \yicomment{annotations?} is still challenging to deliver even with
 the extended guidelines.
@@
 
-We release our dataset and our \yicomment{delete `our'} system as open-source software \yicomment{delete `as open-source software'?} at
+We release our dataset and our system as open-source software at
 \url{http://anonymized}.
@@
 We first review {\sc Tweebank v1} of \citet{kong-EtAl:2014:EMNLP2014},
-which is \yicomment{was} the largest \yicomment{unlabelled} Twitter dependencies annotation
+which is \yicomment{was?} the largest \yicomment{unlabelled?} Twitter dependencies annotation
 (\S\ref{sec:tweebank}).
@@
 contributed a new annotated corpus, \textsc{Tweebank}, consisting of
-929 tweets.  Their annotations added \yicomment{unlabelled} dependencies to a portion of the data
+929 tweets.  Their annotations added \yicomment{unlabelled?} dependencies to a portion of the data
 annotated with POS tags by 
@@
 \citet{ICWSM101540} and that of UD.
-There is a significant \yicomment{significant? not really} tradeoff between preservation of original tweet content and respecting
+There is a significant \yicomment{significant?} tradeoff between preservation of original tweet content and respecting
 the UD guidelines.
@@
 clitics from contractions (e.g., {\it  gonna} is tokenized as {\it gon} and {\it na}; {\it its}
-is tokenized as {\it it} and {\it s} when {\it s} is a copula)\yicomment{I think the examples are not contractions (can't), is there a name for such words?}. But acronyms are not touched
+is tokenized as {\it it} and {\it s} when {\it s} is a copula)\yicomment{are words like gonna called contractions, or do they have another term?}. But acronyms are not touched
 in the UD tokenization guidelines. Thus, we follow the UD tokenization for contractions
@@
 
-In the different direction of splitting tokens, UD guidelines also suggest to merge \yicomment{suggest merging?}
+In the different direction of splitting tokens, UD guidelines also suggest to merge
 {\it multi-token words} (e.g. {\it 20 000}) into one single token in some special
@@
 
-Before turning to UD \yicomment{dependencies} annotations, we (re)annotated the data with 
-POS \yicomment{tags}, for consistency with other UD efforts,
+Before turning to UD annotations, we (re)annotated the data with 
+POS \yicomment{tags?}, for consistency with other UD efforts,
 which adopt the universal POS tagset of \newcite{PETROV12.274}.
@@
 (\texttt{X}), except for emoticons, which are tagged as \emph{symbol}
-(\texttt{SYM}), following UD\_English.
+(\texttt{SYM}), following UD\_English, seen in Figure \ref{fig:non-syn-toks} as an example.
 
@@
 words be ``normalized'' into explicitly spelled out intermediate
-forms? \yicomment{this sentence should be deleted} \yicomment{As we already know from previous sections, \emph{idc} is not tokenized and tagged as verb, we follow ...}
+forms?
+\yicomment{this sentence should be deleted or moved to tokenization?} \yicomment{As we already know from previous sections, \emph{idc} is not tokenized and tagged as verb, we follow ...} \yicomment{Normalization is discussed in the 2.5.2 Annotation Process.
+Actually we did do normalization, but just as auxiliary info, didn't use it for any model.}
 We follow \citet{kong-EtAl:2014:EMNLP2014} and annotate their
@@
 syntactic functions only constitute 0.06\% of the tokens in our
-dataset, we believe that normalization is an unnecessarily complicated step.\yicomment{this should be moved to tokenization section, but we can mention again here for emphasizing.}
+dataset, we believe that normalization is an unnecessarily complicated step.\yicomment{Again we did normalization!}
 % \nascomment{maybe we owe citations to
@@
 used as content words within a sentence\yicomment{at-mentions can be a normal vocative proper noun}; see Figure
-\ref{fig:informal-toks}.  Therefore, the criteria for \yicomment{whether} annotating a
+\ref{fig:informal-toks}.  Therefore, the criteria for annotating a
 token as non-syntactic must be context-dependent.
@@
 \begin{itemize}
-\item For the at-mentions in retweet constructions, we attach them to their retweet markers. We will discuss our choice in the following paragraph;
-\item For the rest non-syntactic tokens, if one token is within a sentence that has a clear predicate, it will be attached to this predicate.
-If the whole sentence is made of a sequence of non-syntactic tokens, we attach all these tokens to the first one;
+%\item For the at-mentions in retweet constructions, we attach them to their retweet markers. We will discuss our choice in the following paragraph;
+\item If one syntactic token is within a sentence that has a clear predicate, it will be attached to this predicate.
+Retweet construction is a special case and we will discuss our choice in the following paragraph
+\item If the whole sentence is made of a sequence of non-syntactic tokens, we attach all these tokens to the first one;
 %\item In parataxis case, when it is difficult to decide which sentence or phrase x should belong to, we always attach x to the previous predicate of the paratactic clause or phrase;
@@
 might be treated as a verb phrase, with \emph{RT} as a verb and the
-at-mention as its object.  This solution would lead to an uninformative root
+at-mention as its object\yicomment{or might be treated as 2 non-syntactic tokens and a punctuation, which should all attach to the predicate of the following retweeted tweet.}.
+This solution would lead to an uninformative root
 word and, since this expression is idiomatic to Twitter, might create
@@
 label and the colon to \emph{RT} with the \emph{punct}(uation) label,
-and attaching \emph{RT} to the predicate of the following sentence\yicomment{since we have introduced retweet at-mentions in the non-syntactic tokens, here we can just briefly justify our choice.}.
+and attaching \emph{RT} to the predicate of the following sentence.
+%\yicomment{since we have introduced retweet at-mentions in the non-syntactic tokens, here we can just briefly justify our choice.}.
 
@@
 that are especially common in tweets are well handled by UD
-conventions: ellipsis, irregular word orders, and paratactic sentences \yicomment{or phrases/component}
+conventions: ellipsis, irregular word orders, and paratactic sentences \yicomment{or phrases/components}
 not explicitly delineated by punctuation.
@@
 mention sb.
-Both cases are similar to general vocative proper noun case in standard texts}.
+Both cases are similar to general vocative proper noun case in standard texts.
+And we need to exclude at-mentions in Retweet Construction.}.
 We
 treat these at-mentions as vocative expressions, labeling them as
-\emph{proper noun} (\texttt{PROPN})\yicomment{here is confusing that PROPN could be a label in dependencies.
-We can say in POS sections that the decisions on some twitter specific tokens can be made only analyzing syntax together.} and attaching them to the
+\emph{proper noun} (\texttt{PROPN})\yicomment{here is confusing that PROPN could be thought as a label in dependencies.} and attaching them to the
 following predicate with the label \emph{vocative} (see Figure \ref{fig:informal-toks} for an example) \yicomment{just as UD guidelines}.
@@
 \subsection{\sc Tweebank v2}\label{sec:anno-process}
-Following the guidelines presented above, we create a new annotated\yicomment{del?} Twitter \yicomment{Twitter dependency} treebank, which we call {\sc Tweebank v2}.
+Following the guidelines presented above, we create a new annotated\yicomment{del?} Twitter \yicomment{Twitter dependency?} treebank, which we call {\sc Tweebank v2}.
 
@@
 layer of word-level normalization\yicomment{see 10 th col of conllu data, also mention we could recover the original tweets also from this col (tokenization)} was manually annotated for data
-analysis purposes. For example, ``idc'' is annotated as
-`I\_don't\_care' and `4 my FAM' is as `for my familiy'.
+analysis purposes. For example, {\em idc} is annotated as
+`I\_don't\_care' and {\em 4 my FAM} is as `for my familiy'.
 Such normalization doesn't change our tokenization annotation.
-\yicomment{should mention tokenization process, say we tokenize V1 and train tokenizer for V2 data, then manually correct them.
-Good story :)}\yjcomment{add ``a tokenizer''}
+\yicomment{should mention tokenization process, say we tokenize V1 and train tokenizer for V2 data, then manually correct them.}\yjcomment{add ``a tokenizer''}
+\yicomment{add final data split} We obtained 3,550 labelled annotated tweets, split into train/dev/test set with /(639 $+$ 1000)/(210 $+$ 500)/(201 $+$ 1000) tweets, where each set consists of both old tweets from \citet{gimpel-EtAl:2011:ACL-HLT2011} and new tweets from the Twitter stream.
+\yicomment{should also mention main annotators (authors) are non-native English speakers?}
 
@@
 
-We trained our tokenizer on the training portion of
+We trained our tokenizer on the training portion\yicomment{set?} of
 \textsc{Tweebank v2} combined with the UD\_English training dataset
@@
 in tokenization do propagate, but tagging performance is above 93\%
-with our tokenizer.
+with our tokenizer. \yicomment{our POS tagger results on automatically tokenized data?}
 
@@
 
-\paragraph{Ensemble.}  Due both to ambiguity in the training
+\paragraph{Ensemble.}  Due both\yicomment{?} to ambiguity in the training
 data---which most loss functions are not robust to \citep{Frnay2014ClassificationIT}, including the log loss we use, following
@@
 Let $q(a \mid s)$ denote the distilled model's
-probability of an action $a$ given parser state $s$; let $p(a \mid s)$ be the probability under the
+probability of an action $a$ given parser state $s$; let $p(a\mid s)$ be the probability under the
 ensemble (i.e., the average of the 20 separately-trained ensemble
@@
 model).  This presents an opportunity to learn with \emph{exploration}, by
-randomly sampling transitions from the ensemble, found useful
+randomly sampling transitions from the ensemble, \yicomment{we?} found useful
 in recent methods for training greedy models that use dynamic oracles
@@
 our model with a stack of the state-of-the-art systems (namely, the {\it SOTA stack}):
-Stanford CoreNLP tokenizer,
+Stanford CoreNLP tokenizer\yicomment{why not compare with UD pipe?},
 \citet{owoputi-EtAl:2013:NAACL-HLT}'s tagger, and \citet{DBLP:journals/corr/DozatM16}'s parser.
@@
 The results also emphasize the
-importance of segmentation:  without gold segmentation, UD parsing
+importance of segmentation\yicomment{you mean word tokenization or sentence segmentation?}:  without gold segmentation, UD parsing
 performance drops by more than four points.
@@
 special constructions in tweets and create
-the {\sc Tweebank v2}, which has 55,607 tokens. We characterize the disagreements
+the {\sc Tweebank v2}, which has 3,550 tweets\yicomment{add tweet \#} and 55,607 tokens. We characterize the disagreements
 among our annotations and argue that inherent ambiguity in this genre

### 2017-12-05 paper.tex
updates and comments.

@@
 (need to mention the annotation process/pipeline system not only consists parsing in abstract)}, we create
-a new tweet treebank ({\sc Tweebank v2}), which has 3,550 tweets\yicomment{add tweet \#} and 55,607 tokens with
+a new tweet treebank ({\sc Tweebank v2}), which has 3,550 tweets\yicomment{add tweet \#}\yjcomment{didn't see necessity of mentioning \# of tweets} and 55,607 tokens with
 labeled attachments. 
@@
 contributed a new annotated corpus, \textsc{Tweebank}, consisting of
-929 tweets.  Their annotations added \yicomment{unlabelled?} dependencies to a portion of the data
+12,149 tokens.  Their annotations added \yicomment{unlabelled?} dependencies to a portion of the data
 annotated with POS tags by 
@@
 cases. We witnessed a small number of tweets that contain multi-token words
-(e.g. {\it Y O}, and {\it R E T W E E T}) but didn't combine them due to simplification.
+(e.g. {\it Y O}, and {\it R E T W E E T}) but didn't combine them for simplification.
 Such tokens only account for 0.067\% and we use the UD
@@
 
-Tokens that do not have a syntactic function (discussed at greater
+Tokens that do not have a syntactic function (see Figure \ref{fig:non-syn-toks}, discussed at greater
 length in the next section) were usually annotated as \emph{other}
 (\texttt{X}), except for emoticons, which are tagged as \emph{symbol}
-(\texttt{SYM}), following UD\_English, seen in Figure \ref{fig:non-syn-toks} as an example.
+(\texttt{SYM}), following UD\_English.
 
@@
 aggressive tokenization than that of \citet{ICWSM101540} which opted
-out of tokenizing contractions and possessives and it was used by 
-\citet{gimpel-EtAl:2011:ACL-HLT2011}. As a consequence, 
+out of splitting contractions and possessives. As a consequence of adopting \citet{ICWSM101540}'s tokenization, 
 Gimpel et al. introduced new parts of speech for these cases
@@
 \yicomment{this sentence should be deleted or moved to tokenization?} \yicomment{As we already know from previous sections, \emph{idc} is not tokenized and tagged as verb, we follow ...} \yicomment{Normalization is discussed in the 2.5.2 Annotation Process.
-Actually we did do normalization, but just as auxiliary info, didn't use it for any model.}
+Actually we did do normalization, but just as auxiliary info, didn't use it for any model.}\yjcomment{i think acronym is a different story to tokenization.}
 We follow \citet{kong-EtAl:2014:EMNLP2014} and annotate their
@@
 canonically non-syntactic), we adopt the following
-conventions:\yicomment{shall we mention how we segment sentences? Seems relevant here}
+conventions:\yicomment{shall we mention how we segment sentences? Seems relevant here}\yjcomment{i don't want to touch sentence segmentation, it will makes the paper more messy.}
 
@@
 \item If one syntactic token is within a sentence that has a clear predicate, it will be attached to this predicate.
-Retweet construction is a special case and we will discuss our choice in the following paragraph
+Retweet construction is a special case and we will discuss our choice in the following paragraph;
 \item If the whole sentence is made of a sequence of non-syntactic tokens, we attach all these tokens to the first one;
@@
 might be treated as a verb phrase, with \emph{RT} as a verb and the
-at-mention as its object\yicomment{or might be treated as 2 non-syntactic tokens and a punctuation, which should all attach to the predicate of the following retweeted tweet.}.
+at-mention as its object\yicomment{or might be treated as 2 non-syntactic tokens and a punctuation, which should all attach to the predicate of the following retweeted tweet.}\yjcomment{i wouldn't like the readers to think in this direction.}.
 This solution would lead to an uninformative root
@@
 Both cases are similar to general vocative proper noun case in standard texts.
-And we need to exclude at-mentions in Retweet Construction.}.
+And we need to exclude at-mentions in Retweet Construction.}\yjcomment{i didn't see any difference between reply and mention, they all starts with a @username.}.
 We
@@
 \subsubsection{Annotation Process}
+\begin{table}
+	\centering
+	\begin{tabular}{rrrr}
+		\hline
+		& train & dev & test \\
+		\hline
+		tweets 		&	1,639 		&	709		&	1,201\\
+		& +1,000 & +709 & +1,000\\
+		tokens 		&	24,753		&	11,742	&	19,112\\
+		\hline
+	\end{tabular}
+\caption{Statistics of {\sc Tweebank v2}.
+The second column shows the number of new tweets compared to
+{\sc Tweebank v1}.\label{tbl:data-stat}
+}
+\end{table}
 Our annotation process was conducted in three stages.
@@
 of this paper manually corrected the parsed data. Finally, an extra
-layer of word-level normalization\yicomment{see 10 th col of conllu data, also mention we could recover the original tweets also from this col (tokenization)} was manually annotated for data
+layer of word-level normalization\yicomment{see 10 th col of conllu data, also mention we could recover the original tweets also from this col (tokenization)}\yjcomment{didn't get your point.
+if mentioning the normalization here introduce too much confusions, we would better remove these.} was manually annotated for data
 analysis purposes. For example, {\em idc} is annotated as
@@
 \yicomment{should mention tokenization process, say we tokenize V1 and train tokenizer for V2 data, then manually correct them.}\yjcomment{add ``a tokenizer''}
-\yicomment{add final data split} We obtained 3,550 labelled annotated tweets, split into train/dev/test set with /(639 $+$ 1000)/(210 $+$ 500)/(201 $+$ 1000) tweets, where each set consists of both old tweets from \citet{gimpel-EtAl:2011:ACL-HLT2011} and new tweets from the Twitter stream.
+\yicomment{add final data split}\yjcomment{it's better to use table \ref{tbl:data-stat}.
+what's more, i don't think we benefit from re-stating our data source.} We obtained 3,550 labelled annotated tweets, split into train/dev/test set with /(639 $+$ 1000)/(210 $+$ 500)/(201 $+$ 1000) tweets, where each set consists of both old tweets from \citet{gimpel-EtAl:2011:ACL-HLT2011} and new tweets from the Twitter stream.
 \yicomment{should also mention main annotators (authors) are non-native English speakers?}
@@
 in tokenization do propagate, but tagging performance is above 93\%
-with our tokenizer. \yicomment{our POS tagger results on automatically tokenized data?}
+with our tokenizer.
 
@@
 our model with a stack of the state-of-the-art systems (namely, the {\it SOTA stack}):
-Stanford CoreNLP tokenizer\yicomment{why not compare with UD pipe?},
+Stanford CoreNLP tokenizer\yicomment{why not compare with UD pipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
 \citet{owoputi-EtAl:2013:NAACL-HLT}'s tagger, and \citet{DBLP:journals/corr/DozatM16}'s parser.
@@
 The results also emphasize the
-importance of segmentation\yicomment{you mean word tokenization or sentence segmentation?}:  without gold segmentation, UD parsing
+importance of segmentation\yicomment{you mean word tokenization or sentence segmentation?}\yjcomment{we didn't touch sentence seg.}:  without gold segmentation, UD parsing
 performance drops by more than four points.

### 2017-12-11 paper.tex
Noah

@@
 universal dependencies \citep[UD;][]{NIVRE16.348}. We extend the UD guidelines to cover
-special constructions in tweets.
-Using the extended guidelines \yicomment{including tokenization, POS tagging and parsing?
-(need to mention the annotation process/pipeline system not only consists parsing in abstract)}, we create
-a new tweet treebank ({\sc Tweebank v2}), which has 3,550 tweets\yicomment{add tweet \#}\yjcomment{didn't see necessity of mentioning \# of tweets} and 55,607 tokens with
-labeled attachments. 
-It is more than four times larger than the (unlabeled) {\sc Tweebank
+special constructions in tweets that affect tokenization,
+part-of-speech tagging, and dependencies. Using the extended guidelines, we create
+a new tweet treebank ({\sc Tweebank v2}) that is four times larger than the (unlabeled) {\sc Tweebank
   v1} introduced by \citet{kong-EtAl:2014:EMNLP2014}. 
-We characterize the disagreement
-among our annotations and show that it is challenging to deliver
+We characterize the disagreements between our annotators
+and show that it is challenging to deliver
 consistent annotation due to ambiguity in
-understanding and explaining tweets. Using the new treebank,
+understanding and explaining tweets. Nonetheless, using the new treebank,
 we build a pipeline system to parse raw tweets into UD. To overcome the
@@
 method to distill an ensemble of 20 transition-based parsers into a single one. Our
-parser achieves an improvement of 2.6 in LAS over \nascomment{which
-  comparison is this?}\yjcomment{my bad, it was fixed.} the baseline
+parser achieves an improvement of 2.6 in LAS over the un-ensembled baseline 
 and outperforms parsers that are state-of-the-art on other treebanks in both accuracy and speed.
@@
 annotated 7,630 tokens' worth of tweets according to the
-phrase-structure conventions of the Penn Treebank \citep[PTB]{Marcus93buildinga}.
-Stanford dependencies were converted afterwards in their work  \nascomment{by who?}\yjcomment{by themselves}. 
+phrase-structure conventions of the Penn Treebank
+\citep[PTB;][]{Marcus93buildinga}, enabling conversion to Stanford dependencies.
 \citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
@@
 tokenization, part-of-speech (POS) tags, and (labeled) universal dependencies.
-We characterize the disagreement among our annotations \yicomment{annotation(s) and disagreement(s).
-check abstract, same sentence, different singularity/plurality.
-I think should be `disagreement' and `annotations'} and find that
-consistent annotation \yicomment{annotations?} is still challenging to deliver even with
+We characterize the disagreements among our annotators and find that
+consistent annotation is still challenging to deliver even with
 the extended guidelines.
@@
 
-Based on these annotations, we designed a pipeline to parse 
+Based on these annotations, we nonetheless designed a pipeline to parse 
 raw tweets into universal dependencies. Our pipeline includes: a
@@
 transition sequence. Experimental results show that an improvement of more
-than 2.6 points \nascomment{again, not sure what this is quoting}\yjcomment{fixed} in LAS over the
+than 2.6 points in LAS over the
 baseline parser can be achieved with our distillation method and it outperforms
-other state-of-the-art parsers in both accuracy and running speed.
+other state-of-the-art parsers in both accuracy and speed.
 
@@
 
-\item We introduce and evaluate a \yicomment{pipeline} system to parse the raw tweet text into
+\item We introduce and evaluate a pipeline system to parse the raw tweet text into
 universal dependencies (\S\ref{sec:parsing}).  Experimental results show
-it performs better than a stack of the state-of-the-art alternatives.
-\nascomment{say it
-  performs better than existing systems?}\yjcomment{added.}
+it performs better than a pipeline of the state-of-the-art alternatives.
 
@@
 We first review {\sc Tweebank v1} of \citet{kong-EtAl:2014:EMNLP2014},
-which is \yicomment{was?} the largest \yicomment{unlabelled?} Twitter dependencies annotation
+the largest Twitter dependency annotation effort to-date
 (\S\ref{sec:tweebank}).
@@
 
-The annotation effort we describe stands in contrast to \yicomment{the?} previous work
+The annotation effort we describe stands in contrast to the previous work
 by \newcite{kong-EtAl:2014:EMNLP2014}.  Their aim was the rapid
@@
 contributed a new annotated corpus, \textsc{Tweebank}, consisting of
-12,149 tokens.  Their annotations added \yicomment{unlabelled?} dependencies to a portion of the data
+12,149 tokens.  Their annotations added unlabeled dependencies to a portion of the data
 annotated with POS tags by 
@@
 Kong et al.'s rapid, small-scale annotation effort was heavily constrained.  It was
-carried out mostly by nonnative speakers \yicomment{should not emphasize non-native speakers (v2 also built by non-native speakers), but emphasize annotators with only cursory training, no clear annotation guidelines, no consensus/agreement on controversial cases, allow annotators to underspecify part of the tree and allow multiple different trees for the same tweets}, in a very short amount of
+carried out by annotators with only cursory training, no clear
+annotation guidelines, and no effort to achieve consensus on controversial
+cases. Annotators were allowed to underspecify their analyses.
+Most of the work was done in a very short amount of
 time (a day).  Driven both by the style of the text they sought to annotate
@@
   tree.  A clear criterion for exclusion was not given, but many
-  tokens were excluded because they were deemed ``non-syntactic''.
+  tokens were excluded because they were deemed ``non-syntactic.''
 \item Allowing an annotator to merge a multiword expression into a
@@
 \citet{ICWSM101540} and that of UD.
-There is a significant \yicomment{significant?} tradeoff between preservation of original tweet content and respecting
+There is a tradeoff between preservation of original tweet content and respecting
 the UD guidelines.
@@
 clitics from contractions (e.g., {\it  gonna} is tokenized as {\it gon} and {\it na}; {\it its}
-is tokenized as {\it it} and {\it s} when {\it s} is a copula)\yicomment{are words like gonna called contractions, or do they have another term?}. But acronyms are not touched
+is tokenized as {\it it} and {\it s} when {\it s} is a copula).
+%\yicomment{are words like gonna called contractions, or do they have
+%another term?}. \nascomment{yes}
+But acronyms are not touched
 in the UD tokenization guidelines. Thus, we follow the UD tokenization for contractions
-and left acronyms like {\em idc} as a single token. \nascomment{unless we make a change, I think we need to say
-  here that acronyms like \emph{idc} are left as a single token}
-\yjcomment{mentioned acronymns, we don't have the problem of normalization, cause
-normalization was just annotated for data study.}
+and leave acronyms like {\em idc} as a single token. 
+%\nascomment{unless we make a change, I think we need to say
+%  here that acronyms like \emph{idc} are left as a single token}
+%\yjcomment{mentioned acronymns, we don't have the problem of normalization, cause
+% normalization was just annotated for data study.}
 
@@
 Before turning to UD annotations, we (re)annotated the data with 
-POS \yicomment{tags?}, for consistency with other UD efforts,
+POS tags, for consistency with other UD efforts,
 which adopt the universal POS tagset of \newcite{PETROV12.274}.
@@
 For twitter specific linguistic phenomena, we have set different strategies and try to align with the UD conventions and UD\textunderscore English as close as possible.\footnote{\url{https://github.com/UniversalDependencies/UD\_English}}
-In some cases, conflicts arose between the UD English 
-treebank conventions \cite[][UD\_English]{Marneffe2014UniversalSD}\footnote{\url{https://github.com/UniversalDependencies/UD_English}}
+In some cases,  non-corresponding tag conflicts arose between the UD English 
+treebank conventions \cite[UD\_English;][]{Marneffe2014UniversalSD}\footnote{\url{https://github.com/UniversalDependencies/UD_English}}
 and the conventions of \newcite{gimpel-EtAl:2011:ACL-HLT2011} and
-\newcite{owoputi-EtAl:2013:NAACL-HLT}.
-\yicomment{The conflicts should refer to a {\bf noncorresponding tag} from that of gimpel to UDEnglish, cuz they dont have the same tagset.} In these cases, we always
+\newcite{owoputi-EtAl:2013:NAACL-HLT}.  %\yicomment{The conflicts
+                                %should refer to a {\bf
+                                %noncorresponding tag} from that of
+                                %gimpel to UDEnglish, cuz they dont
+                                %have the same tagset.} 
+In these cases, we always
 conformed to UD, enabling consistency (e.g., when we exploit the
@@
 
-\paragraph{Acronym abbreviations.}  How should we syntactically
-analyze acronym tokens like \emph{idc}
-(abbreviating ``I don't care'')
- and \emph{rn} (``right now'')?  Should
-they be decomposed into their component words, and if so should those
-words be ``normalized'' into explicitly spelled out intermediate
-forms?
+\paragraph{Acronym abbreviations.}  % How should we syntactically
+% analyze acronym tokens like \emph{idc}
+% (abbreviating ``I don't care'')
+%  and \emph{rn} (``right now'')?  Should
+% they be decomposed into their component words, and if so should those
+% words be ``normalized'' into explicitly spelled out intermediate
+% forms?
 \yicomment{this sentence should be deleted or moved to tokenization?} \yicomment{As we already know from previous sections, \emph{idc} is not tokenized and tagged as verb, we follow ...} \yicomment{Normalization is discussed in the 2.5.2 Annotation Process.
 Actually we did do normalization, but just as auxiliary info, didn't use it for any model.}\yjcomment{i think acronym is a different story to tokenization.}
-We follow \citet{kong-EtAl:2014:EMNLP2014} and annotate their
-syntax as a single word without normalization. Their syntactic functions
+\nascomment{removed redundant stuff here, please check}
+We follow \citet{kong-EtAl:2014:EMNLP2014} and annotate the
+syntax of an acronym as a single word without normalization. Their syntactic functions
 are decided according to their context. \citet{eisenstein:2013:NAACL-HLT} studied the necessity of normalization
@@
 syntactic functions only constitute 0.06\% of the tokens in our
-dataset, we believe that normalization is an unnecessarily complicated step.\yicomment{Again we did normalization!}
+dataset, we believe that normalization is an unnecessarily complicated
+step.\yicomment{Again we did normalization!} \nascomment{maybe just
+  add ``for acronyms'' to the end of that last sentence?}
 % \nascomment{maybe we owe citations to
@@
 7.55\% of all tokens are non-syntactic; detailed statistics can be found in Table \ref{tbl:non-synt-prop}.
-\yjcomment{I've merged retweet marker and retweet at-mention into one.}
+%\yjcomment{I've merged retweet marker and retweet at-mention into one.}
 
@@
 abbreviate the verb {\tt retweet}, and emoticons and hashtags may be
-used as content words within a sentence\yicomment{at-mentions can be a normal vocative proper noun}; see Figure
+used as content words within a sentence, and at-mentions can be normal vocative proper nouns; see Figure
 \ref{fig:informal-toks}.  Therefore, the criteria for annotating a
@@
 canonically non-syntactic), we adopt the following
-conventions:\yicomment{shall we mention how we segment sentences? Seems relevant here}\yjcomment{i don't want to touch sentence segmentation, it will makes the paper more messy.}
+conventions:
+%\yicomment{shall we mention how we segment sentences? Seems relevant
+%here}\yjcomment{i don't want to touch sentence segmentation, it will
+%makes the paper more messy.}\nascomment{agree with Yijia}
 
@@
 %  e.g., for defining features of the input for parsing}
-In order to keep our annotation conventions in line with UD norms \yicomment{and preserve the original tweets as much as possible},
+In order to keep our annotation conventions in line with UD norms and preserve the original tweets as much as possible,
 we include non-syntactic tokens in our annotation following the
@@
 might be treated as a verb phrase, with \emph{RT} as a verb and the
-at-mention as its object\yicomment{or might be treated as 2 non-syntactic tokens and a punctuation, which should all attach to the predicate of the following retweeted tweet.}\yjcomment{i wouldn't like the readers to think in this direction.}.
+at-mention as its object.
+% \yicomment{or might be treated as 2 non-syntactic tokens and a punctuation, which should all attach to the predicate of the following retweeted tweet.}
+%\yjcomment{i wouldn't like the readers to think in this direction.}.
   This solution would lead to an uninformative root
@@
 that are especially common in tweets are well handled by UD
-conventions: ellipsis, irregular word orders, and paratactic sentences \yicomment{or phrases/components}
+conventions: ellipsis, irregular word orders, and paratactic phrases
+and sentences 
 not explicitly delineated by punctuation.
@@
 \paragraph{Vocative at-mentions.}  Another idiomatic construction on
-Twitter is an at-mention %(followed by a colon \nascomment{?})
-as a sign that a tweet is a reply to a tweet by the mentioned user\yicomment{not necessary, can be just mentioning somebody.
+Twitter is a vocative at-mention (sometimes a
+signal that a tweet is a reply to a tweet by the mentioned user).
+% \yicomment{not necessary, can be just mentioning somebody.
 should be careful to say it.
@@
 We
-treat these at-mentions as vocative expressions, labeling them as
-\emph{proper noun} (\texttt{PROPN})\yicomment{here is confusing that PROPN could be thought as a label in dependencies.} and attaching them to the
-following predicate with the label \emph{vocative} (see Figure \ref{fig:informal-toks} for an example) \yicomment{just as UD guidelines}.
+treat these at-mentions as vocative expressions, labeling them with
+POS tag
+\emph{proper noun} (\texttt{PROPN}) and attaching them to the
+following predicate with the label \emph{vocative} as in UD guidelines (see Figure \ref{fig:informal-toks} for an example).
 
@@
 \subsection{\sc Tweebank v2}\label{sec:anno-process}
-Following the guidelines presented above, we create a new annotated\yicomment{del?} Twitter \yicomment{Twitter dependency?} treebank, which we call {\sc Tweebank v2}.
+Following the guidelines presented above, we create a new Twitter
+dependency treebank, which we call {\sc Tweebank v2}.
 
@@
 \caption{Statistics of {\sc Tweebank v2}.
-The second column shows the number of new tweets compared to
+The second row shows the number of new tweets compared to
 {\sc Tweebank v1}.\label{tbl:data-stat}
@@
 proportion and created the initial annotations in one day.
-Before annotating, they were given a tutorial overview of the \yicomment{general} UD
-annotation conventions and our guidelines \yicomment{specifically for annotating tweets}.
+Before annotating, they were given a tutorial overview of the general UD
+annotation conventions and our guidelines specifically for annotating tweets.
 Both the guidelines and annotations
@@
 of this paper manually corrected the parsed data. Finally, an extra
-layer of word-level normalization\yicomment{see 10 th col of conllu data, also mention we could recover the original tweets also from this col (tokenization)}\yjcomment{didn't get your point.
-if mentioning the normalization here introduce too much confusions, we would better remove these.} was manually annotated for data
+layer of word-level normalization\yicomment{see 10 th col of conllu
+  data, also mention we could recover the original tweets also from
+  this col (tokenization)}\yjcomment{didn't get your point. if
+  mentioning the normalization here introduce too much confusions, we
+  would better remove these.} \nascomment{I don't quite follow; maybe
+  return to extra annotation done for data analysis later, when we get
+to data analysis?} was manually annotated for data
 analysis purposes. For example, {\em idc} is annotated as
@@
 \yicomment{should mention tokenization process, say we tokenize V1 and train tokenizer for V2 data, then manually correct them.}\yjcomment{add ``a tokenizer''}
-\yicomment{add final data split}\yjcomment{it's better to use table \ref{tbl:data-stat}.
-what's more, i don't think we benefit from re-stating our data source.} We obtained 3,550 labelled annotated tweets, split into train/dev/test set with /(639 $+$ 1000)/(210 $+$ 500)/(201 $+$ 1000) tweets, where each set consists of both old tweets from \citet{gimpel-EtAl:2011:ACL-HLT2011} and new tweets from the Twitter stream.
-\yicomment{should also mention main annotators (authors) are non-native English speakers?}
+\yicomment{add final data split}\yjcomment{it's better to use table
+  \ref{tbl:data-stat}. what's more, i don't think we benefit from
+  re-stating our data source.} We obtained 3,550 labelled annotated
+tweets, split into train/development/test set with /(639 $+$
+1000)/(210 $+$ 500)/(201 $+$ 1000) tweets, where each set consists of
+both old tweets from \citet{gimpel-EtAl:2011:ACL-HLT2011} and new
+tweets from the Twitter stream. \nascomment{I agree that counts and
+  such should go in tables} \yicomment{should also mention main
+  annotators (authors) are non-native English speakers?}
+\nascomment{I'm torn about that.  has it been brought up in other datasets?}
 
@@
 We report the inter-annotator agreement between the annotators
-in the second stage. There is few disagreement on the tokenization annotation.
+in the second stage. There is very little disagreement on the
+tokenization annotation \nascomment{still better to quantify}.
 The agreement on POS is 96.6\%, the unlabeled
@@
 is 84.3\%. Further analysis shows the major disagreements on POS
-involve entity names (30.6\%) \yicomment{noun phrases or proper noun phrases, do we need example here?}\yjcomment{i wasn't counting PROPN and NOUN confusion, but any type of confusion related with PROPN} and topical hashtags (18.1\%).
-Taking the example in Figure \ref{fig:non-syn-toks}, ``Fix you'' \yicomment{need to relate to previous error analysis, entity names maybe?}can
+involve entity names (30.6\%) %\yicomment{noun phrases or proper noun
+                              %phrases, do we need example
+                              %here?}\yjcomment{i wasn't counting
+                              %PROPN and NOUN confusion, but any type
+                              %of confusion related with PROPN}
+                              %\nascomment{probably don't need examples}
+and topical hashtags (18.1\%).
+Taking the example in Figure \ref{fig:non-syn-toks}, ``Fix you'' 
+%\yicomment{need to relate to previous error analysis, entity names
+%maybe?}
+can
 be understood as a verbal phrase but also as the name of the Coldplay's
 single and tagged as proper noun. 
-\yicomment{need to say the reason why dependency inter-annotator agreement is low?
-1.
-POS disagreement lead to big difference in understanding the semantics.
-2.
-Some special constructions like ellipsis lead to different view of tweets.
-Fig3 is an example of 2.}An example of a disagreement on
+%\yicomment{need to say the reason why dependency inter-annotator
+%agreement is low? 1. POS disagreement lead to big difference in
+%understanding the semantics. 2. Some special constructions like
+%ellipsis lead to different view of tweets. Fig3 is an example of 2.}
+%\nascomment{I don't think we have room to go deeper}
+An example of a disagreement on
 dependencies is shown in Figure \ref{fig:disagree}.  Depending on
@@
 instead of GRU in our model and we also use a larger size of hidden units (64 against 20),
-which has stronger representation power. \nascomment{we need to say what their model was;
-  why does ours work better?  from their paper, it seems that they
-  used a GRU instead of an LSTM ... is that all?  do we win because of
-better tuning, or what?}\yjcomment{done.}
+which has stronger representation power. 
 Our bi-LSTM tokenizer achieves the best accuracy among all these
@@
 
-Results of the \citet{owoputi-EtAl:2013:NAACL-HLT}  with non-greedy
+Results of the \citet{owoputi-EtAl:2013:NAACL-HLT}  tagger with non-greedy
 inference on automatically tokenized data
@@
 Social media applications typically require processing large volumes
-of data, making speed an important desideratum. We therefore 
+of data, making speed an important consideration. We therefore 
 begin with the neural greedy stack LSTM parser introduced by \newcite{ballesteros-EtAl:2016:EMNLP2016},
@@
 labeled attachment score (including punctuation) are reported.
-All the experiments were ran on a Xeon E5-2670 2.6 GHz machine.
+All the experiments were run on a Xeon E5-2670 2.6 GHz machine.
 
@@
 effect, we report the average of five differently-seeded runs, for
-each of our models and the compared ones. \nascomment{please check! we did this for all systems,
-  not just ours, right?}\yjcomment{yes. added}
+each of our models and the compared ones.
 
@@
 		\hline
-		\it System & UAS & LAS & SP \\
+		\it System & UAS & LAS & Kt/s \\
 		\hline
@@
 	\caption{Dependency parser comparison on \textsc{Tweebank v2},
-           with automatic POS tags. The {\it SP} column shows
-           the parsing speed evaluated by the number of thousand tokens
+           with automatic POS tags. The ``Kt/s'' column shows
+           the parsing speed evaluated by thousands of tokens
            the model processed per second. For fair comparison, we limit the
-           number of CPU used in \citet{DBLP:journals/corr/DozatM16} experiments to 1.
+           number of CPUs used in \citet{DBLP:journals/corr/DozatM16} experiments to 1.
             \label{tbl:parse-result}}
@@
  \citet{DBLP:journals/corr/DozatM16}, both of which are graph-based
- parsers requiring superlinear runtime. \nascomment{can we quantify
-   how much time each one takes, either in tweets parsed per second or
-   seconds per tweet?}\yjcomment{done.}
+ parsers requiring superlinear runtime. 
 Both of the comparison systems are re-trained on the same data as our
 system.
-Our system lags behind by nearly two LAS
+Our baseline lags behind by nearly two LAS
 points but runs faster than both of them.
 
-\begin{table*}[t]
+\begin{table}[t]
 	\centering
@@
 		\hline
-		\it Pipeline & Metrics & ours & SOTA stack\\
-		\hline
-		Tokenization & \it F1 & 98.3 & 96.6 \\		
-		POS tagging &  \it Precision F1 & 93.7 & 92.1 \\
-		Universal dependencies & \it LAS F1 & 74.1 & 70.3 \\
+		 Pipeline stage & Score & Ours & SOTA \\
+		\hline
+		Tokenization  & \it $F_1$ & 98.3 & 96.6 \\		
+		POS tagging &  \it Precision $F_1$ & 93.7 & 92.1 \\
+		UD parsing & \it LAS $F_1$ & 74.1 & 70.3 \\
 		\hline
 	\end{tabular}
-	\caption{Evaluating our model in pipeline
-		manner. \nascomment{should this be ``F1''?  shouldn't the
-			last line be LAS?}\yjcomment{added metrics column}\label{tbl:pipline} }
-\end{table*}
-
-\paragraph{Ensemble.}  Due both\yicomment{?} to ambiguity in the training
+	\caption{Evaluating our pipeline against a state-of-the-art pipeline. \nascomment{what is ``precision $F_1$?}\label{tbl:pipline} }
+\end{table}
+
+\paragraph{Ensemble.}  Due to ambiguity in the training
 data---which most loss functions are not robust to \citep{Frnay2014ClassificationIT}, including the log loss we use, following
@@
 
-Our approach follows \newcite{DBLP:journals/corr/HintonVD15}
-and \newcite{kim-rush:2016:EMNLP2016}.  
+Our approach applies techniques from \newcite{DBLP:journals/corr/HintonVD15}
+and \newcite{kim-rush:2016:EMNLP2016} to parsing.
 Note that training a transition-based parser typically involves the
@@
 model).  This presents an opportunity to learn with \emph{exploration}, by
-randomly sampling transitions from the ensemble, \yicomment{we?} found useful
+randomly sampling transitions from the ensemble, found useful
 in recent methods for training greedy models that use dynamic oracles
@@
 pipeline's performance in  Table \ref{tbl:pipline}. We also compare
-our model with a stack of the state-of-the-art systems (namely, the {\it SOTA stack}):
+our model with a pipeline of the state-of-the-art systems (labeled  ``SOTA''):
 Stanford CoreNLP tokenizer\yicomment{why not compare with UD pipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
 \citet{owoputi-EtAl:2013:NAACL-HLT}'s tagger, and \citet{DBLP:journals/corr/DozatM16}'s parser.
-Our system differs with the SOTA stack in the tokenization and parser components.
-From Table \ref{tbl:pipline}, our system outperforms the SOTA stack when
+Our system differs from the SOTA pipeline in the tokenization and parser components.
+From Table \ref{tbl:pipline}, our pipeline outperforms the SOTA when
 evaluated in pipeline manner.
 The results also emphasize the
-importance of segmentation\yicomment{you mean word tokenization or sentence segmentation?}\yjcomment{we didn't touch sentence seg.}:  without gold segmentation, UD parsing
+importance of tokenization:  without gold tokenization
+\nascomment{changed ``segmentation'' to ``tokenization'' here, twice}, UD parsing
 performance drops by more than four points.
@@
 special constructions in tweets and create
-the {\sc Tweebank v2}, which has 3,550 tweets\yicomment{add tweet \#} and 55,607 tokens. We characterize the disagreements
-among our annotations and argue that inherent ambiguity in this genre
+the {\sc Tweebank v2}, which has 3,550 tweets  and 55,607 tokens. We characterize the disagreements
+among our annotators and argue that inherent ambiguity in this genre
 makes
-consistent annotaiton a challenge.  Using this new treebank,
+consistent annotation a challenge.  Using this new treebank,
 we build a pipeline system to parse tweets into UD. We also 
@@
 to overcome annotation noise without sacrificing efficiency.
-Our parser achieves an improvement of 2.6  \nascomment{which
-  comparison are you quoting here?}\yjcomment{fixed} in LAS over a strong baseline
+Our parser achieves an improvement of 2.6  in LAS over a strong baseline
 and outperforms other state-of-the-art parsers in both accuracy and speed.

### 2017-12-12 paper.tex
remove our postagger, remove normalization.

@@
 Actually we did do normalization, but just as auxiliary info, didn't use it for any model.}\yjcomment{i think acronym is a different story to tokenization.}
-\nascomment{removed redundant stuff here, please check}
 We follow \citet{kong-EtAl:2014:EMNLP2014} and annotate the
@@
 syntactic functions only constitute 0.06\% of the tokens in our
-dataset, we believe that normalization is an unnecessarily complicated
-step.\yicomment{Again we did normalization!} \nascomment{maybe just
-  add ``for acronyms'' to the end of that last sentence?}
+dataset, we believe that normalization for acronyms is an unnecessarily complicated
+step.
 % \nascomment{maybe we owe citations to
@@
 \begin{tabular}{lrr}
+\hline
 \multicolumn{2}{r}{syntactic (\%)} & non-syntactic (\%)\\ \hline
@@
  total & 2.08 & 7.55 \\
+ \hline
 \end{tabular}
@@
 		\begin{deptext}
-			@username \& its \& \#awesome \& u \& gonna \& $\heart$ \& it \& Chk \& out \& our \& cooool \& project \& on \& http:// \& + \& RT \& pls\\
+			@username \& its \& \#awesome \& u \& gonna \& $\heart$ \& it \& Chk \& out \& our \& cooool \& project \& on \& http://project\_link \& + \& RT \& pls\\
 			\tiny PROPN \& \tiny PRON \& \tiny ADJ \& \tiny PRON \& \tiny VERB \& \tiny VERB \& \tiny PRON \& \tiny VERB \& \tiny ADP \& \tiny PRON \& \tiny ADJ \& \tiny NOUN \& \tiny ADP \& \tiny X \& \tiny SYM \& \tiny VERB\& \tiny INTJ\\
@@
 For example, besides being a discourse marker, \emph{RT} can
-abbreviate the verb {\tt retweet}, and emoticons and hashtags may be
+abbreviate the verb {\it retweet}, and emoticons and hashtags may be
 used as content words within a sentence, and at-mentions can be normal vocative proper nouns; see Figure
@@
 \end{table}
-Our annotation process was conducted in three stages.
+Our annotation process was conducted in two stages.
 In the first stage, 18 researchers worked on the {\sc Tweebank v1}
@@
 and used to automatically analyze the sampled 2,500 tweets.  Authors 
-of this paper manually corrected the parsed data. Finally, an extra
-layer of word-level normalization\yicomment{see 10 th col of conllu
-  data, also mention we could recover the original tweets also from
-  this col (tokenization)}\yjcomment{didn't get your point. if
-  mentioning the normalization here introduce too much confusions, we
-  would better remove these.} \nascomment{I don't quite follow; maybe
-  return to extra annotation done for data analysis later, when we get
-to data analysis?} was manually annotated for data
-analysis purposes. For example, {\em idc} is annotated as
-`I\_don't\_care' and {\em 4 my FAM} is as `for my familiy'.
-Such normalization doesn't change our tokenization annotation.
+of this paper manually corrected the parsed data and finally achieved 3,550 labeled tweets.
+Newly created annotations are splitted into train, development, and test set and appended
+to the original split of {\sc Twebank v1}. Statistics of our annotations and data split are shown
+in Table \ref{tbl:data-stat}.
+
+%Finally, an extra
+%layer of word-level normalization\yicomment{see 10 th col of conllu
+%  data, also mention we could recover the original tweets also from
+%  this col (tokenization)}\yjcomment{didn't get your point. if
+%  mentioning the normalization here introduce too much confusions, we
+%  would better remove these.} \nascomment{I don't quite follow; maybe
+%  return to extra annotation done for data analysis later, when we get
+%to data analysis?} was manually annotated for data
+%analysis purposes. For example, {\em idc} is annotated as
+%`I\_don't\_care' and {\em 4 my FAM} is as `for my familiy'.
+%Such normalization doesn't change our tokenization annotation.
 \yicomment{should mention tokenization process, say we tokenize V1 and train tokenizer for V2 data, then manually correct them.}\yjcomment{add ``a tokenizer''}
-\yicomment{add final data split}\yjcomment{it's better to use table
-  \ref{tbl:data-stat}. what's more, i don't think we benefit from
-  re-stating our data source.} We obtained 3,550 labelled annotated
-tweets, split into train/development/test set with /(639 $+$
-1000)/(210 $+$ 500)/(201 $+$ 1000) tweets, where each set consists of
-both old tweets from \citet{gimpel-EtAl:2011:ACL-HLT2011} and new
-tweets from the Twitter stream. \nascomment{I agree that counts and
-  such should go in tables} \yicomment{should also mention main
-  annotators (authors) are non-native English speakers?}
-\nascomment{I'm torn about that.  has it been brought up in other datasets?}
+%\yicomment{add final data split}\yjcomment{it's better to use table
+%  \ref{tbl:data-stat}. what's more, i don't think we benefit from
+%  re-stating our data source.}
+%We obtained 3,550 labeled tweets, splitted them into train/development/test set.
+%1000)/(210 $+$ 500)/(201 $+$ 1000) tweets, where each set consists of
+%both old tweets from \citet{gimpel-EtAl:2011:ACL-HLT2011} and new
+%tweets from the Twitter stream. \nascomment{I agree that counts and
+%  such should go in tables} \yicomment{should also mention main
+%  annotators (authors) are non-native English speakers?}
+%\nascomment{I'm torn about that.  has it been brought up in other datasets?}
 
@@
 in the second stage. There is very little disagreement on the
-tokenization annotation \nascomment{still better to quantify}.
+tokenization annotation. % \nascomment{still better to quantify}.
 The agreement on POS is 96.6\%, the unlabeled
@@
 	\includegraphics[width=\columnwidth,trim={0 0 11cm 9cm},clip]{graphics/bilstm_tokenizer}
-	\caption{The bi-LSTM tokenizer model that segments `its gonna be' into `it s gon na be'.}\label{fig:tok-model}
+	\caption{The bi-LSTM tokenizer that segments `{\it its gonna be}' into `{\it it s gon na be}'.}\label{fig:tok-model}
 \end{figure}
@@
 		\hline
-		\it System & \it F1 \\
+		\it System & F1 \\
 		\hline
@@
 % 		UD pipe v1.2 & 94.7 \\
+		\hdashline
 		UD pipe v1.2 & 97.3 \\
-	 	our bi-LSTM tokenizer & \bf 98.3 \\
+	 	our bi-LSTM tokenizer & 98.3 \\
 		\hline
@@
 
-We trained our tokenizer on the training portion\yicomment{set?} of
-\textsc{Tweebank v2} combined with the UD\_English training dataset
+We trained our tokenizer on the training portion of
+\textsc{Tweebank v2} combined with the UD\_English training set
 and tested on the \textsc{Tweebank v2} test set. 
@@
 
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=\columnwidth,trim={0 0 11cm 3cm},clip]{graphics/bilstm_postagger}
-	\caption{The bi-LSTM POS tagger model that tags `it s gon na be' as {\tt PRON AUX VERB PART AUX}.}\label{fig:pos-model}
-	%\yicomment{i'm a little confused by the pic, need discussion}
-\end{figure}
-
-Part-of-speech tagging for tweets has been extensively studied \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}.
+%\begin{figure}[t]
+%	\centering
+%	\includegraphics[width=\columnwidth,trim={0 0 11cm 3cm},clip]{graphics/bilstm_postagger}
+%	\caption{The bi-LSTM POS tagger model that tags `it s gon na be' as {\tt PRON AUX VERB PART AUX}.}\label{fig:pos-model}
+%	%\yicomment{i'm a little confused by the pic, need discussion}
+%\end{figure}
+
+Part-of-speech tagging for tweets has been extensively studied \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,derczynski-EtAl:2013:RANLP-2013,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}.
 On the annotation scheme designed in \S\ref{sec:pos-anno}, based on UD and adapted for
-Twitter, we compared several existing systems and also two bi-LSTM systems similar
-to \citet{DBLP:journals/corr/HuangXY15} and \citet{lample-EtAl:2016:N16-1}, one using
-word vectors and the other using word and character vectors (see Figure \ref{fig:pos-model}).
+Twitter, we compared several existing systems which include the Stanford CoreNLP tagger, 
+\citet{owoputi-EtAl:2013:NAACL-HLT}'s word cluster enhanced tagger (both in greedy and CRF), and 
+also \citet{ma-hovy:2016:P16-1}'s neural network POS tagger 
+which has the state-of-the-art performance  on Penn Treebank data.
+ %and also two bi-LSTM systems similar
+%to \citet{DBLP:journals/corr/HuangXY15} and \citet{lample-EtAl:2016:N16-1}, one using
+%word vectors and the other using word and character vectors (see Figure \ref{fig:pos-model}).
 All systems were re-trained on the combination of the UD\_English and 
@@
 		\hline
-		\it System & \it Precision \\
+		\it System & Precision \\
 		\hline
@@
 		\citealp{owoputi-EtAl:2013:NAACL-HLT} (greedy) & 94.2 \\
-		\citealp{owoputi-EtAl:2013:NAACL-HLT} (CRF) & \bf 95.1 \\
+		\citealp{owoputi-EtAl:2013:NAACL-HLT} (CRF) & 95.1 \\
 		\hdashline
@@
 		\citealp{ma-hovy:2016:P16-1} & 91.8 \\
-		our word bi-LSTM & 89.2 \\
-		our character + word bi-LSTMs & 91.5 \\
+%		our word bi-LSTM & 89.2 \\
+%		our character + word bi-LSTMs & 91.5 \\
 		\hline
@@
 with gold-standard tokenization are shown in
-Table \ref{tbl:pos-result}. The careful feature engineering in the 
-POS tagger of \citet{owoputi-EtAl:2013:NAACL-HLT} outperforms our neural network
-models.  (That tagger also makes use of \citet{Brown:1992:CNG:176313.176316} clusters derived
-from a large collection of unannotated tweets.  Those clusters did not
-improve the performance of our bi-LSTM models.)
+Table \ref{tbl:pos-result}. The careful feature engineering and making use of
+\citet{Brown:1992:CNG:176313.176316} clusters in the 
+POS tagger of \citet{owoputi-EtAl:2013:NAACL-HLT} outperforms \citet{ma-hovy:2016:P16-1}'s neural network
+model. 
+%tagger
+%also makes use of clusters derived
+%from a large collection of unannotated tweets. % Those clusters did not
+%improve the performance of our bi-LSTM models.)
 
@@
 points but runs faster than both of them.
-
-\begin{table}[t]
-	\centering
-	\begin{tabular}{rrcc}
-		\hline
-		 Pipeline stage & Score & Ours & SOTA \\
-		\hline
-		Tokenization  & \it $F_1$ & 98.3 & 96.6 \\		
-		POS tagging &  \it Precision $F_1$ & 93.7 & 92.1 \\
-		UD parsing & \it LAS $F_1$ & 74.1 & 70.3 \\
-		\hline
-	\end{tabular}
-	\caption{Evaluating our pipeline against a state-of-the-art pipeline. \nascomment{what is ``precision $F_1$?}\label{tbl:pipline} }
-\end{table}
 
@@
 ensemble (i.e., the average of the 20 separately-trained ensemble
-members) \nascomment{check} \yjcomment{checked}.
+members).
 To train the distilled model, we minimize the interpolation between
@@
 
+\begin{table}[t]
+	\centering
+	\begin{tabular}{rrcc}
+		\hline
+		\it Pipeline stage & Score & Ours & SOTA \\
+		\hline
+		Tokenization  & \it $F_1$ & 98.3 & 96.6 \\		
+		POS tagging &  \it  $F_1$ & 93.7 & 92.1 \\
+		UD parsing & \it LAS $F_1$ & 74.1 & 70.3 \\
+		\hline
+	\end{tabular}
+	\caption{Evaluating our pipeline against a state-of-the-art pipeline. \label{tbl:pipline} }
+\end{table}
+
 \paragraph{Pipeline evaluation.} Finally, we report  our full
@@
 our model with a pipeline of the state-of-the-art systems (labeled  ``SOTA''):
-Stanford CoreNLP tokenizer\yicomment{why not compare with UD pipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
+Stanford CoreNLP tokenizer, %\yicomment{why not compare with UD pipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
 \citet{owoputi-EtAl:2013:NAACL-HLT}'s tagger, and \citet{DBLP:journals/corr/DozatM16}'s parser.
@@
 importance of tokenization:  without gold tokenization
-\nascomment{changed ``segmentation'' to ``tokenization'' here, twice}, UD parsing
+%\nascomment{changed ``segmentation'' to ``tokenization'' here, twice},
+UD parsing
 performance drops by more than four points.

### 2017-12-13 paper.tex
minor change

@@
 \section{Introduction}
-NLP for social media messages is challenging, both because domain
+NLP for social media messages is challenging, both\yicomment{not only? `both' is still strange to me} because domain
 adaptation is required, but also because creating annotated datasets
@@
 in the UD tokenization guidelines. Thus, we follow the UD tokenization for contractions
-and leave acronyms like {\em idc} as a single token. 
+and leave acronyms like {\em idc} (``I don't care'') as a single token. 
 %\nascomment{unless we make a change, I think we need to say
@@
 
-Tokens that abbreviate multiple words, such as \emph{idc} (``I don't
-care'') are resolved to the POS of the syntactic head of the
+Tokens that abbreviate multiple words, such as \emph{idc} are resolved to the POS of the syntactic head of the
 expression, following UD conventions (in this example, the head \emph{care} is
@@
 		\begin{deptext}
-			@username \& its \& \#awesome \& u \& gonna \& $\heart$ \& it \& Chk \& out \& our \& cooool \& project \& on \& http://project\_link \& + \& RT \& pls\\
-			\tiny PROPN \& \tiny PRON \& \tiny ADJ \& \tiny PRON \& \tiny VERB \& \tiny VERB \& \tiny PRON \& \tiny VERB \& \tiny ADP \& \tiny PRON \& \tiny ADJ \& \tiny NOUN \& \tiny ADP \& \tiny X \& \tiny SYM \& \tiny VERB\& \tiny INTJ\\
+			@username \& its \& \#awesome \& u \& gonna \& $\heart$ \& it \& Chk \& out \& our \& cooool \& project \& on \& http://project\_link \& + \& RT \& it\\
+			\tiny PROPN \& \tiny PRON \& \tiny ADJ \& \tiny PRON \& \tiny VERB \& \tiny VERB \& \tiny PRON \& \tiny VERB \& \tiny ADP \& \tiny PRON \& \tiny ADJ \& \tiny NOUN \& \tiny ADP \& \tiny X \& \tiny SYM \& \tiny VERB\& \tiny PRON\\
 		\end{deptext}
@@
 		\depedge[edge unit distance=1em]{16}{15}{cc}
-		\depedge[edge unit distance=0.37em]{3}{17}{discourse}
+		\depedge[edge unit distance=0.37em]{16}{17}{obj}
 	\end{dependency}
@@
 %\item For the at-mentions in retweet constructions, we attach them to their retweet markers. We will discuss our choice in the following paragraph;
-\item If one syntactic token is within a sentence that has a clear predicate, it will be attached to this predicate.
+\item If a non-syntactic token is within a sentence that has a clear predicate, it will be attached to this predicate.
 Retweet construction is a special case and we will discuss our choice in the following paragraph;
@@
 Part-of-speech tagging for tweets has been extensively studied \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,derczynski-EtAl:2013:RANLP-2013,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}.
+We therefore opt for the existing POS taggers for tweets instead of developing our own's.
 On the annotation scheme designed in \S\ref{sec:pos-anno}, based on UD and adapted for
@@
 our model with a pipeline of the state-of-the-art systems (labeled  ``SOTA''):
-Stanford CoreNLP tokenizer, %\yicomment{why not compare with UD pipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
+Stanford CoreNLP tokenizer\footnote{We choose Stanford CoreNLP tokenizer in the spirit of comparing rule-based and statistical model-based method.}, %\yicomment{why not compare with UD pipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
 \citet{owoputi-EtAl:2013:NAACL-HLT}'s tagger, and \citet{DBLP:journals/corr/DozatM16}'s parser.

### 2017-12-13 paper.tex
remove yi's comment, db.

@@
 \newcommand{\nascomment}[1]{\textcolor{blue}{[#1 ---\textsc{nas}]}}
-\newcommand{\yicomment}[1]{\textcolor{gray}{[#1 ---\textsc{Yi}]}}
+\newcommand{\yicomment}[1]{\textcolor{gray}{[#1 ---\textsc{yi}]}}
 %\newcommand{\yjcomment}[1]{}
@@
 \section{Introduction}
-NLP for social media messages is challenging, both\yicomment{not only? `both' is still strange to me} because domain
+NLP for social media messages is challenging, both because domain
 adaptation is required, but also because creating annotated datasets

### 2017-12-13 paper.tex
Noah

@@
 \section{Introduction}
-NLP for social media messages is challenging, both because domain
-adaptation is required, but also because creating annotated datasets
+NLP for social media messages is challenging, because domain
+adaptation is required, and also because creating annotated datasets
 (e.g., treebanks)
@@
 than 2.6 points in LAS over the
-baseline parser can be achieved with our distillation method and it outperforms
+baseline parser can be achieved with our distillation method.  It outperforms
 other state-of-the-art parsers in both accuracy and speed.
@@
 \item We study the challenges of annotating tweets in UD (\S\ref{sec:anno})
-and created a new tweet treebank ({\sc Tweebank v2}), which includes 
-tokenization, part-of-speech tagging, and labeled universal dependencies annotation.
+and create a new tweet treebank ({\sc Tweebank v2}), which includes 
+tokenization, part-of-speech tagging, and labeled universal dependencies.
 We also characterize the difficulties of creating such annotation.
@@
 We first review {\sc Tweebank v1} of \citet{kong-EtAl:2014:EMNLP2014},
-the largest Twitter dependency annotation effort to-date
+the previous largest Twitter dependency annotation effort 
 (\S\ref{sec:tweebank}).
@@
 In the different direction of splitting tokens, UD guidelines also suggest to merge
-{\it multi-token words} (e.g. {\it 20 000}) into one single token in some special
+{\it multi-token words} (e.g., {\it 20 000}) into one single token in some special
 cases. We witnessed a small number of tweets that contain multi-token words
-(e.g. {\it Y O}, and {\it R E T W E E T}) but didn't combine them for simplification.
+(e.g., {\it Y O}, and {\it R E T W E E T}) but didn't combine them for simplification.
 Such tokens only account for 0.067\% and we use the UD
@@
 out of splitting contractions and possessives. As a consequence of adopting \citet{ICWSM101540}'s tokenization, 
-Gimpel et al. introduced new parts of speech for these cases
+Gimpel et al.~introduced new parts of speech for these cases
 instead.\footnote{These tags only account for 2.7\% of tokens,
@@
 Figure \ref{fig:tok-model} shows our tokenization model.
-Space is treated as an input but consistently assigned a special tag \$.
+Space is treated as an input but deterministically \nascomment{check
+  here}  assigned a special tag \$.
 
@@
 		\hline
-		\it System & F1 \\
+		\it System & $F_1$ \\
 		\hline
@@
 Part-of-speech tagging for tweets has been extensively studied \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,derczynski-EtAl:2013:RANLP-2013,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}.
-We therefore opt for the existing POS taggers for tweets instead of developing our own's.
+We therefore consider existing POS taggers for tweets instead of developing our own.
 On the annotation scheme designed in \S\ref{sec:pos-anno}, based on UD and adapted for
-Twitter, we compared several existing systems which include the Stanford CoreNLP tagger, 
-\citet{owoputi-EtAl:2013:NAACL-HLT}'s word cluster enhanced tagger (both in greedy and CRF), and 
-also \citet{ma-hovy:2016:P16-1}'s neural network POS tagger 
+Twitter, we compared several existing systems: the Stanford CoreNLP tagger, 
+\citet{owoputi-EtAl:2013:NAACL-HLT}'s word cluster enhanced tagger
+(both greedy and CRF variants), and 
+\citet{ma-hovy:2016:P16-1}'s neural network POS tagger 
 which has the state-of-the-art performance  on Penn Treebank data.
@@
 All systems were re-trained on the combination of the UD\_English and 
-\textsc{Tweebank v2} training sets. We use Twitter-specific glove embeddings released by
+\textsc{Tweebank v2} training sets. We use Twitter-specific Glove embeddings released by
 \citet{pennington-socher-manning:2014:EMNLP2014} in all neural taggers
@@
 		\hline
-		\it System & F1 \\
+		\it Tokenization System & $F_1$ \\
 		\hline
@@
 which can parse a sentence in linear time and harnesses 
-character representations, which should help mitigate the challenge of
+character representations to construct word vectors, which should help mitigate the challenge of
 spelling variation. We encourage the reader to refer their paper for
@@
 79.4, outperforming all three systems above (Table~\ref{tbl:parse-result}).
-However, ensembling 20 parsers also significantly slows down the parsing
-speed and leads to the slowest system in our comparison.
 
@@
 course, that it requires twenty times the runtime of a single greedy
-parser.  \newcite{kuncoro-16} proposed the distillation of 20
+parser, making it the slowest system in our comparison.  \newcite{kuncoro-16} proposed the distillation of 20
 greedy transition-based parser into a single \emph{graph-based}

### 2017-12-14 paper.tex
add more word on the compared system, fit into 8 pages.

@@
 Figure \ref{fig:tok-model} shows our tokenization model.
-Space is treated as an input but deterministically \nascomment{check
-  here}  assigned a special tag \$.
+Space is treated as an input but deterministically  assigned a special tag \$.
 
@@
 (both greedy and CRF variants), and 
-\citet{ma-hovy:2016:P16-1}'s neural network POS tagger 
-which has the state-of-the-art performance  on Penn Treebank data.
+\citet{ma-hovy:2016:P16-1}'s neural network tagger 
+which achieves the state-of-the-art performance on PTB.
+\citet{gui-EtAl:2017:EMNLP20172} presented the state-of-the-art neural tagger for Twitter,
+but their code didn't work beyond PTB tag set.
+Thus, we didn't include their tagger in our comparison.\yjcomment{i put some words on \cite{gui-EtAl:2017:EMNLP20172} in case the reviewer challenge our neural/non-neural comparsion.}
  %and also two bi-LSTM systems similar
@@
 %word vectors and the other using word and character vectors (see Figure \ref{fig:pos-model}).
-All systems were re-trained on the combination of the UD\_English and 
+All compared systems were re-trained on the combination of the UD\_English and 
 \textsc{Tweebank v2} training sets. We use Twitter-specific Glove embeddings released by
@@
 		\citet{kong-EtAl:2014:EMNLP2014} &81.6 & 77.2 & 0.3 \\
-		\citet{DBLP:journals/corr/DozatM16} & 81.9 &  77.7 & 1.7 \\
+		\citet{dozat-qi-manning:2017:K17-3} & 81.9 &  77.7 & 1.7 \\
 %		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
@@
            the model processed per second. For fair comparison, we limit the
-           number of CPUs used in \citet{DBLP:journals/corr/DozatM16} experiments to 1.
+           number of CPUs used in \citet{dozat-qi-manning:2017:K17-3} experiments to 1.
             \label{tbl:parse-result}}
@@
 in the CoNLL 2017 evaluations, due to
- \citet{DBLP:journals/corr/DozatM16}, both of which are graph-based
- parsers requiring superlinear runtime. 
-Both of the comparison systems are re-trained on the same data as our
-system.
+ \citet{dozat-qi-manning:2017:K17-3}.
+ \citet{kong-EtAl:2014:EMNLP2014}'s parser is a graph-based
+parser with lexical features and word cluster and it uses dual decomposition
+for decoding. The parser in \citet{dozat-qi-manning:2017:K17-3} is also a graph-based parser
+but includes character-based word representation and uses the biaffine classifier
+to predict if an attachment exists between two words.
+Both of the compared systems require superlinear runtime due to graph-based parsing. 
+They are re-trained on the same data as our
+system. \yjcomment{i briefly describ the compared systems.}
 Our baseline lags behind by nearly two LAS
@@
 Stanford CoreNLP tokenizer\footnote{We choose Stanford CoreNLP tokenizer in the spirit of comparing rule-based and statistical model-based method.}, %\yicomment{why not compare with UD pipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
-\citet{owoputi-EtAl:2013:NAACL-HLT}'s tagger, and \citet{DBLP:journals/corr/DozatM16}'s parser.
+\citet{owoputi-EtAl:2013:NAACL-HLT}'s tagger, and \citet{dozat-qi-manning:2017:K17-3}'s parser.
 Our system differs from the SOTA pipeline in the tokenization and parser components.

### 2017-12-14 paper.tex
minor change, some check

@@
   tree.  A clear criterion for exclusion was not given, but many
-  tokens were excluded because they were deemed ``non-syntactic.''
+  tokens were excluded because they were deemed ``non-syntactic.'' \yicomment{including some Twitter specific tokens, which we will refine the definition in Section 2.3 and 2.4?}
 \item Allowing an annotator to merge a multiword expression into a
@@
 (e.g., {\it Y O}, and {\it R E T W E E T}) but didn't combine them for simplification.
-Such tokens only account for 0.067\% and we use the UD
+Such tokens only account for 0.07\% and we use the UD
   {\it goeswith} relation to resolve these cases in the dependency annotations.
@@
 a large proportion of tokens don't carry any syntactic function. 
-In our annotation, there are five types of non-syntactic tokens: 
+Apart from conventional non-syntactic tokens appearing in both types of texts, such as punctuations and exclamations,
+in our annotation, there are still five types of non-syntactic tokens tweets have\yicomment{need to say it explicitly that here we only refer to Twitter/web specific tokens, not including exclamations or punctuations or other stuffs.
+Or we can say punctuations and exclamations are canonically non-syntacitc}:
 sentiment emoticons, retweet markers and their following at-mentions, topical hashtags, referential URLs, and
@@
 emoticons, which are tagged as \emph{symbol} (\texttt{SYM}).  In our annotation, 
-7.55\% of all tokens are non-syntactic; detailed statistics can be found in Table \ref{tbl:non-synt-prop}.
+7.55\% of all tokens are belong to one of the five types; detailed statistics can be found in Table \ref{tbl:non-synt-prop}.
 %\yjcomment{I've merged retweet marker and retweet at-mention into one.}
@@
 canonically non-syntactic), we adopt the following
-conventions:
+conventions\yicomment{this applies to all non-syntactic tokens including punctuations and excalamations}:
 %\yicomment{shall we mention how we segment sentences? Seems relevant
@@
 \item Non-syntactic tokens are mostly labeled as {\it discourse}, but
-  URLs are always labeled as {\it list}, following the UD\_English dataset.
+  URLs are always labeled as {\it list}, following the UD\_English dataset. \yicomment{need to add punct for punctuations?}
 %\\ \yicomment{For retweet at-mention case, we attach the retweet at-mentions to the RT sign, so that the retweet action and the people whose tweet is being retweeted could be connected.\footnote{We can also follow the first convention to attach the retweet at-mention to its predicate, but we think it is better for downstream tasks.}}
@@
 might be treated as a verb phrase, with \emph{RT} as a verb and the
-at-mention as its object.
+at-mention as its object\yicomment{@coldplay seems not to be an object, could be some modifier like vocative, or some prepositional case (the tweets on/about coldplay)}.
 % \yicomment{or might be treated as 2 non-syntactic tokens and a punctuation, which should all attach to the predicate of the following retweeted tweet.}
@@
 \emph{proper noun} (\texttt{PROPN}) and attaching them to the
-following predicate with the label \emph{vocative} as in UD guidelines (see Figure \ref{fig:informal-toks} for an example).
+following predicate\yicomment{not necessarily following, better to be `the predicate of the sentence it belongs to'} with the label \emph{vocative} as in UD guidelines (see Figure \ref{fig:informal-toks} for an example).
 
@@
 In the first stage, 18 researchers worked on the {\sc Tweebank v1}
-proportion and created the initial annotations in one day.
+proportion\yicomment{and the additional 210 tweets} and created the initial annotations in one day.
 Before annotating, they were given a tutorial overview of the general UD
@@
 the coverage of our guidelines and solve inconsistencies between
-different annotators during this exercise. In the second stage, a tokenizer, a POS tagger, and
+different annotators during this exercise. In the second stage, a tokenizer, a POS tagger, and a
 parser were trained on the annotated data from the first stage (1,050 tweets in total),
@@
 All compared systems were re-trained on the combination of the UD\_English and 
-\textsc{Tweebank v2} training sets. We use Twitter-specific Glove embeddings released by
+\textsc{Tweebank v2} training sets\yicomment{should mention that combination of corpora improves the results, otherwise we should answer why we didn't try training ONLY on Tweebank v2}.
+We use Twitter-specific GloVe embeddings released by
 \citet{pennington-socher-manning:2014:EMNLP2014} in all neural taggers
@@
 Our preliminary experiments confirm this finding, with a gap of 1 LAS on development data
-between the best (75.8) and worst (74.8) runs. To control for this
+between the best (75.8)\yicomment{is this for char stacklstm parser?
+in table 6 it shows the same number.
+If it's average, then number in tab 6 should $< 75.8$?} and worst (74.8) runs.
+To control for this
 effect, we report the average of five differently-seeded runs, for
@@
 	\end{tabular}
-	\caption{Evaluating our pipeline against a state-of-the-art pipeline. \label{tbl:pipline} }
+	\caption{Evaluating our pipeline against a state-of-the-art pipeline. \label{tbl:pipline} \yicomment{see tab5 for our tokenizer the pos tagging number is 93.6, here is 93.7, should be consistent} }
 \end{table}

### 2017-12-15 paper.tex
fix tab 7

@@
 		Stanford CoreNLP & 92.1 \\
-		our bi-LSTM tokenizer (\S\ref{sec:tok}) & 93.6 \\
+		our bi-LSTM tokenizer (\S\ref{sec:tok}) & 93.7 \\
 		\hline
@@
 	\end{tabular}
-	\caption{Evaluating our pipeline against a state-of-the-art pipeline. \label{tbl:pipline} \yicomment{see tab5 for our tokenizer the pos tagging number is 93.6, here is 93.7, should be consistent} }
+	\caption{Evaluating our pipeline against a state-of-the-art pipeline. \label{tbl:pipline} %\yicomment{see tab5 for our tokenizer the pos tagging number is 93.6, here is 93.7, should be consistent}
+	}
 \end{table}

### 2017-12-15 paper.tex
fix and update.

@@
   tree.  A clear criterion for exclusion was not given, but many
-  tokens were excluded because they were deemed ``non-syntactic.'' \yicomment{including some Twitter specific tokens, which we will refine the definition in Section 2.3 and 2.4?}
+  tokens were excluded because they were deemed ``non-syntactic.''% \yicomment{including some Twitter specific tokens, which we will refine the definition in Section 2.3 and 2.4?}
 \item Allowing an annotator to merge a multiword expression into a
@@
 a large proportion of tokens don't carry any syntactic function. 
-Apart from conventional non-syntactic tokens appearing in both types of texts, such as punctuations and exclamations,
-in our annotation, there are still five types of non-syntactic tokens tweets have\yicomment{need to say it explicitly that here we only refer to Twitter/web specific tokens, not including exclamations or punctuations or other stuffs.
+In our annotation, there are five types of non-syntactic tokens commonly seen in tweets: %\yicomment{need to say it explicitly that here we only refer to Twitter/web specific tokens, not including exclamations or punctuations or other stuffs.
 Or we can say punctuations and exclamations are canonically non-syntacitc}:
@@
 canonically non-syntactic), we adopt the following
-conventions\yicomment{this applies to all non-syntactic tokens including punctuations and excalamations}:
+conventions%\yicomment{this applies to all non-syntactic tokens including punctuations and excalamations}
+:
 %\yicomment{shall we mention how we segment sentences? Seems relevant
@@
 \item Non-syntactic tokens are mostly labeled as {\it discourse}, but
-  URLs are always labeled as {\it list}, following the UD\_English dataset. \yicomment{need to add punct for punctuations?}
+  URLs are always labeled as {\it list}, following the UD\_English dataset.% \yicomment{need to add punct for punctuations?}
 %\\ \yicomment{For retweet at-mention case, we attach the retweet at-mentions to the RT sign, so that the retweet action and the people whose tweet is being retweeted could be connected.\footnote{We can also follow the first convention to attach the retweet at-mention to its predicate, but we think it is better for downstream tasks.}}
@@
 might be treated as a verb phrase, with \emph{RT} as a verb and the
-at-mention as its object\yicomment{@coldplay seems not to be an object, could be some modifier like vocative, or some prepositional case (the tweets on/about coldplay)}.
+at-mention as its object\yicomment{@coldplay seems not to be an object, could be some modifier like vocative, or some prepositional case (the tweets on/about coldplay)}\yjcomment{i am okey with current version}.
 % \yicomment{or might be treated as 2 non-syntactic tokens and a punctuation, which should all attach to the predicate of the following retweeted tweet.}
@@
 \emph{proper noun} (\texttt{PROPN}) and attaching them to the
-following predicate\yicomment{not necessarily following, better to be `the predicate of the sentence it belongs to'} with the label \emph{vocative} as in UD guidelines (see Figure \ref{fig:informal-toks} for an example).
+main predicate of the sentence it is within with the label \emph{vocative} as in UD guidelines (see Figure \ref{fig:informal-toks} for an example).\yjcomment{as Yi suggested, change ``following predicate'' to ``main ...
+within''}
 
@@
 In the first stage, 18 researchers worked on the {\sc Tweebank v1}
-proportion\yicomment{and the additional 210 tweets} and created the initial annotations in one day.
+proportion and the additional 210 tweets and created the initial annotations in one day.
 Before annotating, they were given a tutorial overview of the general UD
@@
 \end{table}
-
-We trained our tokenizer on the training portion of
+\citet{wang-EtAl:2017:Long6} shows that combining Singlish\footnote{a dialect of English} treebank with UD\_English
+can achieve parsing performance on Singlish parsing.
+We followed their work and trained our tokenizer on the training portion of
 \textsc{Tweebank v2} combined with the UD\_English training set
-and tested on the \textsc{Tweebank v2} test set. 
+and tested on the \textsc{Tweebank v2} test set. \yicomment{should mention that combination of corpora improves the results, otherwise we should answer why we didn't try training ONLY on Tweebank v2}
 We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
@@
 All compared systems were re-trained on the combination of the UD\_English and 
-\textsc{Tweebank v2} training sets\yicomment{should mention that combination of corpora improves the results, otherwise we should answer why we didn't try training ONLY on Tweebank v2}.
-We use Twitter-specific GloVe embeddings released by
+\textsc{Tweebank v2} training sets. We use Twitter-specific GloVe embeddings released by
 \citet{pennington-socher-manning:2014:EMNLP2014} in all neural taggers
@@
 Our preliminary experiments confirm this finding, with a gap of 1 LAS on development data
-between the best (75.8)\yicomment{is this for char stacklstm parser?
-in table 6 it shows the same number.
-If it's average, then number in tab 6 should $< 75.8$?} and worst (74.8) runs.
-To control for this
+between the best (75.8)
+ and worst (74.8) runs. To control for this
 effect, we report the average of five differently-seeded runs, for
@@
 	\end{tabular}
-	\caption{Dependency parser comparison on \textsc{Tweebank v2},
+	\caption{Dependency parser comparison on \textsc{Tweebank v2} test set,
            with automatic POS tags. The ``Kt/s'' column shows

### 2017-12-15 paper.tex
fit to 8

@@
 		\depedge[edge unit distance=1em]{16}{15}{cc}
-		\depedge[edge unit distance=0.37em]{16}{17}{obj}
+		\depedge[edge unit distance=1em]{16}{17}{obj}
 	\end{dependency}
@@
 \end{table}
-\citet{wang-EtAl:2017:Long6} shows that combining Singlish\footnote{a dialect of English} treebank with UD\_English
-can achieve parsing performance on Singlish parsing.
+\citet{wang-EtAl:2017:Long6} shows that the parser trained 
+on the combination of UD\_English and English dialect (Singlish) treebank
+outperfrom the one only on the dialect treebank.
 We followed their work and trained our tokenizer on the training portion of
 \textsc{Tweebank v2} combined with the UD\_English training set
-and tested on the \textsc{Tweebank v2} test set. \yicomment{should mention that combination of corpora improves the results, otherwise we should answer why we didn't try training ONLY on Tweebank v2}
+and tested on the \textsc{Tweebank v2} test set.
+\yicomment{should mention that combination of corpora improves the results, otherwise we should answer why we didn't try training ONLY on Tweebank v2}\yjcomment{add discussion}
 We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
@@
            the parsing speed evaluated by thousands of tokens
-           the model processed per second. For fair comparison, we limit the
-           number of CPUs used in \citet{dozat-qi-manning:2017:K17-3} experiments to 1.
+           the model processed per second.
             \label{tbl:parse-result}}

### 2017-12-15 paper.tex
Noah

@@
 special constructions in tweets that affect tokenization,
-part-of-speech tagging, and dependencies. Using the extended guidelines, we create
+part-of-speech tagging, and labeled dependencies. Using the extended guidelines, we create
 a new tweet treebank ({\sc Tweebank v2}) that is four times larger than the (unlabeled) {\sc Tweebank
@@
 universal dependencies (\S\ref{sec:parsing}).  Experimental results show
-it performs better than a pipeline of the state-of-the-art alternatives.
+that it performs better than a pipeline of the state-of-the-art alternatives.
 
@@
 	\end{dependency}
-	\caption{An example tweet that contains non-syntactic tokens:
+	\caption{An example to illustrate non-syntactic tokens:
 		\textcolor{red}{sentiment emoticon},
@@
 		\textcolor{cyan}{truncated word}.
-		This example tweet is a concatenation of three real tweets.
+		This is a concatenation of three real tweets.
 	}\label{fig:non-syn-toks}
@@
 	\end{dependency}
-	\caption{An example tweet with informal but syntactic tokens.
+	\caption{An example to illustrate informal but syntactic tokens.
 		This is a contrived example inspired by several tweets.}\label{fig:informal-toks}
@@
 \item If a non-syntactic token is within a sentence that has a clear predicate, it will be attached to this predicate.
-Retweet construction is a special case and we will discuss our choice in the following paragraph;
-\item If the whole sentence is made of a sequence of non-syntactic tokens, we attach all these tokens to the first one;
+Retweet construction is a special case and we will discuss our choice in the following paragraph.
+\item If the whole sentence is made of a sequence of non-syntactic tokens, we attach all these tokens to the first one.
 %\item In parataxis case, when it is difficult to decide which sentence or phrase x should belong to, we always attach x to the previous predicate of the paratactic clause or phrase;
@@
 might be treated as a verb phrase, with \emph{RT} as a verb and the
-at-mention as its object\yicomment{@coldplay seems not to be an object, could be some modifier like vocative, or some prepositional case (the tweets on/about coldplay)}\yjcomment{i am okey with current version}.
+at-mention as an argument \yicomment{@coldplay seems not to be an
+  object, could be some modifier like vocative, or some prepositional
+  case (the tweets on/about coldplay)}\yjcomment{i am okey with
+  current version} \nascomment{changed ``object'' to ``argument'' - better?}.
 % \yicomment{or might be treated as 2 non-syntactic tokens and a punctuation, which should all attach to the predicate of the following retweeted tweet.}
@@
 \end{table}
-\citet{wang-EtAl:2017:Long6} shows that the parser trained 
+\citet{wang-EtAl:2017:Long6} show that the parser trained 
 on the combination of UD\_English and English dialect (Singlish) treebank
-outperfrom the one only on the dialect treebank.
-We followed their work and trained our tokenizer on the training portion of
+outperform the one only on the dialect treebank.  Preliminary results
+showed the same in our case \nascomment{added to address an open issue}, so 
+we follow their work and trained our tokenizer on the training portion of
 \textsc{Tweebank v2} combined with the UD\_English training set
-and tested on the \textsc{Tweebank v2} test set.
-\yicomment{should mention that combination of corpora improves the results, otherwise we should answer why we didn't try training ONLY on Tweebank v2}\yjcomment{add discussion}
+and tested on the \textsc{Tweebank v2} test set.% \yicomment{should mention that combination of corpora improves the results, otherwise we should answer why we didn't try training ONLY on Tweebank v2}\yjcomment{add discussion}
 We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
@@
 which achieves the state-of-the-art performance on PTB.
-\citet{gui-EtAl:2017:EMNLP20172} presented the state-of-the-art neural tagger for Twitter,
-but their code didn't work beyond PTB tag set.
-Thus, we didn't include their tagger in our comparison.\yjcomment{i put some words on \cite{gui-EtAl:2017:EMNLP20172} in case the reviewer challenge our neural/non-neural comparsion.}
+\citet{gui-EtAl:2017:EMNLP20172} presented a state-of-the-art neural tagger for Twitter,
+but their implementation works only with the PTB tagset
+\nascomment{check here -- seems surprising to me, hopefully that's
+  enough for reviewers}, so we exclude
+it. % Thus, we didn't include their tagger in our comparison.\yjcomment{i put some words on \cite{gui-EtAl:2017:EMNLP20172} in case the reviewer challenge our neural/non-neural comparsion.}
  %and also two bi-LSTM systems similar

### 2017-12-16 paper.tex
finalize

@@
 \DeclareMathOperator*{\argmin}{argmin}
-
+\def\aclpaperid{214}
 %%%%%%%
@@
 treebank conventions \cite[UD\_English;][]{Marneffe2014UniversalSD}\footnote{\url{https://github.com/UniversalDependencies/UD_English}}
-and the conventions of \newcite{gimpel-EtAl:2011:ACL-HLT2011} and
-\newcite{owoputi-EtAl:2013:NAACL-HLT}.  %\yicomment{The conflicts
+and the conventions of \newcite{gimpel-EtAl:2011:ACL-HLT2011}.  %\yicomment{The conflicts
                                 %should refer to a {\bf
@@
 might be treated as a verb phrase, with \emph{RT} as a verb and the
-at-mention as an argument \yicomment{@coldplay seems not to be an
-  object, could be some modifier like vocative, or some prepositional
-  case (the tweets on/about coldplay)}\yjcomment{i am okey with
-  current version} \nascomment{changed ``object'' to ``argument'' - better?}.
+at-mention as an argument.
 % \yicomment{or might be treated as 2 non-syntactic tokens and a punctuation, which should all attach to the predicate of the following retweeted tweet.}
@@
 \paragraph{Constructions handled by UD.}  A number of constructions
-that are especially common in tweets are well handled by UD
+that are especially common in tweets are handled by UD
 conventions: ellipsis, irregular word orders, and paratactic phrases
@@
 \emph{proper noun} (\texttt{PROPN}) and attaching them to the
-main predicate of the sentence it is within with the label \emph{vocative} as in UD guidelines (see Figure \ref{fig:informal-toks} for an example).\yjcomment{as Yi suggested, change ``following predicate'' to ``main ...
-within''}
+main predicate of the sentence it is within with the label \emph{vocative} as in UD guidelines (see Figure \ref{fig:informal-toks} for an example).
 
@@
 filtered by the {\it lang} attribute in the tweet JSON and {\it
-  langid.py} toolkit.\footnote{\url{https://github.com/saffsd/langid.py}}
+  langid.py}.\footnote{\url{https://github.com/saffsd/langid.py}}
 
@@
 outperform the one only on the dialect treebank.  Preliminary results
-showed the same in our case \nascomment{added to address an open issue}, so 
+showed the same in our case, so 
 we follow their work and trained our tokenizer on the training portion of
@@
 \citet{gui-EtAl:2017:EMNLP20172} presented a state-of-the-art neural tagger for Twitter,
-but their implementation works only with the PTB tagset
-\nascomment{check here -- seems surprising to me, hopefully that's
-  enough for reviewers}, so we exclude
+but their implementation works only with the PTB tagset, so we exclude
 it. % Thus, we didn't include their tagger in our comparison.\yjcomment{i put some words on \cite{gui-EtAl:2017:EMNLP20172} in case the reviewer challenge our neural/non-neural comparsion.}
@@
 They are re-trained on the same data as our
-system. \yjcomment{i briefly describ the compared systems.}
+system.
 Our baseline lags behind by nearly two LAS
@@
 special constructions in tweets and create
-the {\sc Tweebank v2}, which has 3,550 tweets  and 55,607 tokens. We characterize the disagreements
+the {\sc Tweebank v2}, which has 55,607 tokens. We characterize the disagreements
 among our annotators and argue that inherent ambiguity in this genre

### 2018-01-27 naacl2018_rebuttal.txt
For sync, it's not done.

We thank all the reviewers for your comments.

To the first reviewer:

- "There appear to be two conventions in UD for handling cases like 'gonna' … I would like to see some argumentation for why the authors adapt the first convention."

If we don't consider the normalization, the second convention can be recovered from the first one using the 'SpaceAfter' feature in the last column of our annotation. And it's arguable that normalization on social media data is essential according to Esenstain (2013). Thus, we preserve the original tweet content as much as possible while respecting the UD guideline. What's more, adopting the first convention makes it easier for us to train our parser from the combination of our annotation and the UD_English treebank since they are of the same convention.

- "I would like to see some discussion of why normalization/lemmatization is ignored and why the authors think it does not hurt POS tagging and parsing performance."

As mentioned before, we basically follow the spirit of Essenstain (2013) in treating normalization on social media content. Since he pointed out normalization for social media data is vaguely defined and often impossible without changing the meaning, we don’t include normalization in our annotation. We believe it's an open question and needs more careful study. We also believe that a clean form of the social media content benefits downstream POS and parsing, but reaching this level of cleanness is non-trivial for social media content. So we didn't consider them in our paper.

To the second reviewer:

- "yet do not offer annotation of the more fine­-grained schema from Gimpel et al. (2011)"

We use the second POS column to retain the Gimpel's POS annotation on the overlapped part.

- "I wish authors submitted a sample of 10 tweets as supplementary material"

We will release our data and the reader of this paper can refer to our release for sanity check and future development.

- "authors did not specifically state efforts of tweet anonymization (non­celebrity handles, urls) but the examples exhibit them."

We will make the anonymization effort more clear in future revision.

- "(7) Table 5 and related discussion: is this the greedy or CRF setup?"

It's the CRF setup. We will make it more clear in future revision.

- "how exactly are the F1/accuracy scores computed? Per token? Token boundary?"

It's computed on token.

- "While training the POS tagger on GloVe embeddings, was there a problem with OOV words?"

The compared neural POS taggers from Ma and Hovy (2016) uses a character-CNN as an additional word representation, which can mitigate the OOV problems.

To the third reviewer:

- "In relation to "training with exploration", it would have been relevant to cite the original papers on dynamic oracles (Goldberg and Nivre, 2012, 2013) as well as the paper by Kiperwasser and Goldberg (2016)"

We would cite the dynamic oracle work in our future revision.

- "It is worth pointing out that UD does not use the tag set of Petrov et al. (2012) but a revised and extended version of it (with 17 tags instead of 12)."

We meant the 17 tags set and we will revise our wording in future revision.

### 2018-01-28 naacl2018_rebuttal.txt
Update naacl2018_rebuttal.txt

@@
 We meant the 17 tags set and we will revise our wording in future revision.
+
+- "The claim that "UD tokenisation treats each syntactic word as a token" is confused"
+
+[To be completed by Yi]
+
+- "Using the relation 'discourse' for 'non-syntactic tokens' is highly dubious. it seems better to use the generic relation 'dep'."
+
+The choice of relation on the non-syntactic tokens is arguable since UD doesn't have specified guidelines for this.
+Our choice of 'discourse' was inspired by the observation that emoticon is annotated as 'discourse' in UD_English.
+However, non-syntactic tokens can be easily recovered from our annotation and changing it to other relation in the future development is not difficult.
+
+- "how is sentence segmentation performed? Is every tweet regarded as exactly one sentence?"
+
+We treat every tweet as exactly one sentence in both our annotation and parser but allow more than one root.
+
+- "Are you using a static oracle in all experiments except the one that explicitly mentions exploration? Is it fair to use a dynamic oracle only for the parser with distillation? "
+
+Yes.
+We use static oracle in our experiment.
+It's a good suggestion and we would add dynamic oracle baseline in our future revision.
+Our distillation without exploration can be treated as a fair comparison with the static oracle baseline and our distillation with exploration further improve the performance.
+
+- "There seems to be an apostrophe missing in 'its is tokenised as it and s when is is a copula'."
+
+'its' is an example of the informal nature of tweets that author omit the apostrophe.

### 2018-01-29 naacl2018_rebuttal.txt
yi 1 update rebuttal

@@
 
-If we don't consider the normalization, the second convention can be recovered from the first one using the 'SpaceAfter' feature in the last column of our annotation.
-And it's arguable that normalization on social media data is essential according to Esenstain (2013).
+If we don't consider the normalization,/*YI did not know what you mean by 'if we don't consider normalization'*/ the second convention can be recovered from the first one using the 'SpaceAfter' feature in the last column of our annotation./*YI maybe show a line as example?*/ And it's arguable that normalization on social media data is essential according to Esenstain (2013) /*YI (could be problematic if do normalization)*/.
 Thus, we preserve the original tweet content as much as possible while respecting the UD guideline.
 What's more, adopting the first convention makes it easier for us to train our parser from the combination of our annotation and the UD_English treebank since they are of the same convention.
+/*YI another motivation is UD_English consists of web domain text, we think it is reasonable/compatible to follow UD's convention dealing with the web domain texts.*/
 
@@
 Since he pointed out normalization for social media data is vaguely defined and often impossible without changing the meaning, we don’t include normalization in our annotation.
-We believe it's an open question and needs more careful study.
-We also believe that a clean form of the social media content benefits downstream POS and parsing, but reaching this level of cleanness is non-trivial for social media content.
-So we didn't consider them in our paper.
+We believe it's an open question and needs more careful study./*YI maybe also follow UD_English normalization convention?
+need to check*/ We also believe that a clean form of the social media content benefits downstream POS and parsing, but reaching this level of cleanness is non-trivial for social media content./*YI for both annotation and models*/ So we didn't consider them in our paper.
 
@@
 We use the second POS column to retain the Gimpel's POS annotation on the overlapped part.
+/*YI Did we?
+or say we will include POS tags in the second col of POS.
+More compatability issue.
+Gimpel's schema is great, but difficult to generalize across domain/language within UD framework.
+For example, we also use UD_English as training data, which would be very difficult to incorporate with if we adopt Gimpel's POS*/
 
@@
 
+- "Telling from 3 examples, 2 of which are artificial and one whose POS tagging isn't shown, is not enough for a sanity check of annotation and scheme worth."
+
+/*YI we will add the POS to the example in the paper.*/
+
 - "authors did not specifically state efforts of tweet anonymization (non­celebrity handles, urls) but the examples exhibit them."
 
-We will make the anonymization effort more clear in future revision.
+We will make the anonymization effort clearer in future revision./*YI Ask Noah*/
 
@@
 
-It's the CRF setup. We will make it more clear in future revision.
+It's the CRF setup. We will make it clearer in future revision.
 
@@
 It's computed on token.
+
+- "interannotator agreement: is this figure computed over all annotators? More details are needed."
+
+We have multiple annotators, these are two major(representative) and plausible annotations.
 
@@
 
-[To be completed by Yi]
+We do need to revise the statements as we are wrong about the subject of the sentence (UD) and not rigorous enough. 
+This is actually our tokenization principle, that we treat each syntactic word as a token.
+We try to tokenize multiword tokens, except acronyms, into syntactic words (gonna) and treat them as new tokens.
+It is the same as UD conventions.
+However, we use goeswith relation to resolve multi-token words instead of combining them back as one option suggested by UD.
+
+- "Tagging a title with an internal syntactic structure (like "Fix you") as a proper noun is a clear violation of UD guidelines."
+
+(From UD_English train example)
+20	author	author	NOUN	NN	Number=Sing	8	conj	8:conj	_
+21	of	of	ADP	IN	_	24	case	24:case	_
+22	"	"	PUNCT	``	_	24	punct	24:punct	SpaceAfter=No
+23	Sacred	Sacred	PROPN	NNP	Number=Sing	24	compound	24:compound	_
+24	Space	Space	PROPN	NNP	Number=Sing	20	nmod	20:nmod	_
+25	and	and	CCONJ	CC	_	27	cc	27:cc	_
+26	Holy	Holy	PROPN	NNP	Number=Sing	27	compound	27:compound	_
+27	War	War	PROPN	NNP	Number=Sing	24	conj	24:conj	SpaceAfter=No
+
+18	the	the	DET	DT	Definite=Def|PronType=Art	19	det	19:det	_
+19	book	book	NOUN	NN	Number=Sing	16	obl	16:obl	_
+20	Disposable	Disposable	PROPN	NNP	Number=Sing	21	compound	21:compound	_
+21	Patriot	Patriot	PROPN	NNP	Number=Sing	19	appos	19:appos	SpaceAfter=No
+
+2	the	the	DET	DT	Definite=Def|PronType=Art	3	det	3:det	_
+3	Beatles	Beatles	PROPN	NNPS	Number=Plur	5	nmod:poss	5:nmod:poss	SpaceAfter=No
+4	'	'	PART	POS	_	3	case	3:case	_
+5	song	song	NOUN	NN	Number=Sing	11	obl	11:obl	_
+6	"	"	PUNCT	``	_	7	punct	7:punct	SpaceAfter=No
+7	Get	get	VERB	VB	VerbForm=Inf	5	appos	5:appos	_
+8	Back	back	ADV	RB	_	7	advmod	7:advmod	SpaceAfter=No
+9	"	"	PUNCT	''	_	7	punct	7:punct	_
+
+From most UD_English examples about titles, we are misled by the proper noun with adjective combinations where UD annotates the adjective as PROPN.
+However, after double checking POS PROPN, we realized that it violated the UD annotation.
+We will correct it in both our paper and the data repo.
 
@@
 
-The choice of relation on the non-syntactic tokens is arguable since UD doesn't have specified guidelines for this.
-Our choice of 'discourse' was inspired by the observation that emoticon is annotated as 'discourse' in UD_English.
-However, non-syntactic tokens can be easily recovered from our annotation and changing it to other relation in the future development is not difficult.
+The choice of relation on the non-syntactic tokens is arguable since UD doesn't have specified guidelines for this./*For example, we did write to UD_English asking them the explanation for URLs as list relation, but still did not get answer.*/ Our choice of 'discourse' was inspired by the observation that emoticon is annotated as 'discourse' in UD_English./*YI And tokens like username and hashtags, as non-syntactic tokens, do look like emoticons providing extra information to tweets.*/ However, non-syntactic tokens can be easily recovered from our annotation and changing it to other relation in the future development is not difficult./*Our attempt to categorization of the relations to the non-syntactic tokens are just the first attemps and we believe it could be further refined with more and more researcher involved in.*/
 
@@
 We treat every tweet as exactly one sentence in both our annotation and parser but allow more than one root.
+/*YI Isn't is one tweet have many sentences with their own roots, and all roots connects to a single dummy root??*/
 

### 2018-01-30 naacl2018_rebuttal.txt
update rebuttal

--- 2018-01-28 naacl2018_rebuttal.txt
@@
 
-- "There appear to be two conventions in UD for handling cases like 'gonna' … I would like to see some argumentation for why the authors adapt the first convention."
+- "There appear to be two conventions in UD for handling cases like 'gonna' ...
+The latter seems more powerful and introduce linguistically motivated/normalized tokens.
+I would like to see some argumentation for why the authors adapt the first convention."
 
-If we don't consider the normalization, the second convention can be recovered from the first one using the 'SpaceAfter' feature in the last column of our annotation.
-And it's arguable that normalization on social media data is essential according to Esenstain (2013).
+Without the normalization process, the second convention can be converted from the first one using the 'SpaceAfter' feature in the last column of our annotation (see the following CoNLL-X formatted snippet for example).
+And it's arguable that normalization on social media data is essential according to Eisenstein (2013).
 Thus, we preserve the original tweet content as much as possible while respecting the UD guideline.
-What's more, adopting the first convention makes it easier for us to train our parser from the combination of our annotation and the UD_English treebank since they are of the same convention.
+What's more, adopting the first convention makes it easier for us to train our parser from the combination of our annotation and the UD_English treebank (We use UD_English thanks to its relatively large scale and web domain) since they are of the same convention.
+...
+5 gon _ VERB _ _ 3 parataxis _ SpaceAfter=No
+6 na _ PART _ _ 7 mark _
+...
 
@@
 
-As mentioned before, we basically follow the spirit of Essenstain (2013) in treating normalization on social media content.
-Since he pointed out normalization for social media data is vaguely defined and often impossible without changing the meaning, we don’t include normalization in our annotation.
+As mentioned before, we basically follow the spirit of Eisenstein (2013) in treating normalization on social media content.
+Since he pointed out normalization for social media data is vaguely defined and often impossible without changing the meaning, we don't include normalization in our annotation.
 We believe it's an open question and needs more careful study.
-We also believe that a clean form of the social media content benefits downstream POS and parsing, but reaching this level of cleanness is non-trivial for social media content.
+We also believe that a clean form of the social media content benefits downstream POS and parsing, but reaching this level of cleanness is non-trivial for social media content for both the annotation and model.
 So we didn't consider them in our paper.
@@
 
-We use the second POS column to retain the Gimpel's POS annotation on the overlapped part.
+We would use the second POS column to retain the Gimpel's POS annotation on the overlapped part.
 
@@
 
+- "Telling from 3 examples, 2 of which are artificial and one whose POS tagging isn't shown, is not enough for a sanity check of annotation and scheme worth."
+
+We will add the POS to the example in the paper.
+
 - "authors did not specifically state efforts of tweet anonymization (non­celebrity handles, urls) but the examples exhibit them."
 
-We will make the anonymization effort more clear in future revision.
+We will make the anonymization effort clearer in future revision.
 
@@
 It's computed on token.
+
+- "interannotator agreement: is this figure computed over all annotators? More details are needed."
+
+We have multiple annotators, these are two major (representative) and plausible annotations.
 
@@
 
-[To be completed by Yi]
+We do need to revise the statements as we are wrong about the subject of the sentence (UD) and not rigorous enough.
+This is actually our tokenization principle, that we treat each syntactic word as a token.
+We try to tokenize multiword tokens, except acronyms, into syntactic words (gonna) and treat them as new tokens.
+It is the same as UD conventions.
+However, we use goeswith relation to resolve multi-token words instead of combining them back as one option suggested by UD.
+
+- "Tagging a title with an internal syntactic structure (like "Fix you") as a proper noun is a clear violation of UD guidelines."
+
+During our annotation, some of our annotators was referring to the UD_English for cases that they are not sure and the UD_English presents some cases that violate the guidelines for title (see http://bionlp-www.utu.fi/dep_search/query?search=Sacred&db=UD_English-v2&case_sensitive=True&hits_per_page=50).
+This kind of disagreements was resolved in the final version.
+We will clarify this in the draft in our future revision.
 
@@
 However, non-syntactic tokens can be easily recovered from our annotation and changing it to other relation in the future development is not difficult.
+Our attempt to categorization of the relations to the non-syntactic tokens are just the first attempts and we believe it could be further refined with more and more researcher involved in.
 
@@
 
-We treat every tweet as exactly one sentence in both our annotation and parser but allow more than one root.
+We segment sentences in one tweet with punctuation and retweet symbol (RT). We will clarify this in the future revision.
 
@@
 
-'its' is an example of the informal nature of tweets that author omit the apostrophe.
+'its' is an example of the informal nature of tweets that the author omits the apostrophe.

### 2018-01-30 naacl2018_rebuttal.txt
yi 2 update rebuttal

@@
 
-We would use the second POS column to retain the Gimpel's POS annotation on the overlapped part.
+We will use the second POS column to retain the Gimpel's POS annotation on the overlapped part.
 
@@
 
-We have multiple annotators, these are two major (representative) and plausible annotations.
+We have multiple annotators, these are two major, representative and plausible annotations.
 
@@
 
-We would cite the dynamic oracle work in our future revision.
+We will cite the dynamic oracle work in our future revision.
 
@@
 We do need to revise the statements as we are wrong about the subject of the sentence (UD) and not rigorous enough.
-This is actually our tokenization principle, that we treat each syntactic word as a token.
-We try to tokenize multiword tokens, except acronyms, into syntactic words (gonna) and treat them as new tokens.
+It is actually our tokenization principle, that we treat each syntactic word as a token.
+We try to tokenize multiword tokens, except acronyms, into syntactic words (gonna to gon na) and treat them as new tokens.
 It is the same as UD conventions.
-However, we use goeswith relation to resolve multi-token words instead of combining them back as one option suggested by UD.
+However, we use "goeswith" relation to resolve multi-token words instead of combining them back as one option suggested by UD.
 
@@
 
-During our annotation, some of our annotators was referring to the UD_English for cases that they are not sure and the UD_English presents some cases that violate the guidelines for title (see http://bionlp-www.utu.fi/dep_search/query?search=Sacred&db=UD_English-v2&case_sensitive=True&hits_per_page=50).
+During our annotation, some of our annotators was referring to the UD_English for cases of titles they are not sure about, some of which are exceptions, where nouns and proper nouns with adjectives are all annotated as PROPN for POS tag, (see http://bionlp-www.utu.fi/dep_search/query?search=Sacred&db=UD_English-v2&case_sensitive=True&hits_per_page=50).
 This kind of disagreements was resolved in the final version.
@@
 The choice of relation on the non-syntactic tokens is arguable since UD doesn't have specified guidelines for this.
-Our choice of 'discourse' was inspired by the observation that emoticon is annotated as 'discourse' in UD_English.
-However, non-syntactic tokens can be easily recovered from our annotation and changing it to other relation in the future development is not difficult.
-Our attempt to categorization of the relations to the non-syntactic tokens are just the first attempts and we believe it could be further refined with more and more researcher involved in.
+Our choice of 'discourse' was inspired by the observation that emoticons and interjections are annotated as 'discourse' in UD_English.
+However, non-syntactic tokens can be easily recovered from our annotation and changing their relations to others in the future development is not difficult.
+Our decision to categorize non-syntactic tokens into the 'discourse' label is just the first attempt and we believe it could be further refined with more and more researchers involved in.
 

### 2018-01-31 naacl2018_rebuttal.txt
Noah

@@
 Without the normalization process, the second convention can be converted from the first one using the 'SpaceAfter' feature in the last column of our annotation (see the following CoNLL-X formatted snippet for example).
-And it's arguable that normalization on social media data is essential according to Eisenstein (2013).
-Thus, we preserve the original tweet content as much as possible while respecting the UD guideline.
-What's more, adopting the first convention makes it easier for us to train our parser from the combination of our annotation and the UD_English treebank (We use UD_English thanks to its relatively large scale and web domain) since they are of the same convention.
+
 ...
@@
 
+And it's arguable that normalization of social media data is essential according to Eisenstein (2013).
+Thus, we preserve the original tweet content as much as possible while respecting the UD guidelines.
+What's more, adopting the first convention makes it easier for us to train our parser from the combination of our annotation and the UD_English treebank, since they follow the same conventions.
+(We use UD_English thanks to its relatively large scale and web domain.)
+
 - "I would like to see some discussion of why normalization/lemmatization is ignored and why the authors think it does not hurt POS tagging and parsing performance."
 
-As mentioned before, we basically follow the spirit of Eisenstein (2013) in treating normalization on social media content.
-Since he pointed out normalization for social media data is vaguely defined and often impossible without changing the meaning, we don't include normalization in our annotation.
-We believe it's an open question and needs more careful study.
-We also believe that a clean form of the social media content benefits downstream POS and parsing, but reaching this level of cleanness is non-trivial for social media content for both the annotation and model.
-So we didn't consider them in our paper.
+As mentioned before, we basically follow the spirit of Eisenstein (2013) in treating normalization of social media content.
+Since he pointed out that normalization for social media data is vaguely defined and often impossible without changing the meaning, we don't include normalization in our annotation.
+Of course, we believe it's an open question and needs more careful study.
+We concede that a clean, canoncial form for social media content would benefit downstream POS and parsing, but those transformations are non-trivial for both the annotation and model.
+In this paper, we prioritized compatibility with UD, but we expect that future work will explore integration of normalization into such pipelines.
 
@@
 
-We will release our data and the reader of this paper can refer to our release for sanity check and future development.
+We will release our data and use the extra space to provide more examples of the annotations.
 
@@
 
-We will add the POS to the example in the paper.
+We will add the POS to the examples in the paper.
 
@@
 
-We will make the anonymization effort clearer in future revision.
+We will make the anonymization effort clear in the next version.
 
@@
 
-It's the CRF setup. We will make it clearer in future revision.
+It's the CRF setup. We will make it clear in the next version.
 
@@
 
-We have multiple annotators, these are two major, representative and plausible annotations.
+We have multiple annotators, these are two representative and plausible annotations.
 
@@
 
-The compared neural POS taggers from Ma and Hovy (2016) uses a character-CNN as an additional word representation, which can mitigate the OOV problems.
+The compared neural POS tagger from Ma and Hovy (2016) uses a character-CNN as an additional word representation, which can mitigate the OOV problems.
 
@@
 
-We will cite the dynamic oracle work in our future revision.
+We will cite the dynamic oracle work in the next version.
 
@@
 
-We meant the 17 tags set and we will revise our wording in future revision.
+We meant the 17-tag tagset and we will revise our wording in the next version.
 
@@
 
-We do need to revise the statements as we are wrong about the subject of the sentence (UD) and not rigorous enough.
-It is actually our tokenization principle, that we treat each syntactic word as a token.
+You are correct; this statement needs to be revised.
+What we should have said is that *our* approach to tokenization treats each syntactic word as a token.
 We try to tokenize multiword tokens, except acronyms, into syntactic words (gonna to gon na) and treat them as new tokens.
 It is the same as UD conventions.
-However, we use "goeswith" relation to resolve multi-token words instead of combining them back as one option suggested by UD.
+However, we use the "goeswith" relation to resolve multi-token words instead of combining them back [!!!this is ambiguous -- what is the one option suggested by UD?
+using goeswith or combining them back?] as one option suggested by UD.
 
@@
 
-During our annotation, some of our annotators was referring to the UD_English for cases of titles they are not sure about, some of which are exceptions, where nouns and proper nouns with adjectives are all annotated as PROPN for POS tag, (see http://bionlp-www.utu.fi/dep_search/query?search=Sacred&db=UD_English-v2&case_sensitive=True&hits_per_page=50).
-This kind of disagreements was resolved in the final version.
-We will clarify this in the draft in our future revision.
+During our annotation, some of our annotators referred to the UD_English for cases of titles they are not sure about, some of which are exceptions, where nouns and proper nouns with adjectives are all annotated as PROPN for POS tag, (see http://bionlp-www.utu.fi/dep_search/query?search=Sacred&db=UD_English-v2&case_sensitive=True&hits_per_page=50).
+This kind of disagreement was resolved in the final version.
+We will clarify this in the next version.
 
@@
 
-The choice of relation on the non-syntactic tokens is arguable since UD doesn't have specified guidelines for this.
+The choice of relation on the non-syntactic tokens is arguable since UD doesn't have specific guidelines for this.
 Our choice of 'discourse' was inspired by the observation that emoticons and interjections are annotated as 'discourse' in UD_English.
 However, non-syntactic tokens can be easily recovered from our annotation and changing their relations to others in the future development is not difficult.
-Our decision to categorize non-syntactic tokens into the 'discourse' label is just the first attempt and we believe it could be further refined with more and more researchers involved in.
+Our decision to categorize non-syntactic tokens into the 'discourse' label might be revisited as more researchers become involved in the interface between UD and social media text.
 
@@
 
-We segment sentences in one tweet with punctuation and retweet symbol (RT). We will clarify this in the future revision.
+We segment sentences in one tweet with punctuation [!!!this is too vague] and the retweet symbol (RT). We will clarify this in the future revision.
 
@@
 We use static oracle in our experiment.
-It's a good suggestion and we would add dynamic oracle baseline in our future revision.
-Our distillation without exploration can be treated as a fair comparison with the static oracle baseline and our distillation with exploration further improve the performance.
+It's a good suggestion and we will add dynamic oracle baseline in the next version.
+Our distillation without exploration can be treated as a fair comparison to the static oracle baseline and our distillation with exploration further improves the performance.
 
@@
 
-'its' is an example of the informal nature of tweets that the author omits the apostrophe.
+In carefully edited text, there should be an apostrophe as 'its' is a contraction of 'it' and 'is'.
+However, here, 'its' is an example of the informal nature of tweets -- the author omitted the apostrophe.

### 2018-02-01 naacl2018_rebuttal.txt
resolve one ambiguition

@@
 The choice of relation on the non-syntactic tokens is arguable since UD doesn't have specific guidelines for this.
-Our choice of 'discourse' was inspired by the observation that emoticons and interjections are annotated as 'discourse' in UD_English.
+Our choice of 'discourse' was inspired by the observation that emoticons and interjections are annotated as 'discourse' in UD_English (see http://bionlp-www.utu.fi/dep_search/query?search=%22%3A%29%22&db=UD_English-v2&case_sensitive=True&hits_per_page=50).
 However, non-syntactic tokens can be easily recovered from our annotation and changing their relations to others in the future development is not difficult.
@@
 
-We segment sentences in one tweet with punctuation [!!!this is too vague] and the retweet symbol (RT). We will clarify this in the future revision.
+We segment sentences in one tweet with period, exclamation mark, ellipsis mark, and the retweet symbol (RT). We will clarify this in the next revision.
 

### 2018-02-01 naacl2018_rebuttal.txt
yi 3 update rebuttal

@@
 You are correct; this statement needs to be revised.
-What we should have said is that *our* approach to tokenization treats each syntactic word as a token.
+What we should have said is that UD tokenisation treats each syntactic word as a unit of annotation.
 We try to tokenize multiword tokens, except acronyms, into syntactic words (gonna to gon na) and treat them as new tokens.
 It is the same as UD conventions.
-However, we use the "goeswith" relation to resolve multi-token words instead of combining them back [!!!this is ambiguous -- what is the one option suggested by UD?
-using goeswith or combining them back?] as one option suggested by UD.
+However, we only use the "goeswith" relation to resolve multi-token words, where UD adopts both strategies of combining them back and using "goeswith" relation.
 

### 2018-03-04 paper.tex
copyedits: capitalize Universal Dependencies

@@
 We study the problem of analyzing tweets with
-universal dependencies \citep[UD;][]{NIVRE16.348}. We extend the UD guidelines to cover
+Universal Dependencies \citep[UD;][]{NIVRE16.348}. We extend the UD guidelines to cover
 special constructions in tweets that affect tokenization,
@@
 understanding and explaining tweets. Nonetheless, using the new treebank,
-we build a pipeline system to parse raw tweets into UD. To overcome the
+we build a pipeline system to parse raw tweets into UD. To overcome 
 annotation noise without sacrificing computational efficiency, we propose a new
@@
 phrase-structure conventions of the Penn Treebank
-\citep[PTB;][]{Marcus93buildinga}, enabling conversion to Stanford dependencies.
+\citep[PTB;][]{Marcus93buildinga}, enabling conversion to Stanford Dependencies.
 \citet{kong-EtAl:2014:EMNLP2014} further studied the challenges in
@@
 
-Universal dependencies \citep[UD]{NIVRE16.348} were introduced to enable
+Universal Dependencies \citep[UD]{NIVRE16.348} were introduced to enable
 consistent annotation across different languages. To allow such
@@
 covered by UD guidelines. Our annotation includes 
-tokenization, part-of-speech (POS) tags, and (labeled) universal dependencies.
+tokenization, part-of-speech (POS) tags, and (labeled) Universal Dependencies.
 We characterize the disagreements among our annotators and find that
@@
 Based on these annotations, we nonetheless designed a pipeline to parse 
-raw tweets into universal dependencies. Our pipeline includes: a
+raw tweets into Universal Dependencies. Our pipeline includes: a
 bidirectional LSTM (bi-LSTM) tokenizer, a word cluster-enhanced POS
@@
 and create a new tweet treebank ({\sc Tweebank v2}), which includes 
-tokenization, part-of-speech tagging, and labeled universal dependencies.
+tokenization, part-of-speech tagging, and labeled Universal Dependencies.
 We also characterize the difficulties of creating such annotation.
@@
 \item We introduce and evaluate a pipeline system to parse the raw tweet text into
-universal dependencies (\S\ref{sec:parsing}).  Experimental results show
+Universal Dependencies (\S\ref{sec:parsing}).  Experimental results show
 that it performs better than a pipeline of the state-of-the-art alternatives.
@@
 
-We present a pipeline system to parse tweets into universal
-dependencies.  We evaluate each component individually, and the system
+We present a pipeline system to parse tweets into Universal
+Dependencies.  We evaluate each component individually, and the system
 as a whole.
@@
 \section{Conclusion}
-We study the problem of parsing tweets into universal dependencies.
+We study the problem of parsing tweets into Universal Dependencies.
 We adapt the UD guidelines to cover 

### 2018-03-04 paper.tex
copyedits & comments

@@
 \newcommand{\yicomment}[1]{\textcolor{gray}{[#1 ---\textsc{yi}]}}
+\newcommand{\nss}[1]{\textcolor{magenta}{[$_\mathrm{S}^\mathrm{NS}$#1]}}
 %\newcommand{\yjcomment}[1]{}
@@
 the syntax of tweets can benefit from such adaptability. In this paper,
-we introduce a new tweet treebank of 55,607 tokens that follows the UD
+we introduce a new English tweet treebank of 55,607 tokens that follows the UD
 guidelines, but also contends with social media-specific challenges that were not
-covered by UD guidelines. Our annotation includes 
+covered by UD guidelines.\footnote{We developed our treebank independently of a similar effort for Italian tweets \cite{sanguinetti-17}. 
+See \nss{section ref} for a comparison.} Our annotation includes 
 tokenization, part-of-speech (POS) tags, and (labeled) Universal Dependencies.
@@
 
+\paragraph{Comparison to PoSTWITA-UD.} \nss{discuss similarities and differences of conventions to \cite{sanguinetti-17}. 
+We expect that the official UD guidelines will eventually adopt standards for these issues so the treebanks can be harmonized.}
+
 % \paragraph{At-mention.} At-mention in the beginning of a tweet is the format of indicating the `reply' action.
@@
 and used to automatically analyze the sampled 2,500 tweets.  Authors 
-of this paper manually corrected the parsed data and finally achieved 3,550 labeled tweets.
-Newly created annotations are splitted into train, development, and test set and appended
+of this paper manually corrected the parsed data and finally achieved 3,550 labeled tweets.\nss{What tools did annotators use?}
+Newly created annotations are split into train, development, and test set and appended
 to the original split of {\sc Twebank v1}. Statistics of our annotations and data split are shown
@@
 dependencies is shown in Figure \ref{fig:disagree}.  Depending on
-whether this is an example of an empty auxiliary verb, or a clause-modified
+whether this is an example of a zero copula construction, or a clause-modified
 noun, either annotation is plausible.
@@
 
-\section{Pipeline}
+\section{Parsing Pipeline}
 \label{sec:parsing}
@@
 the asterisk in {\it 4*3} is a separate token signifying
-multiplication, but for the asterisk in {\it sh*t}
+multiplication, but the asterisk in {\it sh*t}
 works as a mask to evoke censorship and should not be segmented.
@@
 sentence as whether it is the beginning of a word (1 as the beginning and 0 otherwise).
-Figure \ref{fig:tok-model} shows our tokenization model.
+Figure \ref{fig:tok-model} shows the architecture of our tokenization model.
 Space is treated as an input but deterministically  assigned a special tag \$.
@@
 		 Twokenizer & 94.4 \\		 
-% 		UD pipe v1.2 & 94.7 \\
+% 		UDPipe v1.2 & 94.7 \\
 		\hdashline
-		UD pipe v1.2 & 97.3 \\
+		UDPipe v1.2 & 97.3 \\
 	 	our bi-LSTM tokenizer & 98.3 \\
@@
 \end{table}
-\citet{wang-EtAl:2017:Long6} show that the parser trained 
-on the combination of UD\_English and English dialect (Singlish) treebank
-outperform the one only on the dialect treebank.  Preliminary results
+\citet{wang-EtAl:2017:Long6} show that the parser\nss{tokenizer?} trained 
+on the combination of the UD\_English and Singapore English dialect (Singlish) treebanks
+outperforms the one trained only on the dialect treebank.  Preliminary results
 showed the same in our case, so 
@@
 \textsc{Tweebank v2} combined with the UD\_English training set
-and tested on the \textsc{Tweebank v2} test set.% \yicomment{should mention that combination of corpora improves the results, otherwise we should answer why we didn't try training ONLY on Tweebank v2}\yjcomment{add discussion}
+and tested on the \textsc{Tweebank v2} test set.
+% \yicomment{should mention that combination of corpora improves the results, otherwise we should answer why we didn't try training ONLY on Tweebank v2}\yjcomment{add discussion}
 We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
@@
  Stanford CoreNLP \cite{manning-EtAl:2014:P14-5} and Twokenizer
-\cite{ICWSM101540} systems are rule-based systems and were not adapted
+\cite{ICWSM101540} are rule-based systems and were not adapted
 to the UD tokenization scheme.
-The UD pipe v1.2
+The UDPipe v1.2
 \cite{straka-strakova:2017:K17-3} model was re-trained on the same
-data as our system. Compared with the UD pipe, we use LSTM
-instead of GRU in our model and we also use a larger size of hidden units (64 against 20),
+data as our system. Compared with UDPipe, we use LSTM
+instead of GRU in our model and we also use a larger size of hidden units (64 vs.~20),
 which has stronger representation power. 
@@
 tokenizers.  These results indicate the value of statistical modeling
-in tokenization for informal texts.
+in tokenization for informal texts.\nss{this paragraph needs copyediting}
 
@@
 		Stanford CoreNLP & 90.4 \\
-%		UD pipe v1.2 & 78.7 \\
+%		UDPipe v1.2 & 78.7 \\
 		\citealp{owoputi-EtAl:2013:NAACL-HLT} (greedy) & 94.2 \\
@@
 		\hdashline
-%		UD pipe v1.2 & 83.8 \\
+%		UDPipe v1.2 & 83.8 \\
 		\citealp{ma-hovy:2016:P16-1} & 91.8 \\
@@
 our model with a pipeline of the state-of-the-art systems (labeled  ``SOTA''):
-Stanford CoreNLP tokenizer\footnote{We choose Stanford CoreNLP tokenizer in the spirit of comparing rule-based and statistical model-based method.}, %\yicomment{why not compare with UD pipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
+Stanford CoreNLP tokenizer\footnote{We choose Stanford CoreNLP tokenizer in the spirit of comparing rule-based and statistical model-based method.}, %\yicomment{why not compare with UDPipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
 \citet{owoputi-EtAl:2013:NAACL-HLT}'s tagger, and \citet{dozat-qi-manning:2017:K17-3}'s parser.

### 2018-03-04 paper.tex
authors

@@
 \DeclareMathOperator*{\argmin}{argmin}
-\def\aclpaperid{214}
+%\def\aclpaperid{214}
+\aclfinalcopy
 %%%%%%%
@@
 
-\author{First Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\\And
-  Second Author \\
-  Affiliation / Address line 1 \\
-  Affiliation / Address line 2 \\
-  Affiliation / Address line 3 \\
-  {\tt email@domain} \\}
+\author{Yijia Liu \\
+  Harbin Institute of Technology \\
+  {\tt oneplus.lau@gmail.com} \\\And
+  Yi Zhu \\
+  University of Cambridge \\
+  {\tt yz568@cam.ac.uk} \\\AND
+  Wanxiang Che \quad Bing Qin\\
+  Harbin Institute of Technology\\\And
+  Nathan Schneider \\
+  Georgetown University \\\And
+  Noah A. Smith \\
+  University of Washington
+  }
 

### 2018-03-04 paper.tex
table comment

@@
 The second row shows the number of new tweets compared to
-{\sc Tweebank v1}.\label{tbl:data-stat}
+{\sc Tweebank v1}.\nss{not obvious how to interpret this: train tokens looks like 1,609+1,000 = 2,609, but maybe it's 609+1,000=1,609? 
+I think it would be easier just to show v1 and v2 as separate rows. Also, a column for totals across the splits.}\label{tbl:data-stat}
 }

### 2018-03-29 paper.tex
wip

--- 2018-03-04 paper.tex
@@
 \newcommand{\nss}[1]{\textcolor{magenta}{[$_\mathrm{S}^\mathrm{NS}$#1]}}
-%\newcommand{\yjcomment}[1]{}
-%\newcommand{\nascomment}[1]{}
-%\newcommand{\yicomment}[1]{}
 
@@
   Harbin Institute of Technology \\
-  {\tt oneplus.lau@gmail.com} \\\And
+  {\tt yjliu@ir.hit.edu.cn} \\\And
   Yi Zhu \\
@@
 covered by UD guidelines.\footnote{We developed our treebank independently of a similar effort for Italian tweets \cite{sanguinetti-17}. 
-See \nss{section ref} for a comparison.} Our annotation includes 
+See \S\ref{sec:postwita} for a comparison.} Our annotation includes 
 tokenization, part-of-speech (POS) tags, and (labeled) Universal Dependencies.
@@
 POS tags, for consistency with other UD efforts,
-which adopt the universal POS tagset of \newcite{PETROV12.274}.
+which adopt the universal POS tagset.\footnote{A revised and extended version of \citet{PETROV12.274} with 17 tags.}
 % The POS annotation of a word in tweets is generally based on its syntactic distribution, which indicates that the POS of word changes on different context.
@@
 
-\paragraph{Comparison to PoSTWITA-UD.} \nss{discuss similarities and differences of conventions to \cite{sanguinetti-17}. 
+\subsection{Comparison to PoSTWITA-UD}\label{sec:postwita}
+\citet{sanguinetti-17} presented the \textit{PosTWITA-UD} which is
+the first Twitter treebank in Universal Dependencies.
+In their convention, tokenization tends to preserve the original
+tweet content but two special cases, \textit{articulated prepositions}
+and \textit{clitic clusters}, are tokenized.
+Beyond tokenization, an extra layer of lemmas is annotated
+to recover ``what is understandable by a human''.
+It's arguable that normalization (the lemmatization in \citet{sanguinetti-17})
+on social media data is essential according to \citet{eisenstein:2013:NAACL-HLT}.
+In this paper, we don't include normalization and leave it an open question for further study.
+
+In the syntax annotation, tweet specific
+constructions are considered by both \citet{sanguinetti-17} and our paper.
+We agree on the syntax head in these constructions but differ on
+the choice of relations for depicting these constructions.
+We use \textit{discourse} for topical hashtag and \citet{sanguinetti-17} used \textit{parataxis}. 
+Similar difference happens in referential URLs where we use \textit{list} by following UD\_English and they use \textit{dep}.
+The choice of relation on the non-syntactic tokens is questionable
+since UD doesn't have specified guideline for this. 
+Our choice of \textit{discourse} is inspired by the observation that emoticon is annotated as \textit{discourse}. Non-syntactic tokens can be easily recovered
+from our annotation and changing it to other relation in the future development is not difficult.
+
+%Ho \textit{non-syntactic tokens} (like sentiment emoticon, topical hashtag).
+
+\nss{discuss similarities and differences of conventions to \cite{sanguinetti-17}. 
 We expect that the official UD guidelines will eventually adopt standards for these issues so the treebanks can be harmonized.}
+\yjcomment{i've finished this part.}
 
@@
   langid.py}.\footnote{\url{https://github.com/saffsd/langid.py}}
+In the same way as \citet{kong-EtAl:2014:EMNLP2014},
+reference unit is always the tweet in its entirety
+-- which may thus consist of multiple sentences -- not the sentence alone.
+Before annotation, we use simple regular expression to anonymize username and URL.
 
@@
 	\centering
-	\begin{tabular}{rrrr}
-		\hline
-		& train & dev & test \\
-		\hline
-		tweets 		&	1,639 		&	709		&	1,201\\
-		& +1,000 & +709 & +1,000\\
-		tokens 		&	24,753		&	11,742	&	19,112\\
+	\begin{tabular}{rrrrr}
+		\hline
+		 & \multicolumn{2}{c}{\textsc{Tweebank v1}} & \multicolumn{2}{c}{\textsc{Tweebank v2}} \\
+		split & tweets & tokens & tweets & tokens \\
+		\hline
+		train & 639 & 9,310 & 1,639 & 24,753 \\
+		dev & - & - & 709 & 11,742 \\
+		test & 201 & 2,839 & 1,201 & 19,112 \\
+		\hline
+		total & 840 & 12,149 & 3,549 & 55,617 \\
+%		\textsc{v1} & tweets & 639 & 0 & 201 & 840 \\
+%		& tokens  & 9,310 & 0 & 2,839 & 12149 \\
+%		\hdashline
+%		\textsc{v2} & tweets & 1,639 & 709 & 1,201 & 3,549 \\
+%		 & tokens &	24,753	&	11,742	&	19,112 & 55,617\\
 		\hline
 	\end{tabular}
-\caption{Statistics of {\sc Tweebank v2}.
-The second row shows the number of new tweets compared to
-{\sc Tweebank v1}.\label{tbl:data-stat}
+
+%	\begin{tabular}{rrrrrr}
+%		\hline
+%		\multicolumn{2}{l}{version} & train & dev & test & total \\
+%		\hline
+%		\textsc{v1} & tweets & 639 & 0 & 201 & 840 \\
+%		& tokens  & 9,310 & 0 & 2,839 & 12149 \\
+%		\hdashline
+%		\textsc{v2} & tweets & 1,639 & 709 & 1,201 & 3,549 \\
+%		 & tokens &	24,753	&	11,742	&	19,112 & 55,617\\
+%		\hline
+%	\end{tabular}
+\caption{Statistics of {\sc Tweebank v2} and the comparison with
+{\sc Tweebank v1} in quantity.\nss{not obvious how to interpret this: train tokens looks like 1,609+1,000 = 2,609, but maybe it's 609+1,000=1,609? 
+I think it would be easier just to show v1 and v2 as separate rows. Also, a column for totals across the splits.}
+\yjcomment{i've fix this.}
+\label{tbl:data-stat}
 }
@@
 and used to automatically analyze the sampled 2,500 tweets.  Authors 
-of this paper manually corrected the parsed data and finally achieved 3,550 labeled tweets.\nss{What tools did annotators use?}
+of this paper manually corrected the parsed data and finally achieved 3,550 labeled tweets\nss{What tooks did annotators use?}\yjcomment{fixed}.\footnote{We use arborator \cite{gerdes:2013:W13-37} in our annotation.}
 Newly created annotations are split into train, development, and test set and appended
@@
 \end{table}
-\citet{wang-EtAl:2017:Long6} show that the parser\nss{tokenizer?} trained 
+\citet{wang-EtAl:2017:Long6} show that the parser\nss{tokenizer?}\yjcomment{it's a parsing work.} trained 
 on the combination of the UD\_English and Singapore English dialect (Singlish) treebanks
@@
 in recent methods for training greedy models that use dynamic oracles
-\citep{ballesteros-EtAl:2016:EMNLP2016}.  
+\citet{goldberg-nivre:2012:PAPERS,TACL145,TACL885,ballesteros-EtAl:2016:EMNLP2016}.  
 We find that this
@@
 
+\section*{Acknowledge}
+We thank Elizabeth Clark, Lucy Lin, Nelson Liu, Kelvin Luu, Phoebe Mulcaire, 
+Hao Peng, Maarten Sap, Chenhao Tan, Sam Thomson,
+and the other colleagues in Georgetown University for the annotation efforts in the first round.
+We also thank the anonymous  reviewers for their helpful comments and suggestions.
+\yjcomment{fonding agency here and anyone else i miss.}
+This work was supported by the National Key Basic Research
+Program of China via grant 2014CB340503 and the
+National Natural Science Foundation of China (NSFC) via
+grant 61632011.
+
 \bibliography{shortdb}

### 2018-04-04 paper.tex
feedback on recent edits

@@
 \newcommand{\heart}{\ensuremath\heartsuit}
+
+\newcommand{\citeposs}[2][]{\citeauthor{#2}'s (\citeyear[#1]{#2})}
+\newcommand{\Citeposs}[2][]{\Citeauthor{#2}'s (\citeyear[#1]{#2})}
 
@@
 \subsection{Comparison to PoSTWITA-UD}\label{sec:postwita}
-\citet{sanguinetti-17} presented the \textit{PosTWITA-UD} which is
-the first Twitter treebank in Universal Dependencies.
+The first Twitter treebank annotated with Universal Dependencies 
+was the \mbox{\textit{PosTWITA-UD}} corpus for Italian \citep{sanguinetti-17}, 
+which consists of \nss{??} tweets (\nss{??} sentences, \nss{??} tokens).
 In their convention, tokenization tends to preserve the original
 tweet content but two special cases, \textit{articulated prepositions}
-and \textit{clitic clusters}, are tokenized.
+and \textit{clitic clusters}, are tokenized.\nss{explain what these two phenomena are. are these the only words that are split?}
 Beyond tokenization, an extra layer of lemmas is annotated
@@
 It's arguable that normalization (the lemmatization in \citet{sanguinetti-17})
-on social media data is essential according to \citet{eisenstein:2013:NAACL-HLT}.
-In this paper, we don't include normalization and leave it an open question for further study.
-
-In the syntax annotation, tweet specific
-constructions are considered by both \citet{sanguinetti-17} and our paper.
-We agree on the syntax head in these constructions but differ on
-the choice of relations for depicting these constructions.
-We use \textit{discourse} for topical hashtag and \citet{sanguinetti-17} used \textit{parataxis}. 
-Similar difference happens in referential URLs where we use \textit{list} by following UD\_English and they use \textit{dep}.
+on social media data is essential according to \citet{eisenstein:2013:NAACL-HLT}.\nss{``It's arguable that normalization...is essential'' suggests that we think it IS essential.
+Did you mean ``whether'' instead of ``that''?}
+In this paper, we don't include normalization and leave it an open question for further study.\nss{Maybe just say: 
+Their lemmas include spelling normalization, whereas our lemmas only normalize casing and inflectional morphology (if that is correct). 
+You could also mention that the current UD guidelines on lemmas (which I wrote) give a lot of flexibility to treebank 
+developers: \url{http://universaldependencies.org/u/overview/morphology.html\#lemmas}}
+
+%In the syntax annotation, tweet specific
+%constructions are considered by both \citet{sanguinetti-17} and our paper.
+With respect to tweet-specific constructions,
+our and \citeposs{sanguinetti-17} interpretation of headedness is the same, 
+but we differ in the relation label.
+For topical hashtags, we use \textit{discourse} while \citet{sanguinetti-17} used \textit{parataxis}. 
+In referential URLs, we use \textit{list} (following the precedent of UD\_English-EWT) while \citet{sanguinetti-17} used \textit{dep}.
 The choice of relation on the non-syntactic tokens is questionable
-since UD doesn't have specified guideline for this. 
-Our choice of \textit{discourse} is inspired by the observation that emoticon is annotated as \textit{discourse}. Non-syntactic tokens can be easily recovered
-from our annotation and changing it to other relation in the future development is not difficult.
+since UD doesn't specify a convention for this. 
+Our choice of \textit{discourse} is inspired by the observation that emoticon is annotated as \textit{discourse}.\nss{what did PosTWITA-UD use for non-syntactic tokens?} 
+% Non-syntactic tokens can be easily recovered
+% from our annotation and changing it to other relation in the future development is not difficult.
+We expect that the official UD guidelines will eventually adopt standards for these constructions so the treebanks can be harmonized.
 
 %Ho \textit{non-syntactic tokens} (like sentiment emoticon, topical hashtag).
-
-\nss{discuss similarities and differences of conventions to \cite{sanguinetti-17}. 
-We expect that the official UD guidelines will eventually adopt standards for these issues so the treebanks can be harmonized.}
-\yjcomment{i've finished this part.}
 
@@
 		train & 639 & 9,310 & 1,639 & 24,753 \\
-		dev & - & - & 709 & 11,742 \\
+		dev & --\hphantom{0} & --\hphantom{00} & 709 & 11,742 \\
 		test & 201 & 2,839 & 1,201 & 19,112 \\
@@
 \caption{Statistics of {\sc Tweebank v2} and the comparison with
-{\sc Tweebank v1} in quantity.\nss{not obvious how to interpret this: train tokens looks like 1,609+1,000 = 2,609, but maybe it's 609+1,000=1,609? 
-I think it would be easier just to show v1 and v2 as separate rows. Also, a column for totals across the splits.}
-\yjcomment{i've fix this.}
+{\sc Tweebank v1} in quantity.
+%\nss{not obvious how to interpret this: train tokens looks like 1,609+1,000 = 2,609, but maybe it's 609+1,000=1,609? 
+%I think it would be easier just to show v1 and v2 as separate rows. Also, a column for totals across the splits.}
+%\yjcomment{i've fix this.}
 \label{tbl:data-stat}
@@
 and used to automatically analyze the sampled 2,500 tweets.  Authors 
-of this paper manually corrected the parsed data and finally achieved 3,550 labeled tweets\nss{What tooks did annotators use?}\yjcomment{fixed}.\footnote{We use arborator \cite{gerdes:2013:W13-37} in our annotation.}
+of this paper manually corrected the parsed data and finally achieved 3,550 labeled tweets.\footnote{Manual annotation was done with Arborator \cite{gerdes:2013:W13-37}, a web platform for drawing dependency trees.}
 Newly created annotations are split into train, development, and test set and appended
@@
 \end{table}
-\citet{wang-EtAl:2017:Long6} show that the parser\nss{tokenizer?}\yjcomment{it's a parsing work.} trained 
+\citet{wang-EtAl:2017:Long6} show that the parser\nss{tokenizer?}\yjcomment{it's a parsing work.}\nss{I guess I don't follow how parsing results 
+on combined training data affect our decision about how to tokenize.} trained 
 on the combination of the UD\_English and Singapore English dialect (Singlish) treebanks
@@
 We thank Elizabeth Clark, Lucy Lin, Nelson Liu, Kelvin Luu, Phoebe Mulcaire, 
-Hao Peng, Maarten Sap, Chenhao Tan, Sam Thomson,
-and the other colleagues in Georgetown University for the annotation efforts in the first round.
+Hao Peng, Maarten Sap, Chenhao Tan, and Sam Thomson at the University of Washington, 
+and Austin Blodgett, Lucia Donatelli, Joe Garman, Emma Manning, Angela Yang, and Yushi Zhang 
+at Georgetown University for their annotation efforts in the first round.
 We also thank the anonymous reviewers for their helpful comments and suggestions.
-\yjcomment{fonding agency here and anyone else i miss.}
+\yjcomment{funding agency here and anyone else i miss.}
 This work was supported by the National Key Basic Research

### 2018-04-11 guideline.tex
upload guideline, wip

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{naaclhlt2018}
\usepackage{times}
\usepackage{tikz-dependency}
\usepackage{subcaption}
\aclfinalcopy
\newcommand{\yjcomment}[1]{\textcolor{orange}{[$_\mathrm{L}^\mathrm{Y}$#1]}}

\title{Annotation Guideline for \textsc{Tweebank v2}}
\author{Yijia Liu \\
	Harbin Institute of Technology \\
	{\tt yjliu@ir.hit.edu.cn} \\\And
	Yi Zhu \\
	University of Cambridge \\
	{\tt yz568@cam.ac.uk} \\\AND
}

\date{}

\begin{document}
\maketitle

\section{Introduction}
Annotating tweets is hard. 
Delivering consistent annotation is even harder.
The original annotation guideline in the universal dependencies (UD) project
gives good definition on the relations, but didn't cover some common
constructions in tweets.
What's more, ambiguities exist. 
Some constructions can either be explained by different guidelines in UD.

In this guideline, we list most common constructions
and annotation difficulties we encountered when creating \textsc{Tweebank v2}.
Our work includes:
\begin{itemize}
	\item specify what guideline to be applied when constructions that are
	uncommon in UD guideline.
	\item specify what guideline to be applied when there are ambiguities in
	applying the guidelines.
\end{itemize}

In this guideline, not only we touch the syntax part of the annotation,
but also the whole pipeline from sentence segmentation to POS tagging. 
\section{Non-syntactic Tokens}

In this section, we give the definition of the non-syntactic tokens
we mentioned in the paper.

\subsection{Retweet Construction}

\begin{figure}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			RT \& @user \& : \& wow \\
			\texttt{X} \& \texttt{X} \& \texttt{PUNCT} \& \texttt{INTJ} \\
		\end{deptext}
		\deproot{4}{root}
		\depedge{4}{1}{discourse}
		\depedge{1}{2}{discourse}
		\depedge{1}{3}{punct}
	\end{dependency}
	\caption{An example for the conventional retweet construction.}\label{fig:rt}
\end{figure}

We consider the special construction in tweet: 
\[
\underline{\textit{RT @user :}}
\]
as the \textit{retweet construction}.
Figure \ref{fig:rt} illustrates the most standard retweet construction.
\yjcomment{copy our discussion from the paper here.}

Besides the discussion in the syntactic aspect, 
retweet construction marks the begining of a sentence and used to
determine the boundary of a sentence in tweets (see Section \ref{sec:sent-seg} for
more details).
However, there are still cases where retweet construction is unconventional, 
as shown in the following examples:
\[
\underline{\textit{RT @user1 : RT @user2 it s hilarious}}
\]
We consider the second as a retweet construction even without the comma.

\subsection{Referential URL}

\begin{figure}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			it \& s \& hilarious \& URL \\
			PRON \& AUX \& ADJ \& X\\
		\end{deptext}
		\deproot{3}{root}
		\depedge{3}{1}{nsubj}
		\depedge{3}{2}{cop}
		\depedge{3}{4}{\textbf{list}}
	\end{dependency}
	\caption{An example for referential URL.}\label{fig:ref-url}
\end{figure}

Figure \ref{fig:ref-url} shows an example for the \textit{referential URL}.
We consider a URL as the referential URL when it meets the following conditions:

\begin{itemize}
	\item The URL is used as a supplementary resource for the tweet.
	\item When removed, the syntax of the rest part of the tweet doesn't change.
	\item The URL is not an appositional modifier of a noun phrase (NP). 
	Figure \ref{fig:non-ref-url}
	shows an example for a URL that was used as an appositional modifier.
\end{itemize}

For a referential URL, we analyze its syntactic head in the same way as
what UD does for \textit{punct}(uation) but use the \textit{list}
relation.

\paragraph{Cases of Non-referential URLs.}
\begin{figure}[t]
\centering
\small
\begin{subfigure}[t]{0.45\columnwidth}
	\centering
	\begin{dependency}[edge slant=2, text only label, label style=above]
	\begin{deptext}
		Photo \& : \& URL \\
		\texttt{NOUN} \& \texttt{PUNCT} \& \texttt{X} \\
	\end{deptext}
	\deproot{1}{root}
	\depedge{1}{2}{punct}
	\depedge{1}{3}{\textbf{appos}}
	\end{dependency}
\end{subfigure}
\begin{subfigure}[t]{0.45\columnwidth}
	\centering
	\begin{dependency}[edge slant=2, text only label, label style=above]
	\begin{deptext}
		click \& URL \\
		\texttt{VERB} \& \texttt{X} \\
	\end{deptext}
	\deproot{1}{root}
	\depedge{1}{2}{\textbf{obj}}
\end{dependency}
\end{subfigure}
\caption{Examples for non-referential URL.}\label{fig:non-ref-url}
\end{figure}

We consider the following cases as non-referential URLs:
\begin{itemize}
	\item \underline{\textit{watch : \textbf{URL}}} 
	In this case, we consider the URL as an object of \textit{watch}.
	\item \underline{\textit{click for details: \textbf{URL}}}
	In this case, we consider the URL as an appositional modifier of \textit{details}.
\end{itemize}

\paragraph{Cases of Referential URLs with Modifiers.}
\begin{figure}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			video \& : \& URL \& via \& @user \\
			\texttt{NOUN} \& \texttt{PUNCT} \& \texttt{X} \& \texttt{ADP} \& \texttt{PROPN} \\
		\end{deptext}
		\deproot{1}{root}
		\depedge{1}{2}{punct}
		\depedge{1}{3}{list}
		\depedge{3}{5}{\textbf{nmod}}
		\depedge{5}{4}{case}
	\end{dependency}
	\caption{An example for URL that has modifier.}\label{fig:ref-w-mod}
\end{figure}
In most cases, referential URLs don't have modifiers.
The following cases are the only exceptions:
\begin{itemize}
	\item \underline{\textit{watch : \textbf{URL} via YouTube}}
	We consider \textit{via YouTube} as the nominal modifier of the URL
	(see Figure \ref{fig:ref-w-mod} for an example).
	\item \underline{\textit{click for details: \textbf{URL1} \textbf{URL2}}}
	We consider the second \textit{URL} as an conjunction of the first one.
\end{itemize}

\subsection{Topical Hashtag, Sentiment Emoticon, and Truncated Words}

\begin{figure}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			I \& come \& conclusion \& that \& ... \& \#topsecret \\
			\texttt{PRON} \& \texttt{VERB} \& \texttt{NOUN} \& \texttt{SCONJ} \& \texttt{PUNCT} \& \texttt{X}\\
		\end{deptext}
		\deproot{2}{root}
		\depedge{2}{1}{nsubj}
		\depedge{2}{3}{obj}
		\depedge{3}{4}{ccomp}
		\depedge[edge unit distance=2ex]{2}{5}{punct}
		\depedge[edge unit distance=2ex]{2}{6}{\textbf{discourse}}
	\end{dependency}
	\caption{An example for topical hashtag.}\label{fig:hashtag}
\end{figure}

\textit{Topical hashtag}, \textit{sentiment emoticon}, and \textit{truncated words}
are defined in the same way as referential URL.
But we use \textit{discourse} to analyze its syntactic head.
Figure \ref{fig:hashtag} shows an example for topical hashtag.

\section{Multiple Sentences in One Tweet}\label{sec:sent-seg}
When encountering a raw tweet, 
the first thing we would do is to segment the tweet to sentences.
However, due to the highly varied styles of tweet, 
it might not be obvious to distinguish which segment is a sentence.
Here we propose several cases:
\begin{enumerate}
	\item Standard punctuations function the same in the normal text,
	i.e. period, exclamation, question mark are the mark of the end of the sentence,
	whereas comma, colon, ellipse mark do not split the tweet;
	\item If there is a retweet construction in the middle of the tweet,
	the RT mark is considered to segment the sentence and is the beginning of a new sentence;
	\item If we can distinguish clearly sentences from tweets, 
	but they are not split by the punctuations or RT. 
	we then treat them as a single sentence with \textit{parataxis};
\end{enumerate}

\begin{figure}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			Yall \& sholl \& is \& quiet \& !! \& SPEAK \& UP \& lol \& RT \& user \& : \& wow \\
%			\texttt{PRON} \& \texttt{VERB} \& \texttt{NOUN} \& \texttt{SCONJ} \& \texttt{PUNCT} \& \texttt{X}\\
		\end{deptext}
		\deproot{4}{\textbf{root}}
		\depedge{4}{1}{nsubj}
		\depedge{4}{2}{aux}
		\depedge{4}{3}{cop}
		\depedge{4}{5}{punct}
		\deproot{6}{\textbf{root}}
		\depedge{6}{7}{compound:prt}
		\depedge{6}{8}{discourse}
		\deproot{12}{\textbf{root}}
		\depedge{12}{9}{discourse}
		\depedge{9}{10}{discourse}
		\depedge{9}{11}{punct}
	\end{dependency}
	\caption{An example for a tweet with multiple sentences. 
		Retweet  construction is also treated as a sentence delimiter.}\label{fig:multi-seg}
\end{figure}

\begin{figure}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			i \& ca \& n't \& login \& no \& i \& do \& n't \& know \& y \& nvr \& c \& nus \& offer \\
			%			\texttt{PRON} \& \texttt{VERB} \& \texttt{NOUN} \& \texttt{SCONJ} \& \texttt{PUNCT} \& \texttt{X}\\
		\end{deptext}
		\deproot{4}{\textbf{root}}
		\depedge{4}{1}{nsubj}
		\depedge{4}{2}{aux}
		\depedge{4}{3}{part}
		\depedge{4}{9}{parataxis}
		\depedge{9}{5}{discourse}
		\depedge{9}{6}{nsubj}
		\depedge{9}{7}{aux}
		\depedge{9}{8}{part}
		\depedge{9}{10}{ccomp}
		\depedge[edge unit distance=2.5ex]{4}{12}{parataxis}
		\depedge{12}{14}{obj}
		\depedge{12}{11}{advmod}
		\depedge{14}{13}{compond}
	\end{dependency}
	\caption{An example for a tweet with multiple sentences. 
		Retweet  construction is also treated as a sentence delimiter.}\label{fig:single-seg}
\end{figure}

For the sentence in Figure \ref{fig:multi-seg},  there are 3 sentences.
RT splits the sentences and is the beginning of a new sentence.
While, for the sentence in Figure \ref{fig:single-seg},
there are only 1 sentence, although many sentences can be distinguished easily.

\begin{figure}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			i \& ca \& n't \& login \& no \& i \& do \& n't \& know \& y \& nvr \& c \& nus \& offer  \& :-/ \\
			%			\texttt{PRON} \& \texttt{VERB} \& \texttt{NOUN} \& \texttt{SCONJ} \& \texttt{PUNCT} \& \texttt{X}\\
		\end{deptext}
		\deproot{4}{root}
		\depedge[edge unit distance=1ex]{4}{9}{parataxis}
		\depedge[edge unit distance=1ex]{4}{12}{parataxis}
		\depedge[edge unit distance=1ex]{4}{15}{\textbf{discourse}}
	\end{dependency}
	\caption{An example for referential URL on parataxis sentences.}\label{fig:ref-url-on-para-sent}
\end{figure}

\subsection{Referential URL in Parataxis Sentences}
For those cases, we analyze the syntactic head of the referential URL
as the root word among the parataxis sentences.
See Figure \ref{fig:ref-url-on-para-sent} for an example.
This rule also applies to topical hashtags, sentiment emoticons, and truncated words.

Finally, we need to note that we didn't include sentence segmentation
as a step in the whole parsing pipeline.
The guideline only suggests how to

\section{Named Entities}
%see newsgroup-groups.google.com\_emails\_ec0a1064de05e74b\_ENG\_20040929\_023800-0047
Compared with those in formal text, Twitter presents 
a wider range of entities.
We categories them as following.

\paragraph{Person name.} 
\begin{figure}[t]
	\begin{subfigure}[t]{0.3\columnwidth}
		\centering
		\small
		\begin{dependency}[edge slant=2, text only label, label style=above]
			\begin{deptext}
				Kevin \& Durant \\
				\texttt{PROPN} \& \texttt{PROPN} \\
			\end{deptext}
			\deproot{1}{}
			\depedge{1}{2}{flat}
		\end{dependency}
	\caption{}\label{fig:per-name:vanilla}
	\end{subfigure}
	\begin{subfigure}[t]{0.3\columnwidth}
		\centering
		\small
		\begin{dependency}[edge slant=2, text only label, label style=above]
			\begin{deptext}
				President \& Obama \\
				\texttt{PROPN} \& \texttt{PROPN} \\
			\end{deptext}
			\deproot{1}{}
			\depedge{1}{2}{flat}
		\end{dependency}
	\caption{}\label{fig:per-name:title}
	\end{subfigure}
	\begin{subfigure}[t]{0.3\columnwidth}
		\centering
		\small
		\begin{dependency}[edge slant=2, text only label, label style=above]
			\begin{deptext}
				Al \& - \& Zaman \\
				\texttt{PROPN} \& \texttt{punct} \& \texttt{PROPN} \\
			\end{deptext}
			\deproot{1}{}
			\depedge{1}{2}{punct}
			\depedge{1}{3}{flat}
		\end{dependency}
		\caption{}\label{fig:per-name:punct}
	\end{subfigure}
\end{figure}
Person name is easy to identify.
For tokens in a person name, their POS tags are \texttt{PROPN} and
we treat the left-most token as the syntactic head
and link the rest of the tokens in the person name to this token (see Figure \ref{fig:per-name:vanilla}).
Here, we show some special cases in person names.
\begin{itemize}
	\item Person name with title, like \underline{\textit{President Obama}} (Figure \ref{fig:per-name:title});
	\item Person name with punctuation, like \underline{\textit{Al - Zaman}} (Figure \ref{fig:per-name:punct});
\end{itemize}

\paragraph{Group name.}
Mentions about groups (music group, sport group, and etc.) are common in tweets.
The names of music group can present complex syntactic structures,
e.g. \underline{\textit{One Direction}}, \underline{\textit{Zac Brown Band}},
and \underline{\textit{Rico Riders}}.
In this guideline, we propose to analyze the in the same way as
person name, using \textit{flat} to the left-most token.

There are several group names presented in \textsc{Tweebank v2}. Here is a comprehensive list:
\textit{One Direction, Super Junior, 
	Higher Authority,
	Eagles of Death Mental, 
	*5 Second of Summer*,
	Carolina Panthers, Rico Riders, Manchester United, Real Madrid,
	49ers, Patriots, Heat, Celtics
}.

\paragraph{Brand name.}
We treat brand name in the same way with group name.
Here is a comprehensive list of brand name in \textsc{Tweebank v2}:
\textit{Amazon, Apple, Louis Vuitton, Facebook, Twitter}.

\paragraph{Location name.}
\begin{figure}[t]
	\begin{subfigure}[t]{0.3\columnwidth}
		\centering
		\small
		\begin{dependency}[edge slant=2, text only label, label style=above]
			\begin{deptext}
				Santa \& Cruz \\
				\texttt{PROPN} \& \texttt{PROPN} \\
			\end{deptext}
			\deproot{2}{}
			\depedge{2}{1}{compound}
		\end{dependency}
		\caption{}\label{fig:loc-name:vanilla}
	\end{subfigure}
	\begin{subfigure}[t]{0.3\columnwidth}
		\centering
		\small
		\begin{dependency}[edge slant=2, text only label, label style=above]
			\begin{deptext}
				101 \& Drive \\
				\texttt{NUM} \& \texttt{PROPN} \\
			\end{deptext}
			\deproot{2}{}
			\depedge{2}{1}{nummod}
		\end{dependency}
		\caption{}\label{fig:loc-name:comp}
	\end{subfigure}
	\begin{subfigure}[t]{0.3\columnwidth}
		\centering
		\small
		\begin{dependency}[edge slant=2, text only label, label style=above]
			\begin{deptext}
				Cleveland \& , \& OH \\
				\texttt{PROPN} \& \texttt{punct} \& \texttt{PROPN} \\
			\end{deptext}
			\deproot{1}{}
			\depedge{1}{2}{punct}
			\depedge{1}{3}{appos}
		\end{dependency}
		\caption{}\label{fig:loc-name:punct}
	\end{subfigure}
\end{figure}
There are three major types of location name:
\begin{itemize}
	\item Vanilla location: like \textit{New York}, \textit{New York City}, and \textit{Santa Cruz}. 
	We use \textit{compound} to analyze their relations (Figure \ref{fig:loc-name:vanilla});
	\item Details location: like \textit{101 Drive} and \textit{Downtown Atlanta}.
	We use their original relation (Figure \ref{fig:loc-name:comp});
	\item Location name with punctuation: \textit{Cleveland , OH}, (Figure \ref{fig:loc-name:punct});
\end{itemize}

\paragraph{Product name.}
We analyze product name as a normal nominal phrase.
Thus, tokens like \textit{shoulder bag} are analyzed as \texttt{NOUN} rather than \texttt{PROPN}.
\begin{itemize}
	\item Apple Music, Didi Chuxing. Zapata Beer
	\item Asus Gaming PC
	\item Louis Vuitton Monogram Marelle Shoulder Bag
	\item Puzzle Sharks
\end{itemize}

Product name usually comes with suffix (version number).
If one token or span of tokens is considered as the suffix, 
it won't be analyzed as syntactic head, but a modifier of the noun phrase prefix.
If the suffix is a number (like \underline{\textit{Kindle \textbf{3}}}), we analyze the POS as \texttt{NUM} and \textit{nummod}.
If the suffix is a noun phrase (like \underline{\textit{Samsung Galaxy \textbf{S6}}}), we analyze the POS as \texttt{PROPN} and \textit{nmod:npmod}.
We need to note that a combination of letter and number as version number is treated as nominal.

\paragraph{Organization name.} 
We analyze organization name as a normal noun phrase.
We use \texttt{PROPN} as the POS tag.
\begin{itemize}
	\item Clinton Global Initiative University
	\item Santander UK
\end{itemize}

\paragraph{Event name.}
\begin{itemize}
	\item Bush Tax Cuts
	\item Down to Lunch
	\item Stanley Cup
\end{itemize}

\paragraph{Title name.}
We analyze the title name as a normal phrase.
\begin{itemize}
	\item Gone with the wind
	\item lone survivor
\end{itemize}

%We collected as list of group names presented in \textsc{Tweebank v2}.
%\begin{itemize}
%	\item \textit{product name}: Apple Music
%	\item \textit{event name}: normal
%	\item \textit{title name}: normal
%	\item \textit{brand name}: 
%	\item \textit{product name}: normal
%	\item \textit{suffix, version}: mixture of \textit{4s}. npmod, conjuction.
%	\item \textit{americans}:
%\end{itemize}
%
%\begin{table}[t]
%	\centering
%	\begin{tabular}{lr}
%		\hline
%		category & POS \\
%		\hline
%		The Eyenimal Cat Video Camera & \\
%		Monogram Marelle Shoulder Bag & \\
%		Apple Music & \\
%		The Power Ball & \\
%		Parag Milk Foods & \\
%		Darby Video App & \\
%		Moon Child glow kit & \\
%		Boise State & \\
%		Dickey Amendment & \\
%		lone survivor & \\
%		Clinton Global Initiative University & \\
%		Zapata Beer & \\
%		LADY PYRAMID & \\
%		Bush Tax Cuts & \\
% Asus Gaming PC
%		Friday Night Lights & \\
%		\hline
%	\end{tabular}
%\end{table}

\section{Special Constructions}

\subsection{List vs Parataxis vs Appos}

Tweets are full of commercials, music references (see Figure \ref{fig:singer-title}).
It's worth studying these constructions.
``Informal and web text often contains passages which are meant to be
interpreted as lists but are parsed as single sentences.'' \yjcomment{copied from UD}

\begin{table}[t]
	\centering
	\begin{tabular}{lrr}
		\hline
		pattern & relation & example \\
		\hline
		singer - title & list & Figure \ref{fig:singer-title} \\
		title - singer & parataxis & Figure \ref{fig:title-singer} \\
		quote - author & parataxis & \\
		author - quote & parataxis & \\
		agency : title & parataxis & \\
		\hline
	\end{tabular}
\caption{text}\label{tbl:list-construct}
\end{table}

In this guideline, we category these special cases in Table \ref{tbl:list-construct}.

\begin{figure}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			Lady  \& Gaga \& - \& Bad \& Romance \\
			\texttt{PRORN} \& \texttt{PROPN} \& \texttt{PUNCT} \& \texttt{ADJ} \& \texttt{NOUN} \\
		\end{deptext}
		\deproot{1}{root}
		\depedge{1}{2}{flat}
		\depedge{1}{3}{punct}
		\depedge{5}{4}{amod}
		\depedge[edge unit distance=2.5ex]{1}{5}{\textbf{list}}
	\end{dependency}
	\caption{A music reference tweet.}\label{fig:singer-title}
\end{figure}

\begin{figure}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			i \& 'd \& do \& anything \& - \& simple \& plan \\
			\texttt{PRON} \& \texttt{AUX} \& \texttt{VERB} \& \texttt{PRON} \& \texttt{PUNCT} \& \texttt{ADJ} \& \texttt{NOUN} \\
		\end{deptext}
		\deproot{3}{root}
		\depedge{3}{1}{nsubj}
		\depedge{3}{2}{aux}
		\depedge{3}{4}{obj}
		\depedge{3}{5}{punct}
		\depedge[edge unit distance=2.5ex]{3}{7}{parataxis}
		\depedge{7}{6}{amod}
	\end{dependency}
	\caption{An example for leading @username.}\label{fig:title-singer}
\end{figure}

%see weblog-blogspot.com\_rigorousintuition\_20060511134300\_ENG\_20060511\_134300-0004
%Refer newsgroup-groups.google.com\_emails\_ec0a1064de05e74b\_ENG\_20040929\_023800-0047
\paragraph{When to Use Appos?}
\begin{figure}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			I \& liked \& a \& @YouTube \& video \& : \& URL \\
			\texttt{PRON} \& \texttt{VERB} \& \texttt{DET} \& \texttt{PROPN} \& \texttt{NOUN} \& \texttt{PUNCT} \& \texttt{X} \\
		\end{deptext}
		\deproot{2}{root}
		\depedge{2}{1}{nsubj}
		\depedge{2}{5}{ojb}
		\depedge{5}{3}{det}
		\depedge{5}{4}{nmod}
		\depedge{5}{6}{punct}
		\depedge{5}{7}{\textbf{appos}}
	\end{dependency}
	\caption{An example for leading @username.}\label{fig:case-02}
\end{figure}

In most the cases, we won't analyze the token with \textit{appos}.
See Figure \ref{fig:case-02}.

\subsection{Noun phrase or Copula Ellipse}
\begin{figure}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			@username \& covered \& in \& magic \& ! \\
			PROPN \& VERB \& ADP \& NOUN \& PUNCT \\
		\end{deptext}
		\deproot{2}{root}
		\depedge{2}{1}{nsubj}
		\depedge{2}{4}{obl}
		\depedge{4}{3}{mark}
		\depedge{2}{5}{punct}
	\end{dependency}
	\caption{An example for leading @username.}\label{fig:case-05-1}
\end{figure}

\begin{itemize}
	\item feb\_jul\_16.1469260380
	\item feb\_jul\_16.1460628240
	\item feb\_jul\_16.1469497200
	\item feb\_jul\_16.1463541180
	\item feb\_jul\_16.1456268400
	\item feb\_jul\_16.1462312200
	\item feb\_jul\_16.1458837000
	\item feb\_jul\_16.1458423240
\end{itemize}

\subsection{Code Switching}

\subsection{Leading @user: vocative or nsubj}
\begin{figure}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			@user1  \& @user2 \& Problem \& is \& how \& we \\
			\texttt{PRORN} \& \texttt{PROPN} \& \texttt{NOUN} \& \texttt{VERB} \& \texttt{ADV} \& \texttt{PRON} \\
		\end{deptext}
		\deproot{4}{root}
		\depedge{4}{1}{\textbf{vocative}}
		\depedge{4}{2}{\textbf{vocative}}
		\depedge{4}{3}{nsubj}
	\end{dependency}
	\caption{An example for leading @user.}\label{fig:vocative}
\end{figure}

\begin{figure}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			@user  \& hiding \& from \& this \& tornado \& . \& How \& are \& you \& ? \\
			\texttt{PROPN} \& \texttt{VERB} \& \texttt{ADP} \& \texttt{DET} \& \texttt{NOUN} \& \& \texttt{ADV} \& \texttt{AUX} \& \texttt{PRON} \\
		\end{deptext}
		\deproot{2}{root}
		\depedge{2}{1}{\textbf{vocative}}
		\depedge{2}{5}{obl}
		\depedge{5}{3}{case}
		\depedge{5}{4}{det}
	\end{dependency}
	\caption{An example for ambiguous leading @user which can either be analyzed as \textbf{nsubj} or \textbf{vocative}.}\label{fig:abnormal-vocative}
\end{figure}

The way of recognizing if a @user token is \textit{vocative}.
See Figure \ref{fig:case-01}.

\section{Worth Noting}
\subsection{Have sth. to}
\begin{figure}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			have \& time \& to \& review \& it \\
			VERB \& NOUN \& PART \& VERB \& PRON \\
		\end{deptext}
		\deproot{1}{root}
		\depedge{1}{2}{obj}
		\depedge{2}{4}{acl}
		\depedge{4}{3}{mark}
		\depedge{4}{5}{obj}
	\end{dependency}
	\caption{An example for leading @username.}\label{fig:case-04}
\end{figure}
See email-enronsent35\_01-0096.

\subsection{for real, fr.}
\begin{figure}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			@username \& covered \& in \& magic \& ! \\
			PROPN \& VERB \& ADP \& NOUN \& PUNCT \\
		\end{deptext}
		\deproot{2}{root}
		\depedge{2}{1}{nsubj}
		\depedge{2}{4}{obl}
		\depedge{4}{3}{mark}
		\depedge{2}{5}{punct}
	\end{dependency}
	\caption{An example for leading @username.}\label{fig:case-06}
\end{figure}
See answers-20111108092643AAXe4lD\_ans-0039

\subsection{U.K.-loving}
\begin{figure}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			U.K. \& - \& loving \& stocks \\
			PROPN \& PUNCT \& VERB \& NOUN \\
		\end{deptext}
		\deproot{4}{root}
		\depedge{4}{3}{?}
	\end{dependency}
	\caption{An example for leading @username.}\label{fig:case-08}
\end{figure}

\subsection{POS for lmao}
is \textsc{INTJ}

\subsection{POS for live}
\begin{itemize}
	\item feb\_jul\_16.1464410640
\end{itemize}

\subsection{Only one clause}
\begin{itemize}
	\item feb\_jul\_16.1468795800
\end{itemize}
Use the root in the clause.

\subsection{Additional adp}
\begin{itemize}
	\item feb\_jul\_16.1454771880
\end{itemize}

\subsection{, you know ,}
\begin{itemize}
	\item feb\_jul\_16.1463121540
\end{itemize}

\subsection{Title modifier}
Several references:
\begin{itemize}
	\item weblog-blogspot.com\_dakbangla\_20050311135387\_ENG\_20050311\_135387-0161
	\item email-enronsent16\_01-0055
\end{itemize}
\begin{itemize}
	\item feb\_jul\_16.1460481960
	\item feb\_jul\_16.1459860060
	\item feb\_jul\_16.1467549120
	\item feb\_jul\_16.1467056520
\end{itemize}

What about `One direction'?

\subsection{Special Token}
\begin{itemize}
	\item tbh: to be honest
	\item dm: direct message: can be noun or verb.
	\item tl: timeline: like dm, can be noun or verb.
\end{itemize}

\subsection{Date}
\begin{itemize}
	\item July 9th where 9th is a NOUN.
	\item April 2, 2016
\end{itemize}

\subsection{Title}
\begin{itemize}
	\item Arsenal chief XX
\end{itemize}

\subsection{title}
6 - game losing streak

pos should concern.
\begin{itemize}
	\item dm?
\end{itemize}

\subsection{Vocative or subject}

\end{document}

### 2018-04-11 guideline.tex
update guideline

@@
 \newcommand{\yjcomment}[1]{\textcolor{orange}{[$_\mathrm{L}^\mathrm{Y}$#1]}}
+\newcommand{\yicomment}[1]{\textcolor{green}{[$_\mathrm{Y}^\mathrm{I}$#1]}}
 
@@
 \begin{itemize}
-	\item specify what guideline to be applied when constructions that are
+	\item specify what guideline to be applied to constructions that are
 	uncommon in UD guideline.
@@
 
-In this guideline, not only we touch the syntax part of the annotation,
-but also the whole pipeline from sentence segmentation to POS tagging. 
+In this guideline, not only do we touch the syntax part of the annotation,
+but also the whole pipeline from sentence segmentation\yicomment{word segmentation?} to POS tagging. 
 \section{Non-syntactic Tokens}
@@
 
-We consider the special construction in tweet: 
+We consider the special construction in Twitter: 
 \[
@@
 Figure \ref{fig:rt} illustrates the most standard retweet construction.
-\yjcomment{copy our discussion from the paper here.}
+\yjcomment{copy our discussion from the paper here.}\yicomment{It is the standard combination of constructions in Twitter that don't have much real information.}
 
 Besides the discussion in the syntactic aspect, 
-retweet construction marks the begining of a sentence and used to
+retweet construction usually marks the beginning of a sentence and used to
 determine the boundary of a sentence in tweets (see Section \ref{sec:sent-seg} for
@@
 \]
-We consider the second as a retweet construction even without the comma.
+We consider \textit{RT @user2} also as a retweet construction even without the comma.\yicomment{we can say that the colon can be omit in the very beginning, so that we don't have to mention it again?}
 
@@
 	\item The URL is used as a supplementary resource for the tweet.
-	\item When removed, the syntax of the rest part of the tweet doesn't change.
-	\item The URL is not an appositional modifier of a noun phrase (NP). 
+	\item When removed, the syntax of the rest part of the tweet doesn't change.\yicomment{It is not core argument in syntax, and it is more an oblique modifier.}
+	\item The URL is not an appositional modifier of a noun phrase (NP). \yicomment{fig3(photo) and 4(video) are the same to me}
 	Figure \ref{fig:non-ref-url}
@@
 		\depedge{1}{2}{punct}
-		\depedge{1}{3}{list}
+		\depedge{1}{3}{list\yicomment{not appos??}}
 		\depedge{3}{5}{\textbf{nmod}}
@@
 	We consider \textit{via YouTube} as the nominal modifier of the URL
-	(see Figure \ref{fig:ref-w-mod} for an example).
+	(see Figure \ref{fig:ref-w-mod} for an example)\yicomment{URL still seems an obj of watch like previous example?}.
 	\item \underline{\textit{click for details: \textbf{URL1} \textbf{URL2}}}
-	We consider the second \textit{URL} as an conjunction of the first one.
+	We consider the second \textit{URL} as an conjunction of the first one.\yicomment{1. both urls are non-referential; 2. non of them have modifiers}
 \end{itemize}
@@
 are defined in the same way as referential URL.
-But we use \textit{discourse} to analyze its syntactic head.
+But we use \textit{discourse} to analyze its syntactic head.\yicomment{the reason is that UD use list for URL without clear explanation, we stick to UD convention for URL.}
 Figure \ref{fig:hashtag} shows an example for topical hashtag.
@@
 	\item If there is a retweet construction in the middle of the tweet,
-	the RT mark is considered to segment the sentence and is the beginning of a new sentence;
+	the RT mark is considered to segment the sentences and is the beginning of a secon sentence;
 	\item If we can distinguish clearly sentences from tweets, 
-	but they are not split by the punctuations or RT. 
+	but they are not split by the punctuations or RT. \yicomment{It is somewhat empirical and subjective, but we tried to reach the agreement among annotators}
 	we then treat them as a single sentence with \textit{parataxis};
@@
 RT splits the sentences and is the beginning of a new sentence.
-While, for the sentence in Figure \ref{fig:single-seg},
-there are only 1 sentence, although many sentences can be distinguished easily.
+While for the sentence in Figure \ref{fig:single-seg},
+there is actually only one sentence, although three sentences can be distinguished easily.
 
@@
 
-\subsection{Referential URL in Parataxis Sentences}
+\subsection{Referential URL in Parataxis Sentences}\yicomment{is it for when to use list and when to use parataxis? maybe not necessary to add it?}
 For those cases, we analyze the syntactic head of the referential URL
@@
 We categories them as following.
+\yicomment{again it is our taxonomy as UD doesn't make it clear, and not sure if we need to add it into this guideline.
+(It's always good if the guideline is just online, but not in the paper appendix).
+Maybe good idea to show Nathan}
 
-\paragraph{Person name.} 
+\paragraph{Person name.} \yicomment{here maybe it's group name, org name, and some title names that are PURELY MWE with NO internal structures}
 \begin{figure}[t]
@@
 
-\paragraph{Group name.}
+\paragraph{Group name.}\yicomment{here maybe it's group/org/brand/loc names that are MWE with internal structures}
+\yicomment{We discuss them according to their syntax, whether 1. it's an simple non phrase without modifiers (only adj or noun); 2. noun phrase with modifier; 3. verb phrase}
 Mentions about groups (music group, sport group, and etc.) are common in tweets.
@@
 
-\paragraph{Event name.}
+\paragraph{Event name.}\yicomment{then another category is event/title/product names that are treated just as normal phrase}
 \begin{itemize}
@@
 	\item Down to Lunch
-	\item Stanley Cup
+	\item Stanley Cup\yicomment{this falls in the previous category}
 \end{itemize}
@@
 ``Informal and web text often contains passages which are meant to be
-interpreted as lists but are parsed as single sentences.'' \yjcomment{copied from UD}
+interpreted as lists but are parsed as single sentences.'' \yjcomment{copied from UD}\yicomment{such a pain for this section}
 

### 2018-04-13 paper.tex
update

@@
 
-We release our dataset and our system as open-source software at
-\url{http://anonymized}.
+Our dataset and system is publicly available at \url{https://github.com/Oneplus/Tweebank}
+and \url{https://github.com/Oneplus/twpipe}.
 
@@
 was the \mbox{\textit{PosTWITA-UD}} corpus for Italian \citep{sanguinetti-17}, 
-which consists of \nss{??} tweets (\nss{??} sentences, \nss{??} tokens).
+which consists of 6,738 tweets (119,726 tokens).
 In their convention, tokenization tends to preserve the original
 tweet content but two special cases, \textit{articulated prepositions}
-and \textit{clitic clusters}, are tokenized.\nss{explain what these two phenomena are. are these the only words that are split?}
-Beyond tokenization, an extra layer of lemmas is annotated
-to recover ``what is understandable by a human''.
-It's arguable that normalization (the lemmatization in \citet{sanguinetti-17})
-on social media data is essential according to \citet{eisenstein:2013:NAACL-HLT}.\nss{``It's arguable that normalization...is essential'' suggests that we think it IS essential.
-Did you mean ``whether'' instead of ``that''?}
-In this paper, we don't include normalization and leave it an open question for further study.\nss{Maybe just say: 
-Their lemmas include spelling normalization, whereas our lemmas only normalize casing and inflectional morphology (if that is correct). 
-You could also mention that the current UD guidelines on lemmas (which I wrote) give a lot of flexibility to treebank 
-developers: \url{http://universaldependencies.org/u/overview/morphology.html\#lemmas}}
+(e.g. \textit{nella} as \textit{in la})
+and \textit{clitic clusters} (e.g. \textit{guardandosi} as \textit{guardando si}), are tokenized.
+\nss{explain what these two phenomena are. are these the only words that are split?}\yjcomment{done}
+%Beyond tokenization, an extra layer of lemmas is annotated
+%to recover ``what is understandable by a human''.
+%It's arguable whether normalization (the lemmatization in \citet{sanguinetti-17})
+%on social media data is essential according to \citet{eisenstein:2013:NAACL-HLT}.
+%In this paper, we don't include normalization and leave it an open question for further study.
+%\nss{Maybe just say: 
+Their lemmas include spelling normalization, whereas our lemmas only normalize casing and inflectional morphology.
+The current UD guidelines on lemmas give a lot of flexibility on treebank development.\footnote{\url{http://universaldependencies.org/u/overview/morphology.html\#lemmas}}
+%You could also mention that the current UD guidelines on lemmas (which I wrote) give a lot of flexibility to treebank 
+%developers: \url{http://universaldependencies.org/u/overview/morphology.html\#lemmas}}
 
@@
 With respect to tweet-specific constructions,
-our and \citeposs{sanguinetti-17} interpretation of headedness is the same, 
+\citeposs{sanguinetti-17} and our  interpretation of headedness is the same, 
 but we differ in the relation label.
@@
 since UD doesn't specify a convention for this. 
-Our choice of \textit{discourse} is inspired by the observation that emoticon is annotated as \textit{discourse}.\nss{what did PosTWITA-UD use for non-syntactic tokens?} 
+Our choice of \textit{discourse} is inspired by the observation that emoticon is annotated as \textit{discourse}.
+\citet{sanguinetti-17} used the same relation for the emoticon but analyze topical hashtag as \textit{parataxis}.\nss{what did PosTWITA-UD use for non-syntactic tokens?}\yjcomment{done}
 % Non-syntactic tokens can be easily recovered
@@
 		\hline
-		  Stanford CoreNLP & 96.6 \\
-		 Twokenizer & 94.4 \\		 
+		  Stanford CoreNLP & 97.3 \\
+		 Twokenizer & 94.6 \\
 % 		UDPipe v1.2 & 94.7 \\
 		\hdashline
-		UDPipe v1.2 & 97.3 \\
+		UDPipe v1.2 & 97.4 \\
 	 	our bi-LSTM tokenizer & 98.3 \\
@@
 \end{table}
-\citet{wang-EtAl:2017:Long6} show that the parser\nss{tokenizer?}\yjcomment{it's a parsing work.}\nss{I guess I don't follow how parsing results 
-on combined training data affect our decision about how to tokenize.} trained 
-on the combination of the UD\_English and Singapore English dialect (Singlish) treebanks
-outperforms the one trained only on the dialect treebank.  Preliminary results
-showed the same in our case, so 
-we follow their work and trained our tokenizer on the training portion of
+%\citet{wang-EtAl:2017:Long6} show that the parser\nss{tokenizer?}\yjcomment{it's a parsing work.}\nss{I guess I don't follow how parsing results 
+%on combined training data affect our decision about how to tokenize.} trained 
+%on the combination of the UD\_English and Singapore English dialect (Singlish) treebanks
+%outperforms the one trained only on the dialect treebank.  
+Our preliminary results
+showed that our model trained on
+the combination of UD\_English and Tweebank v2
+outperforms the one trained only on the UD\_English or Tweebank v2,
+which also was confirmed by previous works on dialect treebank parsing \cite{wang-EtAl:2017:Long6}.
+So we trained our tokenizer on the training portion of
 \textsc{Tweebank v2} combined with the UD\_English training set
@@
 tokenizers.  These results indicate the value of statistical modeling
-in tokenization for informal texts.\nss{this paragraph needs copyediting}
+in tokenization for informal texts.%\nss{this paragraph needs copyediting}
 
@@
 %		Stanford Postagger & 65.6 \\
-		Stanford CoreNLP & 90.4 \\
+		Stanford CoreNLP & 90.6 \\
 %		UDPipe v1.2 & 78.7 \\
-		\citealp{owoputi-EtAl:2013:NAACL-HLT} (greedy) & 94.2 \\
-		\citealp{owoputi-EtAl:2013:NAACL-HLT} (CRF) & 95.1 \\
+		\citealp{owoputi-EtAl:2013:NAACL-HLT} (greedy) & 93.7 \\
+		\citealp{owoputi-EtAl:2013:NAACL-HLT} (CRF) & 94.6 \\
 		\hdashline
 %		UDPipe v1.2 & 83.8 \\
-		\citealp{ma-hovy:2016:P16-1} & 91.8 \\
+		\citealp{ma-hovy:2016:P16-1} & 92.5 \\
 %		our word bi-LSTM & 89.2 \\
@@
 		\hline
-		Stanford CoreNLP & 92.1 \\
-		our bi-LSTM tokenizer (\S\ref{sec:tok}) & 93.7 \\
+		Stanford CoreNLP & 92.3 \\
+		our bi-LSTM tokenizer (\S\ref{sec:tok}) & 93.3 \\
 		\hline
@@
            the parsing speed evaluated by thousands of tokens
-           the model processed per second.
+           the model processed per second.\yjcomment{num will change}
             \label{tbl:parse-result}}
@@
 	\includegraphics[width=\columnwidth,trim={0.3cm 0 0 0},clip]{graphics/alpha}
-	\caption{The effect of $\alpha$ on distillation. \label{fig:effect-alpha}}
+	\caption{The effect of $\alpha$ on distillation. \yjcomment{num will change}\label{fig:effect-alpha}}
 \end{figure}
@@
 	\end{tabular}
-	\caption{Evaluating our pipeline against a state-of-the-art pipeline. \label{tbl:pipline} %\yicomment{see tab5 for our tokenizer the pos tagging number is 93.6, here is 93.7, should be consistent}
+	\caption{Evaluating our pipeline against a state-of-the-art pipeline.
+\yjcomment{num will change}\label{tbl:pipline} %\yicomment{see tab5 for our tokenizer the pos tagging number is 93.6, here is 93.7, should be consistent}
 	}
@@
 at Georgetown University for their annotation efforts in the first round.
+We are grateful for the support from Lingpeng Kong at the initial stage of this project.
 We also thank the anonymous reviewers for their helpful comments and suggestions.

### 2018-04-13 guideline.tex
update

--- 2018-04-11 guideline.tex
@@
 
+Truncated URL.
+
 \section{Multiple Sentences in One Tweet}\label{sec:sent-seg}
@@
 and \underline{\textit{Rico Riders}}.
-In this guideline, we propose to analyze the in the same way as
-person name, using \textit{flat} to the left-most token.
+In this guideline, we propose to analyze the syntax using \textit{compound}.
+However, if there is \texttt{ADP} in the group name like \textit{Eagles of Death Mental}, we analyze them as a normal noun phrase.
 
@@
 	Carolina Panthers, Rico Riders, Manchester United, Real Madrid,
-	49ers, Patriots, Heat, Celtics
+	49ers, Patriots, Heat, Celtics,
+	Mariners,
+	Nature Republic,
+	The weekend,
+	Kiss Daniel,
+	Yung 4,
+	Doncaster Phoenix,
+	West Hartlepool
 }.
@@
 	\item Puzzle Sharks
+	\item After School Snack
+	\item CARVIN BX250 250 W Micro Bass Guitar Amp Amplifier Head / Compressor
+	\item Lake Wind Advisory
+	\item CARVIN BX250
+	\item Australian Gelato
+	\item Pokemon GO
+	\item Windows live
 \end{itemize}
@@
 We use \texttt{PROPN} as the POS tag.
+We analyze most of the organization names as compound.
+But for cases like \textit{Santander UK}.
 \begin{itemize}
@@
 	\item Santander UK
+	\item Parag Milk Foods
+	\item Alabama Banking Department
+	\item Lady Tattoo Studio
+	\item Hartlepool Mail
+	\item Big East
 \end{itemize}
@@
 	\item Stanley Cup
+	\item The CJUSD District College and Career Fair
+	\item \#AV/IT Leadership Summit
+	\item FA Cup
 \end{itemize}

### 2018-04-13 guideline.tex

--- 2018-04-11 guideline.tex
@@
 	\item Stanley Cup\yicomment{this falls in the previous category}
+	\item The CJUSD District College and Career Fair
+	\item \#AV/IT Leadership Summit
+	\item FA Cup
 \end{itemize}

### 2018-04-15 paper.tex
copyedits to paper and bib; clarification

@@
 tweet content but two special cases, \textit{articulated prepositions}
-(e.g. \textit{nella} as \textit{in la})
-and \textit{clitic clusters} (e.g. \textit{guardandosi} as \textit{guardando si}), are tokenized.
-\nss{explain what these two phenomena are. are these the only words that are split?}\yjcomment{done}
+(e.g.~\textit{nella} as \textit{in la})
+and \textit{clitic clusters} (e.g.~\textit{guardandosi} as \textit{guardando si}), are tokenized.
+%\nss{explain what these two phenomena are. are these the only words that are split?}\yjcomment{done}
 %Beyond tokenization, an extra layer of lemmas is annotated
@@
 In referential URLs, we use \textit{list} (following the precedent of UD\_English-EWT) while \citet{sanguinetti-17} used \textit{dep}.
-The choice of relation on the non-syntactic tokens is questionable
-since UD doesn't specify a convention for this. 
-Our choice of \textit{discourse} is inspired by the observation that emoticon is annotated as \textit{discourse}.
-\citet{sanguinetti-17} used the same relation for the emoticon but analyze topical hashtag as \textit{parataxis}.\nss{what did PosTWITA-UD use for non-syntactic tokens?}\yjcomment{done}
+%The choice of relation on the non-syntactic tokens is questionable
+%since UD doesn't specify a convention for this. 
+Our choice of \textit{discourse}\nss{for what? maybe the previous sentences should be swapped} is inspired by the observation that emoticons are annotated as \textit{discourse}.\nss{by whom?}
+\citet{sanguinetti-17} used the same relation for the emoticon but analyze topical hashtag as \textit{parataxis}.
+\nss{topical hashtags already mentioned above}
 % Non-syntactic tokens can be easily recovered
@@
 our model with a pipeline of the state-of-the-art systems (labeled  ``SOTA''):
-Stanford CoreNLP tokenizer\footnote{We choose Stanford CoreNLP tokenizer in the spirit of comparing rule-based and statistical model-based method.}, %\yicomment{why not compare with UDPipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
+Stanford CoreNLP tokenizer,\footnote{We choose the Stanford CoreNLP tokenizer in the spirit of comparing 
+rule-based and statistical methods.} %\yicomment{why not compare with UDPipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
 \citet{owoputi-EtAl:2013:NAACL-HLT}'s tagger, and \citet{dozat-qi-manning:2017:K17-3}'s parser.
@@
 
-\section*{Acknowledge}
+\section*{Acknowledgments}
 We thank Elizabeth Clark, Lucy Lin, Nelson Liu, Kelvin Luu, Phoebe Mulcaire, 
@@
 
+\nss{bibliography: most but not all conference papers have URLs; some but not all have page numbers. 
+``TACL'' is sometimes spelled out.
+Make sure ``LSTM'', ``LSTMs'', etc. are capitalized properly in titles.}
+
 \bibliography{shortdb}

### 2018-04-15 paper.tex
update on result.

--- 2018-04-13 paper.tex
@@
 and \textit{clitic clusters} (e.g. \textit{guardandosi} as \textit{guardando si}), are tokenized.
-\nss{explain what these two phenomena are. are these the only words that are split?}\yjcomment{done}
+%\nss{explain what these two phenomena are. are these the only words that are split?}\yjcomment{done}
 %Beyond tokenization, an extra layer of lemmas is annotated
@@
 Our choice of \textit{discourse} is inspired by the observation that emoticon is annotated as \textit{discourse}.
-\citet{sanguinetti-17} used the same relation for the emoticon but analyze topical hashtag as \textit{parataxis}.\nss{what did PosTWITA-UD use for non-syntactic tokens?}\yjcomment{done}
+\citet{sanguinetti-17} used the same relation for the emoticon but analyze topical hashtag as \textit{parataxis}.%\nss{what did PosTWITA-UD use for non-syntactic tokens?}\yjcomment{done}
 % Non-syntactic tokens can be easily recovered
@@
 Our preliminary experiments confirm this finding, with a gap of 1 LAS on development data
-between the best (75.8)
+between the best (76.2)
  and worst (74.8) runs. To control for this
@@
 		\hline
-		\citet{kong-EtAl:2014:EMNLP2014} &81.6 & 77.2 & 0.3 \\
-		\citet{dozat-qi-manning:2017:K17-3} & 81.9 &  77.7 & 1.7 \\
+		\citet{kong-EtAl:2014:EMNLP2014} & 81.4 & 76.9 & 0.3 \\
+		\citet{dozat-qi-manning:2017:K17-3} & 82.3 & 78.3 & 1.7 \\
 %		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
-		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.4 & 75.8 & 2.3 \\
+		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.2 & 75.7 & 2.3 \\
 		\hdashline
-		Ensemble (20) & 83.5 & 79.4 & 0.2 \\
+		Ensemble (20) & 83.4 & 79.4 & 0.2 \\
 		Distillation ($\alpha =1.0$) & 82.2 & 78.0 & 2.3 \\
@@
 	\includegraphics[width=\columnwidth,trim={0.3cm 0 0 0},clip]{graphics/alpha}
-	\caption{The effect of $\alpha$ on distillation. \yjcomment{num will change}\label{fig:effect-alpha}}
+	\caption{The effect of $\alpha$ on distillation.\label{fig:effect-alpha}}
 \end{figure}
@@
 We also thank the anonymous reviewers for their helpful comments and suggestions.
-\yjcomment{funding agency here and anyone else i miss.}
+%\yjcomment{funding agency here and anyone else i miss.}
 This work was supported by the National Key Basic Research

### 2018-04-15 paper.tex

--- 2018-04-15 paper.tex
@@
 
-\newcommand{\yjcomment}[1]{\textcolor{orange}{[$_\mathrm{L}^\mathrm{Y}$#1]}}
-\newcommand{\nascomment}[1]{\textcolor{blue}{[#1 ---\textsc{nas}]}}
-\newcommand{\yicomment}[1]{\textcolor{gray}{[#1 ---\textsc{yi}]}}
-\newcommand{\nss}[1]{\textcolor{magenta}{[$_\mathrm{S}^\mathrm{NS}$#1]}}
+%\newcommand{\yjcomment}[1]{\textcolor{orange}{[$_\mathrm{L}^\mathrm{Y}$#1]}}
+%\newcommand{\nascomment}[1]{\textcolor{blue}{[#1 ---\textsc{nas}]}}
+%\newcommand{\yicomment}[1]{\textcolor{gray}{[#1 ---\textsc{yi}]}}
+%\newcommand{\nss}[1]{\textcolor{magenta}{[$_\mathrm{S}^\mathrm{NS}$#1]}}
 
@@
 method to distill an ensemble of 20 transition-based parsers into a single one. Our
-parser achieves an improvement of 2.6 in LAS over the un-ensembled baseline 
+parser achieves an improvement of 2.2 in LAS over the un-ensembled baseline 
 and outperforms parsers that are state-of-the-art on other treebanks in both accuracy and speed.
@@
 for training and evaluation is hard. 
-Pioneering work by \citet{AAAIW113912} 
+Pioneering work by \citet{Foster:2011:HPT:2908630.2908634} 
 annotated 7,630 tokens' worth of tweets according to the
@@
 transition sequence. Experimental results show that an improvement of more
-than 2.6 points in LAS over the
+than 2.2 points in LAS over the
 baseline parser can be achieved with our distillation method.  It outperforms
@@
 In some cases,  non-corresponding tag conflicts arose between the UD English 
-treebank conventions \cite[UD\_English;][]{Marneffe2014UniversalSD}\footnote{\url{https://github.com/UniversalDependencies/UD_English}}
+treebank conventions \cite[UD\_English;][]{Marneffe2014UniversalSD}\footnote{\url{https://github.com/UniversalDependencies/UD_English-EWT}}
 and the conventions of \newcite{gimpel-EtAl:2011:ACL-HLT2011}.  %\yicomment{The conflicts
@@
 (\texttt{X}), except for emoticons, which are tagged as \emph{symbol}
-(\texttt{SYM}), following UD\_English.
+(\texttt{SYM}), following UD\_English-EWT.
 
@@
 \item Non-syntactic tokens are mostly labeled as {\it discourse}, but
-  URLs are always labeled as {\it list}, following the UD\_English dataset.% \yicomment{need to add punct for punctuations?}
+  URLs are always labeled as {\it list}, following the UD\_English-EWT dataset.% \yicomment{need to add punct for punctuations?}
 %\\ \yicomment{For retweet at-mention case, we attach the retweet at-mentions to the RT sign, so that the retweet action and the people whose tweet is being retweeted could be connected.\footnote{We can also follow the first convention to attach the retweet at-mention to its predicate, but we think it is better for downstream tasks.}}
@@
 In referential URLs, we use \textit{list} (following the precedent of UD\_English-EWT) while \citet{sanguinetti-17} used \textit{dep}.
+%<<<<<<< HEAD
 %The choice of relation on the non-syntactic tokens is questionable
 %since UD doesn't specify a convention for this. 
-Our choice of \textit{discourse}\nss{for what? maybe the previous sentences should be swapped} is inspired by the observation that emoticons are annotated as \textit{discourse}.\nss{by whom?}
-\citet{sanguinetti-17} used the same relation for the emoticon but analyze topical hashtag as \textit{parataxis}.
-\nss{topical hashtags already mentioned above}
+%Our choice of \textit{discourse} is inspired by the observation that emoticon is annotated as \textit{discourse}.
+%\citet{sanguinetti-17} used the same relation for the emoticon but analyze topical hashtag as \textit{parataxis}.%\nss{what did PosTWITA-UD use for non-syntactic tokens?}\yjcomment{done}
+%=======
+%The choice of relation on the non-syntactic tokens is questionable
+%since UD doesn't specify a convention for this. 
+Our choice of \textit{discourse} for sentiment emoticons
+is inspired by the observation that emoticons are annotated as \textit{discourse} by UD\_English-EWT
+and \citet{sanguinetti-17} used the same relation for the emoticons.
+%\nss{topical hashtags already mentioned above}
+%>>>>>>> a7f86b777a73f64b2f05101f4804421aea0412f3
 % Non-syntactic tokens can be easily recovered
@@
 		train & 639 & 9,310 & 1,639 & 24,753 \\
-		dev & --\hphantom{0} & --\hphantom{00} & 709 & 11,742 \\
+		dev & --\hphantom{0} & --\hphantom{00} & 710 & 11,742 \\
 		test & 201 & 2,839 & 1,201 & 19,112 \\
 		\hline
-		total & 840 & 12,149 & 3,549 & 55,617 \\
+		total & 840 & 12,149 & 3,550 & 55,607 \\
 %		\textsc{v1} & tweets & 639 & 0 & 201 & 840 \\
@@
 showed that our model trained on
-the combination of UD\_English and Tweebank v2
-outperforms the one trained only on the UD\_English or Tweebank v2,
+the combination of UD\_English-EWT and Tweebank v2
+outperforms the one trained only on the UD\_English-EWT or Tweebank v2,
 which also was confirmed by previous works on dialect treebank parsing \cite{wang-EtAl:2017:Long6}.
 So we trained our tokenizer on the training portion of
-\textsc{Tweebank v2} combined with the UD\_English training set
+\textsc{Tweebank v2} combined with the UD\_English-EWT training set
 and tested on the \textsc{Tweebank v2} test set.
@@
 %word vectors and the other using word and character vectors (see Figure \ref{fig:pos-model}).
-All compared systems were re-trained on the combination of the UD\_English and 
+All compared systems were re-trained on the combination of the UD\_English-EWT and 
 \textsc{Tweebank v2} training sets. We use Twitter-specific GloVe embeddings released by
@@
 
-In our preliminary experiments, we train our parser on the combination of UD\_English
+In our preliminary experiments, we train our parser on the combination of UD\_English-EWT
 and \textsc{Tweebank v2} training sets. Gold-standard tokenization and automatic POS
@@
 number generator.
-Our preliminary experiments confirm this finding, with a gap of 1 LAS on development data
-between the best (75.8)
+Our preliminary experiments confirm this finding, with a gap of 1.4 LAS on development data
+between the best (76.2)
  and worst (74.8) runs. To control for this
@@
 		\hline
-		\citet{kong-EtAl:2014:EMNLP2014} &81.6 & 77.2 & 0.3 \\
-		\citet{dozat-qi-manning:2017:K17-3} & 81.9 &  77.7 & 1.7 \\
+		\citet{kong-EtAl:2014:EMNLP2014} & 81.4 & 76.9 & 0.3 \\
+		\citet{dozat-qi-manning:2017:K17-3} & 81.8 & 77.7 & 1.7 \\
 %		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
-		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.4 & 75.8 & 2.3 \\
+		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.2 & 75.7 & 2.3 \\
 		\hdashline
-		Ensemble (20) & 83.5 & 79.4 & 0.2 \\
-		Distillation ($\alpha =1.0$) & 82.2 & 78.0 & 2.3 \\
-		Distillation ($\alpha =0.9$) & 82.4 & 78.1 & 2.3 \\		
-		Distillation w/ exploration & 82.5 & 78.4 & 2.3 \\
+		Ensemble (20) & 83.4 & 79.4 & 0.2 \\
+		Distillation ($\alpha =1.0$) & 81.8 & 77.6 & 2.3 \\
+		Distillation ($\alpha =0.9$) & 82.0 & 77.8 & 2.3 \\		
+		Distillation w/ exploration & 82.1 & 77.9 & 2.3 \\
 		\hline
@@
            the parsing speed evaluated by thousands of tokens
-           the model processed per second.\yjcomment{num will change}
+           the model processed per second.
             \label{tbl:parse-result}}
@@
 Distilling from this 
-parser leads to a single greedy transition-based parser with 78.1
+parser leads to a single greedy transition-based parser with 77.8
 LAS---better than past systems but worse than our more expensive ensemble.
@@
 		\hline
-		Tokenization  & \it $F_1$ & 98.3 & 96.6 \\		
-		POS tagging &  \it  $F_1$ & 93.7 & 92.1 \\
-		UD parsing & \it LAS $F_1$ & 74.1 & 70.3 \\
+		Tokenization  & \it $F_1$ & 98.3 & 97.3 \\		
+		POS tagging &  \it  $F_1$ & 93.3 & 92.2 \\
+		UD parsing & \it LAS $F_1$ & 74.0 & 71.4 \\
 		\hline
 	\end{tabular}
-	\caption{Evaluating our pipeline against a state-of-the-art pipeline.
-\yjcomment{num will change}\label{tbl:pipline} %\yicomment{see tab5 for our tokenizer the pos tagging number is 93.6, here is 93.7, should be consistent}
+	\caption{Evaluating our pipeline against a state-of-the-art pipeline.\label{tbl:pipline} %\yicomment{see tab5 for our tokenizer the pos tagging number is 93.6, here is 93.7, should be consistent}
 	}
@@
 to overcome annotation noise without sacrificing efficiency.
-Our parser achieves an improvement of 2.6  in LAS over a strong baseline
+Our parser achieves an improvement of 2.2  in LAS over a strong baseline
 and outperforms other state-of-the-art parsers in both accuracy and speed.
@@
 
-\nss{bibliography: most but not all conference papers have URLs; some but not all have page numbers. 
-``TACL'' is sometimes spelled out.
-Make sure ``LSTM'', ``LSTMs'', etc. are capitalized properly in titles.}
+%\nss{bibliography: most but not all conference papers have URLs; some but not all have page numbers. 
+%``TACL'' is sometimes spelled out.
+%Make sure ``LSTM'', ``LSTMs'', etc. are capitalized properly in titles.}
 

### 2018-04-15 paper.tex
possessive citations

@@
 aggressive tokenization than that of \citet{ICWSM101540} which opted
-out of splitting contractions and possessives. As a consequence of adopting \citet{ICWSM101540}'s tokenization, 
+out of splitting contractions and possessives. As a consequence of adopting \citeposs{ICWSM101540} tokenization, 
 Gimpel et al.~introduced new parts of speech for these cases
@@
 Twitter, we compared several existing systems: the Stanford CoreNLP tagger, 
-\citet{owoputi-EtAl:2013:NAACL-HLT}'s word cluster enhanced tagger
+\citeposs{owoputi-EtAl:2013:NAACL-HLT} word cluster enhanced tagger
 (both greedy and CRF variants), and 
-\citet{ma-hovy:2016:P16-1}'s neural network tagger 
+\citeposs{ma-hovy:2016:P16-1} neural network tagger 
 which achieves the state-of-the-art performance on PTB.
-\citet{gui-EtAl:2017:EMNLP20172} presented a state-of-the-art neural tagger for Twitter,
+\Citet{gui-EtAl:2017:EMNLP20172} presented a state-of-the-art neural tagger for Twitter,
 but their implementation works only with the PTB tagset, so we exclude
@@
 \citet{Brown:1992:CNG:176313.176316} clusters in the 
-POS tagger of \citet{owoputi-EtAl:2013:NAACL-HLT} outperforms \citet{ma-hovy:2016:P16-1}'s neural network
+POS tagger of \citet{owoputi-EtAl:2013:NAACL-HLT} outperforms \citeposs{ma-hovy:2016:P16-1} neural network
 model. 
@@
  \citet{dozat-qi-manning:2017:K17-3}.
- \citet{kong-EtAl:2014:EMNLP2014}'s parser is a graph-based
+ \Citeposs{kong-EtAl:2014:EMNLP2014} parser is a graph-based
 parser with lexical features and word cluster and it uses dual decomposition
@@
 rule-based and statistical methods.} %\yicomment{why not compare with UDPipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
-\citet{owoputi-EtAl:2013:NAACL-HLT}'s tagger, and \citet{dozat-qi-manning:2017:K17-3}'s parser.
+\citeposs{owoputi-EtAl:2013:NAACL-HLT} tagger, and \citeposs{dozat-qi-manning:2017:K17-3} parser.
 Our system differs from the SOTA pipeline in the tokenization and parser components.

### 2018-04-15 paper.tex
better monospace font

@@
 \usepackage{amsmath}
+\usepackage[scaled=.8]{beramono}
+\usepackage[T1]{fontenc}
+\usepackage[utf8x]{inputenc}
 \usepackage{multirow}
@@
 part-of-speech tagging, and labeled dependencies. Using the extended guidelines, we create
-a new tweet treebank ({\sc Tweebank v2}) that is four times larger than the (unlabeled) {\sc Tweebank
+a new tweet treebank for English ({\sc Tweebank v2}) that is four times larger than the (unlabeled) {\sc Tweebank
   v1} introduced by \citet{kong-EtAl:2014:EMNLP2014}. 
@@
 raw tweets into Universal Dependencies. Our pipeline includes: a
-bidirectional LSTM (bi-LSTM) tokenizer, a word cluster-enhanced POS
+bidirectional LSTM (bi-LSTM) tokenizer, a word cluster--enhanced POS
 tagger \citep[following][]{owoputi-EtAl:2013:NAACL-HLT}, and a stack LSTM parser
@@
 
-Our dataset and system is publicly available at \url{https://github.com/Oneplus/Tweebank}
+Our dataset and system are publicly available at \url{https://github.com/Oneplus/Tweebank}
 and \url{https://github.com/Oneplus/twpipe}.
@@
 Twitter, we compared several existing systems: the Stanford CoreNLP tagger, 
-\citeposs{owoputi-EtAl:2013:NAACL-HLT} word cluster enhanced tagger
+\citeposs{owoputi-EtAl:2013:NAACL-HLT} word cluster--enhanced tagger
 (both greedy and CRF variants), and 

### 2018-04-15 paper.tex
section 2: annotation (tweaks and questions)

@@
 %\newcommand{\yicomment}[1]{\textcolor{gray}{[#1 ---\textsc{yi}]}}
-%\newcommand{\nss}[1]{\textcolor{magenta}{[$_\mathrm{S}^\mathrm{NS}$#1]}}
+\newcommand{\nss}[1]{\textcolor{magenta}{[$_\mathrm{S}^\mathrm{NS}$#1]}}
 
@@
 cases. We witnessed a small number of tweets that contain multi-token words
-(e.g., {\it Y O}, and {\it R E T W E E T}) but didn't combine them for simplification.
+(e.g., {\it Y O}, and {\it R E T W E E T}) but didn't combine them for simplicity.
 Such tokens only account for 0.07\% and we use the UD
@@
 For twitter specific linguistic phenomena, we have set different strategies and try to align with the UD conventions and UD\textunderscore English as close as possible.\footnote{\url{https://github.com/UniversalDependencies/UD\_English}}
-In some cases,  non-corresponding tag conflicts arose between the UD English 
-treebank conventions \cite[UD\_English;][]{Marneffe2014UniversalSD}\footnote{\url{https://github.com/UniversalDependencies/UD_English-EWT}}
+In some cases,  non-corresponding tag conflicts arose between the UD English Web Treebank 
+treebank conventions \cite[UD\_English-EWT;][]{Marneffe2014UniversalSD}\footnote{\url{https://github.com/UniversalDependencies/UD_English-EWT}}
 and the conventions of \newcite{gimpel-EtAl:2011:ACL-HLT2011}.  %\yicomment{The conflicts
@@
 conformed to UD, enabling consistency (e.g., when we exploit the
-existing UD\_English treebank in our parser for tweets, \S\ref{sec:parsing}).  For example,  
+existing UD\_English-EWT treebank in our parser for tweets, \S\ref{sec:parsing}).  For example,  
 the nominal URL in Figure \ref{fig:informal-toks} is tagged as {\it
@@
 
-Tokens that abbreviate multiple words, such as \emph{idc} are resolved to the POS of the syntactic head of the
+Tokens that abbreviate multiple words (such as \emph{idc}) are resolved to the POS of the syntactic head of the
 expression, following UD conventions (in this example, the head \emph{care} is
@@
 For example, besides being a discourse marker, \emph{RT} can
-abbreviate the verb {\it retweet}, and emoticons and hashtags may be
-used as content words within a sentence, and at-mentions can be normal vocative proper nouns; see Figure
-\ref{fig:informal-toks}.  Therefore, the criteria for annotating a
+abbreviate the verb {\it retweet}; emoticons and hashtags may be
+used as content words within a sentence; and at-mentions can be normal vocative proper nouns: see Figure~\ref{fig:informal-toks}.  
+Therefore, the criteria for annotating a
 token as non-syntactic must be context-dependent.
@@
 \item If a non-syntactic token is within a sentence that has a clear predicate, it will be attached to this predicate. 
-Retweet construction is a special case and we will discuss our choice in the following paragraph.
-\item If the whole sentence is made of a sequence of non-syntactic tokens, we attach all these tokens to the first one.
+The retweet construction is a special case and we will discuss its treatment in the following paragraph.
+\item If the whole sentence\nss{tweet?} is a sequence of non-syntactic tokens, we attach all these tokens to the first one.
 %\item In parataxis case, when it is difficult to decide which sentence or phrase x should belong to, we always attach x to the previous predicate of the paratactic clause or phrase;
@@
 They required the annotators to first select the non-syntactic
-tokens and exclude them from the final dependencies annotation.
+tokens and exclude them from the final dependency annotation.
 %  \nascomment{confusing.  were they removed or
@@
 Their lemmas include spelling normalization, whereas our lemmas only normalize casing and inflectional morphology.
-The current UD guidelines on lemmas give a lot of flexibility on treebank development.\footnote{\url{http://universaldependencies.org/u/overview/morphology.html\#lemmas}}
+The current UD guidelines on lemmas are flexible, so variation between treebanks is expected.\footnote{\url{http://universaldependencies.org/u/overview/morphology.html\#lemmas}}
 %You could also mention that the current UD guidelines on lemmas (which I wrote) give a lot of flexibility to treebank 
@@
 is inspired by the observation that emoticons are annotated as \textit{discourse} by UD\_English-EWT
-and \citet{sanguinetti-17} used the same relation for the emoticons.
+and \citet{sanguinetti-17} used the same relation for the emoticons.\nss{how does the other treebank treat the RT construction and truncated words?}
 %\nss{topical hashtags already mentioned above}
@@
 {\sc Tweebank v2} is built on the original data of {\sc Tweebank v1}
-(840 unique tweets, 639/201 for training/test set), along with an 
+(840 unique tweets, 639/201 for training/test), along with an 
 additional 210 tweets sampled from the POS-tagged dataset of
@@
 reference unit is always the tweet in its entirety
--- which may thus consist of multiple sentences -- not the sentence alone.
-Before annotation, we use simple regular expression to anonymize username and URL.
+-- which may thus consist of multiple sentences -- not the sentence alone.\nss{``Each tweet is annotated with a single tree, rather than being split into sentences.''?}
+Before annotation, we use simple regular expression to anonymize usernames and URLs.
 
@@
 In the first stage, 18 researchers worked on the {\sc Tweebank v1}
-proportion and the additional 210 tweets and created the initial annotations in one day.
+portion and the additional 210 tweets and created the initial annotations in one day.
 Before annotating, they were given a tutorial overview of the general UD
@@
 of this paper manually corrected the parsed data and finally achieved 3,550 labeled tweets.\footnote{Manual annotation was done with Arborator \cite{gerdes:2013:W13-37}, a web platform for drawing dependency trees.}
-Newly created annotations are split into train, development, and test set and appended
-to the original split of {\sc Twebank v1}. Statistics of our annotations and data split are shown
-in Table \ref{tbl:data-stat}.
+Newly created annotations are split into train, development, and test sets and appended
+to the original splits of {\sc Twebank v1}. Statistics of our annotations and data splits are shown
+in Table~\ref{tbl:data-stat}.
 
@@
 tokenization annotation. % \nascomment{still better to quantify}.
-The agreement on POS is 96.6\%, the unlabeled
-dependency agreement is 88.8\% and the labeled dependency agreement
-is 84.3\%. Further analysis shows the major disagreements on POS
+The agreement rate is 96.6\% on POS, 
+88.8\% on unlabeled dependencies, and
+84.3\% on labeled dependencies. 
+Further analysis shows the major disagreements on POS
 involve entity names (30.6\%) %\yicomment{noun phrases or proper noun

### 2018-04-15 paper.tex
section 3

@@
 UD conventions to cover tweet-specific constructions (\S\ref{sec:ud-tweet}). 
-Finally, we present our process of creating a new tweet treebank, {\sc
-  Tweebank v2}, and characterize
+Finally, we present our process of creating a new tweet treebank, 
+{\sc Tweebank v2}, and characterize
 the difficulties in reaching consistent annotations (\S\ref{sec:anno-process}).
@@
 Newly created annotations are split into train, development, and test sets and appended
-to the original splits of {\sc Twebank v1}. Statistics of our annotations and data splits are shown
+to the original splits of {\sc Tweebank v1}. Statistics of our annotations and data splits are shown
 in Table~\ref{tbl:data-stat}.
@@
 showed that our model trained on
-the combination of UD\_English-EWT and Tweebank v2
-outperforms the one trained only on the UD\_English-EWT or Tweebank v2,
-which also was confirmed by previous works on dialect treebank parsing \cite{wang-EtAl:2017:Long6}.
+the combination of UD\_English-EWT and \textsc{Tweebank v2}
+outperformed the one trained only on the UD\_English-EWT or \textsc{Tweebank v2},
+consistent with previous work on dialect treebank parsing \cite{wang-EtAl:2017:Long6}.
 So we trained our tokenizer on the training portion of
@@
 \cite{straka-strakova:2017:K17-3} model was re-trained on the same
-data as our system. Compared with UDPipe, we use LSTM
-instead of GRU in our model and we also use a larger size of hidden units (64 vs.~20),
-which has stronger representation power. 
+data as our system. Compared with UDPipe, we use an LSTM
+instead of a GRU in our model and we also use a larger size for hidden units (64 vs.~20),
+which has stronger representational power. 
 Our bi-LSTM tokenizer achieves the best accuracy among all these
-tokenizers.  These results indicate the value of statistical modeling
+tokenizers.  These results speak to the value of statistical modeling
 in tokenization for informal texts.%\nss{this paragraph needs copyediting}
@@
 		\hline
-		\it System & Precision \\
+		\it System & Precision\nss{Accuracy?} \\
 		\hline
@@
 with gold-standard tokenization are shown in
-Table \ref{tbl:pos-result}. The careful feature engineering and making use of
-\citet{Brown:1992:CNG:176313.176316} clusters in the 
-POS tagger of \citet{owoputi-EtAl:2013:NAACL-HLT} outperforms \citeposs{ma-hovy:2016:P16-1} neural network
+Table \ref{tbl:pos-result}. Careful feature engineering and 
+\citet{Brown:1992:CNG:176313.176316} clusters  
+help \citeposs{owoputi-EtAl:2013:NAACL-HLT} feature-based POS taggers to outperform \citeposs{ma-hovy:2016:P16-1} neural network
 model. 
@@
 
-In our preliminary experiments, we train our parser on the combination of UD\_English-EWT
+In our preliminary\nss{initial?} experiments, we train our parser on the combination of UD\_English-EWT
 and \textsc{Tweebank v2} training sets. Gold-standard tokenization and automatic POS
@@
 for decoding. The parser in \citet{dozat-qi-manning:2017:K17-3} is also a graph-based parser
-but includes character-based word representation and uses the biaffine classifier
+but includes character-based word representation and uses a biaffine classifier
 to predict if an attachment exists between two words.
@@
 in recent methods for training greedy models that use dynamic oracles
-\citet{goldberg-nivre:2012:PAPERS,TACL145,TACL885,ballesteros-EtAl:2016:EMNLP2016}.  
+\citep{goldberg-nivre:2012:PAPERS,TACL145,TACL885,ballesteros-EtAl:2016:EMNLP2016}.  
 We find that this
 approach outperforms the  conventional distillation model, coming in
-only one point behind the ensemble (last line of Table~\ref{tbl:parse-result}).
+only one\nss{UAS? LAS is 1.5 points} point behind the ensemble (last line of Table~\ref{tbl:parse-result}).
 
@@
 UD parsing
-performance drops by more than four points.
+performance drops by more than\nss{? 77.9 vs. 74.0, right?} four points.
 

### 2018-04-15 paper.tex
caption formatting; remove top and bottom rules on tables, as they don't really add anything

@@
 \usepackage{graphicx}
+\usepackage[small,bf,skip=5pt]{caption}
 \usepackage{subcaption}
@@
 \begin{tabular}{lrr}
-\hline
+%\hline
 \multicolumn{2}{r}{syntactic (\%)} & non-syntactic (\%)\\ \hline
@@
  total & 2.08 & 7.55 \\
- \hline
+% \hline
 \end{tabular}
 \caption{Proportions of non-syntactic tokens in our annotation. %\yicomment{should add also retweet at-mentions}
-These statistics are obtained on 140 character-limited tweets. \label{tbl:non-synt-prop}}
+These statistics are obtained on 140 character--limited tweets. \label{tbl:non-synt-prop}}
 \end{table}
@@
 	\begin{tabular}{rrrrr}
-		\hline
+%		\hline
 		 & \multicolumn{2}{c}{\textsc{Tweebank v1}} & \multicolumn{2}{c}{\textsc{Tweebank v2}} \\
@@
 %		 & tokens &	24,753	&	11,742	&	19,112 & 55,617\\
-		\hline
+%		\hline
 	\end{tabular}
@@
 	\begin{tabular}{rc}
-		\hline
+%		\hline
 		\it System & $F_1$ \\
@@
 	 	our bi-LSTM tokenizer & 98.3 \\
-		\hline
+%		\hline
 	\end{tabular}
@@
 	\begin{tabular}{rc}
-		\hline
-		\it System & Precision\nss{Accuracy?} \\
+%		\hline
+		\it System & Precision \\
 		\hline
@@
 %		our character + word bi-LSTMs & 91.5 \\
-		\hline
+%		\hline
 	\end{tabular}
 	\caption{POS tagger comparison on gold-standard tokens in the
-          \textsc{Tweebank v2} test set. \label{tbl:pos-result}}
+          \textsc{Tweebank v2} test set.\nss{why Precision and not Accuracy?} \label{tbl:pos-result}}
 \end{table}
@@
 	\begin{tabular}{rc}
-		\hline
+%		\hline
 		\it Tokenization System & $F_1$ \\
@@
 		our bi-LSTM tokenizer (\S\ref{sec:tok}) & 93.3 \\
-		\hline
+%		\hline
 	\end{tabular}
@@
 	\begin{tabular}{rccc}
-		\hline
+%		\hline
 		\it System & UAS & LAS & Kt/s \\
@@
 		Distillation w/ exploration & 82.1 & 77.9 & 2.3 \\
-		\hline
+%		\hline
 	\end{tabular}
@@
 	\begin{tabular}{rrcc}
-		\hline
+%		\hline
 		\it Pipeline stage & Score & Ours & SOTA \\
@@
 		UD parsing & \it LAS $F_1$ & 74.0 & 71.4 \\
-		\hline
+%		\hline
 	\end{tabular}

### 2018-04-15 paper.tex
article

@@
 -- which may thus consist of multiple sentences -- not the sentence alone.\nss{``Each tweet is annotated with a single tree, rather than being split into sentences.''?}
-Before annotation, we use simple regular expression to anonymize usernames and URLs.
+Before annotation, we use a simple regular expression to anonymize usernames and URLs.
 

### 2018-04-16 paper.tex
update

--- 2018-04-15 paper.tex
@@
 %\newcommand{\yicomment}[1]{\textcolor{gray}{[#1 ---\textsc{yi}]}}
-\newcommand{\nss}[1]{\textcolor{magenta}{[$_\mathrm{S}^\mathrm{NS}$#1]}}
+%\newcommand{\nss}[1]{\textcolor{magenta}{[$_\mathrm{S}^\mathrm{NS}$#1]}}
 
@@
 The retweet construction is a special case and we will discuss its treatment in the following paragraph.
-\item If the whole sentence\nss{tweet?} is a sequence of non-syntactic tokens, we attach all these tokens to the first one.
+\item If the whole sentence is a sequence of non-syntactic tokens, we attach all these tokens to the first one.
 %\item In parataxis case, when it is difficult to decide which sentence or phrase x should belong to, we always attach x to the previous predicate of the paratactic clause or phrase;
@@
 is inspired by the observation that emoticons are annotated as \textit{discourse} by UD\_English-EWT
-and \citet{sanguinetti-17} used the same relation for the emoticons.\nss{how does the other treebank treat the RT construction and truncated words?}
+and \citet{sanguinetti-17} used the same relation for the emoticons.
+Retweet constructions and truncated words were not explicitly touched
+in \citet{sanguinetti-17}.
+Judging from the released treebank\footnote{\url{https://github.com/UniversalDependencies/UD_Italian-PoSTWITA}}, the \textit{RT} marker, at-mention, and colon in the retweet construction are all attached to the predicate of the following sentence with \textit{dep}, \textit{vocative:mention} and \textit{punct}.
+%\nss{how does the other treebank treat the RT construction and truncated words?}
 %\nss{topical hashtags already mentioned above}
@@
 reference unit is always the tweet in its entirety
--- which may thus consist of multiple sentences -- not the sentence alone.\nss{``Each tweet is annotated with a single tree, rather than being split into sentences.''?}
-Before annotation, we use simple regular expression to anonymize usernames and URLs.
+-- which may thus consist of multiple sentences -- not the sentence alone.%\nss{``Each tweet is annotated with a single tree, rather than being split into sentences.''?}
+Before annotation, we use a simple regular expression to anonymize usernames and URLs.
 
@@
  Stanford CoreNLP \cite{manning-EtAl:2014:P14-5} and Twokenizer
-\cite{ICWSM101540} are rule-based systems and were not adapted
+\cite{ICWSM101540}\footnote{We use the updated version of Twokenizer from \citet{owoputi-EtAl:2013:NAACL-HLT}.} are rule-based systems and were not adapted
 to the UD tokenization scheme.
@@
 %		\hline
-		\it System & Precision \\
+		\it System & Accuracy \\
 		\hline
@@
 	\caption{POS tagger comparison on gold-standard tokens in the
-          \textsc{Tweebank v2} test set.\nss{why Precision and not Accuracy?} \label{tbl:pos-result}}
+          \textsc{Tweebank v2} test set.%\nss{why Precision and not Accuracy?}
+          \label{tbl:pos-result}}
 \end{table}
@@
 
-In our preliminary\nss{initial?} experiments, we train our parser on the combination of UD\_English-EWT
+In our initial experiments, we train our parser on the combination of UD\_English-EWT
 and \textsc{Tweebank v2} training sets. Gold-standard tokenization and automatic POS
@@
 approach outperforms the  conventional distillation model, coming in
-only one\nss{UAS? LAS is 1.5 points} point behind the ensemble (last line of Table~\ref{tbl:parse-result}).
+1.5 point behind the ensemble (last line of Table~\ref{tbl:parse-result}).
 
@@
 UD parsing
-performance drops by more than\nss{? 77.9 vs. 74.0, right?} four points.
+performance drops by about four points.
 

### 2018-04-16 paper.tex
revise the citation in our baseline.

@@
 of data, making speed an important consideration. We therefore 
-begin with the neural greedy stack LSTM parser introduced by \newcite{ballesteros-EtAl:2016:EMNLP2016},
+begin with the neural greedy stack LSTM parser introduced by \cite{ballesteros-dyer-smith:2015:EMNLP},
 which can parse a sentence in linear time and harnesses 
@@
 %		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
-		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.2 & 75.7 & 2.3 \\
 		\hdashline
+		%\citet{ballesteros-EtAl:2016:EMNLP2016} & & & \\
+		\citet{ballesteros-dyer-smith:2015:EMNLP} & 80.2 & 75.7 & 2.3 \\
 		Ensemble (20) & 83.4 & 79.4 & 0.2 \\
@@
 	\caption{Dependency parser comparison on \textsc{Tweebank v2} test set,
-           with automatic POS tags. The ``Kt/s'' column shows
+           with automatic POS tags. We use \citet{ballesteros-dyer-smith:2015:EMNLP}
+           as our baseline and build the ensemble and distilling model over it.
+           The ``Kt/s'' column shows
            the parsing speed evaluated by thousands of tokens

### 2018-04-16 paper.tex
copyedits

@@
 reference unit is always the tweet in its entirety
--- which may thus consist of multiple sentences -- not the sentence alone.%\nss{``Each tweet is annotated with a single tree, rather than being split into sentences.''?}
+-- which may thus consist of multiple sentences -- not the sentence alone. %\nss{``Each tweet is annotated with a single tree, rather than being split into sentences.''?}
 Before annotation, we use a simple regular expression to anonymize usernames and URLs.
@@
 of data, making speed an important consideration. We therefore 
-begin with the neural greedy stack LSTM parser introduced by \cite{ballesteros-dyer-smith:2015:EMNLP},
+begin with the neural greedy stack LSTM parser introduced by \citet{ballesteros-dyer-smith:2015:EMNLP},
 which can parse a sentence in linear time and harnesses 
@@
 approach outperforms the  conventional distillation model, coming in
-1.5 point behind the ensemble (last line of Table~\ref{tbl:parse-result}).
+1.5 points behind the ensemble (last line of Table~\ref{tbl:parse-result}).
 

### 2018-04-16 paper.tex
move tokenizer results table to nicer location
Noah

@@
 (e.g., treebanks)
-for training and evaluation is hard. 
+for training.
 Pioneering work by \citet{Foster:2011:HPT:2908630.2908634} 
@@
 tweet content but two special cases, \textit{articulated prepositions}
-(e.g.~\textit{nella} as \textit{in la})
+(e.g., \textit{nella} as \textit{in la})
 and \textit{clitic clusters} (e.g.~\textit{guardandosi} as \textit{guardando si}), are tokenized.
@@
 With respect to tweet-specific constructions,
-\citeposs{sanguinetti-17} and our  interpretation of headedness is the same, 
+\citeposs{sanguinetti-17} and our  interpretation of headedness are the same, 
 but we differ in the relation label.
-For topical hashtags, we use \textit{discourse} while \citet{sanguinetti-17} used \textit{parataxis}. 
-In referential URLs, we use \textit{list} (following the precedent of UD\_English-EWT) while \citet{sanguinetti-17} used \textit{dep}.
+For topical hashtags, we use \textit{discourse} while they used \textit{parataxis}. 
+In referential URLs, we use \textit{list} (following the precedent of UD\_English-EWT) while they used \textit{dep}.
 %<<<<<<< HEAD
@@
 Our choice of \textit{discourse} for sentiment emoticons
-is inspired by the observation that emoticons are annotated as \textit{discourse} by UD\_English-EWT
-and \citet{sanguinetti-17} used the same relation for the emoticons.
+is inspired by the observation that emoticons are annotated as \textit{discourse} by UD\_English-EWT;
+\citet{sanguinetti-17} used the same relation for the emoticons.
 Retweet constructions and truncated words were not explicitly touched
-in \citet{sanguinetti-17}.
+by \citet{sanguinetti-17}.
 Judging from the released treebank\footnote{\url{https://github.com/UniversalDependencies/UD_Italian-PoSTWITA}}, the \textit{RT} marker, at-mention, and colon in the retweet construction are all attached to the predicate of the following sentence with \textit{dep}, \textit{vocative:mention} and \textit{punct}.
@@
   langid.py}.\footnote{\url{https://github.com/saffsd/langid.py}}
-In the same way as \citet{kong-EtAl:2014:EMNLP2014},
-reference unit is always the tweet in its entirety
--- which may thus consist of multiple sentences -- not the sentence alone. %\nss{``Each tweet is annotated with a single tree, rather than being split into sentences.''?}
+As done by \citet{kong-EtAl:2014:EMNLP2014}, the
+annotation unit is always the tweet in its entirety---which may consist of multiple sentences---not the sentence alone.
+%\nss{``Each tweet is annotated with a single tree, rather than being split into sentences.''?}
 Before annotation, we use a simple regular expression to anonymize usernames and URLs.
@@
 		train & 639 & 9,310 & 1,639 & 24,753 \\
-		dev & --\hphantom{0} & --\hphantom{00} & 710 & 11,742 \\
+		dev. & --\hphantom{0} & --\hphantom{00} & 710 & 11,742 \\
 		test & 201 & 2,839 & 1,201 & 19,112 \\
@@
 %	\end{tabular}
-\caption{Statistics of {\sc Tweebank v2} and the comparison with
-{\sc Tweebank v1} in quantity.
+\caption{Statistics of {\sc Tweebank v2} and  comparison with
+{\sc Tweebank v1}.
 %\nss{not obvious how to interpret this: train tokens looks like 1,609+1,000 = 2,609, but maybe it's 609+1,000=1,609? 
@@
 
-\begin{table}[t]
-	\centering
-	\begin{tabular}{rc}
-%		\hline
-		\it System & $F_1$ \\
-		\hline
-		  Stanford CoreNLP & 97.3 \\
-		 Twokenizer & 94.6 \\
-% 		UDPipe v1.2 & 94.7 \\
-		\hdashline
-		UDPipe v1.2 & 97.4 \\
-	 	our bi-LSTM tokenizer & 98.3 \\
-%		\hline
-	\end{tabular}
-	\caption{Tokenizer comparison on the \textsc{Tweebank v2} test set.}\label{tbl:tok-result}
-\end{table}
 %\citet{wang-EtAl:2017:Long6} show that the parser\nss{tokenizer?}\yjcomment{it's a parsing work.}\nss{I guess I don't follow how parsing results 
@@
 
+\begin{table}[t]
+	\centering
+	\begin{tabular}{rc}
+%		\hline
+		\it System & $F_1$ \\
+		\hline
+		  Stanford CoreNLP & 97.3 \\
+		 Twokenizer & 94.6 \\
+% 		UDPipe v1.2 & 94.7 \\
+		\hdashline
+		UDPipe v1.2 & 97.4 \\
+	 	our bi-LSTM tokenizer & 98.3 \\
+%		\hline
+	\end{tabular}
+	\caption{Tokenizer comparison on the \textsc{Tweebank v2} test set.}\label{tbl:tok-result}
+\end{table}
+
 \subsection{Part-of-Speech Tagger}
@@
 for decoding. The parser in \citet{dozat-qi-manning:2017:K17-3} is also a graph-based parser
-but includes character-based word representation and uses a biaffine classifier
-to predict if an attachment exists between two words.
+but includes character-based word representations and uses a biaffine classifier
+to predict whether an attachment exists between two words.
 Both of the compared systems require superlinear runtime due to graph-based parsing. 
@@
 \citeposs{owoputi-EtAl:2013:NAACL-HLT} tagger, and \citeposs{dozat-qi-manning:2017:K17-3} parser.
-Our system differs from the SOTA pipeline in the tokenization and parser components.
-From Table \ref{tbl:pipline}, our pipeline outperforms the SOTA when
+Our system differs from the state-of-the-art pipeline in the tokenization and parser components.
+From Table \ref{tbl:pipline}, our pipeline outperforms the state of
+the art when
 evaluated in pipeline manner.

### 2018-04-16 paper.tex
SVA
Noah

@@
 \section{Introduction}
-NLP for social media messages is challenging, because domain
-adaptation is required, and also because creating annotated datasets
+NLP for social media messages is challenging, requiring domain
+adaptation and annotated datasets
 (e.g., treebanks)
-for training.
+for training and evaluation.
 Pioneering work by \citet{Foster:2011:HPT:2908630.2908634} 
@@
 With respect to tweet-specific constructions,
-\citeposs{sanguinetti-17} and our  interpretation of headedness are the same, 
+\citeposs{sanguinetti-17} and our  interpretations of headedness are the same, 
 but we differ in the relation label.
